---
title: "Putting Components Together"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Putting Components Together}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
source("shots.R")
```

Each component page shows one component at a time. An app puts them
together: controls inside a space inside a tab, a form inside a dialog, a
table inside a drawer, all of it inside a config provider, some of it drawn
later by the server. Most of what can go wrong only goes wrong then, so
these apps put the components together on purpose.

Each is a file under `examples/combinations/` in the installed package, run
as it stands --
`shiny::runApp(system.file("examples/combinations/drawn-later", package = "shiny.element"))`.
In the package's sources, `tools/combinations.R` drives each one in a
browser, step by step, and checks what every step should do.

## Folded in, and nested

A component given to another -- a button to a tooltip, controls to a space,
a select to an input's slot -- becomes part of its Vue instance. It keeps
its id all the same: it reports `input$<id>`, `update_el_*()` and
`call_el()` reach it by that id, and in the page the id is on the component
itself, for CSS or `shinyjs`. Here controls sit in a space in a collapse in
a tab, inside a config provider, beside a module whose button is wrapped in
a tooltip; a dialog holds a form, and a popover filters a table output.

A select inside a popover wants `teleported = FALSE`. Otherwise its options
are drawn outside the popover, and choosing one closes the popover -- as in
Element itself.

```{r wrapped-and-nested, file = "../inst/examples/combinations/wrapped-and-nested/app.R", eval = FALSE, shot = TRUE}
```

## Drawn later

`renderUI()` inside a config provider draws components after it: they take
its settings all the same, and follow them when
`update_el_config_provider()` changes them. Two trees in one space each keep
their own methods, a drawer holds tabs with a table and a calendar output
drawn while it was closed, and steps follow a button group.

```{r drawn-later, file = "../inst/examples/combinations/drawn-later/app.R", eval = FALSE, shot = TRUE}
```

## Overlays, and buttons in table cells

A dialog holds tabs and opens a second dialog over it; a message box opens
over both. Tabs drawn in a closed dialog measure themselves once shown. A
table's cells hold a popconfirm and a button, whose `rowAction()` reports
the row; `insertUI()` adds a component and `removeUI()` takes it away.

```{r overlays-and-cells, file = "../inst/examples/combinations/overlays-and-cells/app.R", eval = FALSE, shot = TRUE}
```

## Modules and forms

A module inside a module, its controls wrapped in a space and a tooltip,
each updated through its own session. A form sits in a collapsed panel
inside a watermark: one of its fields reports as it changes
(`el_form_field(report = TRUE)`), and the server resizes the form with it.
An editable table in a dialog, a calendar whose events open their editor,
and a transfer in a drawer complete it.

```{r modules-and-forms, file = "../inst/examples/combinations/modules-and-forms/app.R", eval = FALSE, shot = TRUE}
```

## Components that ask the server

A select searching remotely, a tree and a cascader loading their children
lazily -- all three folded into a space inside a config provider, the
server's answers finding them by their ids. A form in a dialog gains fields
from the server, which are validated with their own rules.

```{r server-answers, file = "../inst/examples/combinations/server-answers/app.R", eval = FALSE, shot = TRUE}
```
