---
title: "Component gallery"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Component gallery}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
source("shots.R")
```

Every picture below was taken from the code above it, run as it stands in a
live Shiny app in headless Chromium. Regenerate them with
`Rscript tools/article-shots.R components` after changing how something
looks.

Each component reports to the server as `input$<id>`, on load as well as on
change, and is updated from the server with the matching `update_el_*()`.

The sections follow Element UI's own documentation, so a page there has a
counterpart here.

## Form

### `el_input()`

Text, textarea and password, with the usual Element trimmings.

```{r input, eval = FALSE, shot = TRUE}
el_input("name", value = "Ada Lovelace", placeholder = "your name")
el_input("notes", type = "textarea", rows = 2)
el_input("pw", type = "password", show_password = TRUE)
```

### `el_input_number()`

```{r input-number, eval = FALSE, shot = TRUE}
el_input_number("age", value = 18, min = 0, max = 150)
```

### `el_select()`

Single or multiple. `choices` takes a named vector or a list of
`list(value=, label=)`.

```{r select, eval = FALSE, shot = TRUE}
el_select("city", choices = c(Beijing = "bj", Shanghai = "sh"))
el_select("tags", choices = c(A = "a", B = "b", C = "c"), multiple = TRUE)
```

### `el_radio_group()`

```{r radio-group, eval = FALSE, shot = TRUE}
el_radio_group("plan", choices = c(Basic = "x", Pro = "y"))
el_radio_group("range", choices = c(Day = "d", Week = "w"), button = TRUE)
```

### `el_checkbox_group()`

```{r checkbox-group, eval = FALSE, shot = TRUE}
el_checkbox_group("langs", choices = c(R = "r", Python = "p", SQL = "s"),
                  selected = c("r", "s"))
```

### `el_switch()`

```{r switch, eval = FALSE, shot = TRUE}
el_switch("live", value = TRUE, active_text = "on", inactive_text = "off")
```

### `el_slider()`

```{r slider, eval = FALSE, shot = TRUE}
el_slider("score", value = 40)
el_slider("band", value = c(20, 70), range = TRUE)
```

### `el_rate()`

```{r rate, eval = FALSE, shot = TRUE}
el_rate("stars", value = 3, show_text = TRUE)
```

### `el_date_picker()`

```{r date-picker, eval = FALSE, shot = TRUE}
el_date_picker("when", value = "2026-03-01")
el_date_picker("span", type = "daterange")
```

### `el_color_picker()`

```{r color-picker, eval = FALSE, shot = TRUE}
el_color_picker("shade", value = "#409EFF")
```

### `el_cascader()`

Nested options; `df_to_cascader_options()` builds them from a data frame.

```{r cascader, eval = FALSE, shot = TRUE}
el_cascader("region", options = list(
  list(value = "zj", label = "Zhejiang", children = list(
    list(value = "hz", label = "Hangzhou")))))
```

### `el_autocomplete()`

A text input that suggests as you type. Filtering happens in the browser;
for suggestions that come from the server pass `fetch_suggestions`.

```{r autocomplete, eval = FALSE, shot = TRUE}
el_autocomplete("city", width = 240, placeholder = "Where to?",
                suggestions = c("Beijing", "Shanghai", "Shenzhen"))
```

### `el_transfer()`

Two lists, for moving items between them. `input$<id>` holds the keys on the
right.

```{r transfer, eval = FALSE, shot = TRUE}
el_transfer("cols", width = 560,
            data = data.frame(key = names(iris), label = names(iris)),
            value = c("Species"), titles = c("Available", "Chosen"))
```

### `el_upload()`

Element's upload over Shiny's own transport, so `input$files` is the data frame
`fileInput()` produces, `datapath` and all. Pass `action` instead to post
straight to a URL.

```{r upload, eval = FALSE, shot = TRUE}
el_upload("files", drag = TRUE, multiple = TRUE, tip = "CSV only", accept = ".csv")
```


### `el_form()`

The form owns its model, so validation runs in the browser and the whole form
reports once on submit rather than field by field. `input$signup` carries the
model, `input$signup_valid` the verdict, `input$signup_submit` a counter.

```{r form, eval = FALSE, shot = TRUE}
el_form(
  id = "signup", label_width = "110px",
  el_form_field("name", "input", label = "Name",
                rules = el_rule(required = TRUE, message = "Name is required")),
  el_form_field("email", "input", label = "Email",
                rules = el_rule(type = "email", message = "Not a valid email")),
  el_form_field("city", "select", label = "City",
                choices = c(Beijing = "bj", Shanghai = "sh"))
)
```

## Data

### `el_button()`

```{r button, eval = FALSE, shot = TRUE}
el_button("save", "Primary", type = "primary")
el_button("go", "Round", type = "primary", round = TRUE)
el_button("wait", "Loading", type = "primary", loading = TRUE)
```

### `el_tag()`

```{r tag, eval = FALSE, shot = TRUE}
el_tag("t", label = "closable", type = "warning", closable = TRUE)
```

### `el_alert()`

```{r alert, eval = FALSE, shot = TRUE}
el_alert("hint", title = "info", type = "info", show_icon = TRUE,
         description = "with a description")
```

### `el_progress()`

Line, circle and dashboard.

```{r progress, eval = FALSE, shot = TRUE}
el_progress("pct", percentage = 70)
el_progress("ring", percentage = 70, type = "circle")
```

### `el_badge()`

```{r badge, eval = FALSE, shot = TRUE}
el_badge(el_button("msg", "messages"), value = 12)
el_badge(el_button("hi", "capped"), value = 200, max = 99)
```

### `el_card()`

```{r card, eval = FALSE, shot = TRUE}
el_card(header = "Card header", "Cards nest any content.")
```

### `el_table()`

Takes a data frame directly and infers its columns. With `selection = TRUE`,
`input$tbl_selected_rows` gives 1-based row numbers with their R types intact.

```{r table, eval = FALSE, shot = TRUE}
el_table(id = "tbl", data = head(iris, 4), selection = TRUE)
```

### `el_avatar()`

From an image, an icon, or text.

```{r avatar, eval = FALSE, shot = TRUE}
el_avatar("anon", icon = "el-icon-user-solid")
el_avatar("initials", content = "KY", shape = "square")
el_avatar("big", content = "40", size = 40)
```

### `el_image()`

An image with a fit mode, optional lazy loading, and an optional full-screen
preview.

```{r image, eval = FALSE, shot = TRUE}
# Serve a folder of images; here, R's own logo
addResourcePath("rdoc", R.home("doc/html"))

el_image("logo", src = "rdoc/logo.jpg", width = 160, fit = "contain")

# Click to open a full-screen preview
el_image("gallery", src = "rdoc/logo.jpg", width = 80, fit = "cover",
         preview_src_list = c("rdoc/logo.jpg", "rdoc/logo.jpg"))
```

### `el_descriptions()`

A read-only grid of labelled values -- the detail view of a record. Content
may be any UI, components included.

```{r descriptions, eval = FALSE, shot = TRUE}
el_descriptions("account", title = "Account", border = TRUE, column = 2,
  items = list(
    list(label = "Name", content = "Ada Lovelace"),
    list(label = "Plan", content = el_tag("plan", "Pro", type = "success")),
    list(label = "Joined", content = "2026-01-12"),
    list(label = "Seats", content = "12"),
    list(label = "Address", content = "12 St James's Square, London", span = 2)
  ))
```

### `el_statistic()`

A headline number with a title.

```{r statistic, eval = FALSE, shot = TRUE}
el_row(gutter = 20,
  el_col(span = 8, el_statistic("users", value = 26048, title = "Active users",
                                group_separator = ",")),
  el_col(span = 8, el_statistic("revenue", value = 1318.5, title = "Revenue",
                                prefix = "$", precision = 2)),
  el_col(span = 8, el_statistic("growth", value = 4.2, title = "Growth",
                                suffix = "%", precision = 1))
)
```

### `el_empty()` and `el_result()`

What a view shows when there is nothing in it yet, and what it shows once
something has finished.

```{r empty, eval = FALSE, shot = TRUE}
el_empty("none", description = "No reports yet", image_size = 100,
         el_button("create", "Create one", type = "primary"))
```

```{r result, eval = FALSE, shot = TRUE}
el_result("done", icon = "success", title = "Report submitted",
          sub_title = "It will be reviewed within a day",
          el_button("back", "Back to the list", type = "primary"))
```

### `el_skeleton()`

Grey shapes in place of content that is still on its way. Switch
`loading` off from the server when the content is ready.

```{r skeleton, eval = FALSE, shot = TRUE}
el_skeleton("report", rows = 3, animated = TRUE, tableOutput("summary"))
```

### `el_pagination()`

```{r pagination, eval = FALSE, shot = TRUE}
el_pagination("pager", total = 200, page_size = 20, current_page = 3)
```

### `el_timeline()`

Entries can be replaced wholesale with `update_el_timeline()`, which suits a
log that grows.

```{r timeline, eval = FALSE, shot = TRUE}
el_timeline("log", items = list(
  list(content = "Order placed", timestamp = "2026-03-01", type = "primary"),
  list(content = "Shipped", timestamp = "2026-03-02", type = "success",
       icon = "el-icon-check", size = "large")))
```

### `el_carousel()`

```{r carousel, eval = FALSE, shot = TRUE}
el_carousel("banner", height = "160px", items = list(
  list(name = "one", content = tags$h3("First")),
  list(name = "two", content = tags$h3("Second"))))
```

### `el_divider()` and `el_link()`

```{r divider, eval = FALSE, shot = TRUE}
el_divider()
el_link("primary", type = "primary")
```

### Icons

Element's icon font ships with the package; any `el-icon-*` class works.

```{r icon, eval = FALSE, shot = TRUE}
tags$i(class = "el-icon-edit")
el_icon("star-on")
```

## Others

These render as plain markup rather than Vue instances, which is what lets them
hold other components from this package. A component placed inside one stays
connected to the server.

### `el_tabs()`

```{r tabs, eval = FALSE, shot = TRUE}
el_tabs("section", tabs = list(
  list(name = "x", label = "Inputs",
       content = tagList(el_input("q"), el_rate("stars"))),
  list(name = "y", label = "Second", content = "Panes hold components.")))
```

### `el_collapse()`

```{r collapse, eval = FALSE, shot = TRUE}
el_collapse("panels", value = "p1", items = list(
  list(name = "p1", title = "Filters",
       content = tagList(el_input("q"), el_switch("live")))))
```

### `el_steps()`

```{r steps, eval = FALSE, shot = TRUE}
el_steps("wizard", active = 1, finish_status = "success", steps = list(
  list(title = "Pick", description = "choose a plan"),
  list(title = "Pay",  description = "enter card"),
  list(title = "Done", description = "all set")))
```

### `el_dialog()` and `el_drawer()`

Open and close them from the server; `input$<id>` is `TRUE` while open. Both
hold live components.

```{r dialog, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#open_container button').click()", shot_sel = ".el-dialog", shot_wait = 1.5}
ui <- el_page(
  el_button("open", "Open dialog", type = "primary"),
  el_dialog("confirm", title = "Why?", width = "420px",
            content = el_input("reason", placeholder = "Tell us why"),
            footer = el_button("ok", "OK", type = "primary"))
)

server <- function(input, output, session) {
  observeEvent(input$open, update_el_dialog(session, "confirm", visible = TRUE))
  observeEvent(input$ok, update_el_dialog(session, "confirm", visible = FALSE))
}

shinyApp(ui, server)
```

```{r drawer, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#open_container button').click()", shot_sel = ".el-drawer", shot_wait = 1.5}
ui <- el_page(
  el_button("open", "Open drawer"),
  el_drawer("settings", title = "Settings", direction = "rtl", size = "320px",
            content = tagList(el_switch("dark", value = TRUE, active_text = "Dark"),
                              tags$p("Drawers hold live components too.")))
)

server <- function(input, output, session) {
  observeEvent(input$open, update_el_drawer(session, "settings", visible = TRUE))
}

shinyApp(ui, server)
```

### `el_tooltip()`

A hint shown on hover. The trigger can be plain markup or a whole component --
a component is folded into the tooltip's own Vue instance, so it keeps
reporting its inputs.

```{r tooltip, eval = FALSE, shot = TRUE, shot_js = "var b = document.querySelector('#shot button'); ['mouseenter','mouseover'].forEach(function(t){ b.dispatchEvent(new MouseEvent(t, {bubbles: true})); });", shot_sel = ".el-tooltip__popper", shot_wait = 1}
el_tooltip("hint", el$button(type = "primary", "Hover me"),
           content = "A hint about this button")

# A component works too
el_tooltip("save_hint", el_button("save", "Save"), content = "Writes to disk")
```

### `el_popover()`

A card on click or hover, with a title and body.

```{r popover, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#shot button').click()", shot_sel = ".el-popover", shot_wait = 1}
el_popover("info",
  reference = el$button(type = "primary", "Details"),
  title = "March", content = "Revenue up 4% on February.")
```

### `el_popconfirm()`

A confirmation anchored to what triggers it, for actions that warrant a check
but not a dialog. `input$<id>_confirm` and `input$<id>_cancel` report the
answer.

```{r popconfirm, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#shot button').click()", shot_sel = ".el-popover", shot_wait = 1}
el_popconfirm("del",
  reference = el$button(type = "danger", "Delete"),
  title = "Delete this row?")
```

### `el_backtop()`

A button that appears once the page is scrolled.

```{r backtop, eval = FALSE, shot = TRUE, shot_js = "document.getElementById('report').scrollTop = 600", shot_sel = ".el-backtop", shot_wait = 1}
tags$div(id = "report", style = "height: 180px; overflow: auto",
         lapply(1:40, function(i) tags$p(paste("Line", i))))

# Scrolls the panel above rather than the page
el_backtop("to_top", target = "#report", visibility_height = 100)
```

### `el_infinite_scroll()`

A scrolling area that asks for more as the user nears the bottom.
`input$<id>_load` rises by one each time.

```{r infinite-scroll, eval = FALSE, shot = TRUE}
el_infinite_scroll("feed", height = "300px", uiOutput("rows"))
```

### `el_row()` / `el_col()`

A 24-column grid.

```{r layout, eval = FALSE, shot = TRUE}
el_row(gutter = 20,
  el_col(span = 12, "span = 12"),
  el_col(span = 12, "span = 12"))
```

### `el_container()`

```{r container, eval = FALSE, shot = TRUE}
el_container(
  el_header("Header"),
  el_container(el_aside(width = "160px", "Aside"), el_main("Main")))
```

## Navigation

### `el_menu()`

Nests to any depth. `input$nav` gives the selected index, `input$nav_path` the
full path down to it.

```{r menu, eval = FALSE, shot = TRUE}
el_menu("nav", active = "home", items = list(
  list(index = "home", label = "Home", icon = "el-icon-house"),
  list(index = "data", label = "Data", children = list(
    list(index = "all", label = "All records")))))
```

### `el_tree()`

`df_to_tree_data()` builds the node list from a data frame.

```{r tree, eval = FALSE, shot = TRUE}
el_tree("picker", show_checkbox = TRUE, checked = "apple", data = list(
  list(id = "fruit", label = "Fruit", children = list(
    list(id = "apple", label = "Apple")))))
```

### `el_breadcrumb()`

A trail of links. `input$<id>` is the label of the step last clicked, so it
can drive navigation inside a Shiny app without any routing.

```{r breadcrumb, eval = FALSE, shot = TRUE}
el_breadcrumb("trail", items = list(
  list(label = "Home"), list(label = "Reports"), list(label = "March")))
```

### `el_page_header()`

A page title with a back link. `input$<id>_back` fires when it is clicked;
what going back means is up to your app.

```{r page-header, eval = FALSE, shot = TRUE}
el_page_header("hdr", title = "All reports", content = "Sales for March")
```

### `el_dropdown()`

```{r dropdown, eval = FALSE, shot = TRUE, shot_js = "var e = document.querySelector('#shot .el-dropdown'); ['mouseenter','mouseover'].forEach(function(t){ e.dispatchEvent(new MouseEvent(t, {bubbles: true})); });", shot_sel = ".el-dropdown-menu", shot_wait = 1}
el_dropdown("actions", trigger_label = "Actions", items = list(
  list(command = "edit", label = "Edit"),
  list(command = "del",  label = "Delete")))
```

## Feedback

`el_notification()` and `el_message()` are called from the server and render
themselves; there is nothing to place in the UI.

```{r feedback, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#notify_container button').click(); document.querySelector('#warn_container button').click();", shot_sel = c(".el-notification", ".el-message"), shot_wait = 1.5}
ui <- el_page(
  el_button("notify", "Notify"),
  el_button("warn", "Warn")
)

server <- function(input, output, session) {
  observeEvent(input$notify, el_notification(session, message = "Saved",
                                             title = "Done", type = "success"))
  observeEvent(input$warn, el_message(session, message = "Check the form",
                                      type = "warning"))
}

shinyApp(ui, server)
```
