---
title: "Dashboards"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Dashboards}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
source("shots.R")
```

Whole apps, built from the layout components and the controls together. Each
is a file under `examples/dashboards/` in the installed package, so it can
be run as it stands --
`shiny::runApp(system.file("examples/dashboards/sales", package = "shiny.element"))`.

## Element's own layout example

Element's documentation closes its Container page with an admin layout: a
side menu of grouped options, a header holding a dropdown, and a table in
the main area. Here it is in R, piece for piece:

```{r admin-layout, file = "../inst/examples/dashboards/admin-layout/app.R", eval = FALSE, shot = TRUE}
```

## A sales overview

Filters in the header drive everything below them: the headline numbers are
`el_statistic()`s moved with `update_el_statistic()`, the chart is an
ordinary `plotOutput()`, and the products table renders a progress bar in a
cell with a `cell` template.

```{r sales, file = "../inst/examples/dashboards/sales/app.R", eval = FALSE, shot = TRUE, shot_wait = 2}
```

## An orders admin page

The table most admin pages are built around: search over it, a status tag
and a pair of buttons in each row, an expanding row for detail, sorting and
paging done by the server, a dialog holding a form to add and edit, and a
confirmation before anything is deleted. Each row's buttons report through
`rowAction()` -- `input$orders_edit` and `input$orders_delete` carry the row.

```{r orders, file = "../inst/examples/dashboards/orders/app.R", eval = FALSE, shot = TRUE, shot_js = "document.querySelectorAll('#shot .el-table__body .el-checkbox')[1].click(); document.querySelectorAll('#shot .el-table__expand-icon')[0].click();", shot_wait = 2}
```

Opening the editor from a row's **Edit** button fills the form from that row:

```{r orders-edit, file = "../inst/examples/dashboards/orders/app.R", eval = FALSE, shot = TRUE, shot_js = "document.querySelectorAll('#shot .el-table__body .el-button')[0].click();", shot_sel = ".el-dialog", shot_wait = 2}
```
