---
title: "Forms"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Forms}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
source("shots.R")
```

Element's form components each report to `input$<id>` and are set from the
server with `update_el_*()`. This covers the pieces that differ from what you
would write with Shiny's own inputs. Every example runs as it stands, and the
picture under it was taken from that code.

## Choices

Anything taking `choices` accepts the shapes Shiny does -- an unnamed vector,
where value and label are the same; a named one, label = value; or a list of
objects, which is how a single choice carries props of its own.

```{r choices, eval = FALSE, shot = TRUE}
el_select("plain", choices = c("Beijing", "Shanghai"), value = "Beijing")

el_select("named", choices = c(Beijing = "bj", Shanghai = "sh"), value = "sh")

el_select("objects", value = "sh", choices = list(
  list(value = "bj", label = "Beijing (full)", disabled = TRUE),
  list(value = "sh", label = "Shanghai")
))
```

For a checkbox or radio group, Element documents `border`, `name` and
`disabled` on the individual item rather than the group, so they go on the
choice:

```{r item-props, eval = FALSE, shot = TRUE}
el_checkbox_group("terms", selected = "a", choices = list(
  list(value = "a", label = "Agree", border = TRUE),
  list(value = "b", label = "Subscribe", border = TRUE),
  list(value = "c", label = "Unavailable", border = TRUE, disabled = TRUE)
))
```

## Validation

`el_form()` renders its own fields rather than accepting standalone input
components, because Element's validation only works inside one component tree:
a form item finds its control through Vue's child chain and listens for events
dispatched up it. A separate Vue instance dropped in is not in that chain.

The form reports three inputs: `input$<id>` is the model as a list,
`input$<id>_valid` whether validation passed, and `input$<id>_submit` a
counter. Here the form was submitted empty:

```{r validation, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#shot .el-button--primary').click()"}
ui <- el_page(
  el_form(
    id = "signup", label_width = "90px",
    el_form_field("name", "input", label = "Name",
                  rules = el_rule(required = TRUE, message = "Name is required")),
    el_form_field("age", "input-number", label = "Age", value = 18),
    el_form_field("city", "select", label = "City",
                  options = c("Beijing", "Shanghai"),
                  rules = el_rule(required = TRUE, message = "Pick a city"))
  ),
  verbatimTextOutput("result")
)

server <- function(input, output, session) {
  output$result <- renderPrint({
    req(input$signup_submit)
    list(valid = input$signup_valid, model = input$signup)
  })
}

shinyApp(ui, server)
```

Validation can be driven from the server as well. `validate()` returns a
promise, which resolves when the form is valid and rejects when it is not;
both arrive as `input$<id>_validate`:

```{r validate-call, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#check_container button').click()", shot_wait = 2}
ui <- el_page(
  el_form(
    id = "profile", submit_label = NULL,
    el_form_field("email", "input", label = "Email",
                  rules = el_rule(required = TRUE, message = "Email is required"))
  ),
  el_button("check", "Check from the server"),
  el_button("clear", "Clear messages"),
  verbatimTextOutput("answer")
)

server <- function(input, output, session) {
  observeEvent(input$check, el_call(session, "profile", "validate"))
  observeEvent(input$clear, el_call(session, "profile", "clearValidate"))
  output$answer <- renderPrint(input$profile_validate)
}

shinyApp(ui, server)
```

## Uploads

`el_upload()` sends files through Shiny's own upload transport by default, so
they arrive in `input$<id>` as the data.frame `fileInput()` gives: `name`,
`size`, `type`, `datapath`.

```{r upload, eval = FALSE, shot = TRUE}
ui <- el_page(
  el_upload("docs", label = "Choose CSV files", multiple = TRUE, accept = ".csv",
            tip = "CSV only, up to 5 MB"),
  tableOutput("files")
)

server <- function(input, output, session) {
  output$files <- renderTable(input$docs[, c("name", "size")])
}

shinyApp(ui, server)
```

`drag = TRUE` gives the drop zone instead of a button:

```{r upload-drag, eval = FALSE, shot = TRUE}
el_upload("photos", label = "Drop images here, or click to choose",
          drag = TRUE, accept = "image/*")
```

Pointing `action` elsewhere switches to Element's own transport, and the file
goes straight to that URL without reaching R. `extra_data` is Element's `data`
prop, renamed so it is not confused with the file itself.

```{r upload-direct, eval = FALSE, shot = TRUE}
el_upload("archive", label = "Upload to the archive",
          action = "https://example.org/upload",
          headers = list(`X-Requested-With` = "shiny.element"),
          extra_data = list(folder = "reports"))
```

## Autocomplete

Suggestions passed up front are filtered in the browser as the user types:

```{r autocomplete, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#shot input').focus()", shot_sel = ".el-autocomplete-suggestion"}
el_autocomplete("city", placeholder = "Where to?", width = 260,
                suggestions = c("Beijing", "Shanghai", "Shenzhen", "Chengdu"))
```

When the list lives on the server -- a database, an API -- update the
suggestions from what has been typed:

```{r autocomplete-server, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#shot input').focus()", shot_sel = ".el-autocomplete-suggestion"}
cities <- c("Beijing", "Baoding", "Baotou", "Shanghai", "Shenzhen", "Chengdu")

ui <- el_page(el_autocomplete("city", placeholder = "Type a city", width = 260))

server <- function(input, output, session) {
  observeEvent(input$city, {
    typed <- tolower(input$city)
    update_el_autocomplete(session, "city",
      suggestions = cities[startsWith(tolower(cities), typed)])
  }, ignoreNULL = FALSE)
}

shinyApp(ui, server)
```

## Transfer

`el_transfer()` takes a data.frame of `key` and `label`, and reports the keys
on the right -- here driving which columns a table shows:

```{r transfer, eval = FALSE, shot = TRUE}
ui <- el_page(
  el_transfer("cols",
              data = data.frame(key = names(iris), label = names(iris)),
              value = c("Species", "Sepal.Length"),
              titles = c("Available", "Shown"),
              filterable = TRUE),
  tableOutput("preview")
)

server <- function(input, output, session) {
  output$preview <- renderTable(head(iris[, input$cols, drop = FALSE], 3))
}

shinyApp(ui, server)
```

## Sizing and layout

Every component takes `width`, which behaves like the `width` of a Shiny
input: `"200px"`, `"50%"`, or a number meaning pixels. For a form,
`label_width` and `label_position` do what Element's do:

```{r layout, eval = FALSE, shot = TRUE}
el_form(
  id = "compact", label_width = "80px", label_position = "left",
  submit_label = NULL,
  el_form_field("name", "input", label = "Name"),
  el_form_field("team", "select", label = "Team", options = c("Data", "Design"))
)

el_input("wide", placeholder = "width = '100%'", width = "100%")
el_input("narrow", placeholder = "width = 160", width = 160)
```
