---
title: "What works, and what does not"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{What works, and what does not}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
source("shots.R")
```

Every component Element Plus 2.14.7 documents is wrapped, with every
documented attribute, event and slot reachable from R and every method
callable by name. What follows is the small print -- the places where this
package behaves differently from Element in a browser, and why.

Coverage is measured rather than claimed. `tools/api-coverage.R` renders every
component and reads the markup back; `tools/api-coverage.py` compares that
with the API tables in Element's own documentation. A method being callable is
not the same as it having been run: the methods exercised end to end in the
package's browser tests are fewer, and a method whose argument is a JavaScript
callback cannot be called from R at all -- Element's promise form, where it
has one, is what `el_call()` uses.

## Where the argument name differs from Element's

Arguments are snake_case versions of Element Plus's prop names, with a few
exceptions. Each is deliberate; the rest translate mechanically
(`show-overflow-tooltip` becomes `show_overflow_tooltip`).

| Element | Here | Why |
|---|---|---|
| `default-active` | `active` | It is the current item, and `update_el_menu()` changes it -- "default" would suggest it is only read once |
| `default-expanded-keys` | `expanded` | As above, for `el_tree()` |
| `default-checked-keys` | `checked` | As above |
| `props` | `label_field`, `children_field`, `disabled_field`, `is_leaf_field` | `el_tree()`'s field map is four arguments rather than a nested list |
| `data` (upload) | `extra_data` | `el_upload()`'s `data` would read as the file, not the fields sent beside it |
| `width` (popover) | `popover_width` | Every component takes `width` for its own size; this one sizes the card |
| `model-value` | `value`, or `visible` (dialog, drawer), `selected` (tabs), `open` (tour) | `v-model`'s prop is the component's value, read back as `input$<id>` |
| `width` (watermark, table-v2) | `watermark_width`, `table_v2_width` | As for the popover |
| a prop named like a child's field | prefixed: `tip_`, `pop_`, `pc_` | A component that absorbs its children keeps their data apart from its own |

### Two names for the choice components

`el_select()`, `el_radio_group()` and `el_checkbox_group()` sit beside
`selectInput()`, `radioButtons()` and `checkboxGroupInput()`, so they take
Shiny's names -- and Element's as well:

| Shiny's name | Element's name | Meaning |
|---|---|---|
| `choices` | `options` | what can be picked |
| `selected` | `value` | what is picked |

Either works, in the components and in their `update_el_*()`, so code reads
naturally to someone coming from either side:

```{r two-names, eval = FALSE, shot = TRUE}
el_select("city_shiny", choices = c(Beijing = "bj", Shanghai = "sh"), selected = "sh")
el_select("city_element", options = c(Beijing = "bj", Shanghai = "sh"), value = "sh")
```

The same holds in the server: `update_el_select(session, "city", selected =
"bj")` and `update_el_select(session, "city", value = "bj")` do one thing.

Given both names in one call, the two must agree; two different values are
an error rather than one quietly winning. The help pages document each pair
as one argument (`selected, value`). No other component has a second name:
everywhere else Shiny and Element already agree on `value`.

A component's `value` prop is its `v-model`, so it is the `value` argument
where the component has one and the binding elsewhere -- `el_tooltip()` and
`el_popover()` use `value` for whether they are open, which
`update_el_*(value =)` sets.

`el_upload()`'s `on-success`, `on-error` and `http-request` are taken: they
are how files reach Shiny. The other hooks (`on-change`, `on-progress`,
`before-upload`, ...) are yours.

Where a name does differ, the component's help page documents both.

## Checked arguments

An argument Element takes from a fixed set -- a button's `type`, an input's
`size`, a tooltip's `placement` -- is checked against that set, and a value
outside it is an error naming the ones that are allowed:

```
el_button("go", "Go", type = "primry")
#> Error: `type` should be one of "default", "primary", "success", "warning",
#> "danger", "info", "text", not "primry".
```

Element itself would draw the button in its default style and say nothing.
The sets are read from Element's documentation, its source and its
stylesheet together, so a value any of them accepts is accepted here.
Matching is exact: `"prim"` is not taken for `"primary"`.

## Containers reimplemented as markup

Tabs, collapse, dialog and drawer are not Element's Vue components here but
their markup and classes, driven by a Shiny input binding -- a Vue instance
over them would recompile the components placed inside and disconnect them.
They follow Element closely:

* stacking, the backdrop, scroll lock, Escape and a click on the backdrop
  go through Element's own popup manager, so a dialog shares one z-index
  counter with every select, popover and message box, and starts where
  `el_page(z_index =)` says;
* `opened` and `closed` follow the end of Element's own transitions, and a
  drawer gives focus back to what had it;
* tabs take the arrow keys and Delete, scroll when they outgrow the bar,
  and carry Element's ARIA; collapse headers take Enter and Space, animate
  open and closed, and carry Element's ARIA.

What remains different: a dialog's or drawer's props other than `visible`,
`title`, `width` and `size` are set when the page is built -- there is no
reactive data behind them for an update to change -- and anything that
reaches into Element's own component instance, `$refs` on a dialog say, has
no instance to reach.

## Browsers, CSP and the road ahead

Element Plus 2.14.7 on Vue 3.5 is bundled -- both under active
development upstream. Each component is its own Vue application, made with
`Vue.createApp()`, so one that fails to mount leaves the rest of the page
working, and a component removed by Shiny unmounts cleanly.

The bridge needs a browser that supports `display: contents`, `:scope`
selectors and regular-expression lookbehind -- every current Chrome, Edge,
Firefox and Safari (16.4 and later); not Internet Explorer. A page with a
strict Content-Security-Policy must allow `'unsafe-eval'`: Vue compiles
templates in the browser, and functions given with `JS()` are evaluated
there.

## Known gaps

**Three attributes are deliberately unbound.** `value` on `el-checkbox` and
`el-radio`, which a group owns through `v-model`, and the deprecated
`auto-complete` spellings on `el-select` and `el-input`, which upstream marks
`@DEPRECATED` beside the `autocomplete` this package binds. They are listed in
`tools/api-coverage.py` with the reason.

**Element's i18n covers the component text, not yours.** `el_page(locale =)`
switches Element's own strings -- a date picker's month names, a table's "No
Data". Text you pass in is yours to translate.

**A component inside a `renderUI()` is re-created, not updated.** That is
Shiny's behaviour rather than this package's, but it matters more here: the
new instance starts from its arguments, so anything the user had changed is
lost. Prefer `update_el_*()` where you can.
