---
title: "Navigation and feedback"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Navigation and feedback}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
source("shots.R")
```

Element's navigation components report where the user went; its feedback
components are called from the server. Neither navigates or blocks on its own
-- what happens next is your app's decision.

## Menus

`el_menu()` takes a nested list. Each item's `index` is what it reports, and
`input$<id>_path` gives the trail to it:

```{r menu, eval = FALSE, shot = TRUE, shot_js = "document.querySelectorAll('#shot .el-menu-item')[0].click()", shot_wait = 2}
ui <- el_page(
  el_menu("nav", mode = "horizontal", active = "reports", items = list(
    list(index = "home", title = "Home", icon = "el-icon-s-home"),
    list(index = "reports", title = "Reports", children = list(
      list(index = "monthly", title = "Monthly"),
      list(index = "annual", title = "Annual")
    )),
    list(index = "settings", title = "Settings", disabled = TRUE)
  )),
  verbatimTextOutput("where")
)

server <- function(input, output, session) {
  output$where <- renderPrint(list(index = input$nav, path = input$nav_path))
}

shinyApp(ui, server)
```

`active` is Element's `default-active`: it is the current item, and
`update_el_menu()` moves it, so "default" would undersell it.

## Breadcrumbs

A breadcrumb reports the label clicked, so it can drive navigation inside a
Shiny app without any routing:

```{r breadcrumb, eval = FALSE, shot = TRUE, shot_js = "document.querySelectorAll('#shot .el-breadcrumb__inner')[1].click()", shot_wait = 2}
ui <- el_page(
  el_breadcrumb("trail", items = list(
    list(label = "Home"), list(label = "Reports"), list(label = "March")
  )),
  verbatimTextOutput("went")
)

server <- function(input, output, session) {
  output$went <- renderText(paste("Go to:", input$trail))
}

shinyApp(ui, server)
```

## Steps

`el_steps()` reports the active step and is moved from the server:

```{r steps, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#next_container button').click()", shot_wait = 2}
ui <- el_page(
  el_steps("wizard", active = 0, finish_status = "success", steps = list(
    list(title = "Details"), list(title = "Payment"), list(title = "Done")
  )),
  el_button("next", "Next step", type = "primary")
)

server <- function(input, output, session) {
  observeEvent(input$`next`, {
    update_el_steps(session, "wizard", active = min(input$wizard + 1, 3))
  })
}

shinyApp(ui, server)
```

## Tabs

`el_tabs()` holds live components, because it renders as markup rather than
as a Vue instance of its own:

```{r tabs, eval = FALSE, shot = TRUE}
el_tabs("views", type = "border-card", tabs = list(
  list(name = "settings", label = "Settings", content = tagList(
    el_switch("dark", value = TRUE, active_text = "Dark mode"),
    el_slider("size", value = 14, min = 10, max = 24)
  )),
  list(name = "about", label = "About", content = tags$p("Version 0.1.0"))
))
```

## Messages and notifications

These are calls from the server rather than UI. Neither waits for an answer:

```{r message, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#save_container button').click()", shot_sel = ".el-message", shot_wait = 1}
ui <- el_page(el_button("save", "Save", type = "primary"))

server <- function(input, output, session) {
  observeEvent(input$save, {
    el_message(session, "Saved", type = "success")
  })
}

shinyApp(ui, server)
```

```{r notification, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#run_container button').click()", shot_sel = ".el-notification", shot_wait = 1.5}
ui <- el_page(el_button("run", "Build report"))

server <- function(input, output, session) {
  observeEvent(input$run, {
    el_notification(session, "The March report is ready to download.",
                    title = "Report ready", type = "success")
  })
}

shinyApp(ui, server)
```

## Asking a question

When you need an answer, `el_message_box()` asks and reports it as
`input$<id>`: `"confirm"`, `"cancel"` or `"close"`. For
`box_type = "prompt"`, a confirmed answer is a list of `action` and the
`value` typed.

```{r message-box, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#delete_container button').click()", shot_sel = ".el-message-box", shot_wait = 1.5}
ui <- el_page(
  el_button("delete", "Delete row", type = "danger"),
  verbatimTextOutput("answer")
)

server <- function(input, output, session) {
  observeEvent(input$delete, {
    el_message_box(session, "confirm_delete", "This cannot be undone.",
                   title = "Delete the row?", type = "warning")
  })
  output$answer <- renderPrint(input$confirm_delete)
}

shinyApp(ui, server)
```

For something smaller than a dialog, `el_popconfirm()` anchors the question
to the button that raised it, and reports `input$<id>_confirm`:

```{r popconfirm, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#shot button').click()", shot_sel = ".el-popover", shot_wait = 1}
el_popconfirm("remove",
  reference = el_button("remove_btn", "Remove", type = "danger"),
  title = "Remove this item?")
```

## Loading

`el_loading()` opens a named mask and `el_loading_close()` shuts it. The
message goes out as soon as it is sent, so a mask opened before slow work is
on screen while the work runs:

```{r loading, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#refresh_container button').click()", shot_sel = ".el-loading-mask", shot_wait = 1}
ui <- el_page(
  el_button("refresh", "Refresh"),
  tags$div(id = "panel", style = "height: 160px; border: 1px solid #ebeef5",
           tableOutput("rows"))
)

server <- function(input, output, session) {
  observeEvent(input$refresh, {
    el_loading(session, "busy", target = "#panel", text = "Fetching rows...")
    on.exit(el_loading_close(session, "busy"), add = TRUE)
    Sys.sleep(3)   # the slow part
    output$rows <- renderTable(head(mtcars, 3))
  })
}

shinyApp(ui, server)
```

Because the mask is named, a second call under the same name replaces the
first rather than stacking.

## Dialogs and drawers

Both are markup with a Shiny input binding, so they hold live components.
`input$<id>` is whether it is open -- closing by the cross or the backdrop is
visible to the server too.

```{r dialog, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#open_container button').click()", shot_sel = ".el-dialog", shot_wait = 1.5}
ui <- el_page(
  el_button("open", "Settings", type = "primary"),
  el_dialog("settings", title = "Settings", width = "420px",
    content = tagList(
      el_switch("dark", value = TRUE, active_text = "Dark mode"),
      tags$br(), tags$br(),
      el_slider("size", value = 14, min = 10, max = 24)
    ),
    footer = el_button("apply", "Apply", type = "primary"))
)

server <- function(input, output, session) {
  observeEvent(input$open, update_el_dialog(session, "settings", visible = TRUE))
  observeEvent(input$apply, update_el_dialog(session, "settings", visible = FALSE))
}

shinyApp(ui, server)
```
