---
title: "Get started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
source("shots.R")
```

shiny.element brings Element UI 2.15.14 -- its inputs, tables, trees,
menus, dialogs and the rest -- to Shiny. Each component reports through
`input$<id>` and is updated from the server, like any other Shiny input.
Element UI and Vue 2.7 ship inside the package, so an app needs no network.

## Installation

```{r install, eval = FALSE}
install.packages("shiny.element")
# or the development version
remotes::install_github("kaipingyang/shiny.element")
```

## Quick start

`el_page()` is the page: it loads Vue and Element and gives the page
Element's look.

```{r quick, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#save_container button').click()", shot_wait = 1.5}
library(shiny)
library(shiny.element)

ui <- el_page(
  el_input("name", label = "Name", placeholder = "Your name", width = "300px"),
  el_rate("score", label = "Score", value = 3),
  el_button("save", "Save", type = "primary"),
  tags$div(style = "height: 12px"),
  el_alert("hint", title = "Nothing saved yet", type = "info", closable = FALSE)
)

server <- function(input, output, session) {
  observeEvent(input$save, {
    update_el_alert(id = "hint", type = "success",
                    title = paste0("Saved ", input$name, " (", input$score, "/5)"))
  })
}

shinyApp(ui, server)
```

Inside another page function -- `fluidPage()`, bslib's `page_sidebar()` --
call `use_element()` once instead, giving it the page's theme so Element
follows it:

```{r bslib, eval = FALSE}
theme <- el_theme(primary = "#7c3aed")
ui <- bslib::page_sidebar(
  theme = theme,
  use_element(theme = theme),
  sidebar = bslib::sidebar(el_select("metric", choices = c("Mean", "Median"))),
  el_table("summary", data = head(iris))
)
```

## Reading and writing

A component with a value reports it as `input$<id>`, on load and on change.
The server changes it with the matching `update_el_*()`, runs one of
Element's methods with `el_call()`, and shows a message, a notification or
a question with `el_message()`, `el_notification()` and `el_message_box()`.
Element's events arrive as `input$<id>_<event>`.

```{r rw, eval = FALSE}
server <- function(input, output, session) {
  output$chosen <- renderText(input$city)                     # read
  observeEvent(input$reset, update_el_select(id = "city", selected = "Beijing"))
  observeEvent(input$clear, el_call(id = "orders", method = "clearSelection"))
  observeEvent(input$orders_row_click, el_message(message = "Row clicked"))
}
```

## Where next

- **Components** -- a page for each of Element's components, in Element's
  own order, each demo of its documentation in R and its API tables beside
  the R names.
- **Forms and validation** -- labels and errors, choices, `el_form()`,
  shinyvalidate, dates.
- **Shiny integration** -- events, methods, modules, bookmarking, shinyjs,
  data from the server, components of your own.
- **Theming, sizes and languages** -- Element's colours and variables from
  the page's theme, sizes, locales.
- **What works, and what does not** -- where this differs from Element in a
  browser.
