---
title: "Shiny integration"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Shiny integration}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
source("shots.R")
```

How the components meet Shiny: what they report, how the server reaches
them, how they behave in modules, with bookmarks and alongside the rest of
the Shiny ecosystem, and how to build components of your own. Each
component's own page -- under Components -- shows what Element does with it.

## Reading and writing a component

A component reports to `input$<id>`, on load as well as on change:

```{r reading, eval = FALSE, shot = TRUE}
ui <- el_page(
  el_select("city", choices = c("Beijing", "Shanghai"), value = "Shanghai"),
  verbatimTextOutput("picked")
)

server <- function(input, output, session) {
  output$picked <- renderPrint(input$city)
}

shinyApp(ui, server)
```

Three separate channels reach back into it, and they do different things:

| | Reaches | Example |
|---|---|---|
| `update_el_*()` | the component's props | `update_el_select(session, "city", selected = "Beijing")` |
| `el_call()` | the component's methods | `el_call(session, "tbl", "clearSelection")` |
| `update_vue_data()` | the Vue instance's fields directly | `update_vue_data(session, "tip", list(tipContent = "..."))` |

Like Shiny's `update*Input()`, each takes the current session by default,
so `update_el_select(id = "city", selected = "Beijing")` is the same call.
An update reaches a component whether or not it has a value to report --
an alert, a timeline, a component only ever drawn by `renderUI()` -- and one
sent to an id that is not on the page, or to a field the component does not
have, logs a `[shiny-vue]` warning in the browser console rather than
vanishing.

`update_el_*()` cannot call a method, because it assigns into the Vue
instance's data and a method is a function. That is what `el_call()` is for. A
method with a return value answers asynchronously, as `input$<id>_<method>`:

```{r methods, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#ask_container button').click()", shot_wait = 2}
ui <- el_page(
  el_tree("tree", show_checkbox = TRUE, node_key = "id",
          default_expand_all = TRUE, checked = c("b1", "c"),
          data = list(
            list(id = "a", label = "Fruit", children = list(
              list(id = "b1", label = "Apple"), list(id = "b2", label = "Pear"))),
            list(id = "c", label = "Bread")
          )),
  el_button("ask", "Which are checked?"),
  verbatimTextOutput("answer")
)

server <- function(input, output, session) {
  observeEvent(input$ask, el_call(session, "tree", "getCheckedKeys"))
  output$answer <- renderPrint(input$tree_get_checked_keys)
}

shinyApp(ui, server)
```

## Events are event inputs

Every forwarded Element event sets its input with event priority. The input
keeps its last value like any other; what event priority adds is that sending
the same value again still counts as a change. Clicking the same row twice
fires an `observeEvent()` twice -- while an output that only reads the value
sees nothing new the second time.

Here is the same row clicked twice. The output reading the value shows where
the last click landed; only the observer knows there were two:

```{r event-inputs, eval = FALSE, shot = TRUE, shot_js = "var td = document.querySelectorAll('#shot .el-table__body tr')[1].querySelector('td'); td.click(); setTimeout(function(){ td.click(); }, 600);", shot_wait = 2.5}
ui <- el_page(
  el_table("tbl", data = head(iris[, c(1, 5)], 3)),
  verbatimTextOutput("polled"),
  verbatimTextOutput("latched")
)

server <- function(input, output, session) {
  # Reading the value: the last row clicked, but not how many times
  output$polled <- renderText({
    paste("last row clicked:", input$tbl_row_click$row_index)
  })

  # Observing the event: runs once per click, repeats included
  clicks <- reactiveVal(0)
  observeEvent(input$tbl_row_click, clicks(clicks() + 1))
  output$latched <- renderText(paste("clicks seen:", clicks()))
}

shinyApp(ui, server)
```

An event whose arguments cannot cross the wire -- a native `FocusEvent`, a DOM
node, a whole Vue instance -- reports `TRUE` instead, so an observer can still
tell that it happened.

## Shiny modules

Components follow Shiny's own rule. In a module's UI, the id is wrapped in
`ns()`, exactly as for `textInput()`; in its server, `input$<id>` and every
`update_el_*()` take the bare id, namespaced by the module's session. That
holds for UI built by `renderUI()` inside the module too, and for the
inputs a component adds to its id -- `input$rows_go` from a row action,
`input$tabs_edit`, `input$rows_selected_rows`.

```{r module, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#orders-rows_container .el-table__body .el-button').click()", shot_wait = 2}
orders_ui <- function(id) {
  ns <- NS(id)
  tagList(
    el_select(ns("status"), choices = c("paid", "pending"), selected = "paid"),
    el_table(ns("rows"), data = data.frame(order = c(101, 102)), columns = list(
      list(prop = "order", label = "Order"),
      list(label = "", cell = el$button(size = "mini",
        "@click" = "rowAction('open', scope)", "Open")))),
    uiOutput(ns("more")),
    verbatimTextOutput(ns("seen"))
  )
}

orders_server <- function(id) {
  moduleServer(id, function(input, output, session) {
    # Built in the server, still wrapped in ns() once
    output$more <- renderUI(el_switch(session$ns("urgent"), active_text = "Urgent"))
    output$seen <- renderPrint(list(status = input$status, urgent = input$urgent,
                                    opened = input$rows_open$row_index))
  })
}

ui <- el_page(orders_ui("orders"))
server <- function(input, output, session) orders_server("orders")
shinyApp(ui, server)
```

Before 0.1.0 the UI functions namespaced their id themselves, from the
session they were built in -- which inside `renderUI()` in a module turned
`ns("urgent")` into `"orders-orders-urgent"`, an input that never reported.
They no longer do; their `session` argument is deprecated, and a session
passed to it still namespaces, with a warning.

## Shiny's own tools

Each component is a Shiny input binding on a host element that carries its
id, so the tools that work on Shiny's inputs work on these.

**Bookmarking.** Under `enableBookmarking()`, every component's value comes
back from a bookmark -- including where a container is: the open tab, the
open panels of a collapse, an open dialog or drawer, the menu's current
item, the pager's page. Nothing needs to be set up beyond what Shiny itself
asks for.

```{r bookmark, eval = FALSE}
ui <- function(request) {
  el_page(
    el_select("city", choices = c("Beijing", "Shanghai")),
    el_tabs("views", tabs = list(
      list(name = "table", label = "Table", content = tags$p("...")),
      list(name = "chart", label = "Chart", content = tags$p("...")))),
    bookmarkButton()
  )
}
server <- function(input, output, session) {}
shinyApp(ui, server, enableBookmarking = "url")
```

**shinyjs.** `shinyjs::hide()` and `show()` take the component and its
label with it; `disable()` and `enable()` set the component's own
`disabled`, so it is drawn disabled as Element draws it rather than having a
native attribute set somewhere underneath.

**Inserting and removing.** `insertUI()` and `renderUI()` mount what they
add; `removeUI()` on a component's id removes it and destroys its Vue
instance, so it stops reporting.

**Validation.** shinyvalidate draws its message the way Element draws a
failed rule; see the forms article.

**Testing.** shinytest2's `set_inputs()` and `get_values()` read and write
a component as they do a `textInput()`.

## Nesting components

Two kinds of component wrap other content, and they behave differently.

**Containers are plain markup.** `el_row()`, `el_col()`, `el_container()`,
`el_collapse()`, `el_tabs()`, `el_dialog()` and `el_drawer()` render Element's
own CSS classes and drive their state through a Shiny input binding. They hold
anything, and what is inside keeps working as it would on its own.

```{r container, eval = FALSE, shot = TRUE}
el_collapse("panels", value = "one", items = list(
  list(name = "one", title = "Settings", content = tagList(
    el_switch("dark", value = TRUE, active_text = "Dark mode"),
    el_rate("stars", value = 4)
  )),
  list(name = "two", title = "About", content = tags$p("Version 0.1.0"))
))
```

**Wrappers absorb what they are given.** `el_tooltip()`, `el_popover()`,
`el_popconfirm()` and `el_infinite_scroll()` compile their content into their
own Vue instance, so a component handed to one is folded in rather than nested:
the two become a single instance carrying both sets of markup, data and
methods.

```{r absorb, eval = FALSE, shot = TRUE, shot_js = "var b = document.querySelector('#shot .el-button'); b.click(); b.click(); ['mouseenter','mouseover'].forEach(function(t){ b.dispatchEvent(new MouseEvent(t, {bubbles: true})); });", shot_sel = ".el-tooltip__popper", shot_wait = 1.5}
ui <- el_page(
  el_tooltip("hint", el_button("save", "Save", type = "primary"),
             content = "Writes to disk", placement = "right"),
  verbatimTextOutput("clicks")
)

server <- function(input, output, session) {
  output$clicks <- renderText(paste("Saved", input$save, "times"))   # still reports
}

shinyApp(ui, server)
```

This costs one thing. An absorbed component has no host of its own, so
nothing to send its `update_el_*()` to, and that stops working -- the
browser console says so, with a `[shiny-vue]` warning naming the id.
Drive it through the wrapper instead:

```{r absorbed-update, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#busy_container button').click()", shot_wait = 2}
ui <- el_page(
  el_tooltip("hint", el_button("save", "Save", type = "primary"),
             content = "Writes to disk"),
  el_button("busy", "Mark as saving")
)

server <- function(input, output, session) {
  observeEvent(input$busy, {
    # Not update_el_button(session, "save", ...): the button has no host
    # of its own any more. Its fields live on the tooltip.
    update_vue_data(session, "hint", list(label = "Saving...", loading = TRUE))
  })
}

shinyApp(ui, server)
```

If two absorbed components declare the same field -- most declare a `label`, a
`type` and a `disabled` -- the second one's fields are renamed on the way in
(`el3_label`), and the markup that names them is rewritten to match. You only
notice when reaching in with `update_vue_data()`, where the renamed field is
what to set.

## Slots

Every component takes `slots`, a named list:

```{r slots, eval = FALSE, shot = TRUE}
el_alert("problem", type = "error", show_icon = TRUE,
         description = "The upload was larger than 5 MB.",
         slots = list(title = tags$span(tags$b("Upload failed"), " -- try again")))
```

A scoped slot -- one where Element hands the template variables that only
exist while Vue renders -- is written with `template()` and passed through
untouched:

```{r scoped-slot, eval = FALSE, shot = TRUE}
el_calendar("cal", value = "2026-03-15", slots = list(
  dateCell = template(
    htmltools::HTML(paste0(
      "<div>{{ data.day.slice(8) }}",
      "<b v-if=\"data.day.slice(8) === '15'\" style=\"color:#F56C6C\">",
      " due</b></div>")),
    slot = "dateCell", scope = "{date, data}"
  )
))
```

Filling a slot replaces what Element put there, default and all. Element's
`el-form-item` error slot, for instance, wraps the message in
`div.el-form-item__error`; a template that renders only the message loses the
styling with it.

## Element's own markup

`el` holds a generator for every Element tag, for markup that needs no Vue
instance of its own -- inside one that already exists. Vue compiles `<el-*>`
tags only within the component it mounts, so a raw tag goes where a
component draws its contents: a `template()`, a slot, a table `cell`, a
wrapper's trigger.

```{r raw-tags, eval = FALSE, shot = TRUE}
# The tooltip's instance compiles the raw button it wraps
el_tooltip("hint", el$button(type = "primary", "Markup only"), content = "No input")
el_button("save", "A component", type = "primary")   # reports input$save
```

Placed at the top level of a page, the same `el$button()` is never compiled
and shows as its bare text. Use the raw tag where a component would be
wasted, and a component where the server needs to hear about it.

## Building your own

`el_widget()` assembles a component the way this package assembles its own,
and is exported for wrapping anything not covered here, or covered
differently:

```{r own-widget, eval = FALSE, shot = TRUE}
initials <- function(id, name, size = 48) {
  el_widget(
    id     = id,
    markup = el$avatar(":size" = "size", "{{ letters }}"),
    data   = list(size = size, letters = paste(substr(strsplit(name, " ")[[1]], 1, 1),
                                               collapse = "")),
    dependency = element_ui_dependency()
  )
}

initials("ada", "Ada Lovelace")
initials("alan", "Alan Mathison Turing", size = 64)
```

### An input of your own, built from `el$` tags

The pattern to follow when Element has the parts but no component here puts
them together the way you need -- say, a price range made of two number
inputs, reported as one value:

* write the markup with `el$` tags, binding each control to a field of
  `data` with `v-model`, and pass the result to `el_widget()`;
* name the fields to report with `report = c(<field> = id)`. The field is
  then `input$<id>` -- on load, on every change, and after an update;
* update it from the server with `update_vue_data()`, wrapped in a function
  of your own so callers do not need to know the field names;
* take `id` as given, so the caller wraps it in `ns()` inside a module;
* pass `element_ui_dependency()` unless the page is an `el_page()`.

```{r own-input, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#cheap_container button').click()", shot_wait = 2}
price_range_input <- function(id, value = c(0, 100), min = 0, max = 1000) {
  el_widget(
    id = id,
    markup = tags$div(style = "display: flex; align-items: center; gap: 8px",
      el$input_number("v-model" = "range[0]", ":min" = "min", ":max" = "range[1]",
                      "controls-position" = "right", size = "small"),
      tags$span("to"),
      el$input_number("v-model" = "range[1]", ":min" = "range[0]", ":max" = "max",
                      "controls-position" = "right", size = "small")),
    data   = list(range = as.list(value), min = min, max = max),
    report = c(range = id),
    dependency = element_ui_dependency()
  )
}

update_price_range <- function(session, id, value) {
  update_vue_data(session, id, list(range = as.list(value)))
}

ui <- el_page(
  price_range_input("price", value = c(20, 300)),
  el_button("cheap", "Under 50"),
  verbatimTextOutput("picked")
)

server <- function(input, output, session) {
  observeEvent(input$cheap, update_price_range(session, "price", c(0, 50)))
  output$picked <- renderPrint(input$price)
}

shinyApp(ui, server)
```

Each component is a host element carrying its id, with the Element markup
inside and a Shiny input binding on it -- the way reactR binds React
components -- so the rest of Shiny can reach it: `shinyjs::hide()`,
`shinyjs::disable()`, `removeUI()`, a test driver's `set_inputs()`. A
component built with `el_widget()` gets all of that. Mounting Vue yourself
gets none of it: there is then no binding, and the id is wherever you put it.

## Without Shiny

The components also work on a page with no Shiny session -- an R Markdown
or Quarto document, a page saved with `htmltools::save_html()`. They render
and respond: a select opens and picks, tabs switch, a collapse folds, a
table's rows tick. What they cannot do there is report: there is no
`input`, and `update_el_*()`, `el_call()` and the feedback functions have no
server to come from. Load the scripts once with `use_element()`, as for any
page that is not an `el_page()`. The examples on this website are built
exactly so.

## Data from the server

Where Element takes a JavaScript function to fetch data, the server can
answer instead, through an input and an update:

| Component | Asks through | Answered by |
|---|---|---|
| `el_select(remote = TRUE)` | `input$<id>_query` | `update_el_select(choices =)` |
| `el_autocomplete(remote = TRUE)` | `input$<id>_query` | `update_el_autocomplete(suggestions =)` |
| `el_tree(lazy = TRUE)` | `input$<id>_load` | `el_load_children()` |
| `el_cascader(props = list(lazy = TRUE))` | `input$<id>_lazy_load` | `el_load_children()` |
| `el_table(lazy = TRUE)` | `input$<id>_load` | `el_load_children()` |
| `el_infinite_scroll()` | `input$<id>_load` | a `uiOutput()` inside it |
| `el_pagination()` | `input$<id>`, the page | `update_el_table(data =)` |

A question the server never answers settles after 30 seconds -- a lazy
load with nothing, a remote search by leaving its loading state -- and a
lazy load's question settles at once when its component is removed or the
session ends. The Select, Input, Tree,
Cascader and Table pages show each one running.

