---
title: "Tables"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tables}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
source("shots.R")
```

`el_table()` is the largest component here, and the one whose Element API is
most worth knowing. It takes a data.frame directly.

```{r basic, eval = FALSE, shot = TRUE}
el_table("cars", data = head(mtcars[, 1:6], 5))
```

Row names that name something -- `mtcars`' car names -- are kept as a first
column, while row numbers are left out; `rownames = TRUE` or `FALSE` decides it
yourself. Column names with a dot are sanitised on the way in -- `Sepal.Length` becomes `Sepal_Length` -- because
Element reads a dotted `prop` as a path into a nested object.

## Columns

Without `columns`, one is inferred per data.frame column. Passing them lets
each carry its own props, which is how Element models them. Names may be
written in snake_case or in Element's own camelCase:

```{r columns, eval = FALSE, shot = TRUE}
el_table("flowers",
  data = head(iris, 6),
  border = TRUE,
  columns = list(
    list(prop = "Species", label = "Species", width = "110", fixed = "left"),
    list(prop = "Sepal_Length", label = "Sepal length", sortable = TRUE,
         align = "right"),
    list(prop = "Sepal_Width", label = "Sepal width", sortable = TRUE,
         align = "right"),
    list(prop = "Petal_Length", label = "Petal length", align = "right",
         header_align = "center")
  ))
```

Every column attribute Element documents is accepted: `align`,
`header_align`, `class_name`, `min_width`, `fixed`, `resizable`, `sortable`,
`sort_by`, `sort_orders`, `show_overflow_tooltip`, `filters`,
`filtered_value`, `filter_multiple`, `filter_placement`, `reserve_selection`,
`index`, and the ones taking a function below.

`el_table_config()` derives both halves from a data.frame, for when you want
to adjust the inferred columns rather than write them out:

```{r config, eval = FALSE, shot = TRUE}
cfg <- el_table_config(mtcars[, 1:5], max_rows = 4)
cfg$columns <- lapply(cfg$columns, function(col) {
  col$sortable <- TRUE
  col
})
el_table("cfg", data = cfg$data, columns = cfg$columns, stripe = TRUE)
```

## Formatting

A column's `formatter` is a JavaScript function, given the row, the column,
the cell value and its index. A column may also render its own header:

```{r formatter, eval = FALSE, shot = TRUE}
sales <- data.frame(region = c("North", "South", "East"),
                    amount = c(1234.5, 987.25, 2050))

el_table("sales", data = sales, columns = list(
  list(prop = "region", label = "Region"),
  list(prop = "amount", label = "Amount", align = "right",
       header_html = "<b>Amount</b> <small>(USD)</small>",
       formatter = htmlwidgets::JS(
         "function(row, col, value) { return '$' + value.toFixed(2); }"
       ))
))
```

`header_html` is inserted as markup, so pass only what you control.
Formatting in R first is usually simpler; reach for `formatter` when the
display depends on something only the browser knows.

## Cell templates and row actions

A column's `cell` is markup drawn once per row, with the row in reach as
`scope.row` -- a tag coloured by the row's status, a progress bar, a pair of
buttons. Element's own tags work there, written with `el$`; the package's
components do not, being one Vue instance each rather than one per row.

A button reports back with `rowAction()`: `rowAction('edit', scope)` sets
`input$<id>_edit` to the row's 1-based number and the row itself. A column
with `type = "expand"` opens each row onto its own `cell`, and `type =
"index"` numbers the rows:

```{r cells, eval = FALSE, shot = TRUE, shot_js = "document.querySelectorAll('#shot .el-table__body .el-button')[2].click(); setTimeout(function(){ document.querySelector('#shot .el-table__expand-icon').click(); }, 600);", shot_wait = 2}
tasks <- data.frame(task = c("Draft", "Review", "Publish"),
                    done = c(100, 60, 0),
                    owner = c("Ada", "Grace", "Linus"))

ui <- el_page(
  el_table("tasks", data = tasks, columns = list(
    list(type = "expand", cell = tags$p("Owner: {{ scope.row.owner }}")),
    list(type = "index", label = "#"),
    list(prop = "task", label = "Task"),
    list(prop = "done", label = "Progress",
         cell = el$progress(":percentage" = "scope.row.done")),
    list(label = "", width = "120", cell = el$button(
      size = "mini", "@click" = "rowAction('nudge', scope)", "Nudge"))
  )),
  verbatimTextOutput("nudged")
)

server <- function(input, output, session) {
  output$nudged <- renderPrint(req(input$tasks_nudge)$row$owner)
}

shinyApp(ui, server)
```

`loading = TRUE`, or `update_el_table(session, id, loading = TRUE)`, covers
the table with Element's loading mask while its data is fetched.

## Selection

`selection = TRUE` adds a checkbox column and reports two inputs:
`input$<id>_selected_rows`, the 1-based row numbers, and
`input$<id>_selected`, the rows themselves. Prefer the row numbers: a row with
mixed column types is simplified to a character vector on its way back
through JSON, so numbers arrive as strings.

```{r selection, eval = FALSE, shot = TRUE, shot_js = "var c = document.querySelectorAll('#shot .el-table__body .el-checkbox'); c[0].click(); c[2].click();", shot_wait = 2}
cars <- head(mtcars[, 1:4], 5)

ui <- el_page(
  el_table("cars", data = cars, selection = TRUE,
           highlight_selection_row = TRUE),
  verbatimTextOutput("picked")
)

server <- function(input, output, session) {
  output$picked <- renderPrint(cars[input$cars_selected_rows, ])
}

shinyApp(ui, server)
```

For single selection, `highlight_current_row = TRUE` reports the clicked row
as `input$<id>_current_change`.

## Row events

Every Element table event is forwarded as `input$<id>_<event>`. They are
event inputs, so read them with `observeEvent()`:

```{r events, eval = FALSE, shot = TRUE, shot_js = "document.querySelectorAll('#shot .el-table__body tr')[1].querySelector('td').click()", shot_wait = 2}
ui <- el_page(
  el_table("flowers", data = head(iris, 4), highlight_current_row = TRUE),
  verbatimTextOutput("clicked")
)

server <- function(input, output, session) {
  clicked <- reactiveVal("Click a row")
  observeEvent(input$flowers_row_click, {
    click <- input$flowers_row_click
    clicked(sprintf("Row %d: %s, sepal %s cm", click$row_index,
                    click$row$Species, click$row$Sepal_Length))
  })
  output$clicked <- renderText(clicked())
}

shinyApp(ui, server)
```

Each arrives as a named list rather than Element's raw arguments. A row event
carries `row_index` -- 1-based, to index your own data with -- the `row`, and
the `column` prop; a cell event adds the cell's `value`; `sort_change` gives
`column` and `order`; `current_change` gives `row_index` and
`previous_index`.

## A fixed header

`height` fixes the header and scrolls the body; `max_height` does the same
once the content exceeds it:

```{r height, eval = FALSE, shot = TRUE}
el_table("all", data = iris, height = "240px", stripe = TRUE)
```

## Summaries

`show_summary` adds a row of column totals. `sum_text` labels it, and
`summary_method` replaces the arithmetic:

```{r summary, eval = FALSE, shot = TRUE}
el_table("sums", data = head(mtcars[, c("mpg", "hp", "wt")], 5),
         show_summary = TRUE, sum_text = "Total", border = TRUE)
```

## Methods

`update_el_table()` changes data and settings; methods need `el_call()`.
`doLayout()` is the one to remember: a table rendered inside a tab or a
collapse that starts hidden measures its columns as zero, and stays that way
until told to measure again.

```{r methods, eval = FALSE, shot = TRUE, shot_js = "document.querySelectorAll('#shot .el-tabs__item')[1].click()", shot_wait = 2}
ui <- el_page(
  el_tabs("views", selected = "about", tabs = list(
    list(name = "about", label = "About", content = tags$p("Open the Data tab.")),
    list(name = "data", label = "Data",
         content = el_table("hidden", data = head(iris, 4)))
  ))
)

server <- function(input, output, session) {
  observeEvent(input$views, {
    if (identical(input$views, "data")) el_call(session, "hidden", "doLayout")
  })
}

shinyApp(ui, server)
```

## Server-side paging

There is no `server = TRUE` as in DT. Pair the table with `el_pagination()`
and send one page at a time. The pager reports `input$<id>_page` and
`input$<id>_size`:

```{r paging, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#shot .btn-next').click()", shot_wait = 2}
page_size <- 5
page_of <- function(n) iris[(n - 1) * page_size + seq_len(page_size), ]

ui <- el_page(
  el_table("rows", data = page_of(1)),
  el_pagination("pager", total = nrow(iris), page_size = page_size,
                layout = "total, prev, pager, next")
)

server <- function(input, output, session) {
  observeEvent(input$pager_page, {
    update_el_table(session, "rows", data = page_of(input$pager_page))
  })
}

shinyApp(ui, server)
```

## Tree data

Rows can nest, keyed by `row_key`. Each row may carry a `children` list:

```{r tree, eval = FALSE, shot = TRUE}
org <- list(
  list(id = 1, name = "Engineering", size = 42, children = list(
    list(id = 11, name = "Platform", size = 18),
    list(id = 12, name = "Product", size = 24)
  )),
  list(id = 2, name = "Design", size = 9)
)

el_table("org", data = org, row_key = "id", default_expand_all = TRUE,
         columns = list(list(prop = "name", label = "Team"),
                        list(prop = "size", label = "People")))
```

With `lazy = TRUE` and a `load` function, children are fetched as their
parent is expanded.
