---
title: "Affix"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Fix the element to a specific visible area.

## Basic Usage

Affix is fixed at the top of the page by default.

You can set `offset` attribute to change the offset top，the default value is 0.

```{r basic, eval = FALSE, shot = TRUE}
el_affix(
  offset = 120,
  el_button("affix_top", "Offset top 120px", type = "primary")
)
```

## Target Container

You can set `target` attribute to keep the affix in the container at all times. It will be hidden if out of range.

Please notice that the container avoid having scrollbar.

```{r target, eval = FALSE, shot = TRUE}
tags$div(
  class = "affix-container",
  style = "height: 400px; background: var(--el-color-primary-light-9)",
  el_affix(
    target = ".affix-container",
    offset = 80,
    el_button("affix_target", "Target container", type = "primary")
  )
)
```

## Fixed Position

The affix component provides two fixed positions: `top` and `bottom`.

You can set `position` attribute to change the fixed position, the default value is `top`.

```{r fixed, eval = FALSE, shot = TRUE}
el_affix(
  position = "bottom",
  offset = 20,
  el_button("affix_bottom", "Offset bottom 20px", type = "primary")
)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("affix")
```
