---
title: "Alert"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Displays important alert messages.

## Basic Usage

Alert components are non-overlay elements in the page that does not disappear automatically.

Alert provides 5 types of themes defined by `type`, whose default value is `info`. `primary` has been added in 2.9.11.

```{r basic, eval = FALSE, shot = TRUE}
types <- c("primary", "success", "info", "warning", "error")
tags$div(
  style = "max-width: 600px; display: grid; gap: 20px",
  lapply(types, function(t) {
    el_alert(title = paste(tools::toTitleCase(t), "alert"), type = t)
  })
)
```

## Theme

Alert provide two different themes, `light` and `dark`.

Set `effect` to change theme, default is `light`.

```{r theme, eval = FALSE, shot = TRUE}
types <- c("primary", "success", "info", "warning", "error")
tags$div(
  style = "max-width: 600px; display: grid; gap: 20px",
  lapply(types, function(t) {
    el_alert(
      title = paste(tools::toTitleCase(t), "alert"),
      type = t,
      effect = "dark"
    )
  })
)
```

## Customizable Close Button

Customize the close button as texts or other symbols.

Alert allows you to configure if it's closable. The close button text and closing callbacks are also customizable. `closable` attribute decides if the component can be closed or not. It accepts `boolean`, and the default is `true`. You can set `close-text` attribute to replace the default cross symbol as the close button. Be careful that `close-text` must be a string. `close` event fires when the component is closed.

Closing reports `input$<id>_close`, where Element Plus's demo raises a
browser alert.

```{r close-button, eval = FALSE, shot = TRUE}
tags$div(
  style = "max-width: 600px; display: grid; gap: 20px",
  el_alert(title = "Unclosable alert", type = "success", closable = FALSE),
  el_alert(
    title = "Customized close text",
    type = "info",
    close_text = "Gotcha"
  ),
  el_alert("alert_cb", title = "Alert with callback", type = "warning")
)
```

## With Icon

Displaying an icon improves readability.

Setting the `show-icon` attribute displays an icon that corresponds with the current Alert type. Or use the `icon` slot to customize icon.

```{r icon, eval = FALSE, shot = TRUE}
types <- c("primary", "success", "info", "warning", "error")
tags$div(
  style = "max-width: 600px; display: grid; gap: 20px",
  lapply(types, function(t) {
    el_alert(
      title = paste(tools::toTitleCase(t), "alert"),
      type = t,
      show_icon = TRUE
    )
  }),
  el_alert(
    title = "Error alert with custom icon",
    type = "error",
    show_icon = TRUE,
    slots = list(icon = el_icon("Bell"))
  )
)
```

## Centered Text

Use the `center` attribute to center the text.

```{r center, eval = FALSE, shot = TRUE}
types <- c("primary", "success", "info", "warning", "error")
tags$div(
  style = "max-width: 600px; display: grid; gap: 20px",
  lapply(types, function(t) {
    el_alert(
      title = paste(tools::toTitleCase(t), "alert"),
      type = t,
      center = TRUE,
      show_icon = TRUE
    )
  })
)
```

## With Description

Description includes a message with more detailed information.

Besides the required `title` attribute, you can add a `description` attribute to help you describe the alert with more details. Description can only store text string, and it will word wrap automatically.

```{r description, eval = FALSE, shot = TRUE}
tags$div(
  style = "max-width: 600px",
  el_alert(
    title = "With description",
    type = "success",
    description = "This is a description."
  )
)
```

## With Icon and Description

At last, this is an example with both icon and description.

```{r icon-description, eval = FALSE, shot = TRUE}
types <- c("primary", "success", "info", "warning", "error")
tags$div(
  style = "max-width: 600px; display: grid; gap: 20px",
  lapply(types, function(t) {
    el_alert(
      title = paste(tools::toTitleCase(t), "alert"),
      type = t,
      description = "More text description",
      show_icon = TRUE
    )
  })
)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("alert")
```
