---
title: "Autocomplete"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Get some recommended tips based on the current input.

## Basic Usage

Autocomplete component provides input suggestions.

The `fetch-suggestions` attribute is a method that return suggested inputs. In this example, `querySearch(queryString, cb)` return suggestions to Autocomplete via `cb(data)` when suggestions are ready.

```{r autocomplete, eval = FALSE, shot = TRUE}
restaurants <- c(
  "vue",
  "element",
  "cooking",
  "mint-ui",
  "vuex",
  "vue-router",
  "babel"
)
tags$div(
  style = "display: flex; gap: 40px",
  tags$div(
    tags$div(class = "demo-title", "list suggestions when activated"),
    el_autocomplete(
      "ac1",
      suggestions = restaurants,
      clearable = TRUE,
      placeholder = "Please Input",
      width = "240px"
    )
  ),
  tags$div(
    tags$div(class = "demo-title", "list suggestions on input"),
    el_autocomplete(
      "ac2",
      suggestions = restaurants,
      trigger_on_focus = FALSE,
      clearable = TRUE,
      placeholder = "Please Input",
      width = "240px"
    )
  )
)
```

## Custom template

Customize how suggestions are displayed.

Use `scoped slot` to customize suggestion items. In the scope, you can access the suggestion object via the `item` key.

Each suggestion drawn with a template of its own: the scoped default slot.

```{r autocomplete-template, eval = FALSE, shot = TRUE}
el_autocomplete(
  "ac_tpl",
  placeholder = "Please input",
  popper_class = "my-autocomplete",
  suggestions = list(
    list(value = "vue", link = "https://github.com/vuejs/vue"),
    list(value = "element", link = "https://github.com/ElemeFE/element")
  ),
  slots = list(
    suffix = el_icon("Edit", class = "el-input__icon"),
    default = template(
      htmltools::HTML(
        '<div class="value">{{ item.value }}</div><span class="link">{{ item.link }}</span>'
      ),
      scope = "{ item }"
    )
  )
)
```

## Remote search

Search data from server-side.

`remote = TRUE` asks the server: `input$<id>_query` is the text typed, and
`update_el_autocomplete(suggestions =)` answers it.

```{r remote-search, eval = FALSE, shot = TRUE}
el_autocomplete("ac_remote", remote = TRUE, placeholder = "Please input")
```

## Custom Loading

Override loading content.

```{r custom-loading, eval = FALSE, shot = TRUE}
el_autocomplete(
  "ac_loading",
  remote = TRUE,
  placeholder = "Please input",
  slots = list(loading = el_icon("Loading", class = "is-loading"))
)
```

## Custom Header & Footer

You can customize both the header and footer of the dropdown using slots

Use slot to customize the content.

```{r custom-header-footer, eval = FALSE, shot = TRUE}
tags$div(
  style = "display: flex; gap: 40px",
  el_autocomplete(
    "ac_header",
    suggestions = c("vue", "element", "cooking"),
    placeholder = "Please input",
    slots = list(header = "header content")
  ),
  el_autocomplete(
    "ac_footer",
    suggestions = c("vue", "element", "cooking"),
    placeholder = "Please input",
    slots = list(footer = "footer content")
  )
)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("autocomplete")
```
