---
title: "Badge"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

A number or status mark on buttons and icons.

## Basic Usage

Displays the amount of new messages.

The amount is defined with value which accepts Number or String.

```{r basic, eval = FALSE, shot = TRUE}
item <- function(...) tags$span(style = "margin-right: 40px", ...)
tagList(
  item(el_badge(value = 12, el_button("bd1", "comments"))),
  item(el_badge(value = 3, el_button("bd2", "replies"))),
  item(el_badge(value = 1, type = "primary", el_button("bd3", "comments"))),
  item(el_badge(value = 2, type = "warning", el_button("bd4", "replies"))),
  item(el_badge(value = 1, color = "green", el_button("bd5", "custom background"))))
```

## Max Value

You can customize the max value.

The max value is defined by property max which is a Number. Note that it only works when value is also a Number.

```{r max, eval = FALSE, shot = TRUE}
tagList(
  tags$span(style = "margin-right: 40px", el_badge(value = 200, max = 99, el_button("bm1", "comments"))),
  el_badge(value = 100, max = 10, el_button("bm2", "replies")))
```

## Customizations

Displays text content other than numbers. Or you can use the `content` slot to customize content.

When value is a String, it can display customized text. Or use the `content` slot.

```{r customize, eval = FALSE, shot = TRUE}
tagList(
  tags$span(style = "margin-right: 40px", el_badge(value = "new", el_button("bc1", "comments"))),
  el_badge(value = "hot", el_button("bc2", "replies")))
```

## Red Dot

Use a red dot to mark content that needs to be noticed.

Use the attribute `is-dot`. It is a Boolean.

```{r dot, eval = FALSE, shot = TRUE}
tagList(
  tags$span(style = "margin-right: 40px", el_badge(is_dot = TRUE, "query")),
  el_badge(is_dot = TRUE, el_button("bdot", NULL, icon = "Share", type = "primary")))
```

## Offset

Set offset of the badge dot, the format is [left, top], which represents the offset of the status dot from the left and top of the default position.

```{r offset, eval = FALSE, shot = TRUE}
el_badge(value = 1, offset = c(10, 5), el_button("boff", "offset"))
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("badge")
```
