---
title: "Breadcrumb"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Displays the location of the current page, making it easier to browser back.

## Basic usage

In `el-breadcrumb`, each `el-breadcrumb-item` is a tag that stands for every level starting from homepage. This component has a `String` attribute `separator`, and it determines the separator. Its default value is '/'.

```{r basic, eval = FALSE, shot = TRUE}
el_breadcrumb(
  "crumbs",
  separator = "/",
  items = list(
    el_breadcrumb_item("homepage", to = "/"),
    el_breadcrumb_item("promotion management"),
    el_breadcrumb_item("promotion list"),
    el_breadcrumb_item("promotion detail")
  )
)
```

## Icon separator

Set `separator-icon` to use `svg icon` as the separator，it will cover `separator`

```{r icon, eval = FALSE, shot = TRUE}
el_breadcrumb(
  "crumbs_icon",
  separator_icon = "ArrowRight",
  items = list(
    el_breadcrumb_item("homepage", to = "/"),
    el_breadcrumb_item("promotion management"),
    el_breadcrumb_item("promotion list"),
    el_breadcrumb_item("promotion detail")
  )
)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("breadcrumb")
```
