---
title: "Button"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Commonly used button.

## Basic usage

Use `type`, `plain`, `round`, `dashed` and `circle` to define Button's style.

```{r basic, eval = FALSE, shot = TRUE}
types <- c("default", "primary", "success", "info", "warning", "danger")
label <- function(t) tools::toTitleCase(t)
row <- function(...) tags$div(style = "margin-bottom: 16px", ...)
tagList(
  row(lapply(types, function(t) {
    el_button(paste0("b_", t), label(t), type = t)
  })),
  row(lapply(types, function(t) {
    el_button(paste0("p_", t), label(t), type = t, plain = TRUE)
  })),
  row(lapply(types, function(t) {
    el_button(paste0("r_", t), label(t), type = t, round = TRUE)
  })),
  row(lapply(types, function(t) {
    el_button(paste0("d_", t), label(t), type = t, dashed = TRUE)
  })),
  row(Map(
    function(t, i) {
      el_button(paste0("c_", t), NULL, type = t, circle = TRUE, icon = i)
    },
    types,
    c("Search", "Edit", "Check", "Message", "Star", "Delete")
  ))
)
```

## Disabled Button

The `disabled` attribute determines if the button is disabled.

Use `disabled` attribute to determine whether a button is disabled. It accepts a `Boolean` value.

```{r disabled, eval = FALSE, shot = TRUE}
types <- c("default", "primary", "success", "info", "warning", "danger")
tagList(
  tags$div(
    style = "margin-bottom: 16px",
    lapply(types, function(t) {
      el_button(
        paste0("dis_", t),
        tools::toTitleCase(t),
        type = t,
        disabled = TRUE
      )
    })
  ),
  lapply(types, function(t) {
    el_button(
      paste0("disp_", t),
      tools::toTitleCase(t),
      type = t,
      plain = TRUE,
      disabled = TRUE
    )
  })
)
```

## Link Button

> **Warning**
>
> `type="text"` has been **deprecated**, and **will be** removed in 3.0.0, consider switching to new API.
> 
> New API `link` has been added in 2.2.1, you can use `type` API to set the theme of your link button

```{r link, eval = FALSE, shot = TRUE}
types <- c("default", "primary", "success", "info", "warning", "danger")
tagList(
  tags$p("Basic link button"),
  tags$div(lapply(types, function(t) {
    el_button(paste0("l_", t), t, type = t, link = TRUE)
  })),
  tags$p("Disabled link button"),
  tags$div(lapply(types, function(t) {
    el_button(paste0("ld_", t), t, type = t, link = TRUE, disabled = TRUE)
  }))
)
```

## Text Button

> **Tip**
>
> Text button has been upgraded with a new design since 2.2.0 , if you want to use the
> previous version like button, you might want to check [Link](link.html#basic) out.
> 
> The API is also updated, because the `type` attribute also represents the button's style. So we have to make a new API
> `text: boolean` for text button.

Buttons without border and background.

```{r text, eval = FALSE, shot = TRUE}
types <- c("default", "primary", "success", "info", "warning", "danger")
tagList(
  tags$p("Basic text button"),
  tags$div(lapply(types, function(t) {
    el_button(paste0("t_", t), t, type = t, text = TRUE)
  })),
  tags$p("Background color always on"),
  tags$div(lapply(types, function(t) {
    el_button(paste0("tb_", t), t, type = t, text = TRUE, bg = TRUE)
  })),
  tags$p("Disabled text button"),
  tags$div(lapply(types, function(t) {
    el_button(paste0("td_", t), t, type = t, text = TRUE, disabled = TRUE)
  }))
)
```

## Icon Button

Use icons to add more meaning to Button. You can use icon alone to save some space, or use it with text.

Use the `icon` attribute to add icon. You can find the icon list in Element Plus icon component. Adding icons to the right side of the text is achievable with an `<i>` tag. Custom icons can be used as well.

```{r icon, eval = FALSE, shot = TRUE}
tagList(
  el_button("i1", NULL, type = "primary", icon = "Edit"),
  el_button("i2", NULL, type = "primary", icon = "Share"),
  el_button("i3", NULL, type = "primary", icon = "Delete"),
  el_button("i4", "Search", type = "primary", icon = "Search"),
  el_button("i5", "Upload", type = "primary", icon = "Upload")
)
```

## Button Group

Displayed as a button group, can be used to group a series of similar operations.

In 2.11.9 you can use the `direction` attribute.

Use tag `<el-button-group>` to group your buttons.

The radios turn the second group, with `update_el_button_group(direction
=)`.

```{r group, eval = FALSE, shot = TRUE, shot_js = "Array.from(document.querySelectorAll('#direction .el-radio')).find(function(r){ return r.innerText.trim() === 'Vertical'; }).click()", shot_expect = "document.querySelector('#dir_group .el-button-group--vertical')"}
ui <- el_page(
  el_button_group(
    el_button("prev", "Previous Page", type = "primary", icon = "ArrowLeft"),
    el_button(
      "next",
      tagList("Next Page", el_icon("ArrowRight", class = "el-icon--right")),
      type = "primary"
    )
  ),
  tags$br(),
  el_radio_group(
    "direction",
    choices = c(Horizontal = "horizontal", Vertical = "vertical"),
    value = "horizontal"
  ),
  tags$br(),
  el_button_group(
    id = "dir_group",
    direction = "horizontal",
    el_button("g1", NULL, type = "primary", icon = "House"),
    el_button("g2", NULL, type = "primary", icon = "Operation"),
    el_button("g3", NULL, type = "primary", icon = "Notification")
  )
)
server <- function(input, output, session) {
  observeEvent(input$direction, ignoreInit = TRUE, {
    update_el_button_group(session, "dir_group", direction = input$direction)
  })
}
shinyApp(ui, server)
```

## Loading Button

Click the button to load data, then the button displays a loading state.

Set `loading` attribute to `true` to display loading state.

> **Tip**
>
> You can use the `loading` slot or `loadingIcon` to customize your loading component
> 
> ps: `loading` slot has higher priority than loadingIcon

```{r loading, eval = FALSE, shot = TRUE}
tagList(
  el_button("ld1", "Loading", type = "primary", loading = TRUE),
  el_button(
    "ld2",
    "Loading",
    type = "primary",
    loading = TRUE,
    loading_icon = "Eleme"
  )
)
```

## Sizes

Besides default size, Button component provides three additional sizes for you to choose among different scenarios.

Use attribute `size` to set additional sizes with `large`, `small`.

```{r size, eval = FALSE, shot = TRUE}
row <- function(...) {
  tags$div(
    style = "margin-bottom: 16px; display: flex; align-items: center; gap: 12px",
    ...
  )
}
sizes <- c(large = "Large", default = "Default", small = "Small")
tagList(
  row(
    Map(
      function(s, l) el_button(paste0("s_", s), l, size = s),
      names(sizes),
      sizes
    ),
    Map(
      function(s) {
        el_button(paste0("si_", s), "Search", size = s, icon = "Search")
      },
      names(sizes)
    )
  ),
  row(
    Map(
      function(s, l) el_button(paste0("sr_", s), l, size = s, round = TRUE),
      names(sizes),
      sizes
    ),
    Map(
      function(s) {
        el_button(
          paste0("sri_", s),
          "Search",
          size = s,
          icon = "Search",
          round = TRUE
        )
      },
      names(sizes)
    )
  ),
  row(Map(
    function(s) {
      el_button(
        paste0("sc_", s),
        NULL,
        size = s,
        icon = "Search",
        circle = TRUE
      )
    },
    names(sizes)
  ))
)
```

## Tag

You can custom element tag, For example button, div, a, router-link, nuxt-link.

```{r tag, eval = FALSE, shot = TRUE}
tagList(
  el_button("tag1", "button"),
  el_button("tag2", "div", tag = "div")
)
```

## Custom Color (beta)

You can custom button color.

We will calculate hover color & active color automatically.

The `color` prop also works with `link` and `text` buttons since 2.13.7.

`color` makes the hover and active shades for it; `dark` for a dark page.

```{r custom, eval = FALSE, shot = TRUE}
opts <- list(
  list("Default"),
  list("Plain", plain = TRUE),
  list("Link", link = TRUE),
  list("Text", text = TRUE),
  list("Text BG", text = TRUE, bg = TRUE)
)
tagList(
  lapply(seq_along(opts), function(i) {
    do.call(
      el_button,
      c(list(paste0("cc", i), opts[[i]][[1]], color = "#626aef"), opts[[i]][-1])
    )
  }),
  lapply(seq_along(opts), function(i) {
    do.call(
      el_button,
      c(
        list(
          paste0("ccd", i),
          paste("Disabled", opts[[i]][[1]]),
          color = "#626aef",
          disabled = TRUE
        ),
        opts[[i]][-1]
      )
    )
  })
)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("button")
```
