---
title: "Calendar"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Display date.

## Basic

Set `value` to specify the currently displayed month. If `value` is not specified, current month is displayed. `value` supports two-way binding.

```{r basic, eval = FALSE, shot = TRUE}
el_calendar("cal", value = Sys.Date())
```

## Controller Type

You can set the type of the controller for Calendar header. When setting `select`, you can use `formatter` to customize `label`.

`controller_type` set in R; Element Plus's demo switches it with radio buttons.

```{r controller-type, eval = FALSE, shot = TRUE}
el_calendar("cal_ctl", value = Sys.Date(), controller_type = "select")
```

## Custom Content

Customize what is displayed in the calendar cell by setting `scoped-slot` named `date-cell`. In `scoped-slot` you can get the date (the date of the current cell), data (including the type, isSelected, day attribute). For details, please refer to the API documentation below.

```{r customize, eval = FALSE, shot = TRUE}
el_calendar(
  "cal_cell",
  slots = list(
    `date-cell` = template(
      htmltools::HTML(paste0(
        "<p :class=\"data.isSelected ? 'is-selected' : ''\">",
        "{{ data.day.split('-').slice(1).join('-') }} ",
        "{{ data.isSelected ? '✔️' : '' }}</p>"
      )),
      slot = "date-cell",
      scope = "{ data }"
    )
  )
)
```

## Range

Set the `range` attribute to specify the display range of the calendar. Start time must be Monday, end time must be Sunday, and the time span cannot exceed two months.

```{r range, eval = FALSE, shot = TRUE}
el_calendar("cal_range", range = c("2019-03-04", "2019-03-24"))
```

## Customize header

The header's buttons move the calendar with Element Plus's `selectDate()`,
called on the calendar's ref, `$refs.calendar`, as upstream names it.

```{r header, eval = FALSE, shot = TRUE}
el_calendar(
  "cal_head",
  slots = list(
    header = template(
      htmltools::HTML(paste0(
        "<span>Custom header content</span><span>{{ date }}</span>",
        "<el-button-group>",
        "<el-button size=\"small\" @click=\"$refs.calendar.selectDate('prev-year')\">Previous Year</el-button>",
        "<el-button size=\"small\" @click=\"$refs.calendar.selectDate('prev-month')\">Previous Month</el-button>",
        "<el-button size=\"small\" @click=\"$refs.calendar.selectDate('today')\">Today</el-button>",
        "<el-button size=\"small\" @click=\"$refs.calendar.selectDate('next-month')\">Next Month</el-button>",
        "<el-button size=\"small\" @click=\"$refs.calendar.selectDate('next-year')\">Next Year</el-button>",
        "</el-button-group>"
      )),
      slot = "header",
      scope = "{ date }"
    )
  )
)
```

## Localization

The default locale of is English, if you need to use other languages, please check [Internationalization](https://element-plus.org/en-US/guide/i18n)

Note, date time locale (month name, first day of the week ...) are also configured in localization.

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("calendar")
```
