---
title: "Card"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Integrate information in a card container.

## Basic usage

Card includes title, content and operations.

Card is made up of `header`, `body` and `footer`. `header` and `footer` are optional, and its content distribution depends on a named slot.

```{r basic, eval = FALSE, shot = TRUE}
el_card(
  header = tags$div(class = "card-header", tags$span("Card name")),
  footer = "Footer content",
  width = "480px",
  lapply(1:4, function(o) tags$p(class = "text item", paste("List item", o)))
)
```

## Simple card

The header part can be omitted.

```{r simple, eval = FALSE, shot = TRUE}
el_card(
  width = "480px",
  lapply(1:4, function(o) tags$p(class = "text item", paste("List item", o)))
)
```

## With images

Display richer content by adding some configs.

The `body-style` attribute defines CSS style of custom `body`.

```{r with-images, eval = FALSE, shot = TRUE}
el_card(
  header = "Yummy hamburger",
  width = "480px",
  tags$img(
    src = "https://shadow.elemecdn.com/app/element/hamburger.9cf7b091-55e9-11e9-a976-7f4d0b07eef6.png",
    alt = "A hamburger",
    style = "width: 100%"
  )
)
```

## Shadow

You can define when to show the card shadows

The `shadow` attribute determines when the card shadows are displayed. It can be `always`, `hover` or `never`.

```{r shadow, eval = FALSE, shot = TRUE}
tags$div(
  style = "display: flex; flex-wrap: wrap; gap: 16px",
  el_card("Always", shadow = "always", width = "480px"),
  el_card("Hover", shadow = "hover", width = "480px"),
  el_card("Never", shadow = "never", width = "480px")
)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("card")
```
