---
title: "Carousel"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Loop a series of images or texts in a limited space

## Basic usage

Combine `el-carousel` with `el-carousel-item`, and you'll get a carousel. Content of each slide is completely customizable, and you just need to place it inside `el-carousel-item` tag. By default the carousel switches when mouse hovers over an indicator. Set `trigger` to `click`, and the carousel switches only when an indicator is clicked.

```{r basic, eval = FALSE, shot = TRUE}
slides <- function(n) {
  lapply(seq_len(n), function(i) {
    el_carousel_item(tags$div(class = "demo-slide", i))
  })
}
tagList(
  tags$span(
    class = "demonstration",
    "Switch when indicator is hovered (default)"
  ),
  el_carousel("car1", height = "150px", items = slides(4)),
  tags$span(class = "demonstration", "Switch when indicator is clicked"),
  el_carousel("car2", trigger = "click", height = "150px", items = slides(4))
)
```

## Motion blur

Add motion blur to infuse dynamism and smoothness into the carousel.

Enabling motion blur enhances the dynamism and smoothness of the carousel. By default, the `motion-blur` parameter is set to `false`, activating this feature and providing a visually engaging experience.

```{r motion-blur, eval = FALSE, shot = TRUE}
slides <- function(n) {
  lapply(seq_len(n), function(i) {
    el_carousel_item(tags$div(class = "demo-slide", i))
  })
}
tagList(
  tags$span(class = "demonstration", "Motion blur the switch (default)"),
  el_carousel(
    "car_mb",
    height = "200px",
    motion_blur = TRUE,
    items = slides(4)
  ),
  tags$p(class = "demonstration", "Vertical effect"),
  el_carousel(
    "car_mbv",
    height = "200px",
    direction = "vertical",
    motion_blur = TRUE,
    autoplay = FALSE,
    items = slides(4)
  )
)
```

## Indicators

Indicators can be displayed outside the carousel

The `indicator-position` attribute determines where the indicators are located. By default they are inside the carousel, and setting `indicator-position` to `outside` moves them outside; setting `indicator-position` to `none` hides the indicators.

```{r indicator, eval = FALSE, shot = TRUE}
el_carousel(
  "car_ind",
  indicator_position = "outside",
  items = lapply(1:4, function(i) {
    el_carousel_item(tags$div(class = "demo-slide", i))
  })
)
```

## Arrows

You can define when arrows are displayed

The `arrow` attribute determines when arrows are displayed. By default they appear when mouse hovers over the carousel. Setting `arrow` to `always` or `never` shows/hides the arrows permanently.

```{r arrows, eval = FALSE, shot = TRUE}
el_carousel(
  "car_arrow",
  interval = 5000,
  arrow = "always",
  items = lapply(1:4, function(i) {
    el_carousel_item(tags$div(class = "demo-slide", i))
  })
)
```

## Auto height

When the `height` of `carousel` is set to `auto`, the `carousel` height will be automatically set according to the height of the `carousel item`

`height = "auto"` takes the height of the slide showing: each slide
sets its own, with `style`.

```{r auto-height, eval = FALSE, shot = TRUE}
el_carousel(
  "car_auto",
  height = "auto",
  items = lapply(c(100, 200, 300), function(h) {
    el_carousel_item(
      tags$div(
        class = "demo-slide",
        style = sprintf("line-height: %dpx", h),
        sprintf("height %dpx", h)
      ),
      style = sprintf("height: %dpx", h)
    )
  })
)
```

## Card mode

When a page is wide enough but has limited height, you can activate card mode for carousels

Setting `type` to `card` activates the card mode. Apart from the appearance, the biggest difference between card mode and common mode is that clicking the slides at both sides directly switches the carousel in card mode.

```{r card, eval = FALSE, shot = TRUE}
el_carousel(
  "car_card",
  interval = 4000,
  type = "card",
  height = "200px",
  items = lapply(1:6, function(i) {
    el_carousel_item(tags$div(class = "demo-slide", i))
  })
)
```

## Vertical

By default, `direction` is `horizontal`. Let carousel be displayed in the vertical direction by setting `direction` to `vertical`.

```{r vertical, eval = FALSE, shot = TRUE}
slides <- function(n) {
  lapply(seq_len(n), function(i) {
    el_carousel_item(tags$div(class = "demo-slide", i))
  })
}
tagList(
  tags$p(class = "demonstration", "normal vertical layout"),
  el_carousel(
    "car_v",
    height = "200px",
    direction = "vertical",
    autoplay = FALSE,
    items = slides(4)
  ),
  tags$p(class = "demonstration", "card vertical layout"),
  el_carousel(
    "car_vc",
    height = "400px",
    direction = "vertical",
    type = "card",
    autoplay = FALSE,
    items = slides(4)
  )
)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("carousel")
```
