---
title: "Cascader"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

If the options have a clear hierarchical structure, Cascader can be used to view and select them.

## Basic usage

There are two ways to expand child option items.

Assigning the `options` attribute to an array of options renders a Cascader. The `props.expandTrigger` attribute defines how child options are expanded.

```{r basic, eval = FALSE, shot = TRUE}
tree <- list(
  list(
    value = "guide",
    label = "Guide",
    children = list(
      list(
        value = "disciplines",
        label = "Disciplines",
        children = list(
          list(value = "consistency", label = "Consistency"),
          list(value = "feedback", label = "Feedback")
        )
      ),
      list(
        value = "navigation",
        label = "Navigation",
        children = list(
          list(value = "side", label = "Side Navigation"),
          list(value = "top", label = "Top Navigation")
        )
      )
    )
  ),
  list(
    value = "component",
    label = "Component",
    children = list(
      list(
        value = "basic",
        label = "Basic",
        children = list(
          list(value = "layout", label = "Layout"),
          list(value = "color", label = "Color")
        )
      )
    )
  )
)
tagList(
  tags$p("Child options expand when clicked (default)"),
  el_cascader("cas_click", options = tree),
  tags$p("Child options expand when hovered"),
  el_cascader(
    "cas_hover",
    options = tree,
    props = list(expandTrigger = "hover")
  )
)
```

## Disabled option

Disable an option by setting a `disabled` field in the option object.

In this example, the first item in `options` array has a `disabled: true` field, so it is disabled. By default, Cascader checks the `disabled` field in each option object; if you are using another field name to indicate whether an option is disabled, you can assign it in the `props.disabled` attribute (see the API table below for details). And of course, field name `value`, `label` and `children` can also be customized in the same way.

```{r option-disabling, eval = FALSE, shot = TRUE}
el_cascader(
  "cas_dis",
  options = list(
    list(
      value = "guide",
      label = "Guide",
      disabled = TRUE,
      children = list(
        list(value = "disciplines", label = "Disciplines")
      )
    ),
    list(
      value = "component",
      label = "Component",
      children = list(
        list(value = "basic", label = "Basic")
      )
    )
  )
)
```

## Clearable

Set `clearable` attribute for `el-cascader` and a clear icon will appear when selected and hovered

```{r clearable, eval = FALSE, shot = TRUE}
el_cascader(
  "cas_clear",
  clearable = TRUE,
  options = list(
    list(
      value = "guide",
      label = "Guide",
      children = list(
        list(value = "disciplines", label = "Disciplines")
      )
    )
  )
)
```

## Custom Clear Icon

You can customize the clear icon by setting the `clear-icon` attribute

```{r clear-icon, eval = FALSE, shot = TRUE}
el_cascader(
  "cas_clear_icon",
  clearable = TRUE,
  clear_icon = "CloseBold",
  placeholder = "Custom clear icon",
  options = list(
    list(
      value = "guide",
      label = "Guide",
      children = list(
        list(value = "disciplines", label = "Disciplines")
      )
    )
  )
)
```

## Display only the last level

The input can display only the last level instead of all levels.

The `show-all-levels` attribute defines if all levels are displayed. If it is `false`, only the last level is displayed.

```{r last-level, eval = FALSE, shot = TRUE}
el_cascader(
  "cas_last",
  show_all_levels = FALSE,
  options = list(
    list(
      value = "guide",
      label = "Guide",
      children = list(
        list(
          value = "disciplines",
          label = "Disciplines",
          children = list(
            list(value = "consistency", label = "Consistency")
          )
        )
      )
    )
  )
)
```

## Multiple Selection

Add `:props="props"` in tag and set data `props = { multiple: true }` to use multiple selection.

Do:

Don't do:

When using multiple selection, all selected tags will display by default. You can set `collapse-tags = true` to fold selected tags. You can set `max-collapse-tags` to show max tags number, default 1. You can check them when mouse hover collapse text by using `collapse-tags-tooltip` attribute.

```{r multiple-selection, eval = FALSE, shot = TRUE}
world <- list(list(
  value = 1,
  label = "Asia",
  children = list(
    list(
      value = 2,
      label = "China",
      children = list(
        list(value = 3, label = "Beijing"),
        list(value = 4, label = "Shanghai"),
        list(value = 5, label = "Hangzhou")
      )
    ),
    list(
      value = 6,
      label = "Japan",
      children = list(
        list(value = 7, label = "Tokyo"),
        list(value = 8, label = "Osaka")
      )
    )
  )
))
tagList(
  tags$p("Display all tags (default)"),
  el_cascader(
    "cas_m1",
    options = world,
    props = list(multiple = TRUE),
    clearable = TRUE
  ),
  tags$p("Collapse tags"),
  el_cascader(
    "cas_m2",
    options = world,
    props = list(multiple = TRUE),
    collapse_tags = TRUE,
    clearable = TRUE
  ),
  tags$p("Collapse tags tooltip"),
  el_cascader(
    "cas_m3",
    options = world,
    props = list(multiple = TRUE),
    collapse_tags = TRUE,
    collapse_tags_tooltip = TRUE,
    clearable = TRUE
  ),
  tags$p("Max Collapse Tags"),
  el_cascader(
    "cas_m4",
    options = world,
    props = list(multiple = TRUE),
    collapse_tags = TRUE,
    collapse_tags_tooltip = TRUE,
    max_collapse_tags = 3,
    clearable = TRUE
  )
)
```

## Select any level of options

In single selection, only the leaf nodes can be checked, and in multiple selection, check parent nodes will lead to leaf nodes be checked eventually. When enable this feature, it can make parent and child nodes unlinked and you can select any level of options.

Set `props.checkStrictly = true` to make checked state of a node not affects its parent nodes and child nodes, and then you can select any level of options.

```{r any-level, eval = FALSE, shot = TRUE}
tree <- list(list(
  value = "guide",
  label = "Guide",
  children = list(
    list(
      value = "disciplines",
      label = "Disciplines",
      children = list(
        list(value = "consistency", label = "Consistency")
      )
    )
  )
))
tagList(
  tags$p("Select any level of options (Single selection)"),
  el_cascader(
    "cas_any1",
    options = tree,
    props = list(checkStrictly = TRUE),
    clearable = TRUE
  ),
  tags$p("Select any level of options (Multiple selection)"),
  el_cascader(
    "cas_any2",
    options = tree,
    props = list(multiple = TRUE, checkStrictly = TRUE),
    clearable = TRUE
  )
)
```

## Dynamic loading

Dynamic load its child nodes when checked a node.

Set `lazy = true` to use dynamic loading, and you have to specify how to load the data source by `lazyload`. There are two parameters of `lazyload`,the first parameter `node` is the node currently clicked, and the `resolve` is a callback that indicate loading is finished which must invoke. To display the status of node more accurately, you can add a `leaf` field (can be modified by `props.leaf`) to indicate whether it is a leaf node. Otherwise, it will be inferred by if has any child nodes.

The server answers each level: `input$<id>_lazy_load` asks, and
`el_load_children()` replies -- see the Shiny integration guide.

```{r dynamic-loading, eval = FALSE, shot = TRUE}
el_cascader("cas_lazy", props = list(lazy = TRUE))
```

## Filterable

Search and select options with a keyword.

Adding `filterable` to `el-cascader` enables filtering. Cascader will match nodes whose label or parent's label (according to `show-all-levels`) includes input keyword. Of course, you can customize search logic by `filter-method` which accepts a function, the first parameter is `node`, the second is `keyword`, and need return a boolean value indicating whether it hits.

```{r filterable, eval = FALSE, shot = TRUE}
tree <- list(list(
  value = "guide",
  label = "Guide",
  children = list(
    list(value = "disciplines", label = "Disciplines"),
    list(value = "navigation", label = "Navigation")
  )
))
tagList(
  tags$p("Filterable (Single selection)"),
  el_cascader(
    "cas_f1",
    options = tree,
    filterable = TRUE,
    placeholder = "Try searching: Guide"
  ),
  tags$p("Filterable (Multiple selection)"),
  el_cascader(
    "cas_f2",
    options = tree,
    filterable = TRUE,
    props = list(multiple = TRUE),
    placeholder = "Try searching: Guide"
  )
)
```

## Custom option content

You can customize the content of cascader node.

You can customize the content of cascader node by `scoped slot`. You'll have access to `node` and `data` in the scope, standing for the Node object and node data of the current node respectively.

```{r custom-content, eval = FALSE, shot = TRUE}
el_cascader(
  "cas_content",
  options = list(
    list(
      value = "guide",
      label = "Guide",
      children = list(
        list(value = "disciplines", label = "Disciplines"),
        list(value = "navigation", label = "Navigation")
      )
    )
  ),
  slots = list(
    default = template(
      htmltools::HTML(paste0(
        "<span>{{ data.label }}</span>",
        "<span v-if=\"!node.isLeaf\"> ({{ data.children.length }}) </span>"
      )),
      scope = "{ node, data }"
    )
  )
)
```

## Custom suggestion item

You can customize the filter suggestion item by `suggestion-item` slot. You'll have access to `item` in the scope, standing for the suggestion item.

```{r custom-suggestion-item, eval = FALSE, shot = TRUE}
el_cascader(
  "cas_sugg",
  filterable = TRUE,
  placeholder = "Try searching: Guide",
  options = list(
    list(
      value = "guide",
      label = "Guide",
      children = list(
        list(value = "disciplines", label = "Disciplines")
      )
    )
  ),
  slots = list(
    `suggestion-item` = template(
      htmltools::HTML(
        "<span>\U0001F50D {{ item.pathLabels.join(' > ') }}</span>"
      ),
      slot = "suggestion-item",
      scope = "{ item }"
    )
  )
)
```

## Cascader panel

`CascaderPanel` is the core component of `Cascader` which has various of features such as single selection, multiple selection, dynamic loading and so on.

Just like `el-cascader`, you can set alternative options by `options`, and enable other features by `props`, see the API form below for details.

```{r panel, eval = FALSE, shot = TRUE}
el_cascader_panel(
  "cas_panel",
  options = list(
    list(
      value = "guide",
      label = "Guide",
      children = list(
        list(value = "disciplines", label = "Disciplines"),
        list(value = "navigation", label = "Navigation")
      )
    ),
    list(
      value = "component",
      label = "Component",
      children = list(
        list(value = "basic", label = "Basic")
      )
    )
  )
)
```

## Custom Tag

You can customize tags.

Insert customized tags into the slot of `el-cascader`. `collapse-tags`, `collapse-tags-tooltip`, `max-collapse-tags` will not work.

```{r custom-tag, eval = FALSE, shot = TRUE}
world <- list(list(
  value = 1,
  label = "Asia",
  children = list(
    list(value = 2, label = "China"),
    list(value = 3, label = "Japan")
  )
))
el_cascader(
  "cas_tag",
  options = world,
  props = list(multiple = TRUE),
  clearable = TRUE,
  slots = list(
    tag = template(
      htmltools::HTML(
        "<el-tag v-for=\"(item, index) in data\" :key=\"item.key\" :color=\"index % 2 === 0 ? '#FFDE0A' : ''\">{{ item.text }}</el-tag>"
      ),
      slot = "tag",
      scope = "{ data }"
    )
  )
)
```

## Show Checked Strategy

Control how selected values are displayed in multiple selection mode.

In multiple selection mode, you can use `show-checked-strategy` to control how selected values are displayed. The default strategy is `child`, which shows all selected child nodes. The `parent` strategy only shows parent nodes when all their children are selected.

```{r show-checked-strategy, eval = FALSE, shot = TRUE}
world <- list(list(
  value = 1,
  label = "Asia",
  children = list(
    list(
      value = 2,
      label = "China",
      children = list(
        list(value = 3, label = "Beijing"),
        list(value = 4, label = "Shanghai")
      )
    )
  )
))
tagList(
  tags$p("Strategy: child (default, show all selected child nodes)"),
  el_cascader(
    "cas_s1",
    options = world,
    props = list(multiple = TRUE),
    show_checked_strategy = "child",
    clearable = TRUE
  ),
  tags$p(
    "Strategy: parent (show only parent nodes when all children are selected)"
  ),
  el_cascader(
    "cas_s2",
    options = world,
    props = list(multiple = TRUE),
    show_checked_strategy = "parent",
    clearable = TRUE
  )
)
```

## Click to Check Node

Only using `multiple` or `checkStrictly` attributes.

You can add `checkOnClickNode` to be able to click on the node in addition with the prefix icon.\
Toggle the visibility of the prefix with `showPrefix`.
:::tip Add `checkOnClickLeaf` to check only the leaf node (last children), enabled by default.
:::

```{r check-on-click-node, eval = FALSE, shot = TRUE}
tree <- list(list(
  value = "guide",
  label = "Guide",
  children = list(
    list(value = "disciplines", label = "Disciplines"),
    list(value = "navigation", label = "Navigation")
  )
))
tagList(
  tags$p("checkStrictly | Single mode"),
  el_cascader(
    "cas_c1",
    options = tree,
    clearable = TRUE,
    props = list(checkStrictly = TRUE, checkOnClickNode = TRUE)
  ),
  tags$p("checkStrictly | Multiple mode"),
  el_cascader(
    "cas_c2",
    options = tree,
    clearable = TRUE,
    props = list(multiple = TRUE, checkStrictly = TRUE, checkOnClickNode = TRUE)
  )
)
```

## Custom Header & Footer

You can customize both the header and footer of the dropdown using slots.

Use slot to customize the content.

```{r custom-header-footer, eval = FALSE, shot = TRUE}
tree <- list(list(
  value = "guide",
  label = "Guide",
  children = list(
    list(value = "disciplines", label = "Disciplines")
  )
))
tagList(
  tags$p("Custom header content"),
  el_cascader(
    "cas_h",
    options = tree,
    props = list(multiple = TRUE),
    clearable = TRUE,
    slots = list(header = "All")
  ),
  tags$p("Custom footer content"),
  el_cascader(
    "cas_ft",
    options = tree,
    clearable = TRUE,
    slots = list(footer = "Footer content")
  )
)
```

## Virtual Scroll

When dealing with large amounts of data, you can enable virtual scrolling to improve performance.

Set `virtual-scroll` to `true` to enable virtual scrolling. You can also customize the menu height with `height` and node height with `item-size`. Default height is 204px and default item size is 34px.

```{r virtual-scroll, eval = FALSE, shot = TRUE}
big <- lapply(1:100, function(i) {
  list(
    value = paste0("v", i),
    label = paste("Option", i),
    children = lapply(1:100, function(j) {
      list(value = paste0("v", i, "-", j), label = paste("Option", i, j))
    })
  )
})
el_cascader(
  "cas_virtual",
  options = big,
  filterable = TRUE,
  virtual_scroll = TRUE,
  clearable = TRUE,
  placeholder = "Select with large data"
)
```

## Custom Suggestion Width

The width of the suggestion panel (when filtering) is calculated by default based on the maximum width of the matched options. If you customize the suggestion options through the `suggestion-item` slot, it is likely that the text displayed in the options is not equal to the value of `label`, resulting in calculation errors. In this case, you can use the `fit-input-width` attribute to fix its width. When the value is `number`, the width is a specific fixed pixel value.

> **Tip**
>
> The `fit-input-width` attribute only controls the width of the suggestion panel during searching, it does not affect the default cascader panel.

```{r fit-input-width, eval = FALSE, shot = TRUE}
el_cascader(
  "cas_fit",
  fit_input_width = TRUE,
  options = list(
    list(
      value = "guide",
      label = "Guide",
      children = list(
        list(value = "disciplines", label = "Disciplines")
      )
    )
  )
)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("cascader")
```
