---
title: "Checkbox"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

A group of options for multiple choices.

> **Warning**
>
> `label` act as `value` has been **deprecated**, `label` is used only as display text, this action **will be** removed in 3.0.0, consider switching to new API.

> **Tip**
>
> New API `value` has been added in 2.6.0, the examples in the document all use the `value`.
> If you are using a version **less than** 2.6.0 and using `checkbox-group`, please refer to:

## Basic usage

Checkbox can be used alone to switch between two states.

Define `v-model`(bind variable) in `el-checkbox`. The default value is a `Boolean` for single `checkbox`, and it becomes `true` when selected. Content inside the `el-checkbox` tag will become the description following the button of the checkbox.

```{r basic, eval = FALSE, shot = TRUE}
row <- function(...) tags$div(style = "margin: 8px 0", ...)
tagList(
  row(
    el_checkbox("cb1", "Option 1", value = TRUE, size = "large"),
    el_checkbox("cb2", "Option 2", size = "large")
  ),
  row(el_checkbox("cb3", "Option 1"), el_checkbox("cb4", "Option 2")),
  row(
    el_checkbox("cb5", "Option 1", size = "small"),
    el_checkbox("cb6", "Option 2", size = "small")
  )
)
```

## Disabled State

Disabled state for checkbox.

Set the `disabled` attribute.

```{r disabled, eval = FALSE, shot = TRUE}
tagList(
  el_checkbox("cbd1", "Disabled", disabled = TRUE),
  el_checkbox("cbd2", "Not disabled", value = TRUE)
)
```

## Checkbox group

It is used for multiple checkboxes which are bound in one group, and indicates whether one option is selected by checking if it is checked.

`checkbox-group` element can manage multiple checkboxes in one group by using `v-model` which is bound as an `Array`. Inside the `el-checkbox` element, `value` is the value of the checkbox. If no content is nested in that tag, `label` will be rendered as the description following the button of the checkbox. `value` also corresponds with the element values in the array. It is selected if the specified value exists in the array, and vice versa.

```{r grouping, eval = FALSE, shot = TRUE}
el_checkbox_group(
  "cbg",
  selected = c("Value selected and disabled", "Value A"),
  choices = list(
    list(label = "Option A", value = "Value A"),
    list(label = "Option B", value = "Value B"),
    list(label = "Option C", value = "Value C"),
    list(label = "disabled", value = "Value disabled", disabled = TRUE),
    list(
      label = "selected and disabled",
      value = "Value selected and disabled",
      disabled = TRUE
    )
  )
)
```

## Options attribute

Shortcut from basic `el-checkbox-group` usage. You can customize the alias of the `options` through the `props` attribute.

Choices given in fields of other names, mapped with `props`.

```{r options, eval = FALSE, shot = TRUE}
el_checkbox_group(
  "cbo",
  selected = c("Value A"),
  props = list(label = "name", value = "id", disabled = "unable"),
  choices = list(
    list(label = "Option A", value = "Value A"),
    list(label = "Option B", value = "Value B"),
    list(label = "Option C", value = "Value C")
  )
)
```

## Indeterminate

The `indeterminate` property can help you to achieve a 'check all' effect.

"Check all" ticks the group from the server, as Element Plus's demo does
in its handler: `observeEvent(input$all, update_el_checkbox_group(...))`.

```{r intermediate, eval = FALSE, shot = TRUE}
tagList(
  el_checkbox("all", "Check all", indeterminate = TRUE),
  el_checkbox_group(
    "cities",
    choices = c("Shanghai", "Beijing", "Guangzhou", "Shenzhen"),
    selected = c("Shanghai", "Beijing")
  )
)
```

## Minimum / Maximum items checked

The `min` and `max` properties can help you to limit the number of checked items.

```{r limitation, eval = FALSE, shot = TRUE}
el_checkbox_group(
  "cities_lim",
  choices = c("Shanghai", "Beijing", "Guangzhou", "Shenzhen"),
  selected = c("Shanghai", "Beijing"),
  min = 1,
  max = 2
)
```

## Button style

Checkbox with button styles.

You just need to change `el-checkbox` element into `el-checkbox-button` element. We also provide `size` attribute.

```{r button-style, eval = FALSE, shot = TRUE}
cities <- c("Shanghai", "Beijing", "Guangzhou", "Shenzhen")
tags$div(
  style = "display: grid; gap: 16px",
  el_checkbox_group(
    "cbb1",
    choices = cities,
    selected = "Shanghai",
    button = TRUE,
    size = "large"
  ),
  el_checkbox_group(
    "cbb2",
    choices = cities,
    selected = "Shanghai",
    button = TRUE
  ),
  el_checkbox_group(
    "cbb3",
    choices = cities,
    selected = "Shanghai",
    button = TRUE,
    size = "small"
  ),
  el_checkbox_group(
    "cbb4",
    choices = cities,
    selected = "Shanghai",
    button = TRUE,
    size = "small",
    disabled = TRUE
  )
)
```

## With borders

The `border` attribute adds a border to Checkboxes.

```{r with-border, eval = FALSE, shot = TRUE}
row <- function(...) tags$div(style = "margin-top: 16px", ...)
tagList(
  row(
    el_checkbox("cbr1", "Option1", value = TRUE, size = "large", border = TRUE),
    el_checkbox("cbr2", "Option2", size = "large", border = TRUE)
  ),
  row(
    el_checkbox("cbr3", "Option1", border = TRUE),
    el_checkbox("cbr4", "Option2", value = TRUE, border = TRUE)
  )
)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("checkbox")
```
