---
title: "Collapse"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Use Collapse to store contents.

## Basic usage

You can expand multiple panels

```{r basic, eval = FALSE, shot = TRUE}
panels <- list(
  list(
    name = "1",
    title = "Consistency",
    tags$div(
      "Consistent with real life: in line with the process and logic of real life, and comply with languages and habits that the users are used to;"
    )
  ),
  list(
    name = "2",
    title = "Feedback",
    tags$div(
      "Operation feedback: enable the users to clearly perceive their operations by style updates and interactive effects;"
    )
  ),
  list(
    name = "3",
    title = "Efficiency",
    tags$div(
      "Simplify the process: keep operating process simple and intuitive;"
    )
  ),
  list(
    name = "4",
    title = "Controllability",
    tags$div(
      "Decision making: giving advices about operations is acceptable, but do not make decisions for the users;"
    )
  )
)
el_collapse("coll", items = panels, value = "1")
```

## Accordion

In accordion mode, only one panel can be expanded at once

Activate accordion mode using the `accordion` attribute.

```{r accordion, eval = FALSE, shot = TRUE}
el_collapse(
  "coll_acc",
  value = "1",
  accordion = TRUE,
  items = list(
    list(
      name = "1",
      title = "Consistency",
      tags$div("Consistent with real life.")
    ),
    list(name = "2", title = "Feedback", tags$div("Operation feedback.")),
    list(name = "3", title = "Efficiency", tags$div("Simplify the process.")),
    list(name = "4", title = "Controllability", tags$div("Decision making."))
  )
)
```

## Custom title

Besides using the `title` attribute, you can customize panel title with named slots, which makes adding custom content, e.g. icons, possible.

> **Tip**
>
> Starting from version 2.9.10, the `title` slot provides an `isActive` property that indicates whether the current collapse item is active.

A title may be markup: an icon beside the text.

```{r customization, eval = FALSE, shot = TRUE}
el_collapse(
  "coll_title",
  accordion = TRUE,
  items = list(
    list(
      name = "1",
      title = tags$span(
        "Consistency ",
        el_icon("InfoFilled", class = "header-icon")
      ),
      tags$div("Consistent with real life.")
    ),
    list(name = "2", title = "Feedback", tags$div("Operation feedback."))
  )
)
```

## Custom icon

Besides using the `icon` attribute, you can customize icon of panel item with named slots, which makes adding custom content.

```{r custom-icon, eval = FALSE, shot = TRUE}
el_collapse(
  "coll_icon",
  value = "1",
  items = list(
    list(
      name = "1",
      title = "Consistency",
      icon = "CaretRight",
      tags$div("Consistent with real life.")
    ),
    list(
      name = "2",
      title = "Feedback",
      icon = "ArrowRightBold",
      tags$div("Operation feedback.")
    )
  )
)
```

## Custom icon position

using the `expand-icon-position` attribute, you can customize icon position.

```{r custom-icon-position, eval = FALSE, shot = TRUE}
el_collapse(
  "coll_pos",
  expand_icon_position = "left",
  items = list(
    list(
      name = "1",
      title = "Consistency",
      tags$div("Consistent with real life.")
    ),
    list(name = "2", title = "Feedback", tags$div("Operation feedback."))
  )
)
```

## Prevent collapsing

set the `before-collapse` property, If `false` is returned or a `Promise` is returned and then is rejected, will stop collapsing.

`before_collapse` may hold a panel as it is: return `false`, or a promise.

```{r prevent-collapsing, eval = FALSE, shot = TRUE}
el_collapse(
  "coll_guard",
  before_collapse = JS(
    "function(name) { return confirm('Toggle ' + name + '?'); }"
  ),
  items = list(
    list(
      name = "1",
      title = "Consistency",
      tags$div("Consistent with real life.")
    ),
    list(name = "2", title = "Feedback", tags$div("Operation feedback."))
  )
)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("collapse")
```
