---
title: "Collapse"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Use Collapse to store contents.

## Basic usage

You can expand multiple panels

```{r basic, eval = FALSE, shot = TRUE}
panels <- list(
  el_collapse_item(
    "Consistency",
    tags$div(
      "Consistent with real life: in line with the process and logic of real life, and comply with languages and habits that the users are used to;"
    ),
    name = "1"
  ),
  el_collapse_item(
    "Feedback",
    tags$div(
      "Operation feedback: enable the users to clearly perceive their operations by style updates and interactive effects;"
    ),
    name = "2"
  ),
  el_collapse_item(
    "Efficiency",
    tags$div(
      "Simplify the process: keep operating process simple and intuitive;"
    ),
    name = "3"
  ),
  el_collapse_item(
    "Controllability",
    tags$div(
      "Decision making: giving advices about operations is acceptable, but do not make decisions for the users;"
    ),
    name = "4"
  )
)
el_collapse("coll", items = panels, value = "1")
```

## Accordion

In accordion mode, only one panel can be expanded at once

Activate accordion mode using the `accordion` attribute.

```{r accordion, eval = FALSE, shot = TRUE}
el_collapse(
  "coll_acc",
  value = "1",
  accordion = TRUE,
  items = list(
    el_collapse_item(
      "Consistency",
      tags$div("Consistent with real life."),
      name = "1"
    ),
    el_collapse_item("Feedback", tags$div("Operation feedback."), name = "2"),
    el_collapse_item(
      "Efficiency",
      tags$div("Simplify the process."),
      name = "3"
    ),
    el_collapse_item(
      "Controllability",
      tags$div("Decision making."),
      name = "4"
    )
  )
)
```

## Custom title

Besides using the `title` attribute, you can customize panel title with named slots, which makes adding custom content, e.g. icons, possible.

> **Tip**
>
> Starting from version 2.9.10, the `title` slot provides an `isActive` property that indicates whether the current collapse item is active.

A title may be markup: an icon beside the text.

```{r customization, eval = FALSE, shot = TRUE}
el_collapse(
  "coll_title",
  accordion = TRUE,
  items = list(
    el_collapse_item(
      tags$span(
        "Consistency ",
        el_icon("InfoFilled", class = "header-icon")
      ),
      tags$div("Consistent with real life."),
      name = "1"
    ),
    el_collapse_item("Feedback", tags$div("Operation feedback."), name = "2")
  )
)
```

## Custom icon

Besides using the `icon` attribute, you can customize icon of panel item with named slots, which makes adding custom content.

```{r custom-icon, eval = FALSE, shot = TRUE}
el_collapse(
  "coll_icon",
  value = "1",
  items = list(
    el_collapse_item(
      "Consistency",
      tags$div("Consistent with real life."),
      name = "1",
      icon = "CaretRight"
    ),
    el_collapse_item(
      "Feedback",
      tags$div("Operation feedback."),
      name = "2",
      icon = "ArrowRightBold"
    )
  )
)
```

## Custom icon position

using the `expand-icon-position` attribute, you can customize icon position.

The switch moves each header's icon, with `update_el_collapse(
expand_icon_position =)`.

```{r custom-icon-position, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#position .el-switch').click()", shot_expect = "document.querySelector('#coll_pos.el-collapse-icon-position-right')"}
ui <- el_page(
  tags$div(
    style = "display: flex; align-items: center; margin-bottom: 16px",
    tags$span(style = "margin-right: 16px", "expand icon position: "),
    el_switch(
      "position",
      value = "left",
      inactive_value = "left",
      active_value = "right",
      inactive_text = "left",
      active_text = "right",
      inactive_color = "#88b8fe"
    )
  ),
  el_collapse(
    "coll_pos",
    expand_icon_position = "left",
    items = list(
      el_collapse_item(
        "Consistency",
        tags$div(
          "Consistent with real life: in line with the process and logic of",
          "real life, and comply with languages and habits that the users are",
          "used to;"
        ),
        tags$div(
          "Consistent within interface: all elements should be consistent,",
          "such as: design style, icons and texts, position of elements, etc."
        ),
        name = "1"
      ),
      el_collapse_item(
        "Feedback",
        tags$div(
          "Operation feedback: enable the users to clearly perceive their",
          "operations by style updates and interactive effects;"
        ),
        tags$div(
          "Visual feedback: reflect current state by updating or rearranging",
          "elements of the page."
        ),
        name = "2"
      ),
      el_collapse_item(
        "Efficiency",
        tags$div(
          "Simplify the process: keep operating process simple and intuitive;"
        ),
        tags$div(
          "Definite and clear: enunciate your intentions clearly so that the",
          "users can quickly understand and make decisions;"
        ),
        name = "3"
      )
    )
  )
)
server <- function(input, output, session) {
  observeEvent(input$position, ignoreInit = TRUE, {
    update_el_collapse(
      session,
      "coll_pos",
      expand_icon_position = input$position
    )
  })
}
shinyApp(ui, server)
```

## Prevent collapsing

set the `before-collapse` property, If `false` is returned or a `Promise` is returned and then is rejected, will stop collapsing.

`before_collapse` returns a promise: the panel turns after a second, or
stays, as the switch says. The switch replaces the function with
`update_el_collapse(before_collapse =)`.

```{r prevent-collapsing, eval = FALSE, shot = TRUE, shot_js = c("document.querySelector('#before .el-switch').click()", "document.querySelectorAll('#coll_guard .el-collapse-item__header')[1].click()"), shot_wait = 2, shot_expect = "!document.querySelectorAll('#coll_guard .el-collapse-item')[1].classList.contains('is-active')"}
guard <- function(allow) {
  JS(sprintf(
    "function() { return new Promise(function(resolve) { setTimeout(function() { resolve(%s); }, 1000); }); }",
    tolower(allow)
  ))
}
ui <- el_page(
  tags$div(
    style = "display: flex; align-items: center; margin-bottom: 16px",
    tags$span(style = "margin-right: 16px", "before collapse return: "),
    el_switch(
      "before",
      value = TRUE,
      inactive_text = "false",
      active_text = "true"
    )
  ),
  el_collapse(
    "coll_guard",
    value = "1",
    before_collapse = guard(TRUE),
    items = list(
      el_collapse_item(
        "Consistency",
        tags$div(
          "Consistent with real life: in line with the process and logic of",
          "real life, and comply with languages and habits that the users are",
          "used to;"
        ),
        name = "1"
      ),
      el_collapse_item(
        "Feedback",
        tags$div(
          "Operation feedback: enable the users to clearly perceive their",
          "operations by style updates and interactive effects;"
        ),
        name = "2"
      )
    )
  )
)
server <- function(input, output, session) {
  observeEvent(input$before, ignoreInit = TRUE, {
    update_el_collapse(
      session,
      "coll_guard",
      before_collapse = guard(input$before)
    )
  })
}
shinyApp(ui, server)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("collapse")
```
