---
title: "Color"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Element Plus uses a specific set of palettes to specify colors, to provide a
consistent look and feel for the products you build. They are its CSS
variables -- `--el-color-primary` and the rest -- and `el_theme()` changes
them: the brand colours by name (`primary`, `success`, `warning`, `danger`,
`info`), any other through `element =`. The swatches below are drawn from
the variables themselves, so they show the theme the page has.

## Main Color

The main color of Element Plus is bright and friendly blue. Its tints,
`--el-color-primary-light-3` to `-light-9`, mix it with white.

```{r main, eval = FALSE, shot = TRUE}
swatch <- function(var, label = var, fg = "white", w = 100) tags$div(
  style = sprintf("display: inline-block; width: %dpx; height: 80px; padding: 10px;
                   vertical-align: top; background: var(%s); color: %s; font-size: 12px",
                  w, var, fg), tags$b(label), tags$br(), var)
tags$div(
  swatch("--el-color-primary", "Brand Color", w = 220),
  lapply(c(3, 5, 7, 8, 9), function(i)
    swatch(paste0("--el-color-primary-light-", i), paste0("Light ", i),
           fg = if (i > 5) "#303133" else "white")),
  swatch("--el-color-primary-dark-2", "Dark 2"))
```

## Secondary Color

Besides the main color, you need to use different scene colors in different
scenarios -- for example, danger color indicates a dangerous operation.

```{r secondary, eval = FALSE, shot = TRUE}
swatch <- function(var, label = var, fg = "white", w = 160) tags$div(
  style = sprintf("display: inline-block; width: %dpx; height: 80px; padding: 10px; margin: 0 10px 10px 0;
                   border-radius: 4px; background: var(%s); color: %s; font-size: 12px",
                  w, var, fg), tags$b(label), tags$br(), var)
tagList(lapply(c("success", "warning", "danger", "info"), function(t)
  swatch(paste0("--el-color-", t), tools::toTitleCase(t))))
```

## Neutral Color

Neutral colors are for text, background and border colors. Different
neutral colors represent the hierarchical structure.

```{r neutral, eval = FALSE, shot = TRUE}
swatch <- function(var, label, fg) tags$div(
  style = sprintf("display: inline-block; width: 160px; height: 60px; padding: 10px; margin: 0 10px 10px 0;
                   border-radius: 4px; background: var(%s); color: %s; font-size: 12px;
                   border: 1px solid var(--el-border-color-lighter)", var, fg),
  tags$b(label), tags$br(), var)
tagList(
  tags$div(
    swatch("--el-text-color-primary", "Primary Text", "white"),
    swatch("--el-text-color-regular", "Regular Text", "white"),
    swatch("--el-text-color-secondary", "Secondary Text", "white"),
    swatch("--el-text-color-placeholder", "Placeholder Text", "white"),
    swatch("--el-text-color-disabled", "Disabled Text", "#303133")),
  tags$div(
    swatch("--el-border-color-darker", "Darker Border", "#303133"),
    swatch("--el-border-color-dark", "Dark Border", "#303133"),
    swatch("--el-border-color", "Base Border", "#303133"),
    swatch("--el-border-color-light", "Light Border", "#303133"),
    swatch("--el-border-color-lighter", "Lighter Border", "#303133"),
    swatch("--el-border-color-extra-light", "Extra Light Border", "#303133")),
  tags$div(
    swatch("--el-fill-color-darker", "Darker Fill", "#303133"),
    swatch("--el-fill-color", "Base Fill", "#303133"),
    swatch("--el-fill-color-light", "Light Fill", "#303133"),
    swatch("--el-fill-color-extra-light", "Extra Light Fill", "#303133"),
    swatch("--el-bg-color-page", "Page Background", "#303133")))
```

## Changing them

A brand colour brings its tints along; anything else is a variable by name.
See the theming guide.

```{r change, eval = FALSE}
el_page(theme = el_theme(primary = "#7c3aed",
                         element = list("text-color-regular" = "#4b5563")))
```
