---
title: "ColorPickerPanel"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

`ColorPickerPanel` is the core component of `ColorPicker`.

## Basic usage

ColorPickerPanel requires a string typed variable to be bound to v-model.

```{r basic, eval = FALSE, shot = TRUE}
el_color_picker_panel("cpp", value = "#409EFF")
```

## Alpha

ColorPickerPanel supports alpha channel selecting. To activate alpha selecting, just add the `show-alpha` attribute.

```{r alpha, eval = FALSE, shot = TRUE}
el_color_picker_panel(
  "cpp_alpha",
  value = "rgba(19, 206, 102, 0.8)",
  show_alpha = TRUE
)
```

## Predefined colors

ColorPickerPanel supports predefined color options

```{r predefined-color, eval = FALSE, shot = TRUE}
el_color_picker_panel(
  "cpp_pre",
  value = "rgba(255, 69, 0, 0.68)",
  show_alpha = TRUE,
  predefine = c(
    "#ff4500",
    "#ff8c00",
    "#ffd700",
    "#90ee90",
    "#00ced1",
    "#1e90ff",
    "#c71585",
    "rgba(255, 69, 0, 0.68)",
    "rgb(255, 120, 0)",
    "hsv(51, 100, 98)",
    "hsva(120, 40, 94, 0.5)",
    "hsl(181, 100%, 37%)",
    "hsla(209, 100%, 56%, 0.73)",
    "#c7158577"
  )
)
```

## Border

By default the color-picker-panel is bordered but in some case you don't want it.

```{r border, eval = FALSE, shot = TRUE}
tagList(
  tags$div(style = "text-align: center", "No border:"),
  el_divider(),
  tags$div(
    style = "display: flex; flex-wrap: wrap; justify-content: center; gap: 16px",
    tags$div(
      style = "padding: 20px",
      el_color_picker_panel("cpp_border1", value = "#409EFF", border = FALSE)
    ),
    el_divider(direction = "vertical", style = "height: auto"),
    el_card(
      el_color_picker_panel("cpp_border2", value = "#409EFF", border = FALSE)
    )
  )
)
```

## Disabled

The `disabled` attribute determines if the color picker is fully disabled.

```{r disabled, eval = FALSE, shot = TRUE}
el_color_picker_panel(
  "cpp_dis",
  value = "#ff6900",
  disabled = TRUE,
  show_alpha = TRUE,
  predefine = c(
    "#ff4500",
    "#ff8c00",
    "#ffd700",
    "#90ee90",
    "#00ced1",
    "#1e90ff",
    "#c71585"
  )
)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("color-picker-panel")
```
