---
title: "ColorPickerPanel"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

`ColorPickerPanel` is the core component of `ColorPicker`.

## Basic usage

ColorPickerPanel requires a string typed variable to be bound to v-model.

```{r basic, eval = FALSE, shot = TRUE}
el_color_picker_panel("cpp", value = "#409EFF")
```

## Alpha

ColorPickerPanel supports alpha channel selecting. To activate alpha selecting, just add the `show-alpha` attribute.

```{r alpha, eval = FALSE, shot = TRUE}
el_color_picker_panel("cpp_alpha", value = "rgba(19, 206, 102, 0.8)", show_alpha = TRUE)
```

## Predefined colors

ColorPickerPanel supports predefined color options

```{r predefined-color, eval = FALSE, shot = TRUE}
el_color_picker_panel("cpp_pre", value = "#ff4500", predefine = c(
  "#ff4500", "#ff8c00", "#ffd700", "#90ee90", "#00ced1", "#1e90ff", "#c71585"))
```

## Border

By default the color-picker-panel is bordered but in some case you don't want it.

```{r border, eval = FALSE, shot = TRUE}
el_color_picker_panel("cpp_border", value = "#409EFF", border = FALSE)
```

## Disabled

The `disabled` attribute determines if the color picker is fully disabled.

```{r disabled, eval = FALSE, shot = TRUE}
el_color_picker_panel("cpp_dis", value = "#409EFF", disabled = TRUE)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("color-picker-panel")
```
