---
title: "Config Provider"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Config Provider is used for providing global configurations, which enables your entire application to access these configurations everywhere.

## i18n Configurations

Configure i18n related properties via Config Provider, to get language switching feature.

Use two attributes to provide i18n related config

The button switches the language of what is inside the provider, with
`update_el_config_provider(locale =)`: the table's empty text, the
pagination's words. The page's own language is `el_page(locale =)`.

```{r usage, eval = FALSE, shot = TRUE, shot_js = c("window.zh = document.querySelector('#cfg .el-pagination').innerText.indexOf('\\u5171') >= 0", "document.querySelector('#toggle button').click()"), shot_expect = c("window.zh", "document.querySelector('#cfg .el-pagination').innerText.indexOf('Total') >= 0")}
ui <- el_page(
  el_button("toggle", "Switch Language"),
  tags$br(),
  el_config_provider(
    id = "cfg",
    locale = "zh-cn",
    el_table(data = data.frame(date = character(), name = character())),
    el_pagination("cfg_pg", total = 100, layout = "total, prev, pager, next")
  )
)
server <- function(input, output, session) {
  language <- reactiveVal("zh-cn")
  observeEvent(input$toggle, {
    language(if (language() == "zh-cn") "en" else "zh-cn")
    update_el_config_provider(session, "cfg", locale = language())
  })
}
shinyApp(ui, server)
```

## Button Configurations

The checkboxes and the select change the provider's `button` settings,
which the button inside takes as its defaults.

```{r button, eval = FALSE, shot = TRUE, shot_js = c("document.querySelector('#cfg_dashed .el-checkbox').click()", "document.querySelector('#cfg_plain .el-checkbox').click()"), shot_expect = c("document.querySelector('#cfg .el-button.is-dashed')", "!document.querySelector('#cfg .el-button.is-plain')")}
ui <- el_page(
  tags$div(
    el_checkbox("cfg_space", "autoInsertSpace", value = TRUE),
    el_checkbox("cfg_plain", "plain", value = TRUE),
    el_checkbox("cfg_round", "round", value = TRUE),
    el_checkbox("cfg_dashed", "dashed"),
    el_checkbox("cfg_text", "text"),
    el_select(
      "cfg_type",
      choices = c("primary", "success", "warning", "danger", "info", "default"),
      selected = "default",
      width = "150px"
    )
  ),
  el_divider(),
  el_config_provider(
    id = "cfg",
    button = list(
      autoInsertSpace = TRUE,
      type = "default",
      plain = TRUE,
      round = TRUE,
      text = FALSE,
      dashed = FALSE
    ),
    el_button("cfg_btn", "中文")
  )
)
server <- function(input, output, session) {
  observe({
    update_el_config_provider(
      session,
      "cfg",
      button = list(
        autoInsertSpace = isTRUE(input$cfg_space),
        type = input$cfg_type %||% "default",
        plain = isTRUE(input$cfg_plain),
        round = isTRUE(input$cfg_round),
        text = isTRUE(input$cfg_text),
        dashed = isTRUE(input$cfg_dashed)
      )
    )
  })
}
shinyApp(ui, server)
```

## Link Configurations

The selects change the provider's `link` settings, which the link inside
takes as its defaults.

```{r link, eval = FALSE, shot = TRUE, shot_js = c("document.querySelector('#cfg_type .el-select__wrapper').click()", "Array.from(document.querySelectorAll('.el-select-dropdown__item')).find(function(o){ return o.innerText.trim() === 'danger'; }).click()"), shot_expect = "document.querySelector('#cfg .el-link--danger')"}
ui <- el_page(
  tags$div(
    style = "display: flex; gap: 16px",
    tags$div(
      style = "display: flex; flex-direction: column; gap: 4px; flex-basis: 150px",
      tags$span("Type:"),
      el_select(
        "cfg_type",
        choices = c(
          "primary",
          "success",
          "warning",
          "info",
          "danger",
          "default"
        ),
        selected = "success"
      )
    ),
    tags$div(
      style = "display: flex; flex-direction: column; gap: 4px; flex-basis: 150px",
      tags$span("Underline:"),
      el_select(
        "cfg_underline",
        choices = c("always", "never", "hover"),
        selected = "always"
      )
    )
  ),
  el_divider(),
  el_config_provider(
    id = "cfg",
    link = list(type = "success", underline = "always"),
    el_link("Link desu!", id = "cfg_link")
  )
)
server <- function(input, output, session) {
  observe({
    update_el_config_provider(
      session,
      "cfg",
      link = list(type = input$cfg_type, underline = input$cfg_underline)
    )
  })
}
shinyApp(ui, server)
```

## Card Configurations

The radios change the provider's `card` settings, which a card inside
takes when it sets no `shadow` of its own.

```{r card, eval = FALSE, shot = TRUE, shot_js = "Array.from(document.querySelectorAll('#cfg_shadow .el-radio')).find(function(r){ return r.innerText.trim() === 'never'; }).click()", shot_expect = "document.querySelector('.el-card.is-never-shadow')"}
ui <- el_page(
  "Shadow:",
  el_radio_group(
    "cfg_shadow",
    choices = c("always", "hover", "never"),
    value = "always"
  ),
  el_divider(),
  el_config_provider(
    id = "cfg",
    card = list(shadow = "always"),
    el_card("Card desu!")
  )
)
server <- function(input, output, session) {
  observeEvent(input$cfg_shadow, ignoreInit = TRUE, {
    update_el_config_provider(
      session,
      "cfg",
      card = list(shadow = input$cfg_shadow)
    )
  })
}
shinyApp(ui, server)
```

## Dialog Configurations

The switches change the provider's `dialog` settings, which the dialog
inside takes as its defaults. Element's `transition` setting is not
taken: the dialog is markup and plays Element's own `dialog-fade`.

```{r dialog, eval = FALSE, shot = TRUE, shot_js = c("document.querySelector('#cfg_align .el-switch').click()", "document.querySelector('#cfg_open button').click()"), shot_sel = ".el-overlay", shot_expect = c("document.querySelector('#cfg_dlg .el-dialog.is-align-center')", "document.querySelector('#cfg_dlg .el-dialog__body').innerText.indexOf('Dialog Content') >= 0")}
ui <- el_page(
  tags$div(
    style = "display: flex; flex-direction: column; gap: 16px",
    el_switch("cfg_align", active_text = "alignCenter"),
    tags$div(
      style = "display: flex; gap: 16px",
      el_switch("cfg_drag", active_text = "draggable"),
      el_switch("cfg_overflow", active_text = "overflow", disabled = TRUE)
    ),
    tags$div(
      el_button("cfg_open", "Open Dialog", type = "primary", size = "small")
    )
  ),
  el_config_provider(
    id = "cfg",
    dialog = list(alignCenter = FALSE, draggable = FALSE, overflow = FALSE),
    el_dialog(
      "cfg_dlg",
      title = "Dialog Title",
      destroy_on_close = TRUE,
      content = "Dialog Content"
    )
  )
)
server <- function(input, output, session) {
  observe({
    update_el_switch(
      session,
      "cfg_overflow",
      disabled = !isTRUE(input$cfg_drag)
    )
    update_el_config_provider(
      session,
      "cfg",
      dialog = list(
        alignCenter = isTRUE(input$cfg_align),
        draggable = isTRUE(input$cfg_drag),
        overflow = isTRUE(input$cfg_overflow)
      )
    )
  })
  observeEvent(
    input$cfg_open,
    update_el_dialog(session, "cfg_dlg", visible = TRUE)
  )
}
shinyApp(ui, server)
```

## Message Configurations

The provider's `message` settings are Element Plus's page-wide message
defaults, so they reach `el_message()` from the server: at most three at
a time, plain, at the bottom.

```{r message, eval = FALSE, shot = TRUE, shot_js = "var b = document.querySelector('.el-button'); [0, 300, 600, 900].forEach(function(t) { setTimeout(function() { b.click(); }, t); });", shot_wait = 2, shot_expect = c("document.querySelectorAll('.el-message').length === 3", "document.querySelector('.el-message.is-plain')", "document.querySelector('.el-message').style.bottom")}
ui <- el_page(
  el_config_provider(
    message = list(max = 3, plain = TRUE, placement = "bottom"),
    el_button("cfg_msg", "OPEN")
  )
)
server <- function(input, output, session) {
  observeEvent(input$cfg_msg, {
    el_message(session, "This is a message from bottom.")
  })
}
shinyApp(ui, server)
```

## Empty Values Configurations

<details>
  <summary>Supported components list</summary>

- Cascader
- ColorPicker 2.10.3
- DatePicker
- Select
- SelectV2
- TimePicker
- TimeSelect
- TreeSelect

</details>

Set `empty-values` to support empty values of components. The fallback value is `['', null, undefined]`. If you think the empty string is meaningful, write `[undefined, null]`.

Set `value-on-clear` to set the return value when cleared. The fallback value is `undefined`. In the date component is `null`. If you want to set `undefined`, use `() => undefined`.

```{r empty-values, eval = FALSE, shot = TRUE}
el_config_provider(
  value_on_clear = NULL,
  empty_values = list(NULL),
  el_select(
    "cfg_sel",
    choices = c("Option1", "Option2", "Option3"),
    clearable = TRUE,
    placeholder = "Select",
    width = "240px"
  )
)
```

## Table Configurations

The checkbox and the select change the provider's `table` settings: a
column that sets no `show_overflow_tooltip` of its own takes them.

```{r table, eval = FALSE, shot = TRUE, shot_js = c("window.tip = Array.from(document.querySelectorAll('#cfg tbody tr:first-child .cell')).map(function(c) { return c.classList.contains('el-tooltip'); }).join()", "document.querySelector('#cfg_tip .el-checkbox').click()"), shot_expect = c("window.tip === 'false,true,true,true,false'", "document.querySelectorAll('#cfg tbody .cell.el-tooltip').length === 0")}
ui <- el_page(
  tags$div(
    el_checkbox("cfg_tip", "showOverflowTooltip", value = TRUE),
    el_select(
      "cfg_effect",
      choices = c(dark = "dark", light = "light"),
      selected = "dark",
      width = "150px"
    )
  ),
  el_divider(),
  el_config_provider(
    id = "cfg",
    table = list(showOverflowTooltip = TRUE, tooltipEffect = "dark"),
    el_table(
      data = data.frame(
        date = c("2016-05-03", "2016-05-02", "2016-05-04"),
        name = "Tom",
        address = "No. 189, Grove St, Los Angeles, a long address for the cell"
      ),
      selection = TRUE,
      columns = list(
        el_table_column("date", "Date", width = 120),
        el_table_column("name", "Name", width = 120),
        el_table_column(
          "address",
          "Address (inherited from config-provider)",
          width = 300
        ),
        el_table_column(
          "address",
          "Address (explicit false)",
          show_overflow_tooltip = FALSE
        )
      )
    )
  )
)
server <- function(input, output, session) {
  observe({
    update_el_config_provider(
      session,
      "cfg",
      table = list(
        showOverflowTooltip = isTRUE(input$cfg_tip),
        tooltipEffect = input$cfg_effect
      )
    )
  })
}
shinyApp(ui, server)
```

## Experimental features

In this section, you can learn how to use Config Provider to provide experimental features. For now, we haven't added any experimental features, but in the feature roadmap, we will add some experimental features. You can use this config to manage the features you want or not.

 <!-- TODO -->

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("config-provider")
```
