---
title: "Config Provider"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Config Provider is used for providing global configurations, which enables your entire application to access these configurations everywhere.

## i18n Configurations

Configure i18n related properties via Config Provider, to get language switching feature.

Use two attributes to provide i18n related config

The page's language and z-index are `el_page(locale =, z_index =)`, given
to every component; a config provider sets the rest for what is inside it
-- here the size of a table's pagination and input.

```{r usage, eval = FALSE, shot = TRUE}
el_config_provider(
  size = "small",
  el_input("cfg_inp", placeholder = "Small, from the provider"),
  el_pagination("cfg_pg", total = 100)
)
```

## Button Configurations

```{r button, eval = FALSE, shot = TRUE}
el_config_provider(
  button = list(
    autoInsertSpace = TRUE,
    plain = TRUE,
    round = TRUE,
    type = "primary"
  ),
  el_button("cfg_b1", "中文"),
  el_button("cfg_b2", "Button")
)
```

## Link Configurations

```{r link, eval = FALSE, shot = TRUE}
el_config_provider(
  link = list(type = "success", underline = "always"),
  el_link("Link", id = "cfg_link")
)
```

## Card Configurations

```{r card, eval = FALSE, shot = TRUE}
el_config_provider(card = list(shadow = "hover"), el_card("Card desu!"))
```

## Dialog Configurations

```{r dialog, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#shot .el-button').click()", shot_sel = ".el-overlay"}
el_config_provider(
  dialog = list(alignCenter = TRUE, draggable = TRUE),
  el_button("cfg_open", "Open dialog"),
  el_dialog("cfg_dlg", title = "Tips", content = "This is a message")
)
```

## Message Configurations

The provider's `message` settings are Element Plus's page-wide message
defaults, so they reach `el_message()` from the server: at most three at
a time, plain, at the bottom.

```{r message, eval = FALSE, shot = TRUE, shot_js = "var b = document.querySelector('#shot button'); [0, 300, 600, 900].forEach(function(t) { setTimeout(function() { b.click(); }, t); });", shot_sel = ".el-message", shot_wait = 1}
ui <- el_page(
  el_config_provider(
    message = list(max = 3, plain = TRUE, placement = "bottom"),
    el_button("cfg_msg", "OPEN")
  )
)
server <- function(input, output, session) {
  observeEvent(input$cfg_msg, {
    el_message(session, "This is a message from bottom.")
  })
}
shinyApp(ui, server)
```

## Empty Values Configurations

<details>
  <summary>Supported components list</summary>

- Cascader
- ColorPicker 2.10.3
- DatePicker
- Select
- SelectV2
- TimePicker
- TimeSelect
- TreeSelect

</details>

Set `empty-values` to support empty values of components. The fallback value is `['', null, undefined]`. If you think the empty string is meaningful, write `[undefined, null]`.

Set `value-on-clear` to set the return value when cleared. The fallback value is `undefined`. In the date component is `null`. If you want to set `undefined`, use `() => undefined`.

```{r empty-values, eval = FALSE, shot = TRUE}
el_config_provider(
  value_on_clear = NULL,
  empty_values = list(NULL),
  el_select(
    "cfg_sel",
    choices = c("Option1", "Option2", "Option3"),
    clearable = TRUE,
    placeholder = "Select",
    width = "240px"
  )
)
```

## Table Configurations

```{r table, eval = FALSE, shot = TRUE}
el_config_provider(
  table = list(showOverflowTooltip = TRUE, tooltipEffect = "light"),
  el_table(
    data = data.frame(
      date = "2016-05-03",
      name = "Tom",
      address = "No. 189, Grove St, Los Angeles, a very long address that overflows"
    )
  )
)
```

## Experimental features

In this section, you can learn how to use Config Provider to provide experimental features. For now, we haven't added any experimental features, but in the feature roadmap, we will add some experimental features. You can use this config to manage the features you want or not.

 <!-- TODO -->

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("config-provider")
```
