---
title: "Container"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Container components for scaffolding basic structure of the page:

`<el-container>`: wrapper container. When nested with a `<el-header>` or `<el-footer>`, all its child elements will be vertically arranged. Otherwise horizontally.

`<el-header>`: container for headers.

`<el-aside>`: container for side sections (usually a side nav).

`<el-main>`: container for main sections.

`<el-footer>`: container for footers.

> **Tip**
>
> These components use flex for layout, so please make sure your browser supports it. Besides, `<el-container>`'s direct child elements have to be one or more of the latter four components. And father element of the latter four components must be a `<el-container>`.

## Common layouts

```{r layout-hm, eval = FALSE, shot = TRUE}
el_container(el_header("Header"), el_main("Main"))
```

```{r layout-hmf, eval = FALSE, shot = TRUE}
el_container(el_header("Header"), el_main("Main"), el_footer("Footer"))
```

```{r layout-am, eval = FALSE, shot = TRUE}
el_container(
  el_aside(width = "200px", "Aside"),
  el_main("Main"),
  el_aside(width = "200px", "Aside")
)
```

```{r layout-ham, eval = FALSE, shot = TRUE}
el_container(
  el_header("Header"),
  el_container(el_aside(width = "200px", "Aside"), el_main("Main"))
)
```

```{r layout-hamf, eval = FALSE, shot = TRUE}
el_container(
  el_header("Header"),
  el_container(
    el_aside(width = "200px", "Aside"),
    el_container(el_main("Main"), el_footer("Footer"))
  )
)
```

```{r layout-ahm, eval = FALSE, shot = TRUE}
el_container(
  el_aside(width = "200px", "Aside"),
  el_container(el_header("Header"), el_main("Main"))
)
```

```{r layout-ahmf, eval = FALSE, shot = TRUE}
el_container(
  el_aside(width = "200px", "Aside"),
  el_container(el_header("Header"), el_main("Main"), el_footer("Footer"))
)
```

## Example

```{r example, eval = FALSE, shot = TRUE}
el_container(
  style = "height: 400px; border: 1px solid var(--el-border-color)",
  el_aside(
    width = "200px",
    el_menu(
      "ctr_menu",
      active = "1-1",
      items = list(
        list(
          index = "1",
          title = "Navigator One",
          icon = "Message",
          children = list(
            list(index = "1-1", label = "Option 1"),
            list(index = "1-2", label = "Option 2")
          )
        ),
        list(
          index = "2",
          title = "Navigator Two",
          icon = "Menu",
          children = list(
            list(index = "2-1", label = "Option 1")
          )
        )
      )
    )
  ),
  el_container(
    el_header(style = "text-align: right; font-size: 12px", tags$span("Tom")),
    el_main(el_table(
      "ctr_tbl",
      data = data.frame(
        Date = rep("2016-05-02", 4),
        Name = rep("Tom", 4),
        Address = rep("No. 189, Grove St, Los Angeles", 4)
      )
    ))
  )
)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("container")
```
