---
title: "Container"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Container components for scaffolding the basic structure of the page:
`el_container()` holds `el_header()`, `el_aside()`, `el_main()` and
`el_footer()`. A container holding a header or a footer lays its children
out vertically, otherwise horizontally.

## Common layouts

```{r layouts, eval = FALSE, shot = TRUE}
box <- function(f, ...) f(..., style = "background: #e9eef3; text-align: center; line-height: 60px")
hdr <- function(...) el_header(..., style = "background: #b3c0d1; text-align: center; line-height: 60px")
side <- function(...) el_aside(width = "200px", ..., style = "background: #d3dce6; text-align: center; line-height: 160px")
tagList(
  el_container(hdr("Header"), box(el_main, "Main")),
  tags$br(),
  el_container(hdr("Header"), box(el_main, "Main"),
               el_footer("Footer", style = "background: #b3c0d1; text-align: center; line-height: 60px")),
  tags$br(),
  el_container(side("Aside"), box(el_main, "Main")),
  tags$br(),
  el_container(hdr("Header"), el_container(side("Aside"), box(el_main, "Main")))
)
```

## Example

A page frame with a menu down the side, a toolbar on top and a table in
the middle -- the dashboard of the same name runs it whole.

```{r example, file = "../../../inst/examples/dashboards/admin-layout/app.R", eval = FALSE, shot = TRUE}
```

## API

```{r api, echo = FALSE, results = "asis"}
api_tables("container")
```
