---
title: "DateTimePicker"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Select date and time in one picker.

> **Tip**
>
> DateTimePicker is derived from DatePicker and TimePicker. For a more detailed explanation on attributes, you can refer to DatePicker and TimePicker.

## Date and time

You can select date and time in one picker at the same time by setting `type` to `datetime`. The way to use shortcuts is the same as Date Picker.

```{r date-and-time, eval = FALSE, shot = TRUE}
tagList(
  tags$div("Default"),
  el_date_picker(
    "dtp1",
    type = "datetime",
    placeholder = "Select date and time"
  ),
  tags$div("With shortcuts"),
  el_date_picker(
    "dtp2",
    type = "datetime",
    placeholder = "Select date and time",
    shortcuts = list(list(text = "Today", value = JS("new Date()")))
  ),
  tags$div("With default time"),
  el_date_picker(
    "dtp3",
    type = "datetime",
    placeholder = "Select date and time",
    default_time = JS("new Date(2000, 1, 1, 12, 0, 0)")
  )
)
```

## DateTime Formats

Use `format` to control displayed text's format in the input box. Use `value-format` to control binding value's format.

By default, the component accepts and emits a `Date` object.

Check the list [here](https://day.js.org/docs/en/display/format#list-of-all-available-formats) of all available formats of Day.js.

> **Warning**
>
> Pay attention to capitalization

```{r date-and-time-formats, eval = FALSE, shot = TRUE}
el_date_picker(
  "dtp_fmt",
  type = "datetime",
  placeholder = "Pick a Date",
  format = "YYYY/MM/DD hh:mm:ss",
  date_format = "YYYY/MM/DD ddd",
  time_format = "A hh:mm:ss"
)
```

## Date and time formats in dropdown panel

Use `date-format` and `time-format` to control displayed text's format in the dropdown panel's input box.

```{r date-and-time-formats-panel, eval = FALSE, shot = TRUE}
el_date_picker(
  "dtp_fmt_panel",
  type = "datetime",
  placeholder = "Pick a Date",
  date_format = "YYYY/MM/DD",
  time_format = "hh:mm:ss"
)
```

## Date and time range

You can select date and time range by setting `type` to `datetimerange`.

```{r date-and-time-range, eval = FALSE, shot = TRUE}
el_date_picker(
  "dtp_range",
  type = "datetimerange",
  range_separator = "To",
  start_placeholder = "Start date",
  end_placeholder = "End date"
)
```

## Single Panel

By default date picker ranges have two panels. If you want one panel set the `single-panel` attribute.

```{r single-panel, eval = FALSE, shot = TRUE}
el_date_picker(
  "dtp_single",
  type = "datetimerange",
  single_panel = TRUE,
  start_placeholder = "Start date",
  end_placeholder = "End date"
)
```

## Default time value for start date and end date

When picking date range on the date panel with type `datetimerange`, `00:00:00` will be used as the default time value for start and end date. We can control it with the `default-time` attribute. `default-time` accepts an array of up to two Date objects. The first item controls time value of the start date and the second item controls time value of the end date.

```{r default-time, eval = FALSE, shot = TRUE}
el_date_picker(
  "dtp_dt",
  type = "datetimerange",
  start_placeholder = "Start Date",
  end_placeholder = "End Date",
  default_time = list(
    JS("new Date(2000, 1, 1, 0, 0, 0)"),
    JS("new Date(2000, 2, 1, 23, 59, 59)")
  )
)
```

## Custom icon

Custom icons available with slots.

```{r custom-icon, eval = FALSE, shot = TRUE}
el_date_picker(
  "dtp_icons",
  type = "datetime",
  placeholder = "Pick a Date",
  slots = list(
    `prev-month` = el_icon("CaretLeft"),
    `next-month` = el_icon("CaretRight")
  )
)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("datetime-picker")
```
