---
title: "DatePicker"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Use Date Picker for date input.

## Enter Date

Basic date picker measured by 'day'.

The measurement is determined by the `type` attribute. You can enable quick options via `shortcuts` property. The disabled date is set by `disabledDate`, which is a function.

The radio buttons resize both pickers with `update_el_date_picker(size
=)`.

```{r enter-date, eval = FALSE, shot = TRUE, shot_js = "document.querySelectorAll('#dp_size .el-radio-button')[0].click()", shot_expect = "document.querySelectorAll('.demo-date-picker .el-input--large').length === 2"}
ui <- el_page(
  tags$style(
    ".demo-date-picker { display: flex; width: 100%; flex-wrap: wrap; }
     .demo-date-picker .block { padding: 1.5rem 0; text-align: center;
       border-right: solid 1px var(--el-border-color); flex: 1; min-width: 300px; }
     .demo-date-picker .block:last-child { border-right: none; }
     .demo-date-picker .demonstration { display: block; margin-bottom: 20px;
       color: var(--el-text-color-secondary); font-size: 14px; }"
  ),
  el_radio_group(
    "dp_size",
    choices = c("large", "default", "small"),
    selected = "default",
    button = TRUE
  ),
  tags$div(
    class = "demo-date-picker",
    tags$div(
      class = "block",
      tags$span(class = "demonstration", "Default"),
      el_date_picker("dp_default", placeholder = "Pick a day")
    ),
    tags$div(
      class = "block",
      tags$span(class = "demonstration", "Picker with quick options"),
      el_date_picker(
        "dp_quick",
        placeholder = "Pick a day",
        shortcuts = list(
          list(text = "Today", value = JS("new Date()")),
          list(
            text = "Yesterday",
            value = JS(
              "function() { var d = new Date(); d.setTime(d.getTime() - 3600 * 1000 * 24); return d; }"
            )
          ),
          list(
            text = "A week ago",
            value = JS(
              "function() { var d = new Date(); d.setTime(d.getTime() - 3600 * 1000 * 24 * 7); return d; }"
            )
          )
        ),
        disabled_date = JS(
          "function(time) { return time.getTime() > Date.now(); }"
        )
      )
    )
  )
)
server <- function(input, output, session) {
  observeEvent(input$dp_size, ignoreInit = TRUE, {
    for (id in c("dp_default", "dp_quick")) {
      update_el_date_picker(session, id, size = input$dp_size)
    }
  })
}
shinyApp(ui, server)
```

## Other measurements

You can choose week, month, year, quarter or multiple dates by extending the standard date picker component.

```{r other-measurements, eval = FALSE, shot = TRUE}
pick <- function(id, type, placeholder, format = NULL) {
  tags$div(
    style = "margin-bottom: 12px",
    tags$div(type),
    el_date_picker(id, type = type, placeholder = placeholder, format = format)
  )
}
tagList(
  pick("dp_week", "week", "Pick a week", format = "[Week] ww"),
  pick("dp_month", "month", "Pick a month"),
  pick("dp_year", "year", "Pick a year"),
  pick("dp_years", "years", "Pick years"),
  pick("dp_months", "months", "Pick months"),
  pick("dp_dates", "dates", "Pick one or more dates")
)
```

## Date Range

Picking a date range is supported.

When in range mode, the left and right panels are linked by default. If you want the two panels to switch current months independently, you can use the `unlink-panels` attribute.

The radio buttons resize both pickers with `update_el_date_picker(size
=)`.

```{r date-range, eval = FALSE, shot = TRUE, shot_js = c("document.querySelectorAll('#dp_range_size .el-radio-button')[2].click()", "document.querySelectorAll('#dp_range_quick input')[0].focus()"), shot_sel = ".el-picker__popper", shot_expect = c("document.querySelectorAll('.demo-date-picker .el-range-editor--small').length === 2", "Array.from(document.querySelectorAll('.el-picker__popper')).filter(function(x) { return x.offsetParent; })[0].querySelectorAll('.el-picker-panel__shortcut').length === 3")}
ui <- el_page(
  tags$style(
    ".demo-date-picker { display: flex; width: 100%; flex-wrap: wrap; }
     .demo-date-picker .block { padding: 1.5rem 0; text-align: center;
       border-right: solid 1px var(--el-border-color); flex: 1; min-width: 300px; }
     .demo-date-picker .block:last-child { border-right: none; }
     .demo-date-picker .demonstration { display: block; margin-bottom: 20px;
       color: var(--el-text-color-secondary); font-size: 14px; }"
  ),
  el_radio_group(
    "dp_range_size",
    choices = c("large", "default", "small"),
    selected = "default",
    button = TRUE
  ),
  tags$div(
    class = "demo-date-picker",
    tags$div(
      class = "block",
      tags$span(class = "demonstration", "Default"),
      el_date_picker(
        "dp_range",
        type = "daterange",
        range_separator = "To",
        start_placeholder = "Start date",
        end_placeholder = "End date"
      )
    ),
    tags$div(
      class = "block",
      tags$span(class = "demonstration", "With quick options"),
      el_date_picker(
        "dp_range_quick",
        type = "daterange",
        unlink_panels = TRUE,
        range_separator = "To",
        start_placeholder = "Start date",
        end_placeholder = "End date",
        shortcuts = list(
          list(
            text = "Last week",
            value = JS(
              "function() { var e = new Date(), s = new Date(); s.setTime(s.getTime() - 3600 * 1000 * 24 * 7); return [s, e]; }"
            )
          ),
          list(
            text = "Last month",
            value = JS(
              "function() { var e = new Date(), s = new Date(); s.setMonth(s.getMonth() - 1); return [s, e]; }"
            )
          ),
          list(
            text = "Last 3 months",
            value = JS(
              "function() { var e = new Date(), s = new Date(); s.setMonth(s.getMonth() - 3); return [s, e]; }"
            )
          )
        )
      )
    )
  )
)
server <- function(input, output, session) {
  observeEvent(input$dp_range_size, ignoreInit = TRUE, {
    for (id in c("dp_range", "dp_range_quick")) {
      update_el_date_picker(session, id, size = input$dp_range_size)
    }
  })
}
shinyApp(ui, server)
```

## Month Range

Picking a month range is supported.

When in range mode, the left and right panels are linked by default. If you want the two panels to switch current years independently, you can use the `unlink-panels` attribute.

```{r month-range, eval = FALSE, shot = TRUE}
el_date_picker(
  "dp_mrange",
  type = "monthrange",
  range_separator = "To",
  start_placeholder = "Start month",
  end_placeholder = "End month"
)
```

## Year Range

Picking a year range is supported.

When in range mode, the left and right panels are linked by default. If you want the two panels to switch years independently, you can use the `unlink-panels` attribute.

```{r year-range, eval = FALSE, shot = TRUE}
el_date_picker(
  "dp_yrange",
  type = "yearrange",
  range_separator = "To",
  start_placeholder = "Start Year",
  end_placeholder = "End Year"
)
```

## Quarter Range

Picking a quarter range is supported.

When in range mode, the left and right panels are linked by default. If you want the two panels to switch years independently, you can use the `unlink-panels` attribute.

```{r quarter-range, eval = FALSE, shot = TRUE}
el_date_picker(
  "dp_qrange",
  type = "quarterrange",
  range_separator = "To",
  start_placeholder = "Start quarter",
  end_placeholder = "End quarter"
)
```

## Single Panel

By default date picker ranges have two panels. If you want one panel set the `single-panel` attribute.

```{r single-panel, eval = FALSE, shot = TRUE}
el_date_picker(
  "dp_single",
  type = "daterange",
  single_panel = TRUE,
  start_placeholder = "Start date",
  end_placeholder = "End date"
)
```

## Default Value

If user hasn't picked a date, shows today's calendar by default. You can use `default-value` to set another date. Its value should be parsable by `new Date()`.

If type is `daterange`, `default-value` sets the left side calendar.

```{r default-value, eval = FALSE, shot = TRUE}
tagList(
  el_date_picker(
    "dp_dv1",
    type = "date",
    placeholder = "Pick a date",
    default_value = "2010-10-01"
  ),
  el_date_picker(
    "dp_dv2",
    type = "daterange",
    start_placeholder = "Start Date",
    end_placeholder = "End Date",
    default_value = c("2010-09-01", "2010-10-01")
  )
)
```

## Date Formats

Use `format` to control displayed text's format in the input box. Use `value-format` to control binding value's format.

By default, the component accepts and emits a `Date` object.

Check the list [here](https://day.js.org/docs/en/display/format#list-of-all-available-formats) of all available formats of Day.js.

> **Warning**
>
> Pay attention to capitalization

`value_format` is the value reported to Shiny; `format` what the input
shows. Both in day.js's tokens.

```{r date-formats, eval = FALSE, shot = TRUE}
tagList(
  tags$div("Emits Date object"),
  el_date_picker("dp_fmt1", value = "2021-10-29", format = "YYYY/MM/DD"),
  tags$div("Use value-format"),
  el_date_picker(
    "dp_fmt2",
    value = "2021-10-29",
    format = "YYYY/MM/DD",
    value_format = "x"
  )
)
```

## Default time for start date and end date

When picking a date range, you can assign the time part for start date and end date.

By default, the time part of start date and end date are both `00:00:00`. Setting `default-time` can change their time respectively. It accepts an array of up to two Date objects. The first string sets the time for the start date, and the second for the end date.

```{r default-time, eval = FALSE, shot = TRUE}
el_date_picker(
  "dp_dt",
  type = "daterange",
  start_placeholder = "Start date",
  end_placeholder = "End date",
  default_time = list(
    JS("new Date(2000, 1, 1, 12, 0, 0)"),
    JS("new Date(2000, 2, 1, 8, 0, 0)")
  )
)
```

## Set custom content of prefix

The content of prefix can be customized.

Setting `prefix-icon` to component which you import form other .vue or generated by the render function.

```{r custom-prefix-icon, eval = FALSE, shot = TRUE}
el_date_picker(
  "dp_prefix",
  placeholder = "Pick a day",
  prefix_icon = "Calendar"
)
```

## Custom content

The content of cell can be customized, in scoped-slot you can get the cell data. Note that the custom content structure should be consistent with the default structure, otherwise style misalignment may occur.

```{r custom-content, eval = FALSE, shot = TRUE}
el_date_picker(
  "dp_cell",
  placeholder = "Pick a day",
  slots = list(
    default = template(
      htmltools::HTML(
        "<div class=\"cell\" :class=\"{ current: cell.isCurrent }\"><span class=\"cell__text\">{{ cell.text }}</span></div>"
      ),
      scope = "cell"
    )
  )
)
```

## Custom icon

Custom icons available with slots.

The panel's arrows are slots: `prev-month`, `next-month`, `prev-year`,
`next-year`.

```{r custom-icon, eval = FALSE, shot = TRUE, shot_js = "document.querySelectorAll('#dp_icon_range input')[0].focus()", shot_sel = ".el-picker__popper", shot_expect = "document.querySelectorAll('.el-picker__popper .d-arrow-left [data-el-icon=Back]').length >= 2"}
arrows <- function(months = TRUE) {
  c(
    if (months) {
      list(
        `prev-month` = el_icon("CaretLeft"),
        `next-month` = el_icon("CaretRight")
      )
    },
    list(`prev-year` = el_icon("Back"), `next-year` = el_icon("Right"))
  )
}
block <- function(title, picker) {
  tags$div(class = "block", tags$div(class = "demonstration", title), picker)
}
tagList(
  tags$style(
    ".demo-date-picker-icon { display: grid; width: 100%;
       grid-template-columns: repeat(2, 1fr); }
     .demo-date-picker-icon .block { padding: 1.5rem 1rem; text-align: center;
       display: flex; flex-direction: column; align-items: center;
       border-right: solid 1px var(--el-border-color);
       border-bottom: solid 1px var(--el-border-color); }
     .demo-date-picker-icon .block:nth-child(2n) { border-right: none; }
     .demo-date-picker-icon .block:nth-child(5) { grid-column: span 2;
       border-right: none; border-bottom: none; }
     .demo-date-picker-icon .block .el-date-editor { width: 100%; max-width: 360px; }
     .demo-date-picker-icon .demonstration { color: var(--el-text-color-secondary);
       font-size: 14px; margin-bottom: 1rem; }"
  ),
  tags$div(
    class = "demo-date-picker-icon",
    block(
      "date",
      el_date_picker(
        "dp_icon_date",
        placeholder = "Pick a day",
        format = "YYYY/MM/DD",
        value_format = "YYYY-MM-DD",
        slots = arrows()
      )
    ),
    block(
      "date range",
      el_date_picker(
        "dp_icon_range",
        type = "daterange",
        start_placeholder = "Start date",
        end_placeholder = "End date",
        format = "YYYY/MM/DD",
        value_format = "YYYY-MM-DD",
        unlink_panels = TRUE,
        slots = arrows()
      )
    ),
    block(
      "month range",
      el_date_picker(
        "dp_icon_month",
        type = "monthrange",
        start_placeholder = "Start date",
        end_placeholder = "End date",
        format = "YYYY/MM/DD",
        value_format = "YYYY-MM-DD",
        unlink_panels = TRUE,
        slots = arrows()
      )
    ),
    block(
      "year range",
      el_date_picker(
        "dp_icon_year",
        type = "yearrange",
        range_separator = "To",
        start_placeholder = "Start Year",
        end_placeholder = "End Year",
        slots = arrows(FALSE)
      )
    ),
    block(
      "quarter range",
      el_date_picker(
        "dp_icon_quarter",
        type = "quarterrange",
        range_separator = "To",
        start_placeholder = "Start quarter",
        end_placeholder = "End quarter",
        slots = arrows(FALSE)
      )
    )
  )
)
```

For data details, please refer:

## Localization

The default locale of is English, if you need to use other languages, please check [Internationalization](https://element-plus.org/en-US/guide/i18n)

Note, date time locale (month name, first day of the week ...) are also configured in localization.

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("date-picker")
```
