---
title: "DatePicker"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Use Date Picker for date input. `input$<id>` is a `Date` -- two for a
range -- as `dateInput()` gives one; another `type` or `value_format`
reports the text the picker produces.

## Enter date

`type` sets the measurement; `picker_options` carries Element's
`shortcuts` and `disabledDate`, written with `JS()`.

```{r enter, eval = FALSE, shot = TRUE, shot_js = "document.querySelectorAll('#shot .el-input__inner')[1].focus()", shot_sel = ".el-picker-panel", shot_wait = 1}
el_date_picker("d1", placeholder = "Pick a day")
el_date_picker("d2", placeholder = "Pick a day", picker_options = list(
  disabledDate = JS("function(time) { return time.getTime() > Date.now(); }"),
  shortcuts = list(
    list(text = "Today", onClick = JS("function(picker) { picker.$emit('pick', new Date()); }")),
    list(text = "Yesterday", onClick = JS(
      "function(picker) { var d = new Date(); d.setTime(d.getTime() - 3600 * 1000 * 24); picker.$emit('pick', d); }")))))
```

## Other measurements

```{r measurements, eval = FALSE, shot = TRUE}
el_date_picker("week", type = "week", format = "Week WW", value_format = "yyyy-WW", placeholder = "Pick a week")
el_date_picker("month", type = "month", value_format = "yyyy-MM", placeholder = "Pick a month")
el_date_picker("year", type = "year", value_format = "yyyy", placeholder = "Pick a year")
el_date_picker("dates", type = "dates", placeholder = "Pick one or more dates")
```

## Date range

`unlink_panels` lets the two months move on their own.

```{r range, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#shot .el-range-input').focus()", shot_sel = ".el-picker-panel", shot_wait = 1}
el_date_picker("trip", type = "daterange", range_separator = "To", unlink_panels = TRUE,
               start_placeholder = "Start date", end_placeholder = "End date")
```

## Month range

```{r month-range, eval = FALSE, shot = TRUE}
el_date_picker("quarter", type = "monthrange", value_format = "yyyy-MM", range_separator = "To",
               start_placeholder = "Start month", end_placeholder = "End month")
```

## Default value

`default_value` is the month the panel opens on when nothing is picked.

```{r default, eval = FALSE, shot = TRUE}
el_date_picker("dv", placeholder = "Pick a date", default_value = "2010-10-01")
```

## Date formats

`format` is what the box shows; `value_format` what `input$<id>` gets.

```{r formats, eval = FALSE, shot = TRUE}
el_date_picker("f1", value = "2026-03-15", format = "yyyy/MM/dd")
el_date_picker("f2", value = "2026-03-15", format = "dd MMM yyyy", value_format = "timestamp")
```

## Default time for start and end date

```{r default-time, eval = FALSE, shot = TRUE}
el_date_picker("dt", type = "daterange", value_format = "yyyy-MM-dd HH:mm:ss",
               start_placeholder = "Start", end_placeholder = "End",
               default_time = c("00:00:00", "23:59:59"))
```

## API

```{r api, echo = FALSE, results = "asis"}
api_tables("date-picker")
```
