---
title: "DatePickerPanel"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

`DatePickerPanel` is the core component of `DatePicker`.

## Enter Date

Basic date picker measured by 'day'.

```{r basic, eval = FALSE, shot = TRUE}
el_date_picker_panel("dpp", value = Sys.Date())
```

## Border

By default the date-picker-panel is bordered but in some case you don't want it.
For example `DatePicker` don't inherit `border`.

```{r border, eval = FALSE, shot = TRUE}
el_date_picker_panel("dpp_border", value = Sys.Date(), border = FALSE)
```

## Disabled

The `disabled` attribute determines if the date picker is fully disabled.

```{r disabled, eval = FALSE, shot = TRUE}
el_date_picker_panel("dpp_dis", value = Sys.Date(), disabled = TRUE)
```

## Types

The measurement is determined by the `type` attribute.

Every type the picker has, its panel open.

```{r all-types, eval = FALSE, shot = TRUE}
tags$div(style = "display: grid; gap: 16px",
  lapply(c("date", "week", "month", "year", "daterange", "monthrange"), function(t)
    tagList(tags$div(t), el_date_picker_panel(paste0("dpp_", t), type = t))))
```

## Localization

The default locale of is English, if you need to use other languages, please check [Internationalization](https://element-plus.org/en-US/guide/i18n)

Note, date time locale (month name, first day of the week ...) are also configured in localization.

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("date-picker-panel")
```
