---
title: "Dialog"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Informs users while preserving the current page state.

## Basic usage

Dialog pops up a dialog box, and it's quite customizable.

Set `model-value / v-model` attribute with a `Boolean`, and Dialog shows when it is `true`. The Dialog has two parts: `body` and `footer`, and the latter requires a `slot` named `footer`. The optional `title` attribute (empty by default) is for defining a title. Finally, this example demonstrates how `before-close` is used.

A dialog opens from the server, `update_el_dialog(visible = TRUE)`;
`input$<id>` is whether it is open. `before_close`, a `JS()` function,
may hold the close back.

```{r basic-usage, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#open_container button').click()", shot_sel = ".el-dialog", shot_wait = 1.5}
ui <- el_page(
  el_button("open", "Click to open the Dialog", plain = TRUE),
  el_dialog(
    "tips",
    title = "Tips",
    width = "500px",
    content = tags$span("This is a message"),
    before_close = JS(
      "function(done) { if (confirm('Are you sure to close this dialog?')) done(); }"
    ),
    footer = tagList(
      el_button("cancel", "Cancel"),
      el_button("confirm", "Confirm", type = "primary")
    )
  )
)
server <- function(input, output, session) {
  observeEvent(input$open, update_el_dialog(id = "tips", visible = TRUE))
  observeEvent(
    c(input$cancel, input$confirm),
    update_el_dialog(id = "tips", visible = FALSE),
    ignoreInit = TRUE
  )
}
shinyApp(ui, server)
```

> **Tip**
>
> `before-close` only works when user clicks the close icon or the backdrop. If you have buttons that close the Dialog in the `footer` named slot, you can add what you would do with `before-close` in the buttons' click event handler.

## Customized Content

The content of Dialog can be anything, even a table or a form. This example shows how to use Element Plus Table and Form with Dialog.

```{r customization-content, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#open_container button').click()", shot_sel = ".el-dialog", shot_wait = 1.5}
ui <- el_page(
  el_button("open", "Open a Form nested Dialog", plain = TRUE),
  el_dialog(
    "shipping",
    title = "Shipping address",
    width = "500px",
    content = tagList(
      el_input(
        "name",
        label = "Promotion name",
        label_position = "left",
        label_width = "140px"
      ),
      el_select(
        "zone",
        choices = c("Zone No.1" = "shanghai", "Zone No.2" = "beijing"),
        placeholder = "Please select a zone",
        label = "Zones",
        label_position = "left",
        label_width = "140px"
      )
    ),
    footer = tagList(
      el_button("cancel", "Cancel"),
      el_button("confirm", "Confirm", type = "primary")
    )
  )
)
server <- function(input, output, session) {
  observeEvent(input$open, update_el_dialog(id = "shipping", visible = TRUE))
}
shinyApp(ui, server)
```

## Customized Header

The `header` slot can be used to customize the area where the title is displayed. In order to maintain accessibility, use the `title` attribute in addition to using this slot, or use the `titleId` slot property to specify which element should be read out as the dialog title.

The title takes markup: a header of your own.

```{r customization-header, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#open_container button').click()", shot_sel = ".el-dialog", shot_wait = 1.5}
ui <- el_page(
  el_button("open", "Open Dialog with customized header", plain = TRUE),
  el_dialog(
    "custom",
    show_close = FALSE,
    width = "500px",
    title = tags$div(
      style = "display: flex; justify-content: space-between; align-items: center",
      tags$h4("This is a custom header!"),
      el_button("close", "Close", type = "danger", icon = "CircleCloseFilled")
    ),
    content = "This is dialog content."
  )
)
server <- function(input, output, session) {
  observeEvent(input$open, update_el_dialog(id = "custom", visible = TRUE))
  observeEvent(input$close, update_el_dialog(id = "custom", visible = FALSE))
}
shinyApp(ui, server)
```

## Nested Dialog

If a Dialog is nested in another Dialog, `append-to-body` is required.

Normally we do not recommend using nested Dialog. If you need multiple Dialogs rendered on the page, you can simply flat them so that they're siblings to each other. If you must nest a Dialog inside another Dialog, set `append-to-body` of the nested Dialog to true, and it will append to body instead of its parent node, so both Dialogs can be correctly rendered.

```{r nested-dialog, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#open_container button').click(); setTimeout(function(){ document.querySelector('#inner_open_container button').click(); }, 800);", shot_sel = ".el-dialog", shot_wait = 2}
ui <- el_page(
  el_button("open", "Open the outer Dialog", plain = TRUE),
  el_dialog(
    "outer",
    title = "Outer Dialog",
    width = "800px",
    content = tagList(
      tags$span("This is the outer Dialog"),
      el_dialog(
        "inner",
        title = "Inner Dialog",
        width = "500px",
        append_to_body = TRUE,
        content = "This is the inner Dialog"
      )
    ),
    footer = el_button("inner_open", "Open the inner Dialog", type = "primary")
  )
)
server <- function(input, output, session) {
  observeEvent(input$open, update_el_dialog(id = "outer", visible = TRUE))
  observeEvent(input$inner_open, update_el_dialog(id = "inner", visible = TRUE))
}
shinyApp(ui, server)
```

## Centered content

Dialog's content can be centered.

Setting `center` to `true` will center dialog's header and footer horizontally. `center` only affects Dialog's header and footer. The body of Dialog can be anything, so sometimes it may not look good when centered. You need to write some CSS if you wish to center the body as well.

```{r centered-content, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#open_container button').click()", shot_sel = ".el-dialog", shot_wait = 1.5}
ui <- el_page(
  el_button("open", "Click to open the Dialog", plain = TRUE),
  el_dialog(
    "warn",
    title = "Warning",
    width = "500px",
    center = TRUE,
    content = "It should be noted that the content will not be aligned in center by default",
    footer = tagList(
      el_button("cancel", "Cancel"),
      el_button("confirm", "Confirm", type = "primary")
    )
  )
)
server <- function(input, output, session) {
  observeEvent(input$open, update_el_dialog(id = "warn", visible = TRUE))
}
shinyApp(ui, server)
```

> **Tip**
>
> The content of Dialog is lazily rendered, which means the default slot is not rendered onto the DOM until it is firstly opened. Therefore, if you need to perform a DOM manipulation or access a component using `ref`, do it in the `open` event callback.

## Align Center dialog

Open dialog from the center of the screen.

Setting `align-center` to `true` will center the dialog both horizontally and vertically. The prop `top` will not work at the same time because the dialog is vertically centered in a flexbox.

```{r align-center, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#open_container button').click()", shot_sel = ".el-dialog", shot_wait = 1.5}
ui <- el_page(
  el_button("open", "Click to open the Dialog", plain = TRUE),
  el_dialog(
    "warn",
    title = "Warning",
    width = "500px",
    align_center = TRUE,
    content = "Open the dialog from the center from the screen",
    footer = tagList(
      el_button("cancel", "Cancel"),
      el_button("confirm", "Confirm", type = "primary")
    )
  )
)
server <- function(input, output, session) {
  observeEvent(input$open, update_el_dialog(id = "warn", visible = TRUE))
}
shinyApp(ui, server)
```

## Destroy on Close

When this is feature is enabled, the content under default slot will be destroyed with a `v-if` directive. Enable this when you have perf concerns.

Note that by enabling this feature, the content will not be rendered before `transition.beforeEnter` dispatched, there will only be `overlay` `header(if any)` `footer(if any)`.

Its content made again each time it opens: inputs inside start fresh.

```{r destroy-on-close, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#open_container button').click()", shot_sel = ".el-dialog", shot_wait = 1.5}
ui <- el_page(
  el_button("open", "Click to open Dialog", plain = TRUE),
  el_dialog(
    "notice",
    title = "Notice",
    width = "500px",
    destroy_on_close = TRUE,
    center = TRUE,
    content = tagList(
      tags$p(
        "Notice: before dialog gets opened for the first time this node and the one below will not be rendered"
      ),
      el_input("note", placeholder = "starts empty each time")
    )
  )
)
server <- function(input, output, session) {
  observeEvent(input$open, update_el_dialog(id = "notice", visible = TRUE))
}
shinyApp(ui, server)
```

## Draggable Dialog

Try to drag the `header` part.

Set `draggable` to `true` to drag. Set `overflow` 2.5.4 to `true` can drag overflow the viewport.

```{r draggable-dialog, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#open_container button').click()", shot_sel = ".el-dialog", shot_wait = 1.5}
ui <- el_page(
  el_button("open", "Click to open Dialog", plain = TRUE),
  el_dialog(
    "drag",
    title = "Tips",
    width = "500px",
    draggable = TRUE,
    content = "It's a draggable Dialog"
  )
)
server <- function(input, output, session) {
  observeEvent(input$open, update_el_dialog(id = "drag", visible = TRUE))
}
shinyApp(ui, server)
```

> **Tip**
>
> When using `modal` = false, please make sure that `append-to-body` was set to **true**, because `Dialog` was positioned by `position: relative`, when `modal` gets removed, `Dialog` will position itself based on the current position in the DOM, instead of `Document.Body`, thus the style will be messed up.

## Fullscreen

Set the `fullscreen` attribute to open fullscreen dialog.

```{r fullscreen, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#open_container button').click()", shot_sel = ".el-dialog", shot_wait = 1.5}
ui <- el_page(
  el_button("open", "Open the fullscreen Dialog", plain = TRUE),
  el_dialog(
    "full",
    title = "Tips",
    fullscreen = TRUE,
    content = "It's a fullscreen Dialog"
  )
)
server <- function(input, output, session) {
  observeEvent(input$open, update_el_dialog(id = "full", visible = TRUE))
}
shinyApp(ui, server)
```

> **Tip**
>
> If `fullscreen` is true, `width` `top` `draggable` attributes don't work.

## Modal

Setting `modal` to `false` will hide modal (overlay) of dialog.

Starting from version 2.10.5, `modal-penetrable` attribute is added, which can be penetrable.

Without a backdrop the page beneath stays in view, and with
`modal_penetrable` it can be used too.

```{r modal, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#open_container button').click()", shot_sel = ".el-dialog", shot_wait = 1.5}
ui <- el_page(
  el_button("open", "Open the modal-less Dialog", plain = TRUE),
  el_dialog(
    "nomodal",
    title = "Tips",
    width = "500px",
    modal = FALSE,
    modal_penetrable = TRUE,
    content = "It's a modal-less Dialog"
  )
)
server <- function(input, output, session) {
  observeEvent(input$open, update_el_dialog(id = "nomodal", visible = TRUE))
}
shinyApp(ui, server)
```

## Custom Animation

Customize dialog animation through the `transition` attribute, which accepts either:

- ​Transition name​​ (string)

- ​​Vue transition configuration​​ (object)

Examples include scale, slide, fade, bounce animations and object-based configurations with custom event handlers.

`transition` names a CSS animation of your own, as Element Plus's does.

```{r custom-animation, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#open_container button').click()", shot_sel = ".el-dialog", shot_wait = 1.5}
ui <- el_page(
  tags$style(".dialog-bounce-enter-active { animation: dialog-fade-in .5s; }"),
  el_button("open", "Open the Dialog", plain = TRUE),
  el_dialog(
    "anim",
    title = "Custom animation",
    width = "500px",
    transition = "dialog-bounce",
    content = "This dialog plays an animation of its own."
  )
)
server <- function(input, output, session) {
  observeEvent(input$open, update_el_dialog(id = "anim", visible = TRUE))
}
shinyApp(ui, server)
```

> **Tip**
>
> Animation classes are dynamically generated based on the transition name. For granular control over animation behavior, you may explicitly define these classes. Refer to [custom-transition-classes](https://vuejs.org/guide/built-ins/transition.html#custom-transition-classes) for details.

## Events

Open developer console (ctrl + shift + J), to see order of events.

Every event is an input: `input$<id>_open`, `_opened`, `_close`,
`_closed`, `_open_auto_focus` and `_close_auto_focus`.

```{r events, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#open_container button').click()", shot_sel = ".el-dialog", shot_wait = 1.5}
ui <- el_page(
  el_button("open", "Open the Dialog", plain = TRUE),
  el_dialog(
    "ev",
    title = "Events",
    width = "500px",
    content = verbatimTextOutput("log")
  )
)
server <- function(input, output, session) {
  seen <- reactiveVal(character())
  for (e in c("open", "opened", "close", "closed")) {
    local({
      e <- e
      observeEvent(input[[paste0("ev_", e)]], seen(c(seen(), e)))
    })
  }
  output$log <- renderText(paste(seen(), collapse = "\n"))
  observeEvent(input$open, update_el_dialog(id = "ev", visible = TRUE))
}
shinyApp(ui, server)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("dialog")
```
