---
title: "Drawer"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Sometimes, `Dialog` does not always satisfy our requirements, let's say you have a massive form, or you need space to display something like `terms & conditions`, `Drawer` has almost identical API with `Dialog`, but it introduces different user experience.

> **Tip**
>
> Since v-model is natively supported for all components, `visible.sync` has been deprecated, use `v-model="visibilityBinding"` to control the visibility of the current drawer.

## Basic Usage

Callout a temporary drawer, from multiple direction

You must set `model-value` for `Drawer` like `Dialog` does to control the visibility of `Drawer` itself, it's `boolean` type. `Drawer` has three parts: `title` & `body` & `footer`, the `title` is a named slot, you can also set the title through attribute named `title`, default to an empty string, the `body` part is the main area of `Drawer`, which contains user defined content. When opening, `Drawer` expand itself from the **right corner to left** which size is **30%** of the browser window by default. You can change that default behavior by setting `direction` and `size` attribute. This show case also demonstrated how to use the `before-close` API, check the Attribute section for more detail

The radios set the edge it slides from, with `update_el_drawer(direction
=)`; closing the first asks first, through `before_close`.

```{r basic-usage, eval = FALSE, shot = TRUE, shot_js = c("Array.from(document.querySelectorAll('#direction .el-radio')).find(function(r){ return r.innerText.indexOf('top to bottom') >= 0; }).click()", "document.querySelector('#open_container button').click()"), shot_sel = ".el-drawer", shot_wait = 1.5, shot_expect = "document.querySelector('#drw .el-drawer.ttb')"}
ui <- el_page(
  el_radio_group(
    "direction",
    choices = c(
      "left to right" = "ltr",
      "right to left" = "rtl",
      "top to bottom" = "ttb",
      "bottom to top" = "btt"
    ),
    value = "rtl"
  ),
  el_button("open", "open", type = "primary"),
  el_button("open2", "with footer", type = "primary"),
  el_drawer(
    "drw",
    title = "I am the title",
    direction = "rtl",
    before_close = JS(
      "function(done) { if (confirm('Are you sure you want to close this?')) done(); }"
    ),
    content = tags$span("Hi, there!")
  ),
  el_drawer(
    "drw2",
    title = tags$h4("set title by slot"),
    direction = "rtl",
    content = el_radio_group(
      "radio1",
      choices = c("Option 1", "Option 2"),
      value = "Option 1",
      size = "large"
    ),
    footer = tags$div(
      style = "flex: auto",
      el_button("cancel", "cancel"),
      el_button("confirm", "confirm", type = "primary")
    )
  )
)
server <- function(input, output, session) {
  observeEvent(input$direction, ignoreInit = TRUE, {
    update_el_drawer(id = "drw", direction = input$direction)
    update_el_drawer(id = "drw2", direction = input$direction)
  })
  observeEvent(input$open, update_el_drawer(id = "drw", visible = TRUE))
  observeEvent(input$open2, update_el_drawer(id = "drw2", visible = TRUE))
  observeEvent(input$cancel, update_el_drawer(id = "drw2", visible = FALSE))
  observeEvent(input$confirm, {
    update_el_drawer(id = "drw2", visible = FALSE)
    el_message(paste("You chose", input$radio1))
  })
}
shinyApp(ui, server)
```

## No Title

When you no longer need a title, you can remove it from the drawer.

Set the `withHeader` attribute to **false**, you can remove the title from drawer, thus your drawer can have more space on screen. If you want to be accessible, make sure to set the `title` attribute.

```{r no-title, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#open_container button').click()", shot_sel = ".el-drawer", shot_wait = 1.5}
ui <- el_page(
  el_button("open", "open", type = "primary"),
  el_drawer(
    "drw",
    title = "I am the title",
    with_header = FALSE,
    content = tags$span("Hi there!")
  )
)
server <- function(input, output, session) {
  observeEvent(input$open, update_el_drawer(id = "drw", visible = TRUE))
}
shinyApp(ui, server)
```

## Customized Content

Like `Dialog`, `Drawer` can be used to display a multitude of diverse interactions.

```{r customization-content, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#open_container button').click()", shot_sel = ".el-drawer", shot_wait = 1.5}
ui <- el_page(
  el_button("open", "Open Drawer with nested form", text = TRUE),
  el_drawer(
    "drw",
    title = "I have a nested form inside!",
    direction = "ltr",
    size = "40%",
    content = tagList(
      el_input(
        "name",
        label = "Name",
        label_position = "left",
        label_width = "80px"
      ),
      el_select(
        "area",
        choices = c("Area1" = "shanghai", "Area2" = "beijing"),
        label = "Area",
        label_position = "left",
        label_width = "80px"
      )
    ),
    footer = tagList(
      el_button("cancel", "Cancel"),
      el_button("submit", "Submit", type = "primary")
    )
  )
)
server <- function(input, output, session) {
  observeEvent(input$open, update_el_drawer(id = "drw", visible = TRUE))
}
shinyApp(ui, server)
```

## Customized Header

The `header` slot can be used to customize the area where the title is displayed. In order to maintain accessibility, use the `title` attribute in addition to using this slot, or use the `titleId` slot property to specify which element should be read out as the drawer title.

```{r customization-header, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#open_container button').click()", shot_sel = ".el-drawer", shot_wait = 1.5}
ui <- el_page(
  el_button("open", "Open Drawer with customized header"),
  el_drawer(
    "drw",
    show_close = FALSE,
    content = "This is drawer content.",
    title = tags$div(
      style = "display: flex; justify-content: space-between; align-items: center",
      tags$h4("This is a custom header!"),
      el_button("close", "Close", type = "danger", icon = "CircleCloseFilled")
    )
  )
)
server <- function(input, output, session) {
  observeEvent(input$open, update_el_drawer(id = "drw", visible = TRUE))
  observeEvent(input$close, update_el_drawer(id = "drw", visible = FALSE))
}
shinyApp(ui, server)
```

## Resizable Drawer

Try to drag the edge part.

Set `resizable` to `true` to resize.

Picking an edge opens it there; dragging its inner edge resizes it,
reported as `input$<id>_resize`.

```{r resizable, eval = FALSE, shot = TRUE, shot_js = "Array.from(document.querySelectorAll('#direction .el-radio-button')).find(function(r){ return r.innerText.trim() === 'bottom'; }).click()", shot_sel = ".el-drawer", shot_wait = 1.5, shot_expect = c("document.querySelector('#drw .el-drawer.btt')", "getComputedStyle(document.getElementById('drw')).display !== 'none'")}
ui <- el_page(
  el_radio_group(
    "direction",
    choices = c(top = "ttb", right = "rtl", bottom = "btt", left = "ltr"),
    value = "rtl",
    button = TRUE
  ),
  el_drawer(
    "drw",
    direction = "rtl",
    resizable = TRUE,
    content = "This is drawer content."
  )
)
server <- function(input, output, session) {
  observeEvent(input$direction, ignoreInit = TRUE, {
    update_el_drawer(id = "drw", direction = input$direction, visible = TRUE)
  })
}
shinyApp(ui, server)
```

## Nested Drawer

You can also have multiple layer of `Drawer` just like `Dialog`.

If you need multiple Drawer in different layer, you must set the `append-to-body` attribute to **true**

```{r nested-drawer, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#open_container button').click(); setTimeout(function(){ document.querySelector('#inner_open_container button').click(); }, 800);", shot_sel = ".el-drawer", shot_wait = 2}
ui <- el_page(
  el_button("open", "open", type = "primary"),
  el_drawer(
    "outer",
    title = "I'm outer Drawer",
    size = "50%",
    content = tagList(
      el_button("inner_open", "Click me!"),
      el_drawer(
        "inner",
        title = "I'm inner Drawer",
        append_to_body = TRUE,
        content = tags$p("_(:з)∠)_")
      )
    )
  )
)
server <- function(input, output, session) {
  observeEvent(input$open, update_el_drawer(id = "outer", visible = TRUE))
  observeEvent(input$inner_open, update_el_drawer(id = "inner", visible = TRUE))
}
shinyApp(ui, server)
```

## Modal

Setting `modal` to `false` will hide modal (overlay) of drawer.

Starting from version 2.11.7, `modal-penetrable` attribute is added, which can be penetrable.

```{r modal, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#open_container button').click()", shot_sel = ".el-drawer", shot_wait = 1.5}
ui <- el_page(
  el_button("open", "Open the modal Drawer", plain = TRUE),
  el_drawer(
    "drw",
    modal = FALSE,
    modal_penetrable = TRUE,
    content = tags$span("It's a modal Drawer"),
    footer = tagList(
      el_button("cancel", "Cancel"),
      el_button("confirm", "Confirm", type = "primary")
    )
  )
)
server <- function(input, output, session) {
  observeEvent(input$open, update_el_drawer(id = "drw", visible = TRUE))
}
shinyApp(ui, server)
```

> **Tip**
>
> The content inside Drawer should be lazy rendered, which means that the content inside Drawer will not impact the initial render performance, therefore any DOM operation should be performed through `ref` or after `open` event emitted.

> **Tip**
>
> Drawer provides an API called `destroy-on-close`, which is a flag variable that indicates should destroy the children content inside Drawer after Drawer was closed. You can use this API when you need your `mounted` life cycle to be called every time the Drawer opens.

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("drawer")
```
