---
title: "Dropdown"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Toggleable menu for displaying lists of links and actions.

## Basic usage

Hover on the dropdown menu to unfold it for more actions.

The triggering element is rendered by the default `slot`, and the dropdown part is rendered by the `slot` named `dropdown`. By default, dropdown list shows when you hover on the triggering element without having to click it.

```{r basic-usage, eval = FALSE, shot = TRUE}
items <- list(
  list(command = "a", label = "Action 1"),
  list(command = "b", label = "Action 2"),
  list(command = "c", label = "Action 3"),
  list(command = "d", label = "Action 4", disabled = TRUE),
  list(command = "e", label = "Action 5", divided = TRUE)
)
el_dropdown("dd", trigger_label = "Dropdown List", items = items)
```

## Placement

Support 6 placements.

Set `placement` property to make dropdown appear in different locations.

```{r placements, eval = FALSE, shot = TRUE}
items <- list(
  list(command = "1", label = "The Action 1st"),
  list(command = "2", label = "The Action 2nd"),
  list(command = "3", label = "The Action 3rd")
)
tags$div(
  style = "display: flex; flex-wrap: wrap; gap: 16px",
  lapply(
    c("top-start", "top", "top-end", "bottom-start", "bottom", "bottom-end"),
    function(p) {
      el_dropdown(
        paste0("dd_", p),
        placement = p,
        items = items,
        trigger_label = el_button(paste0("ddb_", p), p)
      )
    }
  )
)
```

## Triggering element

Use the button to trigger the dropdown list.

Use `split-button` to split the triggering element into a button group with the left button being a normal button and right one the actual triggering target. If you wanna insert a separator line between item three and item four, just add the `divided` attribute to item four.

```{r triggering-element, eval = FALSE, shot = TRUE}
items <- list(
  list(command = "a", label = "Action 1"),
  list(command = "b", label = "Action 2"),
  list(command = "c", label = "Action 3")
)
tags$div(
  style = "display: flex; gap: 16px",
  el_dropdown(
    "dd_btn",
    items = items,
    trigger_label = el_button(
      "dd_btn_t",
      "Dropdown List",
      type = "primary",
      icon = "ArrowDown"
    )
  ),
  el_dropdown(
    "dd_split",
    items = items,
    split_button = TRUE,
    type = "primary",
    trigger_label = "Dropdown List"
  )
)
```

## How to trigger

Click the triggering element or hover on it.

Use the attribute `trigger`. By default, it is `hover`.

```{r how-to-trigger, eval = FALSE, shot = TRUE}
items <- list(
  list(command = "a", label = "Action 1", icon = "Plus"),
  list(command = "b", label = "Action 2", icon = "CirclePlusFilled"),
  list(command = "c", label = "Action 3", icon = "CirclePlus")
)
tags$div(
  style = "display: flex; gap: 40px",
  tagList(
    tags$div("hover to trigger"),
    el_dropdown("dd_hover", items = items, trigger_label = "Dropdown List")
  ),
  tagList(
    tags$div("click to trigger"),
    el_dropdown(
      "dd_click",
      items = items,
      trigger = "click",
      trigger_label = "Dropdown List"
    )
  ),
  tagList(
    tags$div("right click to trigger"),
    el_dropdown(
      "dd_ctx",
      items = items,
      trigger = "contextmenu",
      trigger_label = "Dropdown List"
    )
  )
)
```

## Menu hiding behavior

Use `hide-on-click` to define if menu closes on clicking.

By default menu will close when you click on menu items, and it can be turned off by setting hide-on-click to false.

```{r menu-hiding-behavior, eval = FALSE, shot = TRUE}
el_dropdown(
  "dd_keep",
  hide_on_click = FALSE,
  trigger_label = "Dropdown List",
  items = list(
    list(command = "a", label = "Action 1"),
    list(command = "b", label = "Action 2"),
    list(command = "c", label = "Action 3")
  )
)
```

## Command event

Clicking each dropdown item fires an event whose parameter is assigned by each item.

The item clicked is `input$<id>`, its `command`.

```{r command-event, eval = FALSE, shot = TRUE}
el_dropdown(
  "dd_cmd",
  trigger_label = "Dropdown List",
  items = list(
    list(command = "a", label = "Action 1"),
    list(command = "b", label = "Action 2"),
    list(command = "c", label = "Action 3")
  )
)
```

## Dropdown methods

You can open or close the dropdown menu by manually use `handleOpen` or `handleClose`

`el_call(session, "dd_m", "handleOpen")` opens it from the server;
`"handleClose"` closes it.

```{r dropdown-methods, eval = FALSE, shot = TRUE}
el_dropdown(
  "dd_m",
  trigger = "contextmenu",
  trigger_label = "Dropdown List",
  items = list(
    list(command = "a", label = "Action 1"),
    list(command = "b", label = "Action 2")
  )
)
```

## Sizes

Besides default size, Dropdown component provides three additional sizes for you to choose among different scenarios.

Use attribute `size` to set additional sizes with `large`, `default` or `small`.

```{r sizes, eval = FALSE, shot = TRUE}
items <- list(
  list(command = "a", label = "Action 1"),
  list(command = "b", label = "Action 2")
)
tags$div(
  style = "display: flex; gap: 16px",
  lapply(c("large", "default", "small"), function(s) {
    el_dropdown(
      paste0("dd_s_", s),
      size = s,
      split_button = TRUE,
      type = "primary",
      trigger_label = s,
      items = items
    )
  })
)
```

## Virtual triggering

Sometimes we want to render the dropdown on some other trigger element, we can separate the trigger and the content.

> **In R**
>
> Element Plus's virtual trigger takes a DOM element from the page's own
> script; in R, put the trigger in `trigger_label` instead.

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("dropdown")
```
