---
title: "Empty"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Placeholder hints for empty states.

## Basic usage

```{r basic-usage, eval = FALSE, shot = TRUE}
el_empty(description = "description")
```

## Custom image

Use `image` prop to set image URL.

```{r custom-image, eval = FALSE, shot = TRUE}
el_empty(image = "https://shadow.elemecdn.com/app/element/hamburger.9cf7b091-55e9-11e9-a976-7f4d0b07eef6.png")
```

## Image size

Use `image-size` prop to control image size.

```{r image-size, eval = FALSE, shot = TRUE}
el_empty(image_size = 200)
```

## Bottom content

Use the default slot to insert content at the bottom.

```{r bottom-content, eval = FALSE, shot = TRUE}
el_empty(el_button("empty_btn", "Button", type = "primary"))
```

## Custom styles

Now you can set custom style for empty component.
Use `css/scss` language to change the global or local color. We set some global color variables: `--el-empty-fill-color-0`, `--el-empty-fill-color-1`, `--el-empty-fill-color-2`, ......, `--el-empty-fill-color-9`. You can use like: `:root { --el-empty-fill-color-0: red; --el-empty-fill-color-1: blue; }`.
But usually, if you want to change style, you need to change all color, because these colors are a combination.

### Default Variables

| Variable                | Color                 |
| ----------------------- | --------------------- |
| --el-empty-fill-color-0 | var(--el-color-white) |
| --el-empty-fill-color-1 | #fcfcfd               |
| --el-empty-fill-color-2 | #f8f9fb               |
| --el-empty-fill-color-3 | #f7f8fc               |
| --el-empty-fill-color-4 | #eeeff3               |
| --el-empty-fill-color-5 | #edeef2               |
| --el-empty-fill-color-6 | #e9ebef               |
| --el-empty-fill-color-7 | #e5e7e9               |
| --el-empty-fill-color-8 | #e0e3e9               |
| --el-empty-fill-color-9 | #d5d7de               |

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("empty")
```
