---
title: "Form"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Form consists of inputs, radios, selects, checkboxes and so on; with it you
can collect, verify and submit data. `el_form()` holds its fields, declared
with `el_form_field()`, in one model, and reports it as `input$<id>`,
with `input$<id>_valid` and `input$<id>_submit` when submitted. Its
standalone counterparts -- any input with a `label` -- are in the forms
article.

## Basic form

```{r basic, eval = FALSE, shot = TRUE}
el_form(id = "activity", label_width = "120px", submit_label = "Create", reset_label = "Cancel",
  el_form_field("name", "input", label = "Activity name"),
  el_form_field("region", "select", label = "Activity zone",
                choices = c("Zone one" = "shanghai", "Zone two" = "beijing"),
                placeholder = "please select your zone"),
  el_form_field("date", "date-picker", label = "Activity time", placeholder = "Pick a date"),
  el_form_field("delivery", "switch", label = "Instant delivery"),
  el_form_field("type", "checkbox-group", label = "Activity type",
                choices = c("Online activities", "Promotion activities", "Offline activities")),
  el_form_field("resource", "radio-group", label = "Resources",
                choices = c("Sponsor", "Venue")),
  el_form_field("desc", "textarea", label = "Activity form"))
```

## Inline form

```{r inline, eval = FALSE, shot = TRUE}
el_form(id = "search", inline = TRUE, submit_label = "Query",
  el_form_field("user", "input", label = "Approved by", placeholder = "Approved by"),
  el_form_field("region", "select", label = "Activity zone",
                choices = c("Zone one" = "shanghai", "Zone two" = "beijing")))
```

## Alignment

`label_position` puts the labels `"right"` (the default), `"left"` or on
`"top"`.

```{r alignment, eval = FALSE, shot = TRUE}
el_form(id = "aligned", label_position = "top", submit_label = NULL, width = "360px",
  el_form_field("name", "input", label = "Name"),
  el_form_field("region", "input", label = "Activity zone"),
  el_form_field("type", "input", label = "Activity form"))
```

## Validation

Each field's `rules`, from `el_rule()`, run on blur or change and on
submit.

```{r validation, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#shot .el-button--primary').click()"}
ui <- el_page(
  el_form(id = "rules", label_width = "120px", submit_label = "Create", reset_label = "Reset",
    el_form_field("name", "input", label = "Activity name", rules = list(
      el_rule(required = TRUE, message = "Please input Activity name"),
      el_rule(min = 3, max = 5, message = "Length should be 3 to 5"))),
    el_form_field("region", "select", label = "Activity zone",
                  choices = c("Zone one" = "shanghai", "Zone two" = "beijing"),
                  rules = el_rule(required = TRUE, message = "Please select Activity zone",
                                  trigger = "change")),
    el_form_field("type", "checkbox-group", label = "Activity type",
                  choices = c("Online activities", "Promotion activities"),
                  rules = el_rule(type = "array", required = TRUE, trigger = "change",
                                  message = "Please select at least one activity type"))),
  verbatimTextOutput("verdict"))

server <- function(input, output, session) {
  output$verdict <- renderPrint({ req(input$rules_submit); input$rules_valid })
}

shinyApp(ui, server)
```

## Custom validation rules

`el_rule(validator = JS(...))` is Element's custom rule; `status_icon`
marks each field's verdict.

```{r custom, eval = FALSE, shot = TRUE, shot_js = "var i = document.querySelectorAll('#shot input')[2]; i.value = '17'; i.dispatchEvent(new Event('input')); document.querySelector('#shot .el-button--primary').click();", shot_wait = 2}
ui <- el_page(el_form(id = "account", status_icon = TRUE, label_width = "120px",
  submit_label = "Submit", width = "480px",
  el_form_field("pass", "password", label = "Password",
                rules = el_rule(required = TRUE, message = "Please input the password")),
  el_form_field("check", "password", label = "Confirm",
                rules = el_rule(trigger = "blur", validator = JS(
                  "function(rule, value, callback) {",
                  "  value ? callback() : callback(new Error('Please input the password again'));",
                  "}"))),
  el_form_field("age", "input", label = "Age", rules = el_rule(trigger = "blur", validator = JS(
    "function(rule, value, callback) {",
    "  var n = Number(value);",
    "  if (!value) return callback(new Error('Please input the age'));",
    "  if (isNaN(n)) return callback(new Error('Please input digits'));",
    "  n < 18 ? callback(new Error('Age must be greater than 18')) : callback();",
    "}")))))

shinyApp(ui, function(input, output, session) {})
```

## Delete or add form items dynamically

`update_el_form(fields =)` replaces the field list; what was entered stays.

```{r dynamic, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#more_container button').click()", shot_wait = 1.5}
domain <- function(i) el_form_field(paste0("domain", i), "input", label = paste("Domain", i),
  rules = el_rule(required = TRUE, message = "Domain can not be null"))

ui <- el_page(
  el_form(id = "domains", submit_label = NULL, label_width = "100px", width = "480px",
          el_form_field("email", "input", label = "Email",
                        rules = el_rule(type = "email", message = "Please input a correct email")),
          domain(1)),
  el_button("more", "New domain"), el_button("fewer", "Remove last"))

server <- function(input, output, session) {
  n <- reactiveVal(1)
  redraw <- function() update_el_form(id = "domains", fields = c(
    list(el_form_field("email", "input", label = "Email")), lapply(seq_len(n()), domain)))
  observeEvent(input$more, { n(n() + 1); redraw() })
  observeEvent(input$fewer, { n(max(1, n() - 1)); redraw() })
}

shinyApp(ui, server)
```

## Number validate

```{r number, eval = FALSE, shot = TRUE, shot_js = "var i = document.querySelector('#shot input'); i.value = 'abc'; i.dispatchEvent(new Event('input')); document.querySelector('#shot .el-button--primary').click();", shot_wait = 2}
ui <- el_page(el_form(id = "aged", submit_label = "Submit", label_width = "100px", width = "420px",
  el_form_field("age", "input", label = "Age", rules = list(
    el_rule(required = TRUE, message = "Age is required"),
    el_rule(type = "number", message = "Age must be a number",
            transform = JS("function(v) { return Number(v); }"))))))

shinyApp(ui, function(input, output, session) {})
```

## Size control

`size` sizes every control in the form; a field's own `size` overrides it.

```{r size, eval = FALSE, shot = TRUE}
el_form(id = "small", size = "mini", label_width = "120px", submit_label = "Create", width = "480px",
  el_form_field("name", "input", label = "Activity name"),
  el_form_field("region", "select", label = "Activity zone",
                choices = c("Zone one" = "shanghai", "Zone two" = "beijing")),
  el_form_field("resource", "radio-group", label = "Resources", choices = c("Sponsor", "Venue")))
```

## API

```{r api, echo = FALSE, results = "asis"}
api_tables("form")
```
