---
title: "Form"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Form consists of `input`, `radio`, `select`, `checkbox` and so on. With form, you can collect, verify and submit data.

> **Tip**
>
> The component has been upgraded with a flex layout to replace the old float layout.

## Basic Form

It includes all kinds of input items, such as `input`, `select`, `radio` and `checkbox`.

In each `form` component, you need a `form-item` field to be the container of your input item.

```{r basic-form, eval = FALSE, shot = TRUE}
el_form(
  id = "activity",
  label_width = "120px",
  submit_label = "Create",
  reset_label = "Cancel",
  el_form_field("name", "input", label = "Activity name"),
  el_form_field(
    "region",
    "select",
    label = "Activity zone",
    choices = c("Zone one" = "shanghai", "Zone two" = "beijing"),
    placeholder = "please select your zone"
  ),
  el_form_field(
    "date",
    "date-picker",
    label = "Activity time",
    placeholder = "Pick a date"
  ),
  el_form_field("delivery", "switch", label = "Instant delivery"),
  el_form_field(
    "type",
    "checkbox-group",
    label = "Activity type",
    choices = c(
      "Online activities",
      "Promotion activities",
      "Offline activities"
    )
  ),
  el_form_field(
    "resource",
    "radio-group",
    label = "Resources",
    choices = c("Sponsor", "Venue")
  ),
  el_form_field("desc", "textarea", label = "Activity form")
)
```

> **Tip**
>
> [W3C](https://www.w3.org/MarkUp/html-spec/html-spec_8.html#SEC8.2) regulates that
> 
> > <i>When there is only one single-line text input field in a form, the user agent should accept Enter in that field as a request to submit the form.</i>
> 
> To prevent this behavior, you can add `@submit.prevent` on `<el-form>`.

## Inline Form

When the vertical space is limited and the form is relatively simple, you can put it in one line.

Set the `inline` attribute to `true` and the form will be inline.

```{r inline-form, eval = FALSE, shot = TRUE}
el_form(
  id = "search",
  inline = TRUE,
  submit_label = "Query",
  el_form_field(
    "user",
    "input",
    label = "Approved by",
    placeholder = "Approved by"
  ),
  el_form_field(
    "region",
    "select",
    label = "Activity zone",
    choices = c("Zone one" = "shanghai", "Zone two" = "beijing")
  )
)
```

## Alignment

Depending on your design, there are several different ways to align your label element.

You can set `label-position` of `el-form-item` separately 2.7.7. If the value is empty, the `label-position` of `el-form` is used.

The `label-position` attribute decides how labels align, it can be `top` or `left`. When set to `top`, labels will be placed at the top of the form field.

`label_position` puts the labels `"right"` (the default), `"left"` or on
`"top"`; a field's own `label_position` overrides it.

```{r alignment, eval = FALSE, shot = TRUE}
el_form(
  id = "aligned",
  label_position = "top",
  submit_label = NULL,
  width = "360px",
  el_form_field("name", "input", label = "Name"),
  el_form_field(
    "region",
    "input",
    label = "Activity zone",
    label_position = "right"
  ),
  el_form_field("type", "input", label = "Activity form")
)
```

## Validation

Form component allows you to verify your data, helping you find and correct errors.

Just add the `rules` attribute for `Form` component, pass validation rules, and set `prop` attribute for `FormItem` as a specific key that needs to be validated. See more information at [async-validator](https://github.com/yiminghe/async-validator).

```{r validation, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#shot .el-button--primary').click()"}
ui <- el_page(
  el_form(
    id = "rules",
    label_width = "120px",
    submit_label = "Create",
    reset_label = "Reset",
    el_form_field(
      "name",
      "input",
      label = "Activity name",
      rules = list(
        el_rule(required = TRUE, message = "Please input Activity name"),
        el_rule(min = 3, max = 5, message = "Length should be 3 to 5")
      )
    ),
    el_form_field(
      "region",
      "select",
      label = "Activity zone",
      choices = c("Zone one" = "shanghai", "Zone two" = "beijing"),
      rules = el_rule(
        required = TRUE,
        message = "Please select Activity zone",
        trigger = "change"
      )
    ),
    el_form_field(
      "type",
      "checkbox-group",
      label = "Activity type",
      choices = c("Online activities", "Promotion activities"),
      rules = el_rule(
        type = "array",
        required = TRUE,
        trigger = "change",
        message = "Please select at least one activity type"
      )
    )
  ),
  verbatimTextOutput("verdict")
)

server <- function(input, output, session) {
  output$verdict <- renderPrint({
    req(input$rules_submit)
    input$rules_valid
  })
}

shinyApp(ui, server)
```

## Custom Validation Rules

This example shows how to customize your own validation rules to finish a two-factor password verification.

Here we use `status-icon` to reflect validation result as an icon.

```{r custom-validation, eval = FALSE, shot = TRUE, shot_js = "var i = document.querySelectorAll('#shot input')[2]; i.value = '17'; i.dispatchEvent(new Event('input')); document.querySelector('#shot .el-button--primary').click();", shot_wait = 2}
ui <- el_page(el_form(
  id = "account",
  status_icon = TRUE,
  label_width = "120px",
  submit_label = "Submit",
  width = "480px",
  el_form_field(
    "pass",
    "password",
    label = "Password",
    rules = el_rule(required = TRUE, message = "Please input the password")
  ),
  el_form_field(
    "check",
    "password",
    label = "Confirm",
    rules = el_rule(
      trigger = "blur",
      validator = JS(
        "function(rule, value, callback) {",
        "  value ? callback() : callback(new Error('Please input the password again'));",
        "}"
      )
    )
  ),
  el_form_field(
    "age",
    "input",
    label = "Age",
    rules = el_rule(
      trigger = "blur",
      validator = JS(
        "function(rule, value, callback) {",
        "  var n = Number(value);",
        "  if (!value) return callback(new Error('Please input the age'));",
        "  if (isNaN(n)) return callback(new Error('Please input digits'));",
        "  n < 18 ? callback(new Error('Age must be greater than 18')) : callback();",
        "}"
      )
    )
  )
))

shinyApp(ui, function(input, output, session) {})
```

> **Tip**
>
> Custom validate callback function must be called. See more advanced usage at [async-validator](https://github.com/yiminghe/async-validator).

## Add/Delete Form Item

In addition to passing all validation rules at once on the form component, you can also pass the validation rules or delete rules on a single form field dynamically.

```{r form-items, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#more_container button').click()", shot_wait = 1.5}
domain <- function(i) {
  el_form_field(
    paste0("domain", i),
    "input",
    label = paste("Domain", i),
    rules = el_rule(required = TRUE, message = "Domain can not be null")
  )
}

ui <- el_page(
  el_form(
    id = "domains",
    submit_label = NULL,
    label_width = "100px",
    width = "480px",
    el_form_field(
      "email",
      "input",
      label = "Email",
      rules = el_rule(type = "email", message = "Please input a correct email")
    ),
    domain(1)
  ),
  el_button("more", "New domain"),
  el_button("fewer", "Remove last")
)

server <- function(input, output, session) {
  n <- reactiveVal(1)
  redraw <- function() {
    update_el_form(
      id = "domains",
      fields = c(
        list(el_form_field("email", "input", label = "Email")),
        lapply(seq_len(n()), domain)
      )
    )
  }
  observeEvent(input$more, {
    n(n() + 1)
    redraw()
  })
  observeEvent(input$fewer, {
    n(max(1, n() - 1))
    redraw()
  })
}

shinyApp(ui, server)
```

## Number Validate

Number Validate need a `.number` modifier added on the input `v-model` binding，it's used to transform the string value to the number which is provided by Vue.

```{r number-validate, eval = FALSE, shot = TRUE, shot_js = "var i = document.querySelector('#shot input'); i.value = 'abc'; i.dispatchEvent(new Event('input')); document.querySelector('#shot .el-button--primary').click();", shot_wait = 2}
ui <- el_page(el_form(
  id = "aged",
  submit_label = "Submit",
  label_width = "100px",
  width = "420px",
  el_form_field(
    "age",
    "input",
    label = "Age",
    rules = list(
      el_rule(required = TRUE, message = "Age is required"),
      el_rule(
        type = "number",
        message = "Age must be a number",
        transform = JS("function(v) { return Number(v); }")
      )
    )
  )
))

shinyApp(ui, function(input, output, session) {})
```

> **Tip**
>
> When an `el-form-item` is nested in another `el-form-item`, its label width will be `0`. You can set `label-width` on that `el-form-item` if needed.

## Size Control

All components in a Form inherit their `size` attribute from that Form. Similarly, FormItem also has a `size` attribute.

Still you can fine tune each component's `size` if you don't want that component to inherit its size from From or FormItem.

```{r size-control, eval = FALSE, shot = TRUE}
el_form(
  id = "small",
  size = "small",
  label_width = "120px",
  submit_label = "Create",
  width = "480px",
  el_form_field("name", "input", label = "Activity name"),
  el_form_field(
    "region",
    "select",
    label = "Activity zone",
    choices = c("Zone one" = "shanghai", "Zone two" = "beijing")
  ),
  el_form_field(
    "resource",
    "radio-group",
    label = "Resources",
    choices = c("Sponsor", "Venue")
  )
)
```

## Accessibility

When only a single input (or related control such as select or checkbox) is inside of a `el-form-item`, the form item's label will automatically be attached to that input. However, if multiple inputs are inside of the `el-form-item`, the form item will be assigned the [WAI-ARIA](https://www.w3.org/WAI/standards-guidelines/aria/) role of [group](https://www.w3.org/TR/wai-aria/#group) instead. In this case, it is your responsibility to assign assistive labels to the individual inputs.

Each field's label is tied to its control, so a screen reader announces
it; a field with no label of its own takes `aria_label`.

```{r accessibility, eval = FALSE, shot = TRUE}
el_form(
  id = "a11y",
  label_width = "auto",
  submit_label = NULL,
  width = "480px",
  el_form_field(
    "fullname",
    "input",
    label = "Full name",
    placeholder = "First and last name"
  ),
  el_form_field("email", "input", label = "Email", aria_label = "Email address")
)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("form")
```
