---
title: "Icon"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Element Plus provides a set of common icons: the SVG components of
`@element-plus/icons-vue`, which this package bundles and registers. Each
has a PascalCase name -- `Edit`, `Search`, `CircleCloseFilled` -- and
`el_icon()` draws one by that name. Any component argument that takes an
icon (`icon`, `prefix_icon`, `suffix_icon`, ...) takes the same names.

Element UI's class names still work: `"el-icon-edit"` and `"edit"` are
read as `Edit`, and the few renamed upstream -- `"el-icon-user-solid"` --
as their new names (`UserFilled`).

## Simple Usage

`size` and `color` are `el-icon`'s own props.

```{r simple, eval = FALSE, shot = TRUE}
tagList(
  el_icon("Edit", size = 30),
  el_icon("Edit", size = 30, color = "#409efc")
)
```

## Combined with el-icon

An icon inherits the colour and size of the text around it, unless it is
given its own; `class = "is-loading"` spins it.

```{r combined, eval = FALSE, shot = TRUE}
tags$p(
  style = "font-size: 20px",
  el_icon("Edit", size = 20),
  el_icon("Share", color = "#409efc"),
  el_icon("Delete"),
  el_icon("Loading", class = "is-loading"),
  el_button("search", "Search", type = "primary", icon = "Search")
)
```

## In a Vue template

Inside a component's slot or `template()`, write the icon as Element Plus
does: `<el-icon><Edit /></el-icon>`. Each icon is also registered as
`el-icon-<kebab-name>`, so `<el-icon-edit />` draws the bare SVG.

```{r template, eval = FALSE, shot = TRUE}
el_button(
  "tpl",
  type = "primary",
  slots = list(
    default = template(HTML("<el-icon><Upload /></el-icon><span>Upload</span>"))
  )
)
```

## Other libraries

`el_icon(lib = "font-awesome")` draws a Font Awesome icon instead, through
the fontawesome package.

```{r fa, eval = FALSE, shot = TRUE}
tagList(
  el_icon("r-project", lib = "font-awesome", size = 24),
  el_icon("github", lib = "font-awesome", size = 24)
)
```

## Icon Collection

Every icon of `@element-plus/icons-vue`, by the name `el_icon()` takes:

```{r icons, eval = FALSE, shot = TRUE}
js <- readLines(
  system.file(
    "element-plus",
    "icons-vue.iife.min.js",
    package = "shiny.element"
  ),
  warn = FALSE
)
names <- sort(unique(regmatches(
  js,
  gregexpr('(?<=name:")[A-Z][A-Za-z0-9]*(?=")', js, perl = TRUE)
)[[1]]))
tags$div(
  style = "display: flex; flex-wrap: wrap; border-top: 1px solid var(--el-border-color)",
  lapply(names, function(n) {
    tags$div(
      style = "width: 16.66%; min-width: 110px; height: 90px; text-align: center; font-size: 12px;
             color: var(--el-text-color-regular); border-right: 1px solid var(--el-border-color);
             border-bottom: 1px solid var(--el-border-color); padding-top: 18px",
      el_icon(n, size = 22),
      tags$div(style = "margin-top: 8px", n)
    )
  })
)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("icon")
```
