---
title: "Image"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Besides the native features of img, support lazy load, custom placeholder and load failure, etc.

## Basic Usage

Indicate how the image should be resized to fit its container by `fit`, same as native [object-fit](https://developer.mozilla.org/en-US/docs/Web/CSS/object-fit).

```{r basic-usage, eval = FALSE, shot = TRUE}
url <- "https://fuss10.elemecdn.com/e/5d/4a731a90594a4af544c0c25941171jpeg.jpeg"
tags$div(style = "display: flex; gap: 20px",
  lapply(c("fill", "contain", "cover", "none", "scale-down"), function(f)
    tags$div(style = "text-align: center", tags$div(class = "demonstration", f),
             el_image(src = url, fit = f, alt = f, width = "100px"))))
```

## Placeholder

Custom placeholder content when image hasn't loaded yet by `slot = placeholder`

```{r placeholder, eval = FALSE, shot = TRUE}
src <- "https://cube.elemecdn.com/6/94/4d3ea53c084bad6931a56d5158a48jpeg.jpeg"
tags$div(style = "display: flex; gap: 40px",
  tags$div(tags$div(class = "demonstration", "Default"), el_image(src = src, alt = "Default")),
  tags$div(tags$div(class = "demonstration", "Custom"), el_image(src = src, alt = "Custom",
    slots = list(placeholder = tags$div(class = "image-slot", "Loading", tags$span(class = "dot", "..."))))))
```

## Load Failed

Custom failed content when error occurs to image load by `slot = error` and `slot = viewer-error`.

```{r load-failed, eval = FALSE, shot = TRUE}
tags$div(style = "display: flex; gap: 8px",
  el_image(alt = "Default"),
  el_image(alt = "Custom", slots = list(error = tags$div(class = "image-slot", el_icon("Picture")))))
```

## Lazy Load

> **Tip**
>
> Native `loading` has been supported since 2.2.3, you can use `loading = "lazy"` to replace `lazy = true`.
> 
> If the current browser supports native lazy loading, the native lazy loading will be used first, otherwise will be implemented through scroll.

Use lazy load by `lazy = true`. Image will load until scroll into view when set. You can indicate scroll container that adds scroll listener to by `scroll-container`. If undefined, will be the nearest parent container whose overflow property is auto or scroll.

```{r lazy-load, eval = FALSE, shot = TRUE}
urls <- paste0("https://fuss10.elemecdn.com/", c("a/3f/3302e58f9a181d2509f3dc0fa68b0jpeg.jpeg",
  "1/34/19aa98b1fcb2781c4fba33d850549jpeg.jpeg", "0/6f/e35ff375812e6b0020b6b4e8f9583jpeg.jpeg",
  "9/bb/e27858e973f5d7d3904835f46abbdjpeg.jpeg"))
tags$div(style = "height: 400px; overflow-y: auto",
  lapply(urls, function(u) el_image(src = u, lazy = TRUE, alt = "lazy")))
```

## Image Preview

allow big image preview by setting `previewSrcList` prop. You can initialize the position of the first picture previewed by `initial-index`. The default initial position is 0.

```{r image-preview, eval = FALSE, shot = TRUE}
url <- "https://fuss10.elemecdn.com/a/3f/3302e58f9a181d2509f3dc0fa68b0jpeg.jpeg"
src_list <- paste0("https://fuss10.elemecdn.com/", c("a/3f/3302e58f9a181d2509f3dc0fa68b0jpeg.jpeg",
  "1/34/19aa98b1fcb2781c4fba33d850549jpeg.jpeg", "0/6f/e35ff375812e6b0020b6b4e8f9583jpeg.jpeg"))
el_image(src = url, alt = "preview", fit = "cover", width = "100px", zoom_rate = 1.2,
         max_scale = 7, min_scale = 0.2, preview_src_list = src_list, initial_index = 1)
```

## Manually Open Preview

`el_call(session, "pic", "showPreview")` opens the preview from the server;
`el_image_viewer()` is the viewer alone, opened with `update_el_image_viewer()`.

```{r manually-preview, eval = FALSE, shot = TRUE}
url <- "https://fuss10.elemecdn.com/a/3f/3302e58f9a181d2509f3dc0fa68b0jpeg.jpeg"
tagList(
  el_image("pic", src = url, alt = "preview", width = "100px", preview_src_list = list(url)),
  el_image_viewer("viewer", url_list = c(url)))
```

## Custom Toolbar

Custom toolbar content by `toolbar` slot, starting from version 2.9.7, the slot has a new `setActiveItem` function, which can be switched according to the index.

```{r custom-toolbar, eval = FALSE, shot = TRUE}
src_list <- paste0("https://fuss10.elemecdn.com/", c("a/3f/3302e58f9a181d2509f3dc0fa68b0jpeg.jpeg",
  "1/34/19aa98b1fcb2781c4fba33d850549jpeg.jpeg"))
el_image(src = src_list[1], alt = "preview", fit = "cover", width = "100px",
  preview_src_list = src_list, show_progress = TRUE,
  slots = list(toolbar = template(htmltools::HTML(paste0(
    "<el-icon @click=\"prev\"><Back /></el-icon>",
    "<el-icon @click=\"next\"><Right /></el-icon>",
    "<el-icon @click=\"setActiveItem(0)\"><DArrowLeft /></el-icon>",
    "<el-icon @click=\"actions('zoomOut')\"><ZoomOut /></el-icon>",
    "<el-icon @click=\"actions('zoomIn')\"><ZoomIn /></el-icon>")),
    slot = "toolbar", scope = "{ actions, prev, next, setActiveItem }")))
```

## Custom progress

By setting the `show-progress` prop to control whether to display progress when previewing an image. After version 2.9.8, the progress content will be displayed as long as the `progress` slot is used.

```{r custom-progress, eval = FALSE, shot = TRUE}
src_list <- paste0("https://fuss10.elemecdn.com/", c("a/3f/3302e58f9a181d2509f3dc0fa68b0jpeg.jpeg",
  "1/34/19aa98b1fcb2781c4fba33d850549jpeg.jpeg"))
el_image(src = src_list[1], alt = "preview", fit = "cover", width = "100px",
  preview_src_list = src_list,
  slots = list(progress = template(htmltools::HTML(
    "<span>{{ activeIndex + 1 }} / {{ total }}</span>"),
    slot = "progress", scope = "{ activeIndex, total }")))
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("image")
```
