---
title: "Input"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Input data using mouse or keyboard.

## Basic usage

```{r basic, eval = FALSE, shot = TRUE}
el_input("in_basic", placeholder = "Please input", width = "240px")
```

## Disabled

Disable the Input with the `disabled` attribute.

```{r disabled, eval = FALSE, shot = TRUE}
el_input("in_dis", placeholder = "Please input", disabled = TRUE, width = "240px")
```

## Clearable

Make the Input clearable with the `clearable` attribute. After version 2.13.4, the clearable feature is also available for textarea type of Input.

```{r clearable, eval = FALSE, shot = TRUE}
el_input("in_clear", placeholder = "Please input", clearable = TRUE, width = "240px")
```

## Custom Clear Icon

You can customize the clear icon by setting the `clear-icon` attribute.

```{r clear-icon, eval = FALSE, shot = TRUE}
el_input("in_clear_icon", placeholder = "Please input", clearable = TRUE, clear_icon = "CloseBold",
         width = "240px")
```

## Formatter

Display value within it's situation with `formatter`, and we usually use `parser` at the same time.

`formatter` shows the value its way; `parser` reads it back.

```{r formatter, eval = FALSE, shot = TRUE}
el_input("in_fmt", placeholder = "Please input", width = "240px",
  formatter = JS("function(value) { return `$ ${value}`.replace(/\\B(?=(\\d{3})+(?!\\d))/g, ','); }"),
  parser = JS("function(value) { return value.replace(/\\$\\s?|(,*)/g, ''); }"))
```

## Password box

Make a toggle-able password Input with the `show-password` attribute. Since 2.13.6, the `password-icon` slot is supported to override the default icon.

```{r password, eval = FALSE, shot = TRUE}
el_input("in_pass", type = "password", placeholder = "Please input password",
         show_password = TRUE, width = "240px")
```

## Input with icon

Add an icon to indicate input type.

To add icons in Input, you can simply use `prefix-icon` and `suffix-icon` attributes. Also, the `prefix` and `suffix` named slots works as well.

```{r with-icon, eval = FALSE, shot = TRUE}
tags$div(style = "display: flex; gap: 16px",
  el_input("in_suffix", placeholder = "Pick a date", suffix_icon = "Calendar", width = "240px"),
  el_input("in_prefix", placeholder = "Type something", prefix_icon = "Search", width = "240px"))
```

## Textarea

Resizable for entering multiple lines of text information. Add attribute `type="textarea"` to change `input` into native `textarea`.

Control the height by setting the `rows` prop.

```{r textarea, eval = FALSE, shot = TRUE}
el_input("in_area", type = "textarea", rows = 2, placeholder = "Please input", width = "240px")
```

## Autosize Textarea

Setting the `autosize` prop for a textarea type of Input makes the height to automatically adjust based on the content. An options object can be provided to `autosize` to specify the minimum and maximum number of lines the textarea can automatically adjust.

```{r auto-sizing-textarea, eval = FALSE, shot = TRUE}
tagList(
  el_input("in_auto1", type = "textarea", autosize = TRUE, placeholder = "Please input", width = "240px"),
  tags$div(style = "margin: 20px 0"),
  el_input("in_auto2", type = "textarea", autosize = list(minRows = 2, maxRows = 4),
           placeholder = "Please input", width = "240px"))
```

## Mixed input

Prepend or append an element, generally a label or a button.

Use `slot` to distribute elements that prepend or append to Input.

```{r mixed-input, eval = FALSE, shot = TRUE}
tags$div(style = "display: grid; gap: 16px; max-width: 600px",
  el_input("in_pre", placeholder = "Please input", slots = list(prepend = "Http://")),
  el_input("in_app", placeholder = "Please input", slots = list(append = ".com")),
  el_input("in_both", placeholder = "Please input",
           slots = list(prepend = "Http://", append = el_button("in_search", NULL, icon = "Search"))))
```

## Sizes

Add `size` attribute to change the size of Input. In addition to the default size, there are two other options: `large`, `small`.

```{r various-size, eval = FALSE, shot = TRUE}
tags$div(style = "display: flex; gap: 16px",
  el_input("in_l", size = "large", placeholder = "Please Input", width = "240px"),
  el_input("in_d", placeholder = "Please Input", width = "240px"),
  el_input("in_s", size = "small", placeholder = "Please Input", width = "240px"))
```

## Limit length

`maxlength` and `minlength` attributes of input, they declare a limit on the number of characters a user can input. The "number of characters" is measured using JavaScript string length.Setting the `maxlength` prop for a text or textarea type of Input can limit the length of input value, allows you to show word count by setting `show-word-limit` to `true` at the same time. In 2.11.5, You can set `word-limit-position` to `outside` to display the word count outside the input.

```{r length-limiting, eval = FALSE, shot = TRUE}
tagList(
  el_input("in_lim", maxlength = 10, show_word_limit = TRUE, placeholder = "Please input",
           width = "240px"),
  tags$div(style = "margin: 20px 0"),
  el_input("in_lim_area", type = "textarea", maxlength = 30, show_word_limit = TRUE,
           placeholder = "Please input"))
```

## Count graphemes

Set `count-graphemes` to calculate text length. If it's set, native `maxlength` and `minlength` won't be used.

`count_graphemes` counts as a reader would: an emoji is one character.

```{r count-graphemes, eval = FALSE, shot = TRUE}
el_input("in_graph", maxlength = 10, show_word_limit = TRUE, width = "240px",
  value = "\U0001F468‍\U0001F469‍\U0001F467",
  count_graphemes = JS("function(value) { return [...new Intl.Segmenter().segment(value)].length; }"))
```

> **Tip**
>
> **Browser Support & Fallback Strategy**
> 
> When using the `count-graphemes` prop, the component employs the following approach:
> 
> - **Primary**: Uses `Intl.Segmenter` API (Chrome 87+, Firefox 125+, Safari 14.1+) for proper grapheme cluster handling. This correctly handles complex emoji, combining marks, and Zero Width Joiner sequences.
> 
> - **Fallback**: Older browsers fall back to `Array.from()` for code-point based iteration. Note that this may split multi-codepoint grapheme sequences (e.g., emoji with skin tone modifiers).
> 
> When implementing your own `count-graphemes` function, consider using `Intl.Segmenter` if you need robust support for complex unicode characters.

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("input")
```
