---
title: "Input"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Input numerical values with a customizable range.

## Basic usage

Bind a variable to `v-model` in `<el-input-number>` element and you are set.

```{r basic, eval = FALSE, shot = TRUE}
el_input_number("num", value = 1, min = 1, max = 10)
```

> **Tip**
>
> When inputting invalid string to the input box, input value will emit `NaN` to the upper layer as result of error

## Disabled

The `disabled` attribute accepts a `boolean`, and if the value is `true`, the component is disabled. If you just need to control the value within a range, you can add `min` attribute to set the minimum value and `max` to set the maximum value. By default, the minimum value is `Number.MIN_SAFE_INTEGER`.

```{r disabled, eval = FALSE, shot = TRUE}
el_input_number("num_dis", value = 1, disabled = TRUE)
```

## Steps

Allows you to define incremental steps.

Add `step` attribute to set the step.

```{r steps, eval = FALSE, shot = TRUE}
el_input_number("num_step", value = 5, step = 2)
```

## Step strictly

The `step-strictly` attribute accepts a `boolean`. if this attribute is `true`, input value can only be multiple of step.

```{r step-strictly, eval = FALSE, shot = TRUE}
el_input_number("num_strict", value = 2, step = 2, step_strictly = TRUE)
```

## Precision

Add `precision` attribute to set the precision of input value.

```{r precision, eval = FALSE, shot = TRUE}
el_input_number("num_prec", value = 1, precision = 2, step = 0.1, max = 10)
```

> **Tip**
>
> The value of `precision` must be a non negative integer and should not be less than the decimal places of `step`.

## Size

Use attribute `size` to set additional sizes with `large` or `small`.

```{r size, eval = FALSE, shot = TRUE}
tags$div(
  style = "display: flex; gap: 16px",
  el_input_number("num_l", value = 1, size = "large"),
  el_input_number("num_d", value = 2),
  el_input_number("num_s", value = 3, size = "small")
)
```

## Controls Position

Set `controls-position` to decide the position of control buttons.

```{r controlled, eval = FALSE, shot = TRUE}
tags$div(
  style = "display: flex; flex-wrap: wrap; align-items: center; gap: 16px",
  lapply(c("large", "default", "small"), function(size) {
    el_input_number(
      paste0("num_ctl_", size),
      value = 1,
      min = 1,
      max = 10,
      controls_position = "right",
      size = size
    )
  })
)
```

## Custom Icon

Use `decrease-icon` and `increase-icon` to set custom icons.

```{r custom, eval = FALSE, shot = TRUE, shot_expect = "document.querySelectorAll('.el-input-number [data-el-icon=Plus]').length === 1"}
el_space(
  direction = "vertical",
  el_space(
    el_input_number("num_custom1", value = 1),
    el_input_number(
      "num_custom2",
      value = 1,
      slots = list(
        `decrease-icon` = el_icon("ArrowDown"),
        `increase-icon` = el_icon("ArrowUp")
      )
    )
  ),
  el_space(
    el_input_number("num_custom3", value = 1, controls_position = "right"),
    el_input_number(
      "num_custom4",
      value = 1,
      controls_position = "right",
      slots = list(
        `decrease-icon` = el_icon("Minus"),
        `increase-icon` = el_icon("Plus")
      )
    )
  )
)
```

## With prefix and suffix

Use the prefix and suffix named slots.

```{r with-prefix-suffix, eval = FALSE, shot = TRUE}
el_space(
  el_input_number(
    "num_pre",
    value = 1,
    min = 1,
    max = 10,
    slots = list(prefix = tags$span("￥"))
  ),
  el_input_number(
    "num_suf",
    value = 1,
    min = 1,
    max = 10,
    slots = list(suffix = tags$span("RMB"))
  )
)
```

> **Tip**
>
> For precision purposes, the input number is limited from [Number.MIN_SAFE_INTEGER](https://developer.mozilla.org/en-US/docs/Web/JavaScript/Reference/Global_Objects/Number/MIN_SAFE_INTEGER) to [Number.MAX_SAFE_INTEGER](https://developer.mozilla.org/en-US/docs/Web/JavaScript/Reference/Global_Objects/Number/MAX_SAFE_INTEGER).

## Formatter

Display the value with `formatter`, and typically use `parser` alongside it.

When `formatter` is set, the inner input `type` changes to `text`, which allows non-numeric characters to be entered. Internally, the component processes input with `Number.parseFloat`: when parsing succeeds, the parsed number is written to `model-value`; when parsing returns `NaN`, `model-value` is set to `null`.

```{r formatter, eval = FALSE, shot = TRUE}
el_input_number(
  "num_fmt",
  value = 10000,
  formatter = JS(
    "function(value) { return `$ ${value}`.replace(/\\B(?=(\\d{3})+(?!\\d))/g, ','); }"
  ),
  parser = JS("function(value) { return value.replace(/\\$\\s?|(,*)/g, ''); }")
)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("input-number")
```
