---
title: "Input"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Input data using mouse or keyboard. `input$<id>` is the text, reported a
quarter-second after the user stops typing, as `textInput()` does.

## Basic usage

```{r basic, eval = FALSE, shot = TRUE}
el_input("text", placeholder = "Please input", width = "240px")
```

## Disabled

```{r disabled, eval = FALSE, shot = TRUE}
el_input("dis", placeholder = "Please input", disabled = TRUE, width = "240px")
```

## Clearable

```{r clearable, eval = FALSE, shot = TRUE}
el_input("clr", value = "Clear me", clearable = TRUE, width = "240px")
```

## Password box

```{r password, eval = FALSE, shot = TRUE}
el_input("pwd", value = "secret", show_password = TRUE, width = "240px")
```

## Input with icon

`prefix_icon` and `suffix_icon` take icon classes; the `prefix` and
`suffix` slots take markup.

```{r icon, eval = FALSE, shot = TRUE}
el_input("ic1", placeholder = "Pick a date", suffix_icon = "el-icon-date", width = "240px")
el_input("ic2", placeholder = "Type something", prefix_icon = "el-icon-search", width = "240px")
el_input("ic3", placeholder = "Slot", width = "240px", slots = list(
  suffix = el$icon("date", class = "el-input__icon")))
```

## Textarea

```{r textarea, eval = FALSE, shot = TRUE}
el_input("ta", type = "textarea", rows = 2, placeholder = "Please input", width = "400px")
```

## Autosize textarea

`autosize` grows the box with its text, between optional row limits.

```{r autosize, eval = FALSE, shot = TRUE}
el_input("as1", type = "textarea", autosize = TRUE, placeholder = "Please input", width = "400px")
tags$div(style = "height: 16px")
el_input("as2", type = "textarea", autosize = list(minRows = 2, maxRows = 4),
         placeholder = "Please input", width = "400px")
```

## Mixed input

The `prepend` and `append` slots put an element before or after the input.

```{r mixed, eval = FALSE, shot = TRUE}
el_input("m1", placeholder = "Please input", width = "420px",
         slots = list(prepend = "Http://"))
tags$div(style = "height: 16px")
el_input("m2", placeholder = "Please input", width = "420px", slots = list(append = ".com"))
tags$div(style = "height: 16px")
el_input("m3", placeholder = "Please input", width = "420px", slots = list(
  append = el$button(slot = "append", icon = "el-icon-search")))
```

## Sizes

```{r sizes, eval = FALSE, shot = TRUE}
tagList(lapply(c("default", "medium", "small", "mini"), function(s)
  el_input(paste0("sz_", s), placeholder = s, size = if (s != "default") s,
           suffix_icon = "el-icon-date", width = "200px")))
```

## Autocomplete

`el_autocomplete()` suggests as the user types, from a list sent with the
page, or -- with `remote = TRUE` -- from the server.

```{r autocomplete, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#shot input').focus()", shot_sel = ".el-autocomplete-suggestion"}
el_autocomplete("rest", placeholder = "Please input", width = "260px",
                suggestions = c("vue", "element", "cooking", "mint-ui", "vuex", "vue-router", "babel"))
```

## Custom template

The `default` slot, scoped with `item`, draws each suggestion.

```{r template, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#shot input').focus()", shot_sel = ".el-autocomplete-suggestion"}
el_autocomplete("tpl", width = "300px", placeholder = "Please input", suggestions = list(
  list(value = "vue", link = "https://github.com/vuejs/vue"),
  list(value = "element", link = "https://github.com/ElemeFE/element"),
  list(value = "vuex", link = "https://github.com/vuejs/vuex")),
  slots = list(default = template(
    tags$div(style = "line-height: 1.2; padding: 6px 0",
      tags$div("{{ item.value }}"),
      tags$span(style = "font-size: 12px; color: #b4b4b4", "{{ item.link }}")),
    scope = "{ item }")))
```

## Remote search

```{r remote, eval = FALSE, shot = TRUE, shot_js = "var i = document.querySelector('#shot input'); i.focus(); i.value = 'sh'; i.dispatchEvent(new Event('input'));", shot_sel = ".el-autocomplete-suggestion", shot_wait = 2}
ui <- el_page(el_autocomplete("state", remote = TRUE, placeholder = "A state", width = "260px"))

server <- function(input, output, session) {
  observeEvent(input$state_query, {
    hits <- grep(input$state_query, state.name, ignore.case = TRUE, value = TRUE)
    update_el_autocomplete(id = "state", suggestions = head(hits, 8))
  })
}

shinyApp(ui, server)
```

## Limit length

```{r limit, eval = FALSE, shot = TRUE}
el_input("lim1", value = "Hello", maxlength = 10, show_word_limit = TRUE, width = "300px")
tags$div(style = "height: 16px")
el_input("lim2", type = "textarea", maxlength = 30, show_word_limit = TRUE, width = "300px")
```

## API

```{r api, echo = FALSE, results = "asis"}
api_tables("input")
```
