---
title: "InputTag"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

The InputTag component allows users to add content as tags.

## Basic Usage

Press the Enter key to add the input as a tag.

```{r basic, eval = FALSE, shot = TRUE}
el_input_tag(
  "tags",
  placeholder = "Please input",
  aria_label = "Please click the Enter key after input"
)
```

## Custom Trigger

You can customize the key used to trigger the input tag. The default key is Enter.

The segmented control sets the key that makes a tag, with
`update_el_input_tag(trigger =)`.

```{r trigger, eval = FALSE, shot = TRUE, shot_js = c("Array.from(document.querySelectorAll('#tags_key .el-segmented__item')).find(function(i) { return i.innerText.trim() === 'Enter'; }).click()", "var i = document.querySelector('#tags_trigger input'); i.value = 'one'; i.dispatchEvent(new Event('input')); i.dispatchEvent(new KeyboardEvent('keydown', {key: 'Enter', code: 'Enter', bubbles: true}))"), shot_expect = "document.querySelectorAll('#tags_trigger .el-tag').length === 1"}
ui <- el_page(
  tags$div(
    el_segmented("tags_key", value = "Space", options = c("Enter", "Space"))
  ),
  tags$br(),
  el_input_tag("tags_trigger", trigger = "Space", placeholder = "Please input")
)
server <- function(input, output, session) {
  observeEvent(input$tags_key, ignoreInit = TRUE, {
    update_el_input_tag(session, "tags_trigger", trigger = input$tags_key)
  })
}
shinyApp(ui, server)
```

## Maximum Tags

You can set a limit on the number of tags that can be added.

```{r max, eval = FALSE, shot = TRUE}
el_input_tag("tags_max", max = 3, placeholder = "enter up to 3 tags")
```

## Collapse Tags

Use the collapse tags attribute to merge them into one piece of text. You can use the collapse tags tooltip property to enable the behavior of hovering over collapsed text to display specific selected values. Using the collapse tags tooltip attribute will render the max attribute invalid.

```{r collapse, eval = FALSE, shot = TRUE, shot_expect = "document.querySelectorAll('.el-input-tag')[2].querySelectorAll('.el-tag').length === 4"}
words <- c("tag1", "tag2", "tag3", "tag4", "tag5")
tags$div(
  tags$p("use collapse-tags"),
  el_input_tag(
    "tags_col1",
    value = words,
    collapse_tags = TRUE,
    placeholder = "Please input",
    aria_label = "Please click the Enter key after input"
  ),
  tags$p("use collapse-tags-tooltip"),
  el_input_tag(
    "tags_col2",
    value = words,
    collapse_tags = TRUE,
    collapse_tags_tooltip = TRUE,
    placeholder = "Please input",
    aria_label = "Please click the Enter key after input"
  ),
  tags$p("use max-collapse-tags"),
  el_input_tag(
    "tags_col3",
    value = words,
    collapse_tags = TRUE,
    collapse_tags_tooltip = TRUE,
    max_collapse_tags = 3,
    placeholder = "Please input",
    aria_label = "Please click the Enter key after input"
  )
)
```

## Disabled

You can set the InputTag to be disabled.

```{r disabled, eval = FALSE, shot = TRUE}
el_input_tag(
  "tags_dis",
  value = c("tag1", "tag2", "tag3"),
  disabled = TRUE,
  placeholder = "Please input"
)
```

## Clearable

You can set whether to show the clear button.

```{r clearable, eval = FALSE, shot = TRUE}
el_input_tag(
  "tags_clear",
  value = c("tag1", "tag2", "tag3"),
  clearable = TRUE,
  placeholder = "Please input"
)
```

## Custom Clear Icon

You can customize the clear icon by setting the `clear-icon` attribute.

```{r clear-icon, eval = FALSE, shot = TRUE}
el_input_tag(
  "tags_clear_icon",
  value = c("custom", "clear", "icon"),
  clearable = TRUE,
  clear_icon = "CloseBold",
  placeholder = "Custom clear icon"
)
```

## Draggable

You can set whether tags can be dragged.

```{r draggable, eval = FALSE, shot = TRUE}
el_input_tag(
  "tags_drag",
  value = c("tag1", "tag2", "tag3"),
  draggable = TRUE,
  placeholder = "Please input"
)
```

## Delimiter

You can add a tag when a delimiter is matched.

```{r delimiter, eval = FALSE, shot = TRUE}
el_input_tag(
  "tags_delim",
  draggable = TRUE,
  delimiter = ",",
  placeholder = "Try to separate words with ,"
)
```

## Sizes

Add `size` attribute to change the size of InputTag. In addition to the default size, there are two other options: `large`, `small`.

```{r size, eval = FALSE, shot = TRUE}
tagList(
  el_input_tag("tags_l", size = "large", placeholder = "Please input"),
  tags$br(),
  el_input_tag("tags_d", placeholder = "Please input"),
  tags$br(),
  el_input_tag("tags_s", size = "small", placeholder = "Please input")
)
```

## Custom Tag

You can customize the tag content by `tag` slot.

The segmented controls set the tags' `tag_type` and `tag_effect`, with
`update_el_input_tag()`; the `tag` slot draws each one.

```{r tag, eval = FALSE, shot = TRUE, shot_js = c("Array.from(document.querySelectorAll('#tags_type .el-segmented__item')).find(function(i) { return i.innerText.trim() === 'success'; }).click()", "Array.from(document.querySelectorAll('#tags_effect .el-segmented__item')).find(function(i) { return i.innerText.trim() === 'dark'; }).click()"), shot_expect = c("document.querySelectorAll('#tags_tpl .el-tag--success.el-tag--dark').length === 3", "document.querySelectorAll('#tags_tpl .el-tag [data-el-icon], #tags_tpl .el-tag .el-icon').length >= 3")}
ui <- el_page(
  tags$div(
    style = "display: flex; gap: 20px",
    el_segmented(
      "tags_type",
      value = "primary",
      options = c("primary", "success", "info", "warning", "danger")
    ),
    el_segmented(
      "tags_effect",
      value = "plain",
      options = c("light", "dark", "plain")
    )
  ),
  tags$br(),
  el_input_tag(
    "tags_tpl",
    value = c("tag1", "tag2", "tag3"),
    tag_type = "primary",
    tag_effect = "plain",
    placeholder = "Please input",
    slots = list(
      tag = template(
        slot = "tag",
        scope = "{ value }",
        tags$div(
          style = "display: flex; align-items: center",
          el_icon("ElementPlus", style = "margin-right: 4px"),
          tags$span("{{ value }}")
        )
      )
    )
  )
)
server <- function(input, output, session) {
  observeEvent(input$tags_type, ignoreInit = TRUE, {
    update_el_input_tag(session, "tags_tpl", tag_type = input$tags_type)
  })
  observeEvent(input$tags_effect, ignoreInit = TRUE, {
    update_el_input_tag(session, "tags_tpl", tag_effect = input$tags_effect)
  })
}
shinyApp(ui, server)
```

## Custom Prefix and Suffix

You can customize the prefix and suffix of the InputTag by `prefix` and `suffix` slot.

```{r prefix-suffix, eval = FALSE, shot = TRUE}
el_input_tag(
  "tags_ps",
  clearable = TRUE,
  placeholder = "Please input",
  slots = list(prefix = el_icon("ElementPlus"), suffix = el_icon("Search"))
)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("input-tag")
```
