---
title: "InputOtp"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Used to enter a one-time password (OTP).

## Basic Usage

```{r basic, eval = FALSE, shot = TRUE}
el_input_otp("otp")
```

## Custom Length

The length of the input fields can be customized by setting the `length` prop.

```{r custom-length, eval = FALSE, shot = TRUE}
el_input_otp("otp_len", length = 4)
```

## Types

There are three types available: `outlined` (default), `filled`, and `underlined`.

```{r types, eval = FALSE, shot = TRUE}
tags$div(style = "display: grid; gap: 16px",
  el_input_otp("otp_o", type = "outlined"), el_input_otp("otp_f", type = "filled"),
  el_input_otp("otp_u", type = "underlined"))
```

## Sizes

There are three sizes available: `large`, `default`, and `small`.

```{r sizes, eval = FALSE, shot = TRUE}
tags$div(style = "display: grid; gap: 16px",
  el_input_otp("otp_l", size = "large"), el_input_otp("otp_d"), el_input_otp("otp_s", size = "small"))
```

## Disabled & Readonly

Disabled and readonly states are supported.

```{r disabled, eval = FALSE, shot = TRUE}
el_input_otp("otp_dis", value = "123456", disabled = TRUE)
```

## Mask

Use the `mask` prop to hide the input characters.

```{r mask, eval = FALSE, shot = TRUE}
el_input_otp("otp_mask", mask = TRUE)
```

## Separator

Customize the separator between OTP fields.

```{r separator, eval = FALSE, shot = TRUE}
el_input_otp("otp_sep", separator = "-")
```

## Custom Validation

Set the `validator` prop to validate the input character, and use `inputmode` to specify the keyboard type.

`validator`, a `JS()` function, decides which characters each field takes.

```{r validator, eval = FALSE, shot = TRUE}
el_input_otp("otp_val", validator = JS("function(char) { return /^[0-9]$/.test(char); }"))
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("input-otp")
```
