---
title: "Layout"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Quickly and easily create layouts with the basic 24-column grid:
`el_row()` holds `el_col()`s, each `span`ning some of the 24.


## Basic layout

`span` is how many of the 24 columns a column takes.

```{r basic, eval = FALSE, shot = TRUE}
cell <- function(shade = "#d3dce6") {
  tags$div(style = sprintf("background: %s; border-radius: 4px; min-height: 36px; margin-bottom: 20px", shade))
}
el_row(el_col(span = 24, cell("#99a9bf")))
el_row(el_col(span = 12, cell()), el_col(span = 12, cell("#e5e9f2")))
el_row(el_col(span = 8, cell()), el_col(span = 8, cell("#e5e9f2")), el_col(span = 8, cell()))
el_row(lapply(1:6, function(i) el_col(span = 4, cell(if (i %% 2) "#d3dce6" else "#e5e9f2"))))
```

## Column spacing

`gutter` puts space between the columns, in pixels.

```{r gutter, eval = FALSE, shot = TRUE}
cell <- function() tags$div(style = "background: #d3dce6; border-radius: 4px; min-height: 36px")
el_row(gutter = 20, lapply(1:4, function(i) el_col(span = 6, cell())))
```

## Hybrid layout

Any mix of spans that adds up to 24 in a row.

```{r hybrid, eval = FALSE, shot = TRUE}
cell <- function() tags$div(style = "background: #d3dce6; border-radius: 4px; min-height: 36px; margin-bottom: 20px")
el_row(gutter = 20, el_col(span = 16, cell()), el_col(span = 8, cell()))
el_row(gutter = 20, el_col(span = 8, cell()), el_col(span = 8, cell()),
       el_col(span = 4, cell()), el_col(span = 4, cell()))
el_row(gutter = 20, el_col(span = 4, cell()), el_col(span = 16, cell()), el_col(span = 4, cell()))
```

## Column offset

`offset` moves a column right by that many columns.

```{r offset, eval = FALSE, shot = TRUE}
cell <- function() tags$div(style = "background: #d3dce6; border-radius: 4px; min-height: 36px; margin-bottom: 20px")
el_row(gutter = 20, el_col(span = 6, cell()), el_col(span = 6, offset = 6, cell()))
el_row(gutter = 20, el_col(span = 6, offset = 6, cell()), el_col(span = 6, offset = 6, cell()))
el_row(gutter = 20, el_col(span = 12, offset = 6, cell()))
```

## Alignment

`type = "flex"` lays the row out with flexbox; `justify` places the columns
-- `"start"`, `"center"`, `"end"`, `"space-between"` or `"space-around"`.

```{r align, eval = FALSE, shot = TRUE}
cell <- function(s = "#d3dce6") tags$div(style = sprintf("background: %s; border-radius: 4px; min-height: 36px", s))
rows <- lapply(c("start", "center", "end", "space-between", "space-around"), function(j)
  tags$div(style = "background: #f9fafc; margin-bottom: 20px",
    el_row(type = "flex", justify = j,
      el_col(span = 6, cell()), el_col(span = 6, cell("#e5e9f2")), el_col(span = 6, cell()))))
tagList(rows)
```

## Responsive layout

Five breakpoints, after Bootstrap's: `xs` (<768px), `sm` (≥768px), `md`
(≥992px), `lg` (≥1200px) and `xl` (≥1920px), each a span -- or a list of
`span`, `offset`, `push` and `pull`.

```{r responsive, eval = FALSE, shot = TRUE}
cell <- function(s = "#d3dce6") tags$div(style = sprintf("background: %s; border-radius: 4px; min-height: 36px", s))
el_row(gutter = 10,
  el_col(xs = 8, sm = 6, md = 4, lg = 3, xl = 1, cell()),
  el_col(xs = 4, sm = 6, md = 8, lg = 9, xl = 11, cell("#e5e9f2")),
  el_col(xs = 4, sm = 6, md = 8, lg = 9, xl = 11, cell()),
  el_col(xs = 8, sm = 6, md = 4, lg = 3, xl = 1, cell("#e5e9f2")))
```

## Utility classes for hiding elements

Element's `display.css` is loaded with the package: `hidden-xs-only`,
`hidden-sm-and-up`, `hidden-md-and-down` and the rest hide any tag at
those widths.

```{r hidden, eval = FALSE, shot = TRUE}
tagList(
  tags$div(class = "hidden-sm-and-down", "Shown on a medium screen and wider"),
  tags$div(class = "hidden-md-and-up", "Shown below a medium screen"))
```

The classes, each in `-only`, `-and-up` and `-and-down` forms where they
make sense: `hidden-xs-only`, `hidden-sm-and-up`, `hidden-sm-only`,
`hidden-sm-and-down`, `hidden-md-and-up`, `hidden-md-only`,
`hidden-md-and-down`, `hidden-lg-and-up`, `hidden-lg-only`,
`hidden-lg-and-down`, `hidden-xl-only`.

## API

```{r api, echo = FALSE, results = "asis"}
api_tables("layout")
```
