---
title: "Link"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Text hyperlink

> **Warning**
>
> The `href` prop will be rendered directly to an `<a>` tag. If you pass a value such as `javascript:alert(1)` or a malicious URL, it may cause **XSS** or **open redirect vulnerabilities**.
> 
> Always validate and sanitize the URL before use. For example:
> 
> <details>
> <summary>Show code example</summary>
> 
> 
> 
> </details>

## Basic

Basic text link

```{r basic, eval = FALSE, shot = TRUE}
tags$div(
  style = "display: flex; gap: 16px",
  el_link("default", href = "https://element-plus.org", target = "_blank"),
  lapply(c("primary", "success", "warning", "danger", "info"), function(t) {
    el_link(t, type = t)
  })
)
```

## Disabled

Disabled state of link

```{r disabled, eval = FALSE, shot = TRUE}
tags$div(
  style = "display: flex; gap: 16px",
  lapply(
    c("default", "primary", "success", "warning", "danger", "info"),
    function(t) {
      el_link(t, type = t, disabled = TRUE)
    }
  )
)
```

## Underline

Controlling when underlines should appear

> **Warning**
>
> The `boolean` value has been **deprecated**, and **will be** removed in 3.0.0 , consider switching to new values.

> **Tip**
>
> Starting from 2.9.9 , you can use `'always' | 'hover' | 'never'` to control when underlines should appear. The examples in the document all use these values. If you are using a version **less than** 2.9.9 , please refer to:

```{r underline, eval = FALSE, shot = TRUE}
tags$div(
  style = "display: flex; gap: 16px",
  el_link("default"),
  el_link("always", underline = "always"),
  el_link("hover", underline = "hover"),
  el_link("never", underline = "never")
)
```

## Icon

Link with icon

> **Tip**
>
> Use the `icon` attribute to add icon. You can pass either string for the component name (registered in advance) or the component itself which is a SVG Vue component. Element Plus has provided a set of icon that you can find at [icon](icon.html)

```{r with-icon, eval = FALSE, shot = TRUE}
tags$div(
  style = "display: flex; gap: 16px",
  el_link("Edit", icon = "Edit"),
  el_link(tagList("Check", el_icon("View", class = "el-icon--right")))
)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("link")
```
