---
title: "Loading"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Show animation while loading data.

## Loading inside a container

Displays animation in a container (such as a table) while loading data.

Element Plus provides two ways to invoke Loading: directive and service. For the custom directive `v-loading`, you just need to bind a `boolean` value to it. By default, the loading mask will append to the element where the directive is used. Adding the `body` modifier makes the mask append to the body element.

A table's own `loading` draws Element Plus's mask over it, as `v-loading`
does; `update_el_table(loading =)` turns it on and off.

```{r basic, eval = FALSE, shot = TRUE}
el_table("ld_tbl", loading = TRUE, data = data.frame(
  Date = c("2016-05-02", "2016-05-04", "2016-05-01"), Name = c("John Smith", "John Smith", "John Smith"),
  Address = rep("No.1518,  Jinshajiang Road, Putuo District", 3)))
```

## Customization

You can customize loading text, loading spinner and background color.

Add attribute `element-loading-text` to the element on which `v-loading` is bound, and its value will be displayed under the spinner. Similarly, the `element-loading-spinner / element-loading-svg` and `element-loading-background` attributes are used to set the svg icon, background color value, and loading icon, respectively.

`el_loading()` covers an element of your choice, with your text, spinner
and background.

```{r customization, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#go_container button').click()", shot_wait = 1}
ui <- el_page(
  el_button("go", "Cover the table"),
  tags$div(id = "covered", el_table("ld_tbl2", data = data.frame(Date = "2016-05-02", Name = "John"))))
server <- function(input, output, session) {
  observeEvent(input$go, el_loading(session, "covering", target = "#covered", text = "Loading...",
                                    background = "rgba(122, 122, 122, 0.8)"))
}
shinyApp(ui, server)
```

> **Warning**
>
> Although the `element-loading-spinner / element-loading-svg` attribute supports incoming HTML fragments, it is very dangerous to dynamically render arbitrary HTML on the website, because it is easy to cause [XSS attack](https://en.wikipedia.org/wiki/Cross-site_scripting). Please make sure that the content of `element-loading-spinner / element-loading-svg` is trustworthy. **Never** assign user-submitted content to the `element-loading-spinner / element-loading-svg` attribute.

## Full screen loading

Show a full screen animation while loading data.

When used as a directive, a full screen Loading requires the `fullscreen` modifier, and it will be appended to body. In this case, if you wish to disable scrolling on body, you can add another modifier `lock`. When used as a service, Loading will be full screen by default.

```{r fullscreen, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#full_container button').click()", shot_wait = 1}
ui <- el_page(el_button("full", "As a service", type = "primary"))
server <- function(input, output, session) {
  observeEvent(input$full, {
    el_loading(session, "page", text = "Loading", fullscreen = TRUE, lock = TRUE)
    later::later(function() el_loading_close(session, "page"), 2)
  })
}
shinyApp(ui, server)
```

## Service

You can also invoke Loading with a service. Import Loading service:

Invoke it:

The parameter `options` is the configuration of Loading, and its details can be found in the following table. `LoadingService` returns a Loading instance, and you can close it by invoking its `close` method:

Note that in this case the full screen Loading is singleton. If a new full screen Loading is invoked before an existing one is closed, the existing full screen Loading instance will be returned instead of actually creating another Loading instance:

Calling the `close` method on any one of them can close this full screen Loading.

If Element Plus is imported entirely, a globally method `$loading` will be registered to `app.config.globalProperties`. You can invoke it like this: `this.$loading(options)`, and it also returns a Loading instance.

## App context inheritance

Now loading accepts a `context` as second parameter of the loading constructor which allows you to inject current app's context to loading which allows you to inherit all the properties of the app.

You can use it like this:

> **Tip**
>
> If you globally registered ElLoading component, it will automatically inherit your app context.

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("loading")
```
