---
title: "Mention"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Used to mention someone or something in an input.

## Basic Usage

The most basic usage.

```{r basic, eval = FALSE, shot = TRUE}
el_mention("mention", value = "@", width = "320px", placeholder = "Please input",
           options = c("Fuphoenixes", "kooriookami", "Jeremy", "btea"))
```

## Props

You can customize the alias of the `options` through the `props` attribute.

```{r props, eval = FALSE, shot = TRUE}
el_mention("mention_props", value = "@", width = "320px", placeholder = "Please input",
           props = list(label = "name", value = "id", disabled = "unable"),
           options = list(list(name = "Fuphoenixes", id = "1"), list(name = "kooriookami", id = "2"),
                          list(name = "Jeremy", id = "3", unable = TRUE)))
```

## Textarea

The input type can be set to `textarea`.

```{r textarea, eval = FALSE, shot = TRUE}
el_mention("mention_area", type = "textarea", width = "320px", placeholder = "Please input",
           options = c("Fuphoenixes", "kooriookami", "Jeremy", "btea"))
```

## Customize label

Customize label by `label` slot.

```{r label, eval = FALSE, shot = TRUE}
el_mention("mention_label", width = "320px", placeholder = "Please input",
  options = c("Fuphoenixes", "kooriookami", "Jeremy", "btea"),
  slots = list(label = template(htmltools::HTML(
    "<div style=\"display: flex; align-items: center\"><el-avatar :size=\"24\" style=\"margin-right: 8px\">{{ item.label.charAt(0) }}</el-avatar><span>{{ item.label }}</span></div>"),
    slot = "label", scope = "{ item }")))
```

## Load remote options

Load options asynchronously.

`input$<id>_search` is the text after the trigger, as it is typed; the
server answers with `update_el_mention()` and `loading`.

```{r loading, eval = FALSE, shot = TRUE}
el_mention("mention_load", width = "320px", placeholder = "Please input", loading = TRUE)
```

## Customize trigger token

Customize trigger token by `prefix` props. Default to `@`, `Array<string>` also supported.

```{r prefix, eval = FALSE, shot = TRUE}
el_mention("mention_prefix", width = "320px", placeholder = "Please input",
           prefix = c("@", "#"), options = c("Fuphoenixes", "kooriookami", "Jeremy"))
```

## Delete as a whole

Set the `whole` attribute to `true`, and when you press the backspace, the mention will be deleted as a whole.
Set the `check-is-whole` attribute to customize the checking logic.

```{r whole, eval = FALSE, shot = TRUE}
el_mention("mention_whole", value = "@Fuphoenixes ", whole = TRUE, width = "320px",
           options = c("Fuphoenixes", "kooriookami", "Jeremy"))
```

## Work with form

to work with `el-form`.

```{r form, eval = FALSE, shot = TRUE}
el_form(id = "mention_form", submit_label = "Submit", label_width = "auto", width = "480px",
  el_form_field("message", "input", label = "Message",
                rules = el_rule(required = TRUE, message = "Please input a message")))
```

::: tip
Since this component is developed based on the component [`el-input`](input.html#attributes) , the original properties have not changed, so no repetition here,
and please go to the original component to view the documentation.
:::

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("mention")
```
