---
title: "Menu"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Menu that provides navigation for your website.

::: tip

If you want to override the default height of el-menu, you can use the following CSS:

:::

## Top bar

Top bar Menu can be used in a variety of scenarios.

By default Menu is vertical, but you can change it to horizontal by setting the mode prop to 'horizontal'. In addition, you can use the sub-menu component to create a second level menu. Menu provides `background-color`, `text-color` and `active-text-color` to customize the colors.

```{r basic, eval = FALSE, shot = TRUE}
items <- list(
  list(index = "1", label = "Processing Center"),
  list(index = "2", title = "Workspace", children = list(
    list(index = "2-1", label = "item one"), list(index = "2-2", label = "item two"),
    list(index = "2-3", label = "item three"),
    list(index = "2-4", title = "item four", children = list(
      list(index = "2-4-1", label = "item one"), list(index = "2-4-2", label = "item two"))))),
  list(index = "3", label = "Info", disabled = TRUE),
  list(index = "4", label = "Orders"))
tagList(
  el_menu("top_menu", active = "1", mode = "horizontal", ellipsis = FALSE, items = items),
  tags$div(style = "height: 20px"),
  el_menu("top_menu_dark", active = "1", mode = "horizontal", ellipsis = FALSE,
          background_color = "#545c64", text_color = "#fff", active_text_color = "#ffd04b", items = items))
```

## Left And Right

You can make the menu items to the left or right.

```{r left-and-right, eval = FALSE, shot = TRUE}
el_menu("lr_menu", active = "1", mode = "horizontal", ellipsis = FALSE, items = list(
  list(index = "0", label = "LOGO"),
  list(index = "1", label = "Processing Center"),
  list(index = "2", title = "Workspace", children = list(list(index = "2-1", label = "item one")))))
```

## Side bar

Vertical Menu with sub-menus.

You can use the el-menu-item-group component to create a menu group, and the name of the group is determined by the title prop or a named slot.

```{r vertical, eval = FALSE, shot = TRUE}
items <- list(
  list(index = "1", title = "Navigator One", icon = "Location", children = list(
    list(group = TRUE, title = "Group One", children = list(
      list(index = "1-1", label = "item one"), list(index = "1-2", label = "item two"))),
    list(group = TRUE, title = "Group Two", children = list(list(index = "1-3", label = "item three"))),
    list(index = "1-4", title = "item four", children = list(list(index = "1-4-1", label = "item one"))))),
  list(index = "2", label = "Navigator Two", icon = "Menu"),
  list(index = "3", label = "Navigator Three", icon = "Document", disabled = TRUE),
  list(index = "4", label = "Navigator Four", icon = "Setting"))
el_row(
  el_col(span = 12, tags$h5("Default colors"), el_menu("v_menu", active = "2", items = items)),
  el_col(span = 12, tags$h5("Custom colors"), el_menu("v_menu_dark", active = "2", items = items,
    background_color = "#545c64", text_color = "#fff", active_text_color = "#ffd04b")))
```

## Collapse

Vertical Menu could be collapsed.

```{r collapse, eval = FALSE, shot = TRUE}
el_menu("col_menu", active = "2", collapse = TRUE, items = list(
  list(index = "1", title = "Navigator One", icon = "Location", children = list(
    list(index = "1-1", label = "item one"), list(index = "1-2", label = "item two"))),
  list(index = "2", label = "Navigator Two", icon = "Menu"),
  list(index = "3", label = "Navigator Three", icon = "Document"),
  list(index = "4", label = "Navigator Four", icon = "Setting")))
```

## Popper Offset

Submenu with popperOffset will override Menu's `popper-offset`.

```{r popper-offset, eval = FALSE, shot = TRUE}
el_menu("off_menu", mode = "horizontal", popper_offset = 16, ellipsis = FALSE, items = list(
  list(index = "1", label = "Processing Center"),
  list(index = "2", title = "Workspace", popper_offset = 8, children = list(
    list(index = "2-1", label = "item one"), list(index = "2-2", label = "item two")))))
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("menu")
```
