---
title: "NavMenu"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Menu that provides navigation for your website. `items` nests to any
depth: an item is `list(index =, label =, icon =)`, with `children` it is a
submenu, and with `group = TRUE` a group. `input$<id>` is the index
chosen, `input$<id>_path` the indexes down to it; `active` is the current
item, and `update_el_menu()` moves it.

## Top bar

```{r top, eval = FALSE, shot = TRUE}
items <- list(
  list(index = "1", label = "Processing Center"),
  list(index = "2", label = "Workspace", children = list(
    list(index = "2-1", label = "item one"), list(index = "2-2", label = "item two"),
    list(index = "2-4", label = "item four", children = list(
      list(index = "2-4-1", label = "item one"), list(index = "2-4-2", label = "item two"))))),
  list(index = "3", label = "Info", disabled = TRUE),
  list(index = "4", label = "Orders"))
el_menu("top", mode = "horizontal", active = "1", items = items)
tags$div(style = "height: 20px")
el_menu("dark", mode = "horizontal", active = "1", items = items,
        background_color = "#545c64", text_color = "#fff", active_text_color = "#ffd04b")
```

## Side bar

```{r side, eval = FALSE, shot = TRUE}
el_menu("side", active = "2", width = "240px", items = list(
  list(index = "1", label = "Navigator One", icon = "el-icon-location", children = list(
    list(label = "Group One", group = TRUE, children = list(
      list(index = "1-1", label = "item one"), list(index = "1-2", label = "item two"))),
    list(index = "1-4", label = "item four", children = list(list(index = "1-4-1", label = "item one"))))),
  list(index = "2", label = "Navigator Two", icon = "el-icon-menu"),
  list(index = "3", label = "Navigator Three", icon = "el-icon-document", disabled = TRUE),
  list(index = "4", label = "Navigator Four", icon = "el-icon-setting")))
```

## Collapse

`collapse` folds a vertical menu to its icons; `update_el_menu(collapse =)`
toggles it.

```{r collapse, eval = FALSE, shot = TRUE, shot_js = "document.querySelectorAll('#fold_container .el-radio-button')[1].click()", shot_wait = 1.5}
ui <- el_page(
  el_radio_group("fold", choices = c(expand = "open", collapse = "fold"), selected = "open", button = TRUE),
  el_menu("nav", active = "2", items = list(
    list(index = "1", label = "Navigator One", icon = "el-icon-location", children = list(
      list(index = "1-1", label = "item one"))),
    list(index = "2", label = "Navigator Two", icon = "el-icon-menu"),
    list(index = "4", label = "Navigator Four", icon = "el-icon-setting"))))

server <- function(input, output, session) {
  observeEvent(input$fold, update_el_menu(id = "nav", collapse = input$fold == "fold"))
}

shinyApp(ui, server)
```

## API

```{r api, echo = FALSE, results = "asis"}
api_tables("menu")
```
