---
title: "Message"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

A set of modal boxes simulating system message box, mainly for alerting information, confirm operations and prompting messages.

> **Tip**
>
> By design MessageBox provides simulations of system's `alert`, `confirm` and `prompt`，so it's content should be simple. For more complicated contents, please use Dialog.

## Alert

Alert interrupts user operation until the user confirms.

Open an alert by calling the `ElMessageBox.alert` method. It simulates the system's `alert`, and cannot be closed by pressing ESC or clicking outside the box. In this example, two parameters `message` and `title` are received. It is worth mentioning that when the box is closed, it returns a `Promise` object for further processing. If you are not sure if your target browsers support `Promise`, you should import a third party polyfill or use callbacks instead like this example.

The answer is `input$<id>`: `"confirm"`, `"cancel"` or `"close"`.

```{r alert, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#open_container button').click()", shot_sel = ".el-message-box", shot_wait = 1}
ui <- el_page(el_button("open", "Click to open the Message Box", plain = TRUE))
server <- function(input, output, session) {
  observeEvent(
    input$open,
    el_message_box(
      session,
      "answer",
      "This is a message",
      title = "Title",
      box_type = "alert",
      confirm_button_text = "OK"
    )
  )
}
shinyApp(ui, server)
```

## Confirm

Confirm is used to ask users' confirmation.

Call `ElMessageBox.confirm` method to open a confirm, and it simulates the system's `confirm`. We can also highly customize Message Box by passing a third attribute `options` which is a literal object. The attribute `type` indicates the message type, and it's value can be `primary`, `success`, `error`, `info` and `warning`. Note that the second attribute `title` must be a `string`, and if it is an `object`, it will be handled as the attribute `options`. Here we use `Promise` to handle further processing. `primary` has been added in 2.9.11.

```{r confirm, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#open_container button').click()", shot_sel = ".el-message-box", shot_wait = 1}
ui <- el_page(el_button("open", "Click to open the Message Box", plain = TRUE))
server <- function(input, output, session) {
  observeEvent(
    input$open,
    el_message_box(
      session,
      "answer",
      "proxy will permanently delete the file. Continue?",
      title = "Warning",
      type = "warning",
      confirm_button_text = "OK",
      cancel_button_text = "Cancel"
    )
  )
  observeEvent(
    input$answer,
    el_message(session, paste("Answer:", input$answer))
  )
}
shinyApp(ui, server)
```

## Prompt

Prompt is used when user input is required.

Call `ElMessageBox.prompt` method to open a prompt, and it simulates the system's `prompt`. You can use `inputPattern` parameter to specify your own RegExp pattern. Use `inputValidator` to specify validation method, and it should return `Boolean` or `String`. Returning `false` or `String` means the validation has failed, and the string returned will be used as the `inputErrorMessage`. In addition, you can customize the placeholder of the input box with `inputPlaceholder` parameter.

```{r prompt, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#open_container button').click()", shot_sel = ".el-message-box", shot_wait = 1}
ui <- el_page(el_button("open", "Click to open Message Box", plain = TRUE))
server <- function(input, output, session) {
  observeEvent(
    input$open,
    el_message_box(
      session,
      "email",
      "Please input your e-mail",
      title = "Tip",
      box_type = "prompt",
      confirm_button_text = "OK",
      cancel_button_text = "Cancel",
      input_pattern = "[\\w!#$%&'*+/=?^_`{|}~-]+(?:\\.[\\w!#$%&'*+/=?^_`{|}~-]+)*@(?:[\\w](?:[\\w-]*[\\w])?\\.)+[\\w](?:[\\w-]*[\\w])?",
      input_error_message = "Invalid Email"
    )
  )
}
shinyApp(ui, server)
```

## Use VNode

`message` can be VNode.

A message can be a VNode, built in the browser: give it as `JS()` code
calling `Vue.h()`. One with props that change -- the switch -- is a
function returning the VNode, as upstream says.

```{r use-vnode, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#open_container button').click()", shot_sel = ".el-message-box", shot_wait = 1}
ui <- el_page(
  el_button("open", "Common VNode", plain = TRUE),
  el_button("open1", "Dynamic props", plain = TRUE)
)
server <- function(input, output, session) {
  observeEvent(input$open, {
    el_message_box(
      session,
      "vn",
      JS(
        "Vue.h('p', null, [
          Vue.h('span', null, 'Message can be '),
          Vue.h('i', { style: 'color: teal' }, 'VNode')
        ])"
      ),
      title = "Message",
      box_type = "alert"
    )
  })
  observeEvent(input$open1, {
    el_message_box(
      session,
      "vn1",
      JS(
        "(function() {
          var checked = Vue.ref(false);
          return function() {
            return Vue.h(ElementPlus.ElSwitch, {
              modelValue: checked.value,
              'onUpdate:modelValue': function(v) { checked.value = v; }
            });
          };
        })()"
      ),
      title = "Message",
      box_type = "alert"
    )
  })
}
shinyApp(ui, server)
```

## Use VNode With Action Handlers

You can receive `{ confirm, cancel, close }` as parameters in `message`, which allows custom content to trigger the same MessageBox actions programmatically and automatically close the instance.

A function message is handed the box's own actions, `confirm`, `cancel`
and `close`, for buttons of its own. The answer reaches the server as
`input$handled`, as for any message box.

```{r use-vnode-with-action-handlers, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#open_container button').click()", shot_sel = ".el-message-box", shot_wait = 1}
ui <- el_page(el_button("open", "Click to open Message Box", plain = TRUE))
server <- function(input, output, session) {
  observeEvent(input$open, {
    el_message_box(
      session,
      "handled",
      JS(
        "function({ confirm, cancel, close }) {
          var button = function(props, text) {
            return Vue.h(ElementPlus.ElButton, props, function() { return text; });
          };
          return Vue.h('div', [
            Vue.h('p', { style: 'margin-bottom: 8px' },
              'Custom buttons with MessageBox action handlers'),
            button({ type: 'primary', onClick: function() { confirm(); } }, 'Resolve'),
            button({ type: 'danger', onClick: function() { cancel(); } }, 'Reject'),
            button({ onClick: function() { close(); } }, 'Close')
          ]);
        }"
      ),
      title = "Message",
      show_confirm_button = FALSE,
      show_cancel_button = FALSE,
      distinguish_cancel_and_close = TRUE
    )
  })
  observeEvent(
    input$handled,
    el_message(session, paste("Answer:", input$handled))
  )
}
shinyApp(ui, server)
```

## Customization

Can be customized to show various content.

The three methods mentioned above are repackagings of the `ElMessageBox` method. This example calls `ElMessageBox` method directly using the `showCancelButton` attribute, which is used to indicate if a cancel button is displayed. Besides we can use `cancelButtonClass` to add a custom style and `cancelButtonText` to customize the button text (the confirm button also has these fields, and a complete list of fields can be found at the end of this documentation). This example also uses the `beforeClose` attribute. It is a method and will be triggered when the MessageBox instance will be closed, and its execution will stop the instance from closing. It has three parameters: `action`, `instance` and `done`. Using it enables you to manipulate the instance before it closes, e.g. activating `loading` for confirm button; you can invoke the `done` method to close the MessageBox instance (if `done` is not called inside `beforeClose`, the instance will not be closed).

```{r customization, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#open_container button').click()", shot_sel = ".el-message-box", shot_wait = 1}
ui <- el_page(el_button("open", "Click to open Message Box", plain = TRUE))
server <- function(input, output, session) {
  observeEvent(
    input$open,
    el_message_box(
      session,
      "answer",
      "This is a message",
      title = "Title",
      show_cancel_button = TRUE,
      confirm_button_text = "OK",
      cancel_button_text = "Cancel",
      confirm_button_type = "danger",
      button_size = "small"
    )
  )
}
shinyApp(ui, server)
```

## Use HTML String

`message` supports HTML string.

Set `dangerouslyUseHTMLString` to true and `message` will be treated as an HTML string.

```{r use-html, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#open_container button').click()", shot_sel = ".el-message-box", shot_wait = 1}
ui <- el_page(el_button("open", "Click to open Message Box", plain = TRUE))
server <- function(input, output, session) {
  observeEvent(
    input$open,
    el_message_box(
      session,
      "answer",
      "<strong>proxy is <i>HTML</i> string</strong>",
      title = "HTML String",
      box_type = "alert",
      dangerously_use_html_string = TRUE
    )
  )
}
shinyApp(ui, server)
```

> **Warning**
>
> Although `message` property supports HTML strings, dynamically rendering arbitrary HTML on your website can be very dangerous because it can easily lead to [XSS attacks](https://en.wikipedia.org/wiki/Cross-site_scripting). So when `dangerouslyUseHTMLString` is on, please make sure the content of `message` is trusted, and **never** assign `message` to user-provided content.

## Distinguishing cancel and close

In some cases, clicking the cancel button and close button may have different meanings.

By default, the parameters of Promise's reject callback and `callback` are 'cancel' when the user cancels (clicking the cancel button) and closes (clicking the close button or mask layer, pressing the ESC key) the MessageBox. If `distinguishCancelAndClose` is set to true, the parameters of the above two operations are 'cancel' and 'close' respectively.

```{r distinguishable-close-cancel, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#open_container button').click()", shot_sel = ".el-message-box", shot_wait = 1}
ui <- el_page(el_button("open", "Click to open Message Box", plain = TRUE))
server <- function(input, output, session) {
  observeEvent(
    input$open,
    el_message_box(
      session,
      "answer",
      "You have unsaved changes, save and proceed?",
      title = "Confirm",
      distinguish_cancel_and_close = TRUE,
      confirm_button_text = "Save",
      cancel_button_text = "Discard Changes"
    )
  )
}
shinyApp(ui, server)
```

## Centered content

Content of MessageBox can be centered.

Setting `center` to `true` will center the content.

```{r centered-content, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#open_container button').click()", shot_sel = ".el-message-box", shot_wait = 1}
ui <- el_page(el_button("open", "Click to open Message Box", plain = TRUE))
server <- function(input, output, session) {
  observeEvent(
    input$open,
    el_message_box(
      session,
      "answer",
      "proxy will permanently delete the file. Continue?",
      title = "Warning",
      type = "warning",
      center = TRUE,
      confirm_button_text = "OK",
      cancel_button_text = "Cancel"
    )
  )
}
shinyApp(ui, server)
```

## Customized Icon

The icon can be customized to any Vue component or [render function (JSX)](https://vuejs.org/guide/extras/render-function.html).

```{r customized-icon, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#open_container button').click()", shot_sel = ".el-message-box", shot_wait = 1}
ui <- el_page(el_button("open", "Click to open Message Box", plain = TRUE))
server <- function(input, output, session) {
  observeEvent(
    input$open,
    el_message_box(
      session,
      "answer",
      "Are you sure to delete this?",
      title = "Warning",
      type = "warning",
      icon = "Delete",
      confirm_button_text = "OK",
      cancel_button_text = "Cancel"
    )
  )
}
shinyApp(ui, server)
```

## Draggable

MessageBox can be draggable.

Setting `draggable` to `true` allows user to drag MessageBox. Set `overflow` 2.5.4 to `true` can drag overflow the viewport.

```{r draggable, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#open_container button').click()", shot_sel = ".el-message-box", shot_wait = 1}
ui <- el_page(el_button("open", "Click to open Message Box", plain = TRUE))
server <- function(input, output, session) {
  observeEvent(
    input$open,
    el_message_box(
      session,
      "answer",
      "proxy will permanently delete the file. Continue?",
      title = "Warning",
      type = "warning",
      draggable = TRUE,
      confirm_button_text = "OK",
      cancel_button_text = "Cancel"
    )
  )
}
shinyApp(ui, server)
```

## Global method

If Element Plus is fully imported, it will add the following global methods for `app.config.globalProperties`: `$msgbox`, `$alert`, `$confirm` and `$prompt`. So in a Vue instance you can call `MessageBox` like what we did in this page. The parameters are:

- `$msgbox(options)`
- `$alert(message, title, options)` or `$alert(message, options)`
- `$confirm(message, title, options)` or `$confirm(message, options)`
- `$prompt(message, title, options)` or `$prompt(message, options)`

## App context inheritance > 2.0.4

Now message box accepts a `context` as second (fourth if you are using message box variants) parameter of the message constructor which allows you to inject current app's context to message which allows you to inherit all the properties of the app.

## Local import

If you prefer importing `MessageBox` on demand:

The corresponding methods are: `ElMessageBox`, `ElMessageBox.alert`, `ElMessageBox.confirm` and `ElMessageBox.prompt`. The parameters are the same as above.

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("message-box")
```
