---
title: "Message"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Used to show feedback after an activity. The difference with Notification is that the latter is often used to show a system level passive notification.

## Basic usage

Displays at the top by default, and disappears after 3 seconds. You can control the position using the `placement` property.

The setup of Message is very similar to notification, so parts of the options won't be explained in detail here. You can check the options table below combined with notification doc to understand it. Element Plus has registered a `$message` method for invoking. Message can take a string or a VNode as parameter, and it will be shown as the main body.

Messages are sent from the server, `el_message(session, ...)`.

```{r basic, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#show_container button').click()", shot_sel = ".el-message", shot_wait = 1}
ui <- el_page(el_button("show", "Show message", plain = TRUE))
server <- function(input, output, session) {
  observeEvent(input$show, el_message(session, "This is a message."))
}
shinyApp(ui, server)
```

## Types

Used to show the feedback of Primary, Success, Warning, Info and Error activities.

When you need more customizations, Message component can also take an object as parameter. For example, setting value of `type` can define different types, and its default is `info`. In such cases the main body is passed in as the value of `message`. Also, we have registered methods for different types, so you can directly call it without passing a type like `open4`. `primary` has been added in 2.9.11.

```{r different-types, eval = FALSE, shot = TRUE, shot_js = "document.querySelectorAll('#shot button').forEach(function(b){ b.click(); })", shot_sel = ".el-message", shot_wait = 1}
types <- c("primary", "success", "warning", "info", "error")
ui <- el_page(lapply(types, function(t) el_button(paste0("m_", t), tools::toTitleCase(t), plain = TRUE)))
server <- function(input, output, session) {
  for (t in types) local({
    t <- t
    observeEvent(input[[paste0("m_", t)]],
                 el_message(session, paste("Congrats, this is a", t, "message."), type = t))
  })
}
shinyApp(ui, server)
```

## Plain

Set `plain` to have a plain background.

```{r plain, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#show_container button').click()", shot_sel = ".el-message", shot_wait = 1}
ui <- el_page(el_button("show", "Success", plain = TRUE))
server <- function(input, output, session) {
  observeEvent(input$show, el_message(session, "Congrats, this is a success message.",
                                      type = "success", plain = TRUE))
}
shinyApp(ui, server)
```

## Closable

A close button can be added.

A default Message cannot be closed manually. If you need a closable message, you can set `showClose` field. Besides, same as notification, message has a controllable `duration`. Default duration is 3000 ms, and it won't disappear when set to `0`.

```{r closable, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#show_container button').click()", shot_sel = ".el-message", shot_wait = 1}
ui <- el_page(el_button("show", "Message", plain = TRUE))
server <- function(input, output, session) {
  observeEvent(input$show, el_message(session, "This is a message.", show_close = TRUE, duration = 0))
}
shinyApp(ui, server)
```

## Use HTML string

`message` supports HTML string.

Set `dangerouslyUseHTMLString` to true and `message` will be treated as an HTML string.

```{r raw-html, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#show_container button').click()", shot_sel = ".el-message", shot_wait = 1}
ui <- el_page(el_button("show", "Use HTML String", plain = TRUE))
server <- function(input, output, session) {
  observeEvent(input$show, el_message(session, "<strong>This is <i>HTML</i> string</strong>",
                                      dangerously_use_html_string = TRUE))
}
shinyApp(ui, server)
```

> **Warning**
>
> Although `message` property supports HTML strings, dynamically rendering arbitrary HTML on your website can be very dangerous because it can easily lead to [XSS attacks](https://en.wikipedia.org/wiki/Cross-site_scripting). So when `dangerouslyUseHTMLString` is on, please make sure the content of `message` is trusted, and **never** assign `message` to user-provided content.

## Grouping

merge messages with the same content.

Set `grouping` to true and the same content of `message` will be merged.

```{r grouping, eval = FALSE, shot = TRUE, shot_js = "var b = document.querySelector('#show_container button'); b.click(); b.click(); b.click();", shot_sel = ".el-message", shot_wait = 1}
ui <- el_page(el_button("show", "Show grouping message", plain = TRUE))
server <- function(input, output, session) {
  observeEvent(input$show, el_message(session, "This is a message", grouping = TRUE,
                                      type = "success"))
}
shinyApp(ui, server)
```

## Placement

Control the position where messages appear. Messages can be displayed at the top (default) or other placements of the viewport.

```{r placement, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#show_container button').click()", shot_sel = ".el-message", shot_wait = 1}
ui <- el_page(el_button("show", "Bottom", plain = TRUE))
server <- function(input, output, session) {
  observeEvent(input$show, el_message(session, "This is a message at the bottom", placement = "bottom"))
}
shinyApp(ui, server)
```

## Global method

Element Plus has added a global method `$message` for `app.config.globalProperties`. So in a vue instance you can call `Message` like what we did in this page.

## Local import

In this case you should call `ElMessage(options)`. We have also registered methods for different types, e.g. `ElMessage.success(options)`. You can call `ElMessage.closeAll()` to manually close all the instances.

## App context inheritance

Now message accepts a `context` as second parameter of the message constructor which allows you to inject current app's context to message which allows you to inherit all the properties of the app.

You can use it like this:

> **Tip**
>
> If you globally registered ElMessage component, it will automatically inherit your app context.

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("message")
```
