---
title: "Notification"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Displays a global notification message at a corner of the page.

## Basic usage

Element Plus has registered the `$notify` method and it receives an object as its parameter. In the simplest case, you can set the `title` field and the` message` field for the title and body of the notification. By default, the notification automatically closes after 4500ms, but by setting `duration` you can control its duration. Specifically, if set to `0`, it will not close automatically. Note that `duration` receives a `Number` in milliseconds.

Notifications are sent from the server, `el_notification(session, ...)`.

```{r basic, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#show_container button').click()", shot_sel = ".el-notification", shot_wait = 1}
ui <- el_page(el_button("show", "Closes automatically", plain = TRUE))
server <- function(input, output, session) {
  observeEvent(
    input$show,
    el_notification(session, title = "Title", message = "This is a reminder")
  )
}
shinyApp(ui, server)
```

## With types

We provide five types: primary, success, warning, info and error.

Element Plus provides five notification types: `primary`, `success`, `warning`, `info` and `error`. They are set by the `type` field, and other values will be ignored. We also registered methods for these types that can be invoked directly like `open3` and `open4` without passing a `type` field. `primary` has been added in 2.9.11.

```{r different-types, eval = FALSE, shot = TRUE, shot_js = "document.querySelectorAll('#shot button').forEach(function(b){ b.click(); })", shot_sel = ".el-notification", shot_wait = 1}
types <- c("primary", "success", "warning", "info", "error")
ui <- el_page(lapply(types, function(t) {
  el_button(paste0("n_", t), tools::toTitleCase(t), plain = TRUE)
}))
server <- function(input, output, session) {
  for (t in types) {
    local({
      t <- t
      observeEvent(
        input[[paste0("n_", t)]],
        el_notification(
          session,
          title = tools::toTitleCase(t),
          type = t,
          message = paste("This is a", t, "message")
        )
      )
    })
  }
}
shinyApp(ui, server)
```

## Custom position

Notification can emerge from any corner you like.

The `position` attribute defines which corner Notification slides in. It can be `top-right`, `top-left`, `bottom-right` or `bottom-left`. Defaults to `top-right`.

```{r positioning, eval = FALSE, shot = TRUE, shot_js = "document.querySelectorAll('#shot button').forEach(function(b){ b.click(); })", shot_sel = ".el-notification", shot_wait = 1}
pos <- c("top-right", "bottom-right", "bottom-left", "top-left")
ui <- el_page(lapply(pos, function(p) {
  el_button(paste0("n_", gsub("-", "_", p)), p, plain = TRUE)
}))
server <- function(input, output, session) {
  for (p in pos) {
    local({
      p <- p
      observeEvent(
        input[[paste0("n_", gsub("-", "_", p))]],
        el_notification(
          session,
          title = "Custom Position",
          position = p,
          message = paste("I'm at the", p, "corner")
        )
      )
    })
  }
}
shinyApp(ui, server)
```

## With offset

Customize Notification's offset from the edge of the screen.

Set the `offset` attribute to customize Notification's offset from the edge of the screen. Note that every Notification instance of the same moment should have the same offset.

```{r offsetting, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#show_container button').click()", shot_sel = ".el-notification", shot_wait = 1}
ui <- el_page(el_button("show", "Notification with offset", plain = TRUE))
server <- function(input, output, session) {
  observeEvent(
    input$show,
    el_notification(
      session,
      title = "Success",
      offset = 100,
      message = "This is a success message"
    )
  )
}
shinyApp(ui, server)
```

## Use HTML string

`message` supports HTML string.

Set `dangerouslyUseHTMLString` to true and `message` will be treated as an HTML string.

```{r raw-html, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#show_container button').click()", shot_sel = ".el-notification", shot_wait = 1}
ui <- el_page(el_button("show", "Use HTML String", plain = TRUE))
server <- function(input, output, session) {
  observeEvent(
    input$show,
    el_notification(
      session,
      title = "HTML String",
      dangerously_use_html_string = TRUE,
      message = "<strong>This is <i>HTML</i> string</strong>"
    )
  )
}
shinyApp(ui, server)
```

> **Warning**
>
> Although `message` property supports HTML strings, dynamically rendering arbitrary HTML on your website can be very dangerous because it can easily lead to [XSS attacks](https://en.wikipedia.org/wiki/Cross-site_scripting). So when `dangerouslyUseHTMLString` is on, please make sure the content of `message` is trusted, and **never** assign `message` to user-provided content.

## Message using functions

`message` can be VNode.

After 2.9.0, `message` supports a function whose return value is a VNode.

A message can be a VNode, given as `JS()` code calling `Vue.h()`; one
whose props change is a function returning it.

```{r use-vnode, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#open_container button').click()", shot_sel = ".el-notification", shot_wait = 1}
ui <- el_page(
  el_button("open", "Common VNode", plain = TRUE),
  el_button("open1", "Dynamic props", plain = TRUE)
)
server <- function(input, output, session) {
  observeEvent(input$open, {
    el_notification(
      session,
      title = "Use Vnode",
      message = JS(
        "Vue.h('p', null, [
          Vue.h('span', null, 'Message can be '),
          Vue.h('i', { style: 'color: teal' }, 'VNode')
        ])"
      )
    )
  })
  observeEvent(input$open1, {
    el_notification(
      session,
      title = "Use Vnode",
      message = JS(
        "(function() {
          var checked = Vue.ref(false);
          return function() {
            return Vue.h(ElementPlus.ElSwitch, {
              modelValue: checked.value,
              'onUpdate:modelValue': function(v) { checked.value = v; }
            });
          };
        })()"
      )
    )
  })
}
shinyApp(ui, server)
```

## With progress bar

Display a progress bar indicating the remaining time before the notification auto-closes.

Set `progress` to `true` to enable the progress bar. The progress bar will show a countdown matching the `duration`. Pass an object to `progress` to customize it with the options of [Progress](./progress.html#attributes), e.g. `color`, which overrides the `type`-based status color. When `pauseOnHover` is `true` (default), hovering over the notification will pause both the timer and the progress bar.

```{r progress-bar, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#show_container button').click()", shot_sel = ".el-notification", shot_wait = 1}
ui <- el_page(el_button("show", "With progress bar", plain = TRUE))
server <- function(input, output, session) {
  observeEvent(
    input$show,
    el_notification(
      session,
      title = "Progress",
      progress = TRUE,
      duration = 5000,
      message = "Closes when the bar runs out"
    )
  )
}
shinyApp(ui, server)
```

## Hide close button

It is possible to hide the close button

Set the `showClose` attribute to `false` so the notification cannot be closed by the user.

```{r no-close, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#show_container button').click()", shot_sel = ".el-notification", shot_wait = 1}
ui <- el_page(el_button("show", "Hide close button", plain = TRUE))
server <- function(input, output, session) {
  observeEvent(
    input$show,
    el_notification(
      session,
      title = "Info",
      type = "info",
      show_close = FALSE,
      message = "This is a message without close button"
    )
  )
}
shinyApp(ui, server)
```

## Global method

Element Plus has added a global method `$notify` for `app.config.globalProperties`. So in a vue instance you can call `Notification` like what we did in this page.

## Local import

In this case you should call `ElNotification(options)`. We have also registered methods for different types, e.g. `ElNotification.success(options)`. You can call `ElNotification.closeAll()` to manually close all the instances. In 2.10.5 you can manually update the offsets of all instances in a specific direction by calling `ElNotification.updateOffsets(position)`.

## App context inheritance > 2.0.4

Now notification accepts a `context` as second parameter of the message constructor which allows you to inject current app's context to notification which allows you to inherit all the properties of the app.

You can use it like this:

> **Tip**
>
> If you globally registered ElNotification component, it will automatically inherit your app context.

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("notification")
```
