---
title: "Pagination"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

If you have too much data to display in one page, use pagination.

## Basic usage

Set `layout` with different pagination elements you wish to display separated with a comma. Pagination elements are: `prev` (a button navigating to the previous page), `next` (a button navigating to the next page), `pager` (page list), `jumper` (a jump-to input), `total` (total item count), `sizes` (a select to determine page size) and `->`(every element after this symbol will be pulled to the right).

```{r basic-usage, eval = FALSE, shot = TRUE}
tags$div(style = "display: grid; gap: 16px",
  tags$div("When you have few pages"), el_pagination("pg1", layout = "prev, pager, next", total = 50),
  tags$div("When you have more than 7 pages"), el_pagination("pg2", layout = "prev, pager, next", total = 1000))
```

## Number of pagers

By default, Pagination collapses extra pager buttons when it has more than 7 pages. This can be configured with the `pager-count` attribute.

```{r number-of-pagers, eval = FALSE, shot = TRUE}
el_pagination("pg_pagers", page_size = 20, pager_count = 11, layout = "prev, pager, next", total = 1000)
```

## Buttons with background color

Set the `background` attribute and the buttons will have a background color.

```{r background-color, eval = FALSE, shot = TRUE}
el_pagination("pg_bg", background = TRUE, layout = "prev, pager, next", total = 1000)
```

## Small Pagination

Use small pagination in the case of limited space.

set size to change the `size`. Here is a demonstration of `small`

```{r small-pagination, eval = FALSE, shot = TRUE}
tags$div(style = "display: grid; gap: 16px",
  el_pagination("pg_s1", size = "small", layout = "prev, pager, next", total = 50),
  el_pagination("pg_s2", size = "small", background = TRUE, layout = "prev, pager, next", total = 50))
```

## Hide pagination when there is only one page

When there is only one page, hide the pagination by setting the `hide-on-single-page` attribute.

```{r auto-hide-pagination, eval = FALSE, shot = TRUE}
el_pagination("pg_hide", hide_on_single_page = FALSE, total = 5, layout = "prev, pager, next")
```

## More elements

Add more modules based on your scenario.

This example is a complete use case. It uses `size-change` and `current-change` event to handle page size changes and current page changes. `page-sizes` accepts an array of integers, each of which represents a different page size in the `sizes` select options, e.g. `[100, 200, 300, 400]` indicates that the select will have four options: 100, 200, 300 or 400 items per page.

```{r more-elements, eval = FALSE, shot = TRUE}
tags$div(style = "display: grid; gap: 16px",
  tags$div("Total item count"), el_pagination("pg_m1", current_page = 5, page_size = 100,
    layout = "total, prev, pager, next", total = 1000),
  tags$div("Change page size"), el_pagination("pg_m2", current_page = 5, page_size = 100,
    page_sizes = c(100, 200, 300, 400), layout = "sizes, prev, pager, next", total = 1000),
  tags$div("Jump to"), el_pagination("pg_m3", current_page = 5, page_size = 100,
    layout = "prev, pager, next, jumper", total = 1000),
  tags$div("All combined"), el_pagination("pg_m4", current_page = 4, page_size = 100,
    page_sizes = c(100, 200, 300, 400), layout = "total, sizes, prev, pager, next, jumper", total = 400))
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("pagination")
```
