---
title: "Popconfirm"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

A simple confirmation dialog of an element click action.

## Placement

popconfirm has 9 placements.

Use attribute `title` to set the display content when click the reference element. The attribute `placement` determines the position of the popconfirm. Its value is `[orientation]-[alignment]` with four orientations `top`, `left`, `right`, `bottom` and three alignments `start`, `end`, `null`, and the default alignment is null. Take `placement="left-end"` for example, popconfirm will display on the left of the element which you are hovering and the bottom of the popconfirm aligns with the bottom of the element.

```{r placement, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#shot button').click()", shot_sel = ".el-popper", shot_wait = 1}
places <- c("top-start", "top", "top-end", "left", "right", "bottom-start", "bottom", "bottom-end")
tags$div(style = "padding: 60px 100px; display: flex; flex-wrap: wrap; gap: 12px", lapply(places, function(p)
  el_popconfirm(paste0("pc_", gsub("-", "_", p)), reference = el_button(paste0("pcb_", gsub("-", "_", p)), p),
                title = paste(p, "prompts info"), placement = p)))
```

## Basic usage

Popconfirm is similar to Popover. So for some duplicated attributes, please refer to the documentation of Popover.

Only `title` attribute is available in Popconfirm, `content` will be ignored.

```{r basic-usage, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#shot button').click()", shot_sel = ".el-popper", shot_wait = 1}
el_popconfirm("del", reference = el_button("del_btn", "Delete"),
              title = "Are you sure to delete this?")
```

## Customize

You can customize Popconfirm like:

```{r customize, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#shot button').click()", shot_sel = ".el-popper", shot_wait = 1}
el_popconfirm("good", reference = el_button("go", "Delete"), title = "Are you sure to delete this?",
              confirm_button_text = "OK", cancel_button_text = "No, Thanks",
              icon = "InfoFilled", icon_color = "#626AEF", width = "220px")
```

## Trigger event

Click the button to trigger the event

Confirming and cancelling are inputs: `input$<id>_confirm`,
`input$<id>_cancel`.

```{r trigger-event, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#shot button').click()", shot_sel = ".el-popper", shot_wait = 1}
el_popconfirm("ev", reference = el_button("ev_btn", "Delete"), title = "Are you sure to delete this?",
              confirm_button_text = "Yes", cancel_button_text = "No")
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("popconfirm")
```
