---
title: "Popover"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

## Placement

Popover has 9 placements.

Use attribute `content` to set the display content when hover. The attribute `placement` determines the position of the Popover. Its value is `[orientation]-[alignment]` with four orientations `top`, `left`, `right`, `bottom` and three alignments `start`, `end`, `null`, and the default alignment is null. Take `placement="left-end"` for example, Popover will display on the left of the element which you are hovering and the bottom of the Popover aligns with the bottom of the element.

```{r placement, eval = FALSE, shot = TRUE, shot_js = "var b = document.querySelector('#shot button'); ['mouseenter','mouseover'].forEach(function(t){ b.dispatchEvent(new MouseEvent(t, {bubbles: true})); });", shot_sel = ".el-popper", shot_wait = 1}
places <- c(
  "top-start",
  "top",
  "top-end",
  "left",
  "right",
  "bottom-start",
  "bottom",
  "bottom-end"
)
tags$div(
  style = "padding: 60px 100px; display: flex; flex-wrap: wrap; gap: 12px",
  lapply(places, function(p) {
    el_popover(
      paste0("po_", gsub("-", "_", p)),
      reference = el$button(p),
      placement = p,
      title = "Title",
      popover_width = 200,
      content = "this is content, this is content, this is content"
    )
  })
)
```

## Basic usage

Popover is built with `ElTooltip`. So for some duplicated attributes, please refer to the documentation of Tooltip.

The `trigger` attribute is used to define how popover is triggered: `hover`, `click`, `focus` or `contextmenu` . If you want to manually control it, you can set `:visible`.

Each button opens its popover as its label says: `contextmenu` on a
right-click, as the browser's own menu, not on a left click. The last
one is opened and closed by the server, `update_el_popover(visible =)`.

```{r basic-usage, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#p_manual_btn button, #p_manual .el-button:last-child').click()", shot_sel = ".el-popper", shot_wait = 1.5, shot_expect = "Array.from(document.querySelectorAll('.el-popover.el-popper')).filter(function(p) { return p.offsetParent; }).length === 1"}
pop <- function(id, label, trigger, placement = NULL, ...) {
  el_popover(
    id,
    reference = el_button(label = label),
    trigger = trigger,
    placement = placement,
    title = "Title",
    popover_width = 200,
    content = "this is content, this is content, this is content",
    ...
  )
}
ui <- el_page(
  tags$style(".el-button + .el-button { margin-left: 8px; }"),
  pop("p_hover", "Hover to activate", "hover", "top-start"),
  pop("p_click", "Click to activate", "click", "bottom"),
  pop("p_focus", "Focus to activate", "focus", "right"),
  pop("p_contextmenu", "contextmenu to activate", "contextmenu"),
  el_popover(
    "p_manual",
    reference = el_button("p_manual_btn", "Manual to activate"),
    visible = FALSE,
    placement = "bottom",
    title = "Title",
    popover_width = 200,
    content = "this is content, this is content, this is content"
  )
)
server <- function(input, output, session) {
  observeEvent(input$p_manual_btn, {
    update_el_popover(
      session,
      "p_manual",
      visible = input$p_manual_btn %% 2 == 1
    )
  })
}
shinyApp(ui, server)
```

## Virtual triggering

Like Tooltip, Popover can be triggered by virtual elements, if your use case includes separate the triggering element and the content element, you should definitely use the mechanism, normally we use `#reference` to place our triggering element, with `virtual-ref` API you can set your triggering element anywhere you like, but notice that the triggering element should be an element that accepts `mouse` and `keyboard` event.

> **Warning**
>
> `v-popover` is about to be deprecated, please use `virtual-ref` as alternative.

`virtual_ref` is a CSS selector for the element that opens the popover,
wherever it is on the page.

```{r virtual-triggering, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#shot button').click()", shot_sel = ".el-popper", shot_wait = 1}
tagList(
  el_button("vp_btn", "Click me"),
  el_popover(
    "vp",
    title = "With title",
    content = "Some content",
    trigger = "click",
    virtual_ref = "#vp_btn"
  )
)
```

## Rich content

Other components/elements can be nested in popover. Following is an example of nested table.

replace the `content` attribute with a default `slot`.

A popover holds any UI: a table, or rich content beside an avatar.

```{r nested-information, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#addr .el-button').click()", shot_sel = ".el-popper", shot_wait = 1, shot_expect = "document.querySelectorAll('.el-popper .el-table__body tr').length === 4"}
avatar <- "https://avatars.githubusercontent.com/u/72015883?v=4"
tags$div(
  style = "display: flex; align-items: center",
  el_popover(
    "addr",
    reference = el_button(
      label = "Click to activate",
      style = "margin-right: 16px"
    ),
    trigger = "click",
    popover_width = 400,
    placement = "right",
    body = el_table(
      data = data.frame(
        date = c("2016-05-02", "2016-05-04", "2016-05-01", "2016-05-03"),
        name = "Jack",
        address = "New York City"
      ),
      columns = list(
        el_table_column("date", "date", width = 150),
        el_table_column("name", "name", width = 100),
        el_table_column("address", "address", width = 300)
      )
    )
  ),
  el_popover(
    "rich",
    reference = el_avatar(src = avatar),
    popover_width = 300,
    popper_style = paste(
      "box-shadow: rgb(14 18 22 / 35%) 0px 10px 38px -10px,",
      "rgb(14 18 22 / 20%) 0px 10px 20px -15px; padding: 20px;"
    ),
    body = tags$div(
      class = "demo-rich-conent",
      style = "display: flex; gap: 16px; flex-direction: column",
      el_avatar(size = 60, src = avatar, style = "margin-bottom: 8px"),
      tags$div(
        tags$p(
          class = "demo-rich-content__name",
          style = "margin: 0; font-weight: 500",
          "Element Plus"
        ),
        tags$p(
          class = "demo-rich-content__mention",
          style = "margin: 0; font-size: 14px; color: var(--el-color-info)",
          "@element-plus"
        )
      ),
      tags$p(
        class = "demo-rich-content__desc",
        style = "margin: 0",
        "Element Plus, a Vue 3 based component library for developers,",
        "designers and product managers"
      )
    )
  )
)
```

## Nested operation

Of course, you can nest other operations. It's more light-weight than using a dialog.

Opened and closed from the server with `update_el_popover(visible =)`.

```{r nested-operation, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#shot .el-button').click()", shot_sel = ".el-popper", shot_wait = 1.5}
ui <- el_page(el_popover(
  "confirm",
  popover_width = 160,
  placement = "top",
  reference = el_button("delete", "Delete"),
  body = tagList(
    tags$p("Are you sure to delete this?"),
    el_button("no", "cancel", size = "small", text = TRUE),
    el_button("yes", "confirm", size = "small", type = "primary")
  )
))
server <- function(input, output, session) {
  observeEvent(input$delete, update_el_popover(id = "confirm", visible = TRUE))
  observeEvent(
    c(input$no, input$yes),
    update_el_popover(id = "confirm", visible = FALSE),
    ignoreInit = TRUE
  )
}
shinyApp(ui, server)
```

## Directive

You can still using popover in directive way but this is **not recommended** anymore since this makes your application
complicated, you may refer to the virtual triggering for more information.

> **In R**
>
> Element Plus's `v-popover` directive is template syntax on another
> component's element, and each component here is an application of its own,
> so it has no R form. `virtual_ref` does what it does -- see Virtual
> triggering above.

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("popover")
```
