---
title: "Progress"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Progress is used to show the progress of current operation, and inform the user the current status.

## Linear progress bar

Use `percentage` attribute to set the percentage. It's **required** and must be between `0-100`. You can custom text format by setting `format`.

```{r linear-progress-bar, eval = FALSE, shot = TRUE}
tags$div(style = "max-width: 600px; display: grid; gap: 15px",
  el_progress("pr1", percentage = 50), el_progress("pr2", percentage = 100, format = JS("function(p) { return p === 100 ? 'Full' : p + '%'; }")),
  el_progress("pr3", percentage = 100, status = "success"), el_progress("pr4", percentage = 100, status = "warning"),
  el_progress("pr5", percentage = 50, status = "exception"))
```

## Internal percentage

In this case the percentage takes no additional space.

`stroke-width` attribute decides the `width` of progress bar, and use `text-inside` attribute to put description inside the progress bar.

```{r internal-percentage, eval = FALSE, shot = TRUE}
tags$div(style = "max-width: 600px; display: grid; gap: 15px",
  el_progress("pri1", percentage = 70, text_inside = TRUE, stroke_width = 26),
  el_progress("pri2", percentage = 100, text_inside = TRUE, stroke_width = 24, status = "success"),
  el_progress("pri3", percentage = 80, text_inside = TRUE, stroke_width = 22, status = "warning"),
  el_progress("pri4", percentage = 50, text_inside = TRUE, stroke_width = 20, status = "exception"))
```

## Custom color

You can use `color` attr to set the progress bar color. it accepts color string, function, or array.

```{r custom-color, eval = FALSE, shot = TRUE}
tags$div(style = "max-width: 600px; display: grid; gap: 15px",
  el_progress("prc1", percentage = 20, color = "#409eff"),
  el_progress("prc2", percentage = 40, color = JS("function(p) { return p < 30 ? '#909399' : p < 70 ? '#e6a23c' : '#67c23a'; }")),
  el_progress("prc3", percentage = 60, color = list(list(color = "#f56c6c", percentage = 20),
    list(color = "#e6a23c", percentage = 40), list(color = "#5cb87a", percentage = 60),
    list(color = "#1989fa", percentage = 80), list(color = "#6f7ad3", percentage = 100))))
```

## Circular progress bar

You can specify `type` attribute to `circle` to use circular progress bar, and use `width` attribute to change the size of circle.

```{r circular-progress-bar, eval = FALSE, shot = TRUE}
tags$div(style = "display: flex; gap: 20px",
  el_progress("prcl1", type = "circle", percentage = 0),
  el_progress("prcl2", type = "circle", percentage = 25),
  el_progress("prcl3", type = "circle", percentage = 100, status = "success"),
  el_progress("prcl4", type = "circle", percentage = 70, status = "warning"),
  el_progress("prcl5", type = "circle", percentage = 50, status = "exception"))
```

## Dashboard progress bar

You also can specify `type` attribute to `dashboard` to use dashboard progress bar.

```{r dashboard-progress-bar, eval = FALSE, shot = TRUE}
el_progress("prd", type = "dashboard", percentage = 70, color = list(
  list(color = "#f56c6c", percentage = 20), list(color = "#e6a23c", percentage = 40),
  list(color = "#5cb87a", percentage = 60), list(color = "#1989fa", percentage = 80),
  list(color = "#6f7ad3", percentage = 100)))
```

## Customized content

Use default slot to add customized content.

```{r customized-content, eval = FALSE, shot = TRUE}
tags$div(style = "display: flex; gap: 20px; align-items: center",
  el_progress("prx1", percentage = 50, slots = list(default = el_button("prx_b", "Content", text = TRUE))),
  el_progress("prx2", type = "circle", percentage = 50, slots = list(default = template(htmltools::HTML(
    "<span class=\"percentage-value\">{{ percentage }}%</span><span class=\"percentage-label\">Progressing</span>"),
    scope = "{ percentage }"))))
```

## Indeterminate progress

Use `indeterminate` attribute to set indeterminate progress, with `duration` to control the animation duration.

```{r indeterminate-progress, eval = FALSE, shot = TRUE}
tags$div(style = "max-width: 600px; display: grid; gap: 15px",
  el_progress("prin1", percentage = 50, indeterminate = TRUE),
  el_progress("prin2", percentage = 100, format = JS("function() { return 'Full'; }"), indeterminate = TRUE),
  el_progress("prin3", percentage = 100, status = "success", indeterminate = TRUE, duration = 5))
```

## Striped progress

Use `striped` attribute to set striped progress. You can use `striped-flow` to get the stripes to flow, with `duration` to control the animation duration.

```{r striped-progress, eval = FALSE, shot = TRUE}
tags$div(style = "max-width: 600px; display: grid; gap: 15px",
  el_progress("prs1", percentage = 50, stroke_width = 15, striped = TRUE),
  el_progress("prs2", percentage = 30, stroke_width = 15, status = "warning", striped = TRUE, striped_flow = TRUE),
  el_progress("prs3", percentage = 100, stroke_width = 15, status = "success", striped = TRUE,
              striped_flow = TRUE, duration = 10))
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("progress")
```
