---
title: "Progress"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Progress is used to show the progress of current operation, and inform the user the current status.

## Linear progress bar

Use `percentage` attribute to set the percentage. It's **required** and must be between `0-100`. You can custom text format by setting `format`.

```{r linear-progress-bar, eval = FALSE, shot = TRUE}
tags$div(
  style = "max-width: 600px; display: grid; gap: 15px",
  el_progress("pr1", percentage = 50),
  el_progress(
    "pr2",
    percentage = 100,
    format = JS("function(p) { return p === 100 ? 'Full' : p + '%'; }")
  ),
  el_progress("pr3", percentage = 100, status = "success"),
  el_progress("pr4", percentage = 100, status = "warning"),
  el_progress("pr5", percentage = 50, status = "exception")
)
```

## Internal percentage

In this case the percentage takes no additional space.

`stroke-width` attribute decides the `width` of progress bar, and use `text-inside` attribute to put description inside the progress bar.

```{r internal-percentage, eval = FALSE, shot = TRUE}
tags$div(
  style = "max-width: 600px; display: grid; gap: 15px",
  el_progress("pri1", percentage = 70, text_inside = TRUE, stroke_width = 26),
  el_progress(
    "pri2",
    percentage = 100,
    text_inside = TRUE,
    stroke_width = 24,
    status = "success"
  ),
  el_progress(
    "pri3",
    percentage = 80,
    text_inside = TRUE,
    stroke_width = 22,
    status = "warning"
  ),
  el_progress(
    "pri4",
    percentage = 50,
    text_inside = TRUE,
    stroke_width = 20,
    status = "exception"
  )
)
```

## Custom color

You can use `color` attr to set the progress bar color. it accepts color string, function, or array.

The buttons step every bar by ten, with `update_el_progress()`.

```{r custom-color, eval = FALSE, shot = TRUE, shot_js = c("document.querySelectorAll('.demo-progress .el-button')[1].click()", "document.querySelectorAll('.demo-progress .el-button')[1].click()"), shot_expect = "document.querySelectorAll('.el-progress__text')[0].innerText.trim() === '40%'"}
colors <- list(
  list(color = "#f56c6c", percentage = 20),
  list(color = "#e6a23c", percentage = 40),
  list(color = "#5cb87a", percentage = 60),
  list(color = "#1989fa", percentage = 80),
  list(color = "#6f7ad3", percentage = 100)
)
ids <- c("prc1", "prc2", "prc3", "prc4")
ui <- el_page(
  tags$style(
    ".demo-progress .el-progress--line { margin-bottom: 15px; max-width: 600px; }"
  ),
  tags$div(
    class = "demo-progress",
    el_progress("prc1", percentage = 20, color = "#409eff"),
    el_progress(
      "prc2",
      percentage = 20,
      color = JS(
        "function(p) { return p < 30 ? '#909399' : p < 70 ? '#e6a23c' : '#67c23a'; }"
      )
    ),
    el_progress("prc3", percentage = 20, color = colors),
    el_progress("prc4", percentage = 20, color = colors),
    tags$div(
      el_button_group(
        el_button("prc_minus", label = NULL, icon = "Minus"),
        el_button("prc_plus", label = NULL, icon = "Plus")
      )
    )
  )
)
server <- function(input, output, session) {
  percentage <- reactiveVal(20)
  step <- function(by) {
    percentage(min(100, max(0, percentage() + by)))
    for (id in ids) {
      update_el_progress(session, id, percentage = percentage())
    }
  }
  observeEvent(input$prc_minus, step(-10))
  observeEvent(input$prc_plus, step(10))
}
shinyApp(ui, server)
```

## Circular progress bar

You can specify `type` attribute to `circle` to use circular progress bar, and use `width` attribute to change the size of circle.

```{r circular-progress-bar, eval = FALSE, shot = TRUE}
tags$div(
  style = "display: flex; gap: 20px",
  el_progress("prcl1", type = "circle", percentage = 0),
  el_progress("prcl2", type = "circle", percentage = 25),
  el_progress("prcl3", type = "circle", percentage = 100, status = "success"),
  el_progress("prcl4", type = "circle", percentage = 70, status = "warning"),
  el_progress("prcl5", type = "circle", percentage = 50, status = "exception")
)
```

## Dashboard progress bar

You also can specify `type` attribute to `dashboard` to use dashboard progress bar.

The buttons step the first dial; the second goes round on its own,
updated from the server every half second.

```{r dashboard-progress-bar, eval = FALSE, shot = TRUE, shot_js = "document.querySelectorAll('.demo-progress .el-button')[1].click()", shot_expect = "document.querySelectorAll('.el-progress__text')[0].innerText.trim() === '20%'"}
colors <- list(
  list(color = "#f56c6c", percentage = 20),
  list(color = "#e6a23c", percentage = 40),
  list(color = "#5cb87a", percentage = 60),
  list(color = "#1989fa", percentage = 80),
  list(color = "#6f7ad3", percentage = 100)
)
ui <- el_page(
  tags$div(
    class = "demo-progress",
    el_progress("prd1", type = "dashboard", percentage = 10, color = colors),
    el_progress("prd2", type = "dashboard", percentage = 0, color = colors),
    tags$div(
      el_button_group(
        el_button("prd_minus", label = NULL, icon = "Minus"),
        el_button("prd_plus", label = NULL, icon = "Plus")
      )
    )
  )
)
server <- function(input, output, session) {
  percentage <- reactiveVal(10)
  step <- function(by) {
    percentage(min(100, max(0, percentage() + by)))
    update_el_progress(session, "prd1", percentage = percentage())
  }
  observeEvent(input$prd_minus, step(-10))
  observeEvent(input$prd_plus, step(10))
  going <- reactiveVal(0)
  observe({
    invalidateLater(500)
    going(isolate(going()) %% 100 + 10)
    update_el_progress(session, "prd2", percentage = isolate(going()))
  })
}
shinyApp(ui, server)
```

## Customized content

Use default slot to add customized content.

```{r customized-content, eval = FALSE, shot = TRUE}
tags$div(
  style = "display: flex; gap: 20px; align-items: center",
  el_progress(
    "prx1",
    percentage = 50,
    slots = list(default = el_button("prx_b", "Content", text = TRUE))
  ),
  el_progress(
    "prx2",
    type = "circle",
    percentage = 50,
    slots = list(
      default = template(
        htmltools::HTML(
          "<span class=\"percentage-value\">{{ percentage }}%</span><span class=\"percentage-label\">Progressing</span>"
        ),
        scope = "{ percentage }"
      )
    )
  )
)
```

## Indeterminate progress

Use `indeterminate` attribute to set indeterminate progress, with `duration` to control the animation duration.

```{r indeterminate-progress, eval = FALSE, shot = TRUE}
tags$div(
  style = "max-width: 600px; display: grid; gap: 15px",
  el_progress("prin1", percentage = 50, indeterminate = TRUE),
  el_progress(
    "prin2",
    percentage = 100,
    format = JS("function() { return 'Full'; }"),
    indeterminate = TRUE
  ),
  el_progress(
    "prin3",
    percentage = 100,
    status = "success",
    indeterminate = TRUE,
    duration = 5
  )
)
```

## Striped progress

Use `striped` attribute to set striped progress. You can use `striped-flow` to get the stripes to flow, with `duration` to control the animation duration.

The buttons step the last bar by ten, and its stripes' `duration` with
it.

```{r striped-progress, eval = FALSE, shot = TRUE, shot_js = "document.querySelectorAll('.demo-progress .el-button')[0].click()", shot_expect = "document.querySelectorAll('.el-progress-bar__inner')[3].style.width === '60%'"}
ui <- el_page(
  tags$style(
    ".demo-progress .el-progress--line { margin-bottom: 15px; max-width: 600px; }"
  ),
  tags$div(
    class = "demo-progress",
    el_progress("prs1", percentage = 50, stroke_width = 15, striped = TRUE),
    el_progress(
      "prs2",
      percentage = 30,
      stroke_width = 15,
      status = "warning",
      striped = TRUE,
      striped_flow = TRUE
    ),
    el_progress(
      "prs3",
      percentage = 100,
      stroke_width = 15,
      status = "success",
      striped = TRUE,
      striped_flow = TRUE,
      duration = 10
    ),
    el_progress(
      "prs4",
      percentage = 70,
      stroke_width = 15,
      status = "exception",
      striped = TRUE,
      striped_flow = TRUE,
      duration = 7
    ),
    el_button_group(
      el_button("prs_minus", label = NULL, icon = "Minus"),
      el_button("prs_plus", label = NULL, icon = "Plus")
    )
  )
)
server <- function(input, output, session) {
  percentage <- reactiveVal(70)
  step <- function(by) {
    percentage(min(100, max(0, percentage() + by)))
    update_el_progress(
      session,
      "prs4",
      percentage = percentage(),
      duration = floor(percentage() / 10)
    )
  }
  observeEvent(input$prs_minus, step(-10))
  observeEvent(input$prs_plus, step(10))
}
shinyApp(ui, server)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("progress")
```
