---
title: "Radio"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Single selection among multiple options.

> **Warning**
>
> `label` act as `value` has been **deprecated**, `label` is used only as display text, this action **will be** removed in 3.0.0, consider switching to new API.

> **Tip**
>
> New API `value` has been added in 2.6.0, the examples in the document all use the `value`.
> If you are using a version **less than** 2.6.0, please refer to:

## Basic usage

Radio should not have too many options. Otherwise, use the Select component instead.

Creating a radio component is easy, you just need to bind a variable to Radio's `v-model`. It equals to the value of `value` of the chosen radio. The type of `value` is `String`, `Number` or `Boolean`.

```{r basic-usage, eval = FALSE, shot = TRUE}
tags$div(
  style = "display: grid; gap: 12px",
  el_radio_group(
    "rd_l",
    choices = c("Option 1" = "1", "Option 2" = "2"),
    selected = "1",
    size = "large"
  ),
  el_radio_group(
    "rd_d",
    choices = c("Option 1" = "1", "Option 2" = "2"),
    selected = "1"
  ),
  el_radio_group(
    "rd_s",
    choices = c("Option 1" = "1", "Option 2" = "2"),
    selected = "1",
    size = "small"
  ),
  el_radio_group(
    "rd_x",
    choices = c("Option 1" = "1", "Option 2" = "2"),
    selected = "1",
    size = "small",
    disabled = TRUE
  )
)
```

## Disabled

`disabled` attribute is used to disable the radio.

You just need to add the `disabled` attribute.

```{r disabled, eval = FALSE, shot = TRUE}
el_radio_group(
  "rd_dis",
  choices = c("Option A" = "a", "Option B" = "b"),
  selected = "a",
  disabled = TRUE
)
```

## Radio Group

Suitable for choosing from some mutually exclusive options.

Combine `el-radio-group` with `el-radio` to display a radio group. Bind a variable with `v-model` of `el-radio-group` element and set label value in `el-radio`. It also provides `change` event with the current value as its parameter.

```{r radio-group, eval = FALSE, shot = TRUE}
el_radio_group(
  "rd_group",
  choices = c("Option A" = 3, "Option B" = 6, "Option C" = 9),
  selected = 3
)
```

## With borders

The `border` attribute adds a border to Radios.

A choice's `border = TRUE` draws it bordered.

```{r with-borders, eval = FALSE, shot = TRUE}
tags$div(
  style = "display: grid; gap: 12px",
  el_radio_group(
    "rd_b1",
    selected = "1",
    size = "large",
    choices = list(
      list(label = "Option A", value = "1", border = TRUE),
      list(label = "Option B", value = "2", border = TRUE)
    )
  ),
  el_radio_group(
    "rd_b2",
    selected = "1",
    choices = list(
      list(label = "Option A", value = "1", border = TRUE),
      list(label = "Option B", value = "2", border = TRUE)
    )
  )
)
```

## Options attribute

Shortcut from basic `el-radio-group` usage. You can customize the alias of the `options` through the `props` attribute.

```{r options, eval = FALSE, shot = TRUE}
el_radio_group(
  "rd_opts",
  selected = "Value A",
  props = list(label = "name", value = "id", disabled = "unable"),
  choices = list(
    list(label = "Option A", value = "Value A"),
    list(label = "Option B", value = "Value B"),
    list(label = "Option C", value = "Value C")
  )
)
```

## Radio Button

Radio with button group visual effect.

You just need to change `el-radio` element into `el-radio-button` element. You can also set the style of the button when it is active by using `fill` and `text-color`.

```{r radio-button, eval = FALSE, shot = TRUE}
cities <- c("New York", "Washington", "Los Angeles", "Chicago")
tags$div(
  style = "display: grid; gap: 12px",
  el_radio_group(
    "rdb1",
    choices = cities,
    selected = "New York",
    button = TRUE,
    size = "large"
  ),
  el_radio_group(
    "rdb2",
    choices = cities,
    selected = "New York",
    button = TRUE
  ),
  el_radio_group(
    "rdb3",
    choices = cities,
    selected = "New York",
    button = TRUE,
    size = "small"
  )
)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("radio")
```
