---
title: "Scrollbar"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Used to replace the browser's native scrollbar.

## Basic usage

Use `height` property to set the height of the scrollbar, or if not set, it adapts according to the parent container height.

```{r basic-usage, eval = FALSE, shot = TRUE}
item <- function(i) {
  tags$p(
    class = "scrollbar-demo-item",
    style = paste(
      "display: flex; align-items: center; justify-content: center; height: 50px; margin: 10px;",
      "text-align: center; border-radius: 4px; background: var(--el-color-primary-light-9);",
      "color: var(--el-color-primary)"
    ),
    i
  )
}
el_scrollbar(height = "400px", lapply(1:20, item))
```

## Horizontal scroll

When the element width is greater than the scrollbar width, the horizontal scrollbar is displayed.

```{r horizontal-scroll, eval = FALSE, shot = TRUE}
item <- function(i) {
  tags$p(
    style = paste(
      "flex-shrink: 0; display: flex; align-items: center; justify-content: center; width: 100px;",
      "height: 50px; margin: 10px; border-radius: 4px; background: var(--el-color-danger-light-9);",
      "color: var(--el-color-danger)"
    ),
    i
  )
}
el_scrollbar(tags$div(style = "display: flex", lapply(1:50, item)))
```

## Max height

The scrollbar is displayed only when the element height exceeds the max height.

The buttons add and delete items: the scrollbar appears once they pass
`max_height`.

```{r max-height, eval = FALSE, shot = TRUE, shot_js = c("document.querySelectorAll('button')[0].click()", "document.querySelectorAll('button')[0].click()", "document.querySelectorAll('button')[0].click()", "document.querySelectorAll('button')[0].click()", "document.querySelectorAll('button')[0].click()"), shot_expect = c("document.querySelectorAll('.scrollbar-demo-item').length === 8", "document.querySelector('.el-scrollbar__wrap').clientHeight === 400")}
ui <- el_page(
  tags$style(
    ".scrollbar-demo-item { display: flex; align-items: center;
       justify-content: center; height: 50px; margin: 10px; text-align: center;
       border-radius: 4px; background: var(--el-color-primary-light-9);
       color: var(--el-color-primary); }"
  ),
  el_button("sb_add", "Add Item"),
  el_button("sb_delete", "Delete Item"),
  el_scrollbar(max_height = "400px", uiOutput("sb_items"))
)
server <- function(input, output, session) {
  count <- reactiveVal(3)
  observeEvent(input$sb_add, count(count() + 1))
  observeEvent(input$sb_delete, count(max(0, count() - 1)))
  output$sb_items <- renderUI({
    lapply(seq_len(count()), function(i) {
      tags$p(class = "scrollbar-demo-item", i)
    })
  })
}
shinyApp(ui, server)
```

## Manual scroll

Use `setScrollTop` and `setScrollLeft` methods can control scrollbar manually.

The slider scrolls the area from the server, `call_el(session, "sb",
"setScrollTop", list(px))`, and follows it back: `input$sb_scroll` says
where it is. Twenty items of 60px and a margin make 1210px, 830px more
than the 380px shown.

```{r manual-scroll, eval = FALSE, shot = TRUE, shot_js = "Shiny.setInputValue('sb_slider', 300)", shot_wait = 2, shot_expect = "Math.abs(document.querySelector('#sb .el-scrollbar__wrap').scrollTop - 300) < 2"}
ui <- el_page(
  tags$style(
    ".scrollbar-demo-item { display: flex; align-items: center;
       justify-content: center; height: 50px; margin: 10px; text-align: center;
       border-radius: 4px; background: var(--el-color-primary-light-9);
       color: var(--el-color-primary); }
     .el-slider { margin-top: 20px; }"
  ),
  el_scrollbar(
    id = "sb",
    height = "400px",
    events = "scroll",
    always = TRUE,
    tags$div(lapply(1:20, function(i) tags$p(class = "scrollbar-demo-item", i)))
  ),
  el_slider(
    "sb_slider",
    value = 0,
    max = 830,
    format_tooltip = JS("function(value) { return value + ' px'; }")
  )
)
server <- function(input, output, session) {
  observeEvent(input$sb_slider, ignoreInit = TRUE, {
    call_el(session, "sb", "setScrollTop", list(input$sb_slider))
  })
  observeEvent(input$sb_scroll, {
    update_el_slider(
      session,
      "sb_slider",
      value = round(input$sb_scroll$scrollTop)
    )
  })
}
shinyApp(ui, server)
```

## Infinite scroll

`end-reached` is triggered when the scrollbar reaches the end. It can be used as an infinite scroll.

Reaching an end is `input$<id>_end_reached`: `"bottom"`, `"top"`, ...

```{r infinite-scroll, eval = FALSE, shot = TRUE}
item <- function(i) {
  tags$p(
    style = paste(
      "display: flex; align-items: center; justify-content: center; height: 50px; margin: 10px;",
      "border-radius: 4px; background: var(--el-color-primary-light-9); color: var(--el-color-primary)"
    ),
    i
  )
}
el_scrollbar(id = "sb_more", height = "400px", lapply(1:30, item))
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("scrollbar")
```
