---
title: "Scrollbar"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Used to replace the browser's native scrollbar.

## Basic usage

Use `height` property to set the height of the scrollbar, or if not set, it adapts according to the parent container height.

```{r basic-usage, eval = FALSE, shot = TRUE}
item <- function(i) {
  tags$p(
    class = "scrollbar-demo-item",
    style = paste(
      "display: flex; align-items: center; justify-content: center; height: 50px; margin: 10px;",
      "text-align: center; border-radius: 4px; background: var(--el-color-primary-light-9);",
      "color: var(--el-color-primary)"
    ),
    i
  )
}
el_scrollbar(height = "400px", lapply(1:20, item))
```

## Horizontal scroll

When the element width is greater than the scrollbar width, the horizontal scrollbar is displayed.

```{r horizontal-scroll, eval = FALSE, shot = TRUE}
item <- function(i) {
  tags$p(
    style = paste(
      "flex-shrink: 0; display: flex; align-items: center; justify-content: center; width: 100px;",
      "height: 50px; margin: 10px; border-radius: 4px; background: var(--el-color-danger-light-9);",
      "color: var(--el-color-danger)"
    ),
    i
  )
}
el_scrollbar(tags$div(style = "display: flex", lapply(1:50, item)))
```

## Max height

The scrollbar is displayed only when the element height exceeds the max height.

```{r max-height, eval = FALSE, shot = TRUE}
item <- function(i) {
  tags$p(
    style = paste(
      "display: flex; align-items: center; justify-content: center; height: 50px; margin: 10px;",
      "border-radius: 4px; background: var(--el-color-primary-light-9); color: var(--el-color-primary)"
    ),
    i
  )
}
el_scrollbar(max_height = "400px", lapply(1:3, item))
```

## Manual scroll

Use `setScrollTop` and `setScrollLeft` methods can control scrollbar manually.

`call_el(session, "sb", "setScrollTop", list(200))` scrolls it from the
server; `input$<id>_scroll` reports where it is.

```{r manual-scroll, eval = FALSE, shot = TRUE}
item <- function(i) {
  tags$p(
    style = paste(
      "display: flex; align-items: center; justify-content: center; height: 50px; margin: 10px;",
      "border-radius: 4px; background: var(--el-color-primary-light-9); color: var(--el-color-primary)"
    ),
    i
  )
}
el_scrollbar(id = "sb", height = "400px", always = TRUE, lapply(1:20, item))
```

## Infinite scroll

`end-reached` is triggered when the scrollbar reaches the end. It can be used as an infinite scroll.

Reaching an end is `input$<id>_end_reached`: `"bottom"`, `"top"`, ...

```{r infinite-scroll, eval = FALSE, shot = TRUE}
item <- function(i) {
  tags$p(
    style = paste(
      "display: flex; align-items: center; justify-content: center; height: 50px; margin: 10px;",
      "border-radius: 4px; background: var(--el-color-primary-light-9); color: var(--el-color-primary)"
    ),
    i
  )
}
el_scrollbar(id = "sb_more", height = "400px", lapply(1:30, item))
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("scrollbar")
```
