---
title: "Segmented"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Display multiple options and allow users to select a single option.

## Basic Usage

Set `v-model` to the option value is selected.

```{r basic, eval = FALSE, shot = TRUE}
days <- c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun")
tags$div(
  style = "display: grid; gap: 16px; justify-items: start",
  el_segmented("seg_l", options = days, value = "Mon", size = "large"),
  el_segmented("seg_d", options = days, value = "Mon"),
  el_segmented("seg_s", options = days, value = "Mon", size = "small")
)
```

## Direction Usage

Set `vertical` to change direction.

```{r custom-direction, eval = FALSE, shot = TRUE}
el_segmented(
  "seg_v",
  direction = "vertical",
  value = "Apple",
  options = c("Apple", "Cherry", "Grape", "Orange", "Pear")
)
```

## Disabled

Set `disabled` of segmented or option to `true` to disable it.

```{r disabled, eval = FALSE, shot = TRUE}
opts <- list(
  list(label = "Mon", value = "Mon"),
  list(label = "Tue", value = "Tue", disabled = TRUE),
  list(label = "Wed", value = "Wed")
)
tags$div(
  style = "display: grid; gap: 16px; justify-items: start",
  el_segmented("seg_dis1", options = opts, value = "Mon", disabled = TRUE),
  el_segmented("seg_dis2", options = opts, value = "Mon")
)
```

## Aliases for custom options

When your `options` format is different from the default format, you can customize the alias of the `options` through the `props` attribute

Element Plus's `props` names the fields an option carries.

```{r props, eval = FALSE, shot = TRUE}
el_segmented(
  "seg_props",
  value = "Mon",
  options = c("Mon", "Tue", "Wed", "Thu", "Fri")
)
```

## Block

Set `block` to `true` to fit the width of parent element.

```{r block, eval = FALSE, shot = TRUE}
el_segmented(
  "seg_block",
  block = TRUE,
  value = "Mon",
  options = c("Mon", "Tue", "Wednesday", "Thu", "Fri", "Saturday", "Sun")
)
```

## Custom Content

Set default slot to render custom content.

```{r custom-content, eval = FALSE, shot = TRUE}
el_segmented(
  "seg_icons",
  value = "Apple",
  options = list(
    list(label = "Apple", value = "Apple", icon = "Apple"),
    list(label = "Cherry", value = "Cherry", icon = "Cherry"),
    list(label = "Grape", value = "Grape", icon = "Grape")
  ),
  slots = list(
    default = template(
      htmltools::HTML(paste0(
        "<div style=\"display: flex; flex-direction: column; align-items: center; gap: 8px; padding: 8px\">",
        "<el-icon size=\"20\"><component :is=\"scope.item.icon\" /></el-icon><div>{{ scope.item.label }}</div></div>"
      )),
      scope = "scope"
    )
  )
)
```

## Custom Style

Set custom styles using CSS variables.

```{r custom-style, eval = FALSE, shot = TRUE}
tags$div(
  style = paste(
    "--el-segmented-item-selected-color: var(--el-text-color-primary);",
    "--el-segmented-item-selected-bg-color: #ffd100; --el-border-radius-base: 16px"
  ),
  el_segmented(
    "seg_style",
    value = "Mon",
    options = c("Mon", "Tue", "Wed", "Thu", "Fri")
  )
)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("segmented")
```
