---
title: "Virtualized Select"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

> **Tip**
>
> This component is still under testing, if you found any bug or issue please report it at [GitHub](https://github.com/element-plus/element-plus/issues) for us to fix.

## Background

In some use-cases, a single selector may end up loading tens of thousands of rows of data.
Rendering that much data into the DOM could be a burden to the browser, which can result in performance issues.
For a better user and developer experience, we decided to add this component.

## Basic usage

The simplest selector

```{r basic-usage, eval = FALSE, shot = TRUE}
el_select_v2(
  "v2_basic",
  options = paste("Option", 1:1000),
  placeholder = "Please select",
  width = "240px"
)
```

## Multi select

The basic multi-select selector with tags

```{r multiple, eval = FALSE, shot = TRUE}
opts <- paste("Option", 1:1000)
tags$div(
  style = "display: grid; gap: 16px",
  el_select_v2(
    "v2_m1",
    options = opts,
    multiple = TRUE,
    placeholder = "Please select",
    width = "240px"
  ),
  el_select_v2(
    "v2_m2",
    options = opts,
    multiple = TRUE,
    collapse_tags = TRUE,
    placeholder = "Please select",
    width = "240px"
  ),
  el_select_v2(
    "v2_m3",
    options = opts,
    multiple = TRUE,
    collapse_tags = TRUE,
    collapse_tags_tooltip = TRUE,
    placeholder = "Please select",
    width = "240px"
  )
)
```

## Sizes

Add `size` attribute to change the size of Select-V2. In addition to the default size, there are two other options: `large`, `small`.

```{r size, eval = FALSE, shot = TRUE}
opts <- paste("Option", 1:1000)
tags$div(
  style = "display: grid; gap: 16px",
  el_select_v2(
    "v2_l",
    options = opts,
    size = "large",
    placeholder = "Please select",
    width = "240px"
  ),
  el_select_v2(
    "v2_d",
    options = opts,
    placeholder = "Please select",
    width = "240px"
  ),
  el_select_v2(
    "v2_s",
    options = opts,
    size = "small",
    placeholder = "Please select",
    width = "240px"
  )
)
```

## Hide extra tags when the selected items are too many

You can collapse tags to a text by using `collapse-tags` attribute. You can check them when mouse hover collapse text by using `collapse-tags-tooltip` attribute.

```{r hide-extra-tags, eval = FALSE, shot = TRUE}
el_select_v2(
  "v2_hide",
  options = paste("Option", 1:1000),
  multiple = TRUE,
  collapse_tags = TRUE,
  max_collapse_tags = 3,
  placeholder = "Please select",
  width = "240px"
)
```

## Filterable multi-select

When the options are overwhelmingly too many, you can use `filterable` option to enable filter feature for finding out the desired option

```{r filterable, eval = FALSE, shot = TRUE}
el_select_v2(
  "v2_filter",
  options = paste("Option", 1:1000),
  filterable = TRUE,
  multiple = TRUE,
  placeholder = "Please select",
  width = "240px"
)
```

## Disabled selector and select options

You can choose to disable selector itself or the option.

```{r disabled, eval = FALSE, shot = TRUE}
tagList(
  el_select_v2(
    "v2_dis1",
    options = list(
      list(value = "a", label = "Option a"),
      list(value = "b", label = "Option b", disabled = TRUE)
    ),
    placeholder = "Please select",
    width = "240px"
  ),
  el_select_v2(
    "v2_dis2",
    options = c("a", "b"),
    disabled = TRUE,
    placeholder = "Please select",
    width = "240px"
  )
)
```

## Option Grouping

We can group option as we wanted, as long as the data satisfies the pattern.

```{r grouping, eval = FALSE, shot = TRUE}
el_select_v2(
  "v2_group",
  placeholder = "Please select",
  width = "240px",
  options = lapply(1:10, function(g) {
    list(
      label = paste("Group", g),
      options = lapply(1:10, function(i) {
        list(value = paste0(g, "-", i), label = paste("Option", g, i))
      })
    )
  })
)
```

## Clearable selector

We can clear all the selected options at once, also applicable for single select.

```{r clearable, eval = FALSE, shot = TRUE}
el_select_v2(
  "v2_clear",
  options = paste("Option", 1:1000),
  multiple = TRUE,
  clearable = TRUE,
  placeholder = "Please select",
  width = "240px"
)
```

## Customized option renderer

We can define our own template for rendering the option in the popup.

```{r customized-option, eval = FALSE, shot = TRUE}
el_select_v2(
  "v2_opt",
  options = paste("Option", 1:1000),
  placeholder = "Please select",
  width = "240px",
  slots = list(
    default = template(
      htmltools::HTML(
        "<div style=\"display: flex; justify-content: space-between\"><span>{{ item.label }}</span><span style=\"color: var(--el-text-color-secondary)\">{{ item.value }}</span></div>"
      ),
      scope = "{ item }"
    )
  )
)
```

## Header of the dropdown

You can customize the header of the dropdown.

Use slot to customize the content.

```{r custom-header, eval = FALSE, shot = TRUE}
el_select_v2(
  "v2_head",
  options = paste("Option", 1:100),
  multiple = TRUE,
  placeholder = "Please select",
  width = "240px",
  slots = list(header = "Header content")
)
```

## Footer of the dropdown

You can customize the footer of the dropdown.

Use slot to customize the content.

```{r custom-footer, eval = FALSE, shot = TRUE}
el_select_v2(
  "v2_foot",
  options = paste("Option", 1:100),
  placeholder = "Please select",
  width = "240px",
  slots = list(footer = "Footer content")
)
```

## Create Option

Create and select new items that are not included in select options

By using the `allow-create` attribute, users can create new items by typing in the input box. Note that for `allow-create` to work, `filterable` must be `true`. This example also demonstrates `default-first-option`. When this attribute is set to `true`, you can select the first option in the current option list by hitting enter without having to navigate with mouse or arrow keys.

> **Tip**
>
> It will be better to set `:reserve-keyword="false"` when use `allow-create`

```{r allow-create, eval = FALSE, shot = TRUE}
el_select_v2(
  "v2_create",
  options = c("HTML", "CSS", "JavaScript"),
  multiple = TRUE,
  filterable = TRUE,
  allow_create = TRUE,
  default_first_option = TRUE,
  placeholder = "Please select",
  width = "240px"
)
```

## Remote search

Enter keywords and search data from server.

Set the value of `filterable` and `remote` with `true` to enable remote search, and you should pass the `remote-method`. `remote-method` is a `Function` that gets called when the input value changes, and its parameter is the current input value.

A `remote_method` of your own, a `JS()` function, fetches options in the
browser; for the server's options use `el_select(remote = TRUE)`.

```{r remote-search, eval = FALSE, shot = TRUE}
el_select_v2(
  "v2_remote",
  filterable = TRUE,
  remote = TRUE,
  placeholder = "Please enter a keyword",
  width = "240px",
  remote_method = JS("function(q) {}")
)
```

## Use value-key attribute

when `options.value` is an object, you should set a unique identity key name for value

::: tip

Before 2.4.0, `value-key` was used both as the unique value of the selected object and as an alias for the value in `options`. Now `value-key` is only used as the unique value of the selected object, and the alias for the value in options is `props.value`.

:::

```{r use-valuekey, eval = FALSE, shot = TRUE}
el_select_v2(
  "v2_vkey",
  value_key = "id",
  placeholder = "Please select",
  width = "240px",
  options = list(
    list(value = list(id = 1, name = "a"), label = "Option a"),
    list(value = list(id = 2, name = "b"), label = "Option b")
  )
)
```

## Aliases for custom options

When your `options` format is different from the default format, you can customize the alias of the `options` through the `props` attribute

`props` names the fields each option carries.

```{r props, eval = FALSE, shot = TRUE}
el_select_v2(
  "v2_props",
  placeholder = "Please select",
  width = "240px",
  options = c("Option 1", "Option 2", "Option 3")
)
```

## Custom Tag

You can customize tags.

Insert customized tags into the slot of `el-select`. `collapse-tags`, `collapse-tags-tooltip`, `max-collapse-tags` will not work.

```{r custom-tag, eval = FALSE, shot = TRUE}
el_select_v2(
  "v2_tag",
  options = c("Red" = "#ff0000", "Green" = "#00ff00"),
  value = c("#ff0000"),
  multiple = TRUE,
  placeholder = "Please select",
  width = "240px"
)
```

## Custom Loading

Override loading content.

```{r custom-loading, eval = FALSE, shot = TRUE}
el_select_v2(
  "v2_load",
  loading = TRUE,
  filterable = TRUE,
  remote = TRUE,
  placeholder = "Please enter a keyword",
  width = "240px",
  remote_method = JS("function(q) {}"),
  slots = list(loading = el_icon("Loading", class = "is-loading"))
)
```

## Empty Values

If you want to support empty string, please set `empty-values` to `[null, undefined]`.

If you want to change the clear value to `null`, please set `value-on-clear` to `null`.

```{r empty-values, eval = FALSE, shot = TRUE}
el_select_v2(
  "v2_empty",
  options = c("Option1", "Option2"),
  clearable = TRUE,
  empty_values = list(NULL),
  value_on_clear = NULL,
  placeholder = "Please select",
  width = "240px"
)
```

## Custom Label

You can customize label.

```{r custom-label, eval = FALSE, shot = TRUE}
el_select_v2(
  "v2_label",
  options = c("Option1", "Option2"),
  value = "Option1",
  width = "240px",
  slots = list(
    label = template(
      htmltools::HTML("<span>{{ label }}: </span><b>{{ value }}</b>"),
      slot = "label",
      scope = "{ label, value }"
    )
  )
)
```

## Custom Width

The width of dropdown box is calculated by default based on the value of `label`. If you customize the dropdown box options through the `default slot`, it is likely that the text displayed in the options is not equal to the value of `label`, resulting in calculation errors. In this case, you can set the `fit-input-width` attribute to a number to fix its width.

```{r custom-width, eval = FALSE, shot = TRUE}
el_select_v2(
  "v2_width",
  options = paste("A much longer option, number", 1:100),
  fit_input_width = FALSE,
  placeholder = "Please select",
  width = "240px"
)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("select-v2")
```
