---
title: "Select"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

When there are plenty of options, use a drop-down menu to display and select desired ones.

> **Tip**
>
> After version 2.5.0, the default width of `el-select` changed to `100%`. When used in a inline form, the width will collapse. In order to display the width properly, you need to give `el-select` a specific width (eg: [Example](https://github.com/element-plus/element-plus/issues/15834#issuecomment-1936919229)) .

## Basic usage

`v-model` is the value of `el-option` that is currently selected.

```{r basic-usage, eval = FALSE, shot = TRUE}
opts <- c("Option1", "Option2", "Option3", "Option4", "Option5")
tags$div(
  style = "display: flex; gap: 16px",
  el_select(
    "sel_l",
    choices = opts,
    placeholder = "Select",
    size = "large",
    width = "240px"
  ),
  el_select("sel_d", choices = opts, placeholder = "Select", width = "240px"),
  el_select(
    "sel_s",
    choices = opts,
    placeholder = "Select",
    size = "small",
    width = "240px"
  )
)
```

## Options attribute

Shortcut from basic `el-option` usage. You can customize the alias of the `options` through the `props` attribute.

```{r options, eval = FALSE, shot = TRUE}
el_select(
  "sel_opts",
  placeholder = "Select",
  width = "240px",
  choices = list(
    el_option("Option 1", "Option1"),
    el_option("Option 2", "Option2"),
    el_option("Option 3", "Option3", disabled = TRUE)
  )
)
```

## Disabled option

Set the value of `disabled` in `el-option` to `true` to disable this option.

```{r disabled-option, eval = FALSE, shot = TRUE}
el_select(
  "sel_dis_opt",
  placeholder = "Select",
  width = "240px",
  choices = list(
    el_option("Option1"),
    el_option("Option2", disabled = TRUE),
    el_option("Option3")
  )
)
```

## Disabled select

Disable the whole component.

Set `disabled` of `el-select` to make it disabled.

```{r disabled, eval = FALSE, shot = TRUE}
el_select(
  "sel_dis",
  choices = c("Option1", "Option2"),
  placeholder = "Select",
  disabled = TRUE,
  width = "240px"
)
```

## Clearable

You can clear Select using a clear icon.

Set `clearable` attribute for `el-select` and a clear icon will appear.

```{r clearable, eval = FALSE, shot = TRUE}
el_select(
  "sel_clear",
  choices = c("Option1", "Option2", "Option3"),
  selected = "Option1",
  clearable = TRUE,
  width = "240px"
)
```

## Sizes

Add `size` attribute to change the size of Select. In addition to the default size, there are two other options: `large`, `small`.

```{r size, eval = FALSE, shot = TRUE}
opts <- c("Option1", "Option2", "Option3")
tags$div(
  style = "display: grid; gap: 16px",
  el_select("sel_sz_l", choices = opts, size = "large", width = "240px"),
  el_select("sel_sz_d", choices = opts, width = "240px"),
  el_select("sel_sz_s", choices = opts, size = "small", width = "240px")
)
```

## Basic multiple select

Multiple select uses tags to display selected options.

Set `multiple` attribute for `el-select` to enable multiple mode. In this case, the value of `v-model` will be an array of selected options. By default the selected options will be displayed as Tags. You can collapse them to a text by using `collapse-tags` attribute. You can check them when mouse hover collapse text by using `collapse-tags-tooltip` attribute.

```{r multiple, eval = FALSE, shot = TRUE}
opts <- c("Option1", "Option2", "Option3", "Option4", "Option5")
tags$div(
  style = "display: grid; gap: 16px",
  el_select(
    "sel_m1",
    choices = opts,
    multiple = TRUE,
    placeholder = "Select",
    width = "240px"
  ),
  el_select(
    "sel_m2",
    choices = opts,
    multiple = TRUE,
    collapse_tags = TRUE,
    placeholder = "Select",
    width = "240px"
  ),
  el_select(
    "sel_m3",
    choices = opts,
    multiple = TRUE,
    collapse_tags = TRUE,
    collapse_tags_tooltip = TRUE,
    placeholder = "Select",
    width = "240px"
  ),
  el_select(
    "sel_m4",
    choices = opts,
    multiple = TRUE,
    collapse_tags = TRUE,
    collapse_tags_tooltip = TRUE,
    max_collapse_tags = 3,
    placeholder = "Select",
    width = "240px"
  )
)
```

## Custom template

You can customize HTML templates for options.

Insert customized HTML templates into the slot of `el-option`.

```{r custom-template, eval = FALSE, shot = TRUE}
el_select(
  "sel_tpl",
  placeholder = "Select",
  width = "240px",
  choices = list(
    list(value = "Beijing", label = "Beijing", code = "BJ"),
    list(value = "Shanghai", label = "Shanghai", code = "SH"),
    list(value = "Nanjing", label = "Nanjing", code = "NJ")
  ),
  option_template = tagList(
    tags$span(style = "float: left", "{{ opt.label }}"),
    tags$span(
      style = "float: right; color: var(--el-text-color-secondary); font-size: 13px",
      "{{ opt.code }}"
    )
  )
)
```

## Header of the dropdown

You can customize the header of the dropdown.

Use slot to customize the content.

```{r custom-header, eval = FALSE, shot = TRUE}
el_select(
  "sel_head",
  choices = c("Option1", "Option2", "Option3"),
  multiple = TRUE,
  clearable = TRUE,
  collapse_tags = TRUE,
  placeholder = "Select",
  width = "240px",
  slots = list(header = el_checkbox("sel_all", "All"))
)
```

## Footer of the dropdown

You can customize the footer of the dropdown.

Use slot to customize the content.

```{r custom-footer, eval = FALSE, shot = TRUE}
el_select(
  "sel_foot",
  choices = c("Option1", "Option2", "Option3"),
  placeholder = "Select",
  width = "240px",
  slots = list(
    footer = el_button("sel_add", "Add an option", text = TRUE, size = "small")
  )
)
```

## Grouping

Display options in groups.

Use `el-option-group` to group the options, and its `label` attribute stands for the name of the group.

```{r grouping, eval = FALSE, shot = TRUE}
el_select(
  "sel_group",
  placeholder = "Select",
  width = "240px",
  choices = list(
    "Popular cities" = c(Shanghai = "Shanghai", Beijing = "Beijing"),
    "City name" = c(
      Chengdu = "Chengdu",
      Shenzhen = "Shenzhen",
      Guangzhou = "Guangzhou",
      Dalian = "Dalian"
    )
  )
)
```

## Option filtering

You can filter options for your desired ones.

Adding `filterable` to `el-select` enables filtering. By default, Select will find all the options whose `label` attribute contains the input value. If you prefer other filtering strategies, you can pass the `filter-method`. `filter-method` is a `Function` that gets called when the input value changes, and its parameter is the current input value.

```{r filterable, eval = FALSE, shot = TRUE}
el_select(
  "sel_filter",
  choices = c("Option1", "Option2", "Option3", "Option4"),
  filterable = TRUE,
  placeholder = "Select",
  width = "240px"
)
```

## Remote Search

Enter keywords and search data from server.

Set the value of `filterable` and `remote` with `true` to enable remote search, and you should pass the `remote-method`. `remote-method` is a `Function` that gets called when the input value changes, and its parameter is the current input value. Note that if `el-option` is rendered with the `v-for` directive, you should add the `key` attribute for `el-option`. Its value needs to be unique, such as `item.value` in the following example.

The server does the search: `input$<id>_query` is the text typed, and
`update_el_select(choices =)` answers it.

```{r remote-search, eval = FALSE, shot = TRUE}
el_select(
  "sel_remote",
  multiple = TRUE,
  filterable = TRUE,
  remote = TRUE,
  reserve_keyword = FALSE,
  placeholder = "Please enter a keyword",
  width = "240px"
)
```

## Create new items

Create and select new items that are not included in select options

By using the `allow-create` attribute, users can create new items by typing in the input box. Note that for `allow-create` to work, `filterable` must be `true`. This example also demonstrates `default-first-option`. When this attribute is set to `true`, you can select the first option in the current option list by hitting enter without having to navigate with mouse or arrow keys.

```{r allow-create, eval = FALSE, shot = TRUE}
el_select(
  "sel_create",
  choices = c("HTML", "CSS", "JavaScript"),
  multiple = TRUE,
  filterable = TRUE,
  allow_create = TRUE,
  default_first_option = TRUE,
  reserve_keyword = FALSE,
  placeholder = "Choose tags for your article",
  width = "240px"
)
```

## Use value-key attribute

If the binding value of Select is an object, make sure to assign `value-key` as its unique identity key name.

By using the `value-key` attribute, data with duplicate labels can be properly handled. The value of the `label` property is duplicated, but the option can be identified through the `id`.

Values that are objects need `value_key`, the field that tells them apart.

```{r value-key, eval = FALSE, shot = TRUE}
el_select(
  "sel_vkey",
  value_key = "id",
  placeholder = "Select",
  width = "240px",
  choices = list(
    el_option("Option A", list(id = 1, name = "Option A")),
    el_option("Option B", list(id = 2, name = "Option B"))
  )
)
```

## Custom Tag

You can customize tags.

Insert customized tags into the slot of `el-select`. `collapse-tags`, `collapse-tags-tooltip`, `max-collapse-tags` will not work.

```{r custom-tag, eval = FALSE, shot = TRUE}
el_select(
  "sel_tag",
  choices = c("Red" = "#ff0000", "Green" = "#00ff00", "Blue" = "#0000ff"),
  selected = c("#ff0000", "#00ff00"),
  multiple = TRUE,
  placeholder = "Select",
  width = "240px",
  slots = list(
    tag = template(
      htmltools::HTML(
        "<el-tag v-for=\"color in value\" :key=\"color\" :color=\"color\" closable :style=\"{ color: '#fff' }\">{{ color }}</el-tag>"
      ),
      slot = "tag",
      scope = "{ value }"
    )
  )
)
```

## Custom Loading

Override loading content.

```{r custom-loading, eval = FALSE, shot = TRUE}
el_select(
  "sel_load",
  remote = TRUE,
  filterable = TRUE,
  loading = TRUE,
  placeholder = "Please enter a keyword",
  width = "240px",
  slots = list(loading = el_icon("Loading", class = "is-loading"))
)
```

## Empty Values

If you want to support empty string, please set `empty-values` to `[null, undefined]`.

If you want to change the clear value to `null`, please set `value-on-clear` to `null`.

```{r empty-values, eval = FALSE, shot = TRUE}
el_select(
  "sel_empty",
  choices = c("Option1", "Option2"),
  clearable = TRUE,
  empty_values = list(NULL),
  value_on_clear = NULL,
  placeholder = "Select",
  width = "240px"
)
```

## Custom Label

You can customize label.

```{r custom-label, eval = FALSE, shot = TRUE}
el_select(
  "sel_label",
  choices = c("Option1", "Option2", "Option3"),
  selected = "Option1",
  width = "240px",
  slots = list(
    label = template(
      htmltools::HTML(
        "<span>{{ label }}: </span><span style=\"font-weight: bold\">{{ value }}</span>"
      ),
      slot = "label",
      scope = "{ label, value }"
    )
  )
)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("select")
```
