---
title: "Skeleton"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

When loading data, and you need a rich experience for visual and interactions for your end users, you can choose `skeleton`.

## Basic usage

The basic skeleton.

```{r basic-usage, eval = FALSE, shot = TRUE}
el_skeleton()
```

## Configurable Rows

You can configure the row numbers yourself, for more precise rendering effect, the actual rendered row number will always be 1 row more than the given number, that is because we are rendering a title row with 33% width of the others.

```{r configurable-rows, eval = FALSE, shot = TRUE}
el_skeleton(rows = 5)
```

## Animation

We have provided a switch flag indicating whether showing the loading animation, called `animated` when this is true, all children of `el-skeleton` will show animation

```{r animation, eval = FALSE, shot = TRUE}
el_skeleton(rows = 5, animated = TRUE)
```

## Customized Template

Element Plus only provides the most common template, sometimes that could be a problem, so you have a slot named `template` to do that work.

Also we have provided different types skeleton unit that you can choose, for more detailed info, please scroll down to the bottom of this page to see the API description. Also, when building your own customized skeleton structure, you should be structuring them as closer to the real DOM as possible, which avoiding the DOM bouncing caused by the height difference.

```{r customized-template, eval = FALSE, shot = TRUE}
el_skeleton(
  width = "240px",
  slots = list(
    template = tagList(
      el$skeleton_item(
        variant = "image",
        style = "width: 240px; height: 240px"
      ),
      tags$div(
        style = "padding: 14px",
        el$skeleton_item(variant = "p", style = "width: 50%"),
        tags$div(
          style = "display: flex; align-items: center; justify-items: space-between; margin-top: 16px; height: 16px",
          el$skeleton_item(variant = "text", style = "margin-right: 16px"),
          el$skeleton_item(variant = "text", style = "width: 30%")
        )
      )
    )
  )
)
```

## Loading state

When `Loading` ends, we always need to show the real UI with data to our end users. with the attribute `loading` we can control whether showing the DOM. You can also use slot `default` to structure the real DOM element.

The switch turns the placeholder off and on with
`update_el_skeleton(loading =)`.

```{r loading-state, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#sk_switch .el-switch').click()", shot_expect = "document.querySelector('#sk_load .el-card img') && !document.querySelector('#sk_load .el-skeleton__item')"}
hamburger <- "https://shadow.elemecdn.com/app/element/hamburger.9cf7b091-55e9-11e9-a976-7f4d0b07eef6.png"
placeholder <- function(height = "240px") {
  tagList(
    el$skeleton_item(
      variant = "image",
      style = paste0("width: 240px; height: ", height)
    ),
    tags$div(
      style = "padding: 14px",
      el$skeleton_item(variant = "h3", style = "width: 50%"),
      tags$div(
        style = "display: flex; align-items: center; justify-items: space-between; margin-top: 16px; height: 16px",
        el$skeleton_item(variant = "text", style = "margin-right: 16px"),
        el$skeleton_item(variant = "text", style = "width: 30%")
      )
    )
  )
}
card <- function(src, name, button = "Operation button") {
  el_card(
    body_style = list(padding = "0px", marginBottom = "1px"),
    tags$img(src = src, style = "width: 100%; display: block"),
    tags$div(
      style = "padding: 14px",
      tags$span(name),
      tags$div(
        style = "margin-top: 13px; line-height: 12px; display: flex; justify-content: space-between; align-items: center",
        tags$div(
          style = "font-size: 12px; color: #999",
          format(Sys.Date(), "%a %b %d %Y")
        ),
        el_button(label = button, text = TRUE)
      )
    )
  )
}
switch_ui <- function(id, value) {
  tags$div(
    tags$label(style = "margin-right: 16px", "Switch Loading"),
    el_switch(id, value = value)
  )
}
ui <- el_page(
  tags$div(
    style = "display: flex; flex-direction: column; align-items: flex-start; gap: 8px",
    switch_ui("sk_switch", TRUE),
    el_skeleton(
      "sk_load",
      loading = TRUE,
      animated = TRUE,
      style = "width: 240px",
      card(hamburger, "Delicious hamburger"),
      slots = list(template = placeholder())
    )
  )
)
server <- function(input, output, session) {
  observeEvent(input$sk_switch, ignoreInit = TRUE, {
    update_el_skeleton(session, "sk_load", loading = input$sk_switch)
  })
}
shinyApp(ui, server)
```

## Rendering a list of data

Most of the time, skeleton is used as indicators of rendering a list of data which haven't been fetched from server yet, then we need to create a list of skeleton out of no where to make it look like it is loading, with `count` attribute, you can control how many these templates you need to render to the browser.

> **Tip**
>
> We do not recommend rendering lots of fake UI to the browser, it will still cause the performance issue, it also costs longer to destroy the skeleton. Keep `count` as small as it can be to make better user experience.

The button shows the placeholders again for two seconds, as a reload
would.

```{r rendering-with-data, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#sk_reload button').click()", shot_wait = 0.5, shot_expect = "document.querySelectorAll('#sk_list .el-skeleton__image').length === 3"}
pictures <- c(
  Deer = "https://fuss10.elemecdn.com/a/3f/3302e58f9a181d2509f3dc0fa68b0jpeg.jpeg",
  Horse = "https://fuss10.elemecdn.com/1/34/19aa98b1fcb2781c4fba33d850549jpeg.jpeg",
  "Mountain Lion" = "https://fuss10.elemecdn.com/0/6f/e35ff375812e6b0020b6b4e8f9583jpeg.jpeg"
)
card <- function(src, name) {
  el_card(
    body_style = list(padding = "0px", marginBottom = "1px"),
    style = "flex: 1",
    tags$img(src = src, style = "max-width: 100%; display: block"),
    tags$div(
      style = "padding: 14px",
      tags$span(name),
      tags$div(
        style = "margin-top: 13px; line-height: 12px; display: flex; justify-content: space-between; align-items: center",
        tags$div(
          style = "font-size: 12px; color: #999",
          format(Sys.Date(), "%a %b %d %Y")
        ),
        el_button(label = "Operation button", text = TRUE)
      )
    )
  )
}
ui <- el_page(
  tags$div(
    style = "display: flex; flex-direction: column; gap: 8px",
    tags$div(el_button("sk_reload", "Click me to reload")),
    el_skeleton(
      "sk_list",
      loading = FALSE,
      animated = TRUE,
      count = 3,
      style = "display: flex; gap: 8px",
      tags$div(
        style = "display: flex; gap: 8px",
        unname(Map(card, pictures, names(pictures)))
      ),
      slots = list(
        template = tags$div(
          style = "flex: 1",
          el$skeleton_item(variant = "image", style = "height: 240px"),
          tags$div(
            style = "padding: 14px",
            el$skeleton_item(variant = "h3", style = "width: 50%"),
            tags$div(
              style = "display: flex; align-items: center; justify-items: space-between; margin-top: 16px; height: 16px",
              el$skeleton_item(variant = "text", style = "margin-right: 16px"),
              el$skeleton_item(variant = "text", style = "width: 30%")
            )
          )
        )
      )
    )
  )
)
server <- function(input, output, session) {
  observeEvent(input$sk_reload, {
    update_el_skeleton(session, "sk_list", loading = TRUE)
    later::later(
      function() update_el_skeleton(session, "sk_list", loading = FALSE),
      2
    )
  })
}
shinyApp(ui, server)
```

## Avoiding rendering bouncing.

Sometimes API responds very quickly, when that happens, the skeleton just gets rendered to the DOM then it needs to switch back to real DOM, that causes the sudden flashy. To avoid such thing, you can use the `throttle` attribute.

> **Tip**
>
> Since 2.8.8, the `throttle` attribute supports two values: `number` and `object`. When passing a `number`, it is equivalent to `{leading: xxx}`, controlling the throttling of the skeleton screen display. Of course, you can also control the throttling of the skeleton screen disappearance by passing `{trailing: xxx}`

The placeholder shows only when loading lasts longer than `throttle`: switch it on and off quickly, and it never appears.

```{r avoiding-rendering-bouncing, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#sk_throttle_switch .el-switch').click()", shot_wait = 1.5, shot_expect = "document.querySelector('#sk_throttle .el-skeleton__item')"}
hamburger <- "https://shadow.elemecdn.com/app/element/hamburger.9cf7b091-55e9-11e9-a976-7f4d0b07eef6.png"
ui <- el_page(
  tags$div(
    style = "display: flex; flex-direction: column; align-items: flex-start; gap: 8px",
    tags$div(
      tags$label(style = "margin-right: 16px", "Switch Loading"),
      el_switch("sk_throttle_switch", value = FALSE)
    ),
    el_skeleton(
      "sk_throttle",
      loading = FALSE,
      animated = TRUE,
      throttle = 500,
      style = "width: 240px",
      el_card(
        body_style = list(padding = "0px", marginBottom = "1px"),
        tags$img(src = hamburger, style = "width: 100%; display: block"),
        tags$div(
          style = "padding: 14px",
          tags$span("Delicious hamburger"),
          tags$div(
            style = "margin-top: 13px; line-height: 12px; display: flex; justify-content: space-between; align-items: center",
            tags$div(
              style = "font-size: 12px; color: #999",
              format(Sys.Date(), "%a %b %d %Y")
            ),
            el_button(label = "operation button", text = TRUE)
          )
        )
      ),
      slots = list(
        template = tagList(
          el$skeleton_item(
            variant = "image",
            style = "width: 240px; height: 265px"
          ),
          tags$div(
            style = "padding: 14px",
            el$skeleton_item(variant = "h3", style = "width: 50%"),
            tags$div(
              style = "display: flex; align-items: center; justify-items: space-between; margin-top: 16px; height: 16px",
              el$skeleton_item(variant = "text", style = "margin-right: 16px"),
              el$skeleton_item(variant = "text", style = "width: 30%")
            )
          )
        )
      )
    )
  )
)
server <- function(input, output, session) {
  observeEvent(input$sk_throttle_switch, ignoreInit = TRUE, {
    update_el_skeleton(
      session,
      "sk_throttle",
      loading = input$sk_throttle_switch
    )
  })
}
shinyApp(ui, server)
```

## Initial rendering loading

When the initial value of loading is true, you can set `throttle: {initVal: true, leading: xxx}` to control the immediate display of the initial skeleton screen without throttling.

`initVal = TRUE` shows the placeholder from the start; afterwards it appears only after the leading delay.

```{r initial-rendering-loading, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#sk_initial_switch .el-switch').click()", shot_wait = 1.5, shot_expect = "document.querySelector('#sk_initial .el-card img')"}
hamburger <- "https://shadow.elemecdn.com/app/element/hamburger.9cf7b091-55e9-11e9-a976-7f4d0b07eef6.png"
ui <- el_page(
  tags$div(
    style = "display: flex; flex-direction: column; align-items: flex-start; gap: 8px",
    tags$div(
      tags$label(style = "margin-right: 16px", "Switch Loading"),
      el_switch("sk_initial_switch", value = TRUE)
    ),
    el_skeleton(
      "sk_initial",
      loading = TRUE,
      animated = TRUE,
      throttle = list(leading = 500, initVal = TRUE),
      style = "width: 240px",
      el_card(
        body_style = list(padding = "0px", marginBottom = "1px"),
        tags$img(src = hamburger, style = "width: 100%; display: block"),
        tags$div(
          style = "padding: 14px",
          tags$span("Delicious hamburger"),
          tags$div(
            style = "margin-top: 13px; line-height: 12px; display: flex; justify-content: space-between; align-items: center",
            tags$div(
              style = "font-size: 12px; color: #999",
              format(Sys.Date(), "%a %b %d %Y")
            ),
            el_button(label = "operation button", text = TRUE)
          )
        )
      ),
      slots = list(
        template = tagList(
          el$skeleton_item(
            variant = "image",
            style = "width: 240px; height: 265px"
          ),
          tags$div(
            style = "padding: 14px",
            el$skeleton_item(variant = "h3", style = "width: 50%"),
            tags$div(
              style = "display: flex; align-items: center; justify-items: space-between; margin-top: 16px; height: 16px",
              el$skeleton_item(variant = "text", style = "margin-right: 16px"),
              el$skeleton_item(variant = "text", style = "width: 30%")
            )
          )
        )
      )
    )
  )
)
server <- function(input, output, session) {
  observeEvent(input$sk_initial_switch, ignoreInit = TRUE, {
    update_el_skeleton(session, "sk_initial", loading = input$sk_initial_switch)
  })
}
shinyApp(ui, server)
```

## Toggle show/hide without rending bouncing

> **Tip**
>
> You can set `throttle: {initVal: true, leading: xxx, trailing: xxx}` to control the initial display of the skeleton effect and to make the transition of the skeleton more smooth when switching loading states.

Sometimes you want to render the business components more smoothly when loading toggle show or hide. You can use set the `throttle: {leading: xxx, trailing:xxx}` to control the rendering bouncing.

`leading` delays the placeholder, `trailing` keeps it a while after loading ends.

```{r leading-trailing-without-bouncing, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#sk_lt_switch .el-switch').click()", shot_wait = 1.5, shot_expect = "document.querySelector('#sk_lt .el-skeleton__item')"}
hamburger <- "https://shadow.elemecdn.com/app/element/hamburger.9cf7b091-55e9-11e9-a976-7f4d0b07eef6.png"
ui <- el_page(
  tags$div(
    style = "display: flex; flex-direction: column; align-items: flex-start; gap: 8px",
    tags$div(
      tags$label(style = "margin-right: 16px", "Switch Loading"),
      el_switch("sk_lt_switch", value = FALSE)
    ),
    el_skeleton(
      "sk_lt",
      loading = FALSE,
      animated = TRUE,
      throttle = list(leading = 500, trailing = 500, initVal = TRUE),
      style = "width: 240px",
      el_card(
        body_style = list(padding = "0px", marginBottom = "1px"),
        tags$img(src = hamburger, style = "width: 100%; display: block"),
        tags$div(
          style = "padding: 14px",
          tags$span("Delicious hamburger"),
          tags$div(
            style = "margin-top: 13px; line-height: 12px; display: flex; justify-content: space-between; align-items: center",
            tags$div(
              style = "font-size: 12px; color: #999",
              format(Sys.Date(), "%a %b %d %Y")
            ),
            el_button(label = "operation button", text = TRUE)
          )
        )
      ),
      slots = list(
        template = tagList(
          el$skeleton_item(
            variant = "image",
            style = "width: 240px; height: 265px"
          ),
          tags$div(
            style = "padding: 14px",
            el$skeleton_item(variant = "h3", style = "width: 50%"),
            tags$div(
              style = "display: flex; align-items: center; justify-items: space-between; margin-top: 16px; height: 16px",
              el$skeleton_item(variant = "text", style = "margin-right: 16px"),
              el$skeleton_item(variant = "text", style = "width: 30%")
            )
          )
        )
      )
    )
  )
)
server <- function(input, output, session) {
  observeEvent(input$sk_lt_switch, ignoreInit = TRUE, {
    update_el_skeleton(session, "sk_lt", loading = input$sk_lt_switch)
  })
}
shinyApp(ui, server)
```

##

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("skeleton")
```
