---
title: "Skeleton"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

A placeholder while data loads. `update_el_skeleton(loading = FALSE)` swaps
in the real content, given in `...`.

## Basic usage

```{r basic, eval = FALSE, shot = TRUE}
el_skeleton("sk1")
```

## Configurable rows

```{r rows, eval = FALSE, shot = TRUE}
el_skeleton("sk2", rows = 6)
```

## Animation

```{r animated, eval = FALSE, shot = TRUE}
el_skeleton("sk3", rows = 6, animated = TRUE)
```

## Customized template

The `template` slot draws the placeholder, from `el$skeleton_item()`s.

```{r template, eval = FALSE, shot = TRUE}
el_skeleton("sk4", slots = list(template = tags$div(style = "width: 240px",
  el$skeleton_item(variant = "image", style = "width: 240px; height: 240px"),
  tags$div(style = "padding: 14px",
    el$skeleton_item(variant = "p", style = "width: 50%"),
    tags$div(style = "display: flex; justify-content: space-between; margin-top: 16px",
      el$skeleton_item(variant = "text", style = "margin-right: 16px"),
      el$skeleton_item(variant = "text", style = "width: 30%"))))))
```

## Loading state

```{r loading, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#done_container .el-switch').click()", shot_wait = 1.5}
ui <- el_page(
  el_switch("done", active_text = "Loaded"),
  el_skeleton("card", rows = 4, animated = TRUE,
    el_card(header = "Delicious hamburger", tags$p("Tasty as it looks."))))

server <- function(input, output, session) {
  observeEvent(input$done, update_el_skeleton(id = "card", loading = !input$done))
}

shinyApp(ui, server)
```

## Rendering a list of data

`count` repeats the placeholder.

```{r count, eval = FALSE, shot = TRUE}
el_skeleton("sk5", count = 3, rows = 1)
```

## Avoiding rendering bouncing

`throttle` waits that many milliseconds before showing the placeholder,
so a quick load never flashes it.

```{r throttle, eval = FALSE, shot = TRUE}
el_skeleton("sk6", throttle = 500, rows = 2, tags$p("Loaded"))
```

## API

```{r api, echo = FALSE, results = "asis"}
api_tables("skeleton")
```
