---
title: "Slider"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Drag the slider within a fixed range.

## Basic usage

The current value is displayed when the slider is being dragged.

Customize the initial value of the slider by setting the binding value.

```{r basic-usage, eval = FALSE, shot = TRUE}
tags$div(style = "max-width: 600px",
  tags$span("Default value"), el_slider("sl1", value = 0),
  tags$span("Customized initial value"), el_slider("sl2", value = 50),
  tags$span("Hide Tooltip"), el_slider("sl3", value = 36, show_tooltip = FALSE),
  tags$span("Format Tooltip"), el_slider("sl4", value = 48, format_tooltip = JS("function(v) { return v / 100; }")),
  tags$span("Disabled"), el_slider("sl5", value = 42, disabled = TRUE))
```

## Discrete values

The options can be discrete.

Set step size with the `step` attribute. You can display breakpoints by setting the `show-stops` attribute.

```{r discrete-values, eval = FALSE, shot = TRUE}
tags$div(style = "max-width: 600px",
  tags$span("Breakpoints not displayed"), el_slider("sld1", value = 0, step = 10),
  tags$span("Breakpoints displayed"), el_slider("sld2", value = 0, step = 10, show_stops = TRUE))
```

## Slider with input box

Set value via a input box.

Set the `show-input` attribute to display an input box on the right.

```{r slider-with-input-box, eval = FALSE, shot = TRUE}
el_slider("sl_input", value = 0, show_input = TRUE, width = "600px")
```

## Sizes

```{r sizes, eval = FALSE, shot = TRUE}
tags$div(style = "max-width: 600px",
  el_slider("sls_l", value = 0, show_input = TRUE, size = "large"),
  el_slider("sls_d", value = 0, show_input = TRUE),
  el_slider("sls_s", value = 0, show_input = TRUE, size = "small"))
```

## Placement

You can custom tooltip placement.

```{r placement, eval = FALSE, shot = TRUE}
tags$div(style = "max-width: 600px; padding-top: 40px",
  el_slider("slp1", value = 0, placement = "top"), el_slider("slp2", value = 0, placement = "bottom"),
  el_slider("slp3", value = 0, placement = "right"), el_slider("slp4", value = 0, placement = "left"))
```

## Range selection

Selecting a range of values is supported.

Setting the `range` attribute activates range mode, where the binding value is an array made up of two boundary values.

```{r range-selection, eval = FALSE, shot = TRUE}
el_slider("sl_range", value = c(4, 8), range = TRUE, show_stops = TRUE, max = 10, width = "600px")
```

## Vertical mode

Setting the `vertical` attribute to `true` enables vertical mode. In vertical mode, the `height` attribute is required.

```{r vertical-mode, eval = FALSE, shot = TRUE}
el_slider("sl_vert", value = 0, vertical = TRUE, height = "200px")
```

## Show marks

Setting this `marks` attribute can show mark on slider.

```{r show-marks, eval = FALSE, shot = TRUE}
el_slider("sl_marks", value = c(30, 60), range = TRUE, width = "600px",
          marks = list("0" = "0°C", "8" = "8°C", "37" = "37°C",
                       "50" = list(style = list(color = "#1989FA"), label = "50%")))
```

## Restrict value

Set `step="mark"` to restrict the slider value to marks.

`min` and `max` bound what can be picked.

```{r restrict-value, eval = FALSE, shot = TRUE}
el_slider("sl_restrict", value = 20, min = 10, max = 80, width = "600px")
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("slider")
```
