---
title: "Space"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Even though we have [Divider](divider.html), but sometimes we need more than one [Divider](divider.html) to split the elements apart, so we stack each elements upon [Divider](divider.html), but doing so not only makes our code ugly but also makes it difficult to maintain. **Space** is this kind of component provides us both productivity and elegance.

## Basic usage

The basic use case is using this component to provide unified space between each components

Using Space to provide space

```{r basic, eval = FALSE, shot = TRUE}
card <- function(i) el_card(width = "250px",
  header = tags$div(style = "display: flex; justify-content: space-between; align-items: center",
    tags$span("Card name"), el_button(paste0("sp_op", i), "Operation button", text = TRUE)),
  lapply(1:4, function(o) tags$div(paste("List item", o))))
el_space(wrap = TRUE, lapply(1:3, card))
```

## Vertical layout

Using `direction` attribute to control the layout, we use `flex-direction` to implement this.

We also provide vertical layout.

```{r vertical-layout, eval = FALSE, shot = TRUE}
card <- function(i) el_card(width = "250px", header = "Card name",
  lapply(1:2, function(o) tags$div(paste("List item", o))))
el_space(direction = "vertical", lapply(1:2, card))
```

## Control the size of the space

Control the space size via `size` API.

You can set the size with built-in sizes `small`, `default`, `large`, these size corresponds to `8px`, `12px`, `16px`. The default size is `small`, A.K.A. `8px`

You can also using customized size to override it. Refer to the next part.

```{r control-size, eval = FALSE, shot = TRUE}
card <- function(i) el_card(width = "250px", header = "Card name", tags$div("List item"))
el_space(direction = "vertical", alignment = "start", size = 30,
         el_space(size = "large", lapply(1:2, card)))
```

## Customized Size

Sometimes built-in sizes could not meet the business needs, we can use custom size (number type) to control the space between items.

```{r customized-size, eval = FALSE, shot = TRUE}
card <- function(i) el_card(width = "250px", header = "Card name", tags$div("List item"))
el_space(wrap = TRUE, size = 20, lapply(1:2, card))
```

> **Tip**
>
> Do not use `ElSpace` with components that depend on ancestor width (height), e.g. `ElSlider`, in this case when you drag the trigger button the bar will grow which causes misplacement between cursor and trigger button.

## Auto wrapping

When in **horizontal** mode, using `wrap` (**bool type**) to control auto wrapping behavior.

Using `wrap` to control line wrap

```{r auto-wrapping, eval = FALSE, shot = TRUE}
el_space(wrap = TRUE, lapply(1:20, function(i) el_button(paste0("sp_w", i), "Text button", text = TRUE)))
```

## Spacer

Sometimes we want something more than blank space, so we have (spacer) to help us.

## Literal type spacer

```{r literal-type-spacer, eval = FALSE, shot = TRUE}
el_space(size = 10, spacer = "|", el_button("sp_l1", "button 1"), el_button("sp_l2", "button 2"))
```

## Spacer can also be VNode

> **In R**
>
> A VNode spacer is a Vue render function's; give `spacer` a string -- `"|"`.

## Alignment

Setting this attribute can adjust the alignment of child nodes, the desirable value can be found at [align-items](https://developer.mozilla.org/en-US/docs/Web/CSS/align-items).

Using `alignment`

```{r alignment, eval = FALSE, shot = TRUE}
tags$div(style = "width: 240px; margin-bottom: 8px; padding: 8px; border: 1px solid var(--el-border-color)",
  el_space("string", el_button("sp_a", "button"), el_card(header = "header", "body")))
```

## Fill the container

Through the `fill` **(Boolean type)** parameter, you can control whether the child node automatically fills the container.

In the following example, when set to `fill`, the width of the child node will automatically adapt to the width of the container.

Use fill to automatically fill the container with child nodes

```{r fill, eval = FALSE, shot = TRUE}
el_space(fill = TRUE, wrap = TRUE, lapply(1:3, function(i) el_card(header = "Card name", "List item")))
```

You can also use the `fillRatio` parameter to customize the filling ratio. The default value is `100`, which represents filling based on the width of the parent container at `100%`.

It should be noted that the expression of horizontal layout and vertical layout is slightly different, the specific effect can be viewed in the following example.

Use fillRatio to customize the fill ratio

```{r fill-ratio, eval = FALSE, shot = TRUE}
el_space(fill = TRUE, fill_ratio = 30, wrap = TRUE, lapply(1:5, function(i) el_card(header = "Card name", "List item")))
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("space")
```
