---
title: "Splitter"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Divide the area horizontally or vertically, and freely drag to adjust the size of each area.

## Basic usage

The most basic usage, if no default size is passed, it will be automatically divided equally.

```{r basic, eval = FALSE, shot = TRUE}
panel <- function(x) tags$div(style = "display: flex; align-items: center; justify-content: center; height: 100%", x)
tags$div(style = "height: 250px; box-shadow: var(--el-border-color-light) 0px 0px 10px",
  el_splitter(el_splitter_panel(size = "30%", panel(1)), el_splitter_panel(panel(2))))
```

## Vertical

Use vertical orientation.

```{r vertical, eval = FALSE, shot = TRUE}
panel <- function(x) tags$div(style = "display: flex; align-items: center; justify-content: center; height: 100%", x)
tags$div(style = "height: 250px; box-shadow: var(--el-border-color-light) 0px 0px 10px",
  el_splitter(layout = "vertical", el_splitter_panel(panel(1)), el_splitter_panel(panel(2))))
```

## Collapsible

Configuring `collapsible` provides quick shrinking capability. You can use the `min` property to prevent expanding through dragging after collapsing.

```{r collapsible, eval = FALSE, shot = TRUE}
panel <- function(x) tags$div(style = "display: flex; align-items: center; justify-content: center; height: 100%", x)
tags$div(style = "height: 250px; box-shadow: var(--el-border-color-light) 0px 0px 10px",
  el_splitter(el_splitter_panel(collapsible = TRUE, min = 50, panel(1)),
              el_splitter_panel(collapsible = TRUE, panel(2)),
              el_splitter_panel(panel(3))))
```

## Disable drag

When either panel disables `resizable`, dragging will be disabled.

```{r disabledrag, eval = FALSE, shot = TRUE}
panel <- function(x) tags$div(style = "display: flex; align-items: center; justify-content: center; height: 100%", x)
tags$div(style = "height: 250px; box-shadow: var(--el-border-color-light) 0px 0px 10px",
  el_splitter(el_splitter_panel(resizable = FALSE, panel(1)), el_splitter_panel(panel(2))))
```

## Panel size

`v-model:size` can get the panel size.

Dragging reports `input$<id>_resize_start`, `_resize` and `_resize_end`.

```{r size, eval = FALSE, shot = TRUE}
panel <- function(x) tags$div(style = "display: flex; align-items: center; justify-content: center; height: 100%", x)
tags$div(style = "height: 250px; box-shadow: var(--el-border-color-light) 0px 0px 10px",
  el_splitter(id = "split_size", el_splitter_panel(size = "200px", panel(1)), el_splitter_panel(panel(2))))
```

## Lazy

When `lazy` is enabled, the panel size will not update in real time during dragging, but only after the drag ends.

```{r lazy, eval = FALSE, shot = TRUE}
panel <- function(x) tags$div(style = "display: flex; align-items: center; justify-content: center; height: 100%", x)
tags$div(style = "height: 250px; box-shadow: var(--el-border-color-light) 0px 0px 10px",
  el_splitter(lazy = TRUE, el_splitter_panel(panel(1)), el_splitter_panel(panel(2))))
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("splitter")
```
