---
title: "Splitter"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Divide the area horizontally or vertically, and freely drag to adjust the size of each area.

## Basic usage

The most basic usage, if no default size is passed, it will be automatically divided equally.

```{r basic, eval = FALSE, shot = TRUE}
panel <- function(x) {
  tags$div(
    style = "display: flex; align-items: center; justify-content: center; height: 100%",
    x
  )
}
tags$div(
  style = "height: 250px; box-shadow: var(--el-border-color-light) 0px 0px 10px",
  el_splitter(
    el_splitter_panel(size = "30%", panel(1)),
    el_splitter_panel(panel(2))
  )
)
```

## Vertical

Use vertical orientation.

```{r vertical, eval = FALSE, shot = TRUE}
panel <- function(x) {
  tags$div(
    style = "display: flex; align-items: center; justify-content: center; height: 100%",
    x
  )
}
tags$div(
  style = "height: 250px; box-shadow: var(--el-border-color-light) 0px 0px 10px",
  el_splitter(
    layout = "vertical",
    el_splitter_panel(panel(1)),
    el_splitter_panel(panel(2))
  )
)
```

## Collapsible

Configuring `collapsible` provides quick shrinking capability. You can use the `min` property to prevent expanding through dragging after collapsing.

The switch makes the panels collapsible or not, each by its own id with
`update_el_splitter_panel()` -- the inner splitter's too.

```{r collapsible, eval = FALSE, shot = TRUE, shot_js = c("window.icons = document.querySelectorAll('.el-splitter-bar__collapse-icon').length", "document.querySelector('#spl_collapsible .el-switch').click()"), shot_expect = c("window.icons > 0", "document.querySelectorAll('.el-splitter-bar__collapse-icon').length === 0")}
panel <- function(x) {
  tags$div(
    style = "display: flex; align-items: center; justify-content: center; height: 100%",
    x
  )
}
collapsible <- c("spl_p1", "spl_p2", "spl_p4", "spl_p4a", "spl_p4b")
ui <- el_page(
  tags$div(
    style = "margin-bottom: 8px",
    el_switch(
      "spl_collapsible",
      value = TRUE,
      active_text = "enable",
      inactive_text = "disable",
      inline_prompt = TRUE
    )
  ),
  tags$div(
    style = "height: 250px; box-shadow: var(--el-border-color-light) 0px 0px 10px",
    el_splitter(
      el_splitter_panel(id = "spl_p1", collapsible = TRUE, min = 50, panel(1)),
      el_splitter_panel(id = "spl_p2", collapsible = TRUE, panel(2)),
      el_splitter_panel(panel(3)),
      el_splitter_panel(
        id = "spl_p4",
        collapsible = TRUE,
        el_splitter(
          layout = "vertical",
          el_splitter_panel(id = "spl_p4a", collapsible = TRUE, panel(4)),
          el_splitter_panel(id = "spl_p4b", collapsible = TRUE, panel(5))
        )
      )
    )
  )
)
server <- function(input, output, session) {
  observeEvent(input$spl_collapsible, ignoreInit = TRUE, {
    for (id in collapsible) {
      update_el_splitter_panel(session, id, collapsible = input$spl_collapsible)
    }
  })
}
shinyApp(ui, server)
```

## Disable drag

When either panel disables `resizable`, dragging will be disabled.

The switch lets the middle panel be dragged or not, with
`update_el_splitter_panel(resizable =)`.

```{r disabledrag, eval = FALSE, shot = TRUE, shot_js = c("window.locked = document.querySelectorAll('.el-splitter-bar__dragger.is-disabled').length", "document.querySelector('#spl_resizable .el-switch').click()"), shot_expect = c("window.locked === 2", "document.querySelectorAll('.el-splitter-bar__dragger.is-disabled').length === 0", "document.querySelector('#spl_drag').innerText === 'drag enable'")}
panel <- function(x) {
  tags$div(
    style = "display: flex; align-items: center; justify-content: center; height: 100%",
    x
  )
}
ui <- el_page(
  tags$div(
    style = "margin-bottom: 8px",
    el_switch(
      "spl_resizable",
      value = FALSE,
      active_text = "enable",
      inactive_text = "disable",
      inline_prompt = TRUE
    )
  ),
  tags$div(
    style = "height: 250px; box-shadow: var(--el-border-color-light) 0px 0px 10px",
    el_splitter(
      el_splitter_panel(panel(1)),
      el_splitter_panel(
        id = "spl_middle",
        resizable = FALSE,
        panel(uiOutput("spl_drag"))
      ),
      el_splitter_panel(panel(3))
    )
  )
)
server <- function(input, output, session) {
  output$spl_drag <- renderUI({
    paste("drag", if (isTRUE(input$spl_resizable)) "enable" else "disable")
  })
  observeEvent(input$spl_resizable, ignoreInit = TRUE, {
    update_el_splitter_panel(
      session,
      "spl_middle",
      resizable = input$spl_resizable
    )
  })
}
shinyApp(ui, server)
```

## Panel size

`v-model:size` can get the panel size.

Dragging reports `input$<id>_resize_start`, `_resize` and `_resize_end`.

```{r size, eval = FALSE, shot = TRUE}
panel <- function(x) {
  tags$div(
    style = "display: flex; align-items: center; justify-content: center; height: 100%",
    x
  )
}
tags$div(
  style = "height: 250px; box-shadow: var(--el-border-color-light) 0px 0px 10px",
  el_splitter(
    id = "split_size",
    el_splitter_panel(size = "200px", panel(1)),
    el_splitter_panel(panel(2))
  )
)
```

## Lazy

When `lazy` is enabled, the panel size will not update in real time during dragging, but only after the drag ends.

```{r lazy, eval = FALSE, shot = TRUE}
panel <- function(x) {
  tags$div(
    style = "display: flex; align-items: center; justify-content: center; height: 100%",
    x
  )
}
tags$div(
  style = "height: 250px; box-shadow: var(--el-border-color-light) 0px 0px 10px",
  el_splitter(
    lazy = TRUE,
    el_splitter_panel(panel(1)),
    el_splitter_panel(panel(2))
  )
)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("splitter")
```
