---
title: "Switch"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Switch is used for switching between two opposing states.

## Basic usage

Bind `v-model` to a `Boolean` typed variable. The `--el-switch-on-color` and `--el-switch-off-color` CSS variables decides the background color in two states.

```{r basic, eval = FALSE, shot = TRUE}
tagList(
  el_switch("sw1", value = TRUE),
  el_switch(
    "sw2",
    value = TRUE,
    active_color = "#13ce66",
    inactive_color = "#ff4949"
  )
)
```

## Sizes

```{r sizes, eval = FALSE, shot = TRUE}
tags$div(
  style = "display: flex; gap: 16px; align-items: center",
  el_switch(
    "sw_l",
    value = TRUE,
    size = "large",
    active_text = "Open",
    inactive_text = "Close"
  ),
  el_switch(
    "sw_d",
    value = TRUE,
    active_text = "Open",
    inactive_text = "Close"
  ),
  el_switch(
    "sw_s",
    value = TRUE,
    size = "small",
    active_text = "Open",
    inactive_text = "Close"
  )
)
```

## Text description

You can add `active-text` and `inactive-text` attribute to show texts. use `inline-prompt` attribute to control text is displayed inside dot.

You can add `active-text` and `inactive-text` attribute to show texts.

```{r text-description, eval = FALSE, shot = TRUE}
tags$div(
  style = "display: grid; gap: 12px",
  el_switch(
    "sw_t1",
    value = TRUE,
    active_text = "Pay by month",
    inactive_text = "Pay by year"
  ),
  el_switch(
    "sw_t2",
    value = TRUE,
    inline_prompt = TRUE,
    active_text = "Y",
    inactive_text = "N"
  ),
  el_switch(
    "sw_t3",
    value = TRUE,
    inline_prompt = TRUE,
    active_text = "是",
    inactive_text = "否"
  )
)
```

## Display custom icons

> **Tip**
>
> Use the `active-icon` and `inactive-icon` attribute to add icon. You can pass either string for the component name (registered in advance) or the component itself which is a SVG Vue component. Element Plus has provided a set of icon that you can find at [icon](icon.html)

You can add `active-icon` and `inactive-icon` attribute to show icons. use `inline-prompt` attribute to control icon is displayed inside dot.

```{r custom-icons, eval = FALSE, shot = TRUE}
tags$div(
  style = "display: flex; gap: 16px",
  el_switch(
    "sw_i1",
    value = TRUE,
    active_icon = "Check",
    inactive_icon = "Close"
  ),
  el_switch(
    "sw_i2",
    value = TRUE,
    inline_prompt = TRUE,
    active_icon = "Check",
    inactive_icon = "Close"
  )
)
```

## Extended value types

You can set `active-value` and `inactive-value` attributes. They both receive a `Boolean`, `String` or `Number` typed value.

```{r extended-value-types, eval = FALSE, shot = TRUE}
el_switch(
  "sw_ext",
  value = "100",
  active_value = "100",
  inactive_value = "0",
  active_color = "#13ce66",
  inactive_color = "#ff4949"
)
```

## Disabled

Adding the `disabled` attribute disables Switch.

```{r disabled, eval = FALSE, shot = TRUE}
tagList(
  el_switch("sw_dis1", value = TRUE, disabled = TRUE),
  el_switch("sw_dis2", disabled = TRUE)
)
```

## Loading

Setting the `loading` attribute to `true` indicates a loading state on the Switch.

```{r loading, eval = FALSE, shot = TRUE}
tagList(
  el_switch("sw_ld1", value = TRUE, loading = TRUE),
  el_switch("sw_ld2", loading = TRUE)
)
```

## Prevent switching

set the `before-change` property, If `false` is returned or a `Promise` is returned and then is rejected, will stop switching.

`before_change`, a `JS()` function, may hold the switch -- return `false`,
or a promise.

```{r prevent-switching, eval = FALSE, shot = TRUE}
el_switch(
  "sw_guard",
  before_change = JS(
    "function() { return new Promise(function(r) { setTimeout(function() { r(true); }, 1000); }); }"
  )
)
```

## Custom action icon

You can add `active-action-icon` and `inactive-action-icon` attribute to show icons.

```{r custom-action-icon, eval = FALSE, shot = TRUE}
tags$div(
  style = "display: flex; gap: 16px",
  el_switch(
    "sw_ai1",
    value = TRUE,
    active_action_icon = "View",
    inactive_action_icon = "Hide"
  )
)
```

## Custom action slot

You can use `active-action` and `inactive-action` slot to customize action.

```{r custom-action-slot, eval = FALSE, shot = TRUE}
el_switch(
  "sw_slot",
  value = TRUE,
  slots = list(
    `active-action` = tags$span(class = "custom-active-action", "T"),
    `inactive-action` = tags$span(class = "custom-inactive-action", "F")
  )
)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("switch")
```
