---
title: "Virtualized Table"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Along with evolutionary web development, table component has always been the most popular component in our web apps especially for dashboards, data analysis. For [Table V1](table.html), with even just 1000 records of data, it can be very annoying when using it, because of the poor performance.

With Virtualized Table, you can render massive chunks of data in a blink of an eye.

> **Tip**
>
> This component is **still under testing**, use at your own risk. If you find any bugs or issues, please report them at [GitHub](https://github.com/element-plus/element-plus/issues) for us to fix. Also there were some APIs which are not mentioned in this documentation, some of them were not
> fully developed yet, which is why they are not mentioned here.
> 
> **Even though** Virtualized Table is efficient, when the data load is too large, your **network** and **memory size** can become the bottleneck of your app. So keep in mind that Virtualized Table is never the ultimate solution for everything, consider paginating your data, adding filters etc.

## Basic usage

Let's demonstrate the performance of the Virtualized Table by rendering a basic example with 10 columns and 1000 rows.

A data.frame, its columns made from its variables.

```{r basic, eval = FALSE, shot = TRUE}
df <- as.data.frame(setNames(
  lapply(1:10, function(j) paste0("Row ", 1:1000, " - Col ", j)),
  paste0("column-", 1:10)
))
el_table_v2("tv_basic", data = df, table_v2_width = 700, height = 400)
```

## Auto resizer

When you do not want to manually pass the `width` and `height` properties to the table, you can wrap the table component with the AutoResizer.
This will automatically update the width and height for you.

Resize your browser to see how it works.

> **Tip**
>
> Make sure the parent node of the `AutoResizer` **HAS A FIXED HEIGHT**, since its default height value is set to 100%.
> Alternatively, you can define it by passing the `style` attribute to `AutoResizer`.

Element Plus's table needs a width and height in pixels; give the size
the space has.

```{r auto-resizer, eval = FALSE, shot = TRUE}
df <- data.frame(
  id = 1:1000,
  name = paste("Name", 1:1000),
  value = round(runif(1000) * 100)
)
el_table_v2("tv_auto", data = df, table_v2_width = 700, height = 400)
```

## Customize Cell Renderer{#customize-cell-renderer}

Of course, you can render the table cell according to your needs. Here's a simple example of how to customize your cell.

A cell drawn with a template: the `cell` slot, its scope the row and column.

```{r cell-templating, eval = FALSE, shot = TRUE}
df <- data.frame(
  name = paste("User", 1:200),
  state = sample(c("active", "inactive"), 200, TRUE)
)
el_table_v2(
  "tv_cell",
  data = df,
  table_v2_width = 700,
  height = 300,
  slots = list(
    cell = template(
      htmltools::HTML(paste0(
        "<el-tag v-if=\"column.dataKey === 'state'\" :type=\"rowData.state === 'active' ? 'success' : 'info'\">",
        "{{ rowData.state }}</el-tag><span v-else>{{ rowData[column.dataKey] }}</span>"
      )),
      slot = "cell",
      scope = "{ rowData, column }"
    )
  )
)
```

## Table with selections

Using customized cell renderer to allow selection for your table.

> **In R**
>
> Selection columns are drawn with a JSX cell renderer in Element Plus's demo;
> in R, use `el_table(selection = TRUE)`, or a `cell` slot with a checkbox.

## Inline editing

Just as we demonstrated with selections above, you can use the same method to enable inline editing.

> **In R**
>
> Editing in place is a JSX cell renderer upstream; in R, edit with a `cell`
> slot that holds an input, as `el_table()`'s cell templates do.

## Table with status

You can highlight your table content to distinguish between "success, information, warning, danger" and other states.

To customize the appearance of rows, use the `row-class-name` attribute. For example, every 10th row is highlighted using the `bg-blue-200` class, and every 5th row with the `bg-red-100` class.

```{r row-class, eval = FALSE, shot = TRUE}
df <- data.frame(id = 1:200, name = paste("Name", 1:200))
tagList(
  tags$style(".tv-odd { background: var(--el-color-primary-light-9); }"),
  el_table_v2(
    "tv_rowclass",
    data = df,
    table_v2_width = 700,
    height = 300,
    row_class = JS(
      "function({ rowIndex }) { return rowIndex % 2 ? 'tv-odd' : ''; }"
    )
  )
)
```

## Table with sticky rows

You can make some rows stick to the top of the table, and that can be very easily achieved by using the `fixed-data` attribute.

You can dynamically set the sticky row based on scroll events, as shown in this example.

```{r sticky-rows, eval = FALSE, shot = TRUE}
df <- data.frame(id = 1:200, name = paste("Name", 1:200))
el_table_v2(
  "tv_sticky",
  data = df,
  table_v2_width = 700,
  height = 300,
  fixed_data = list(list(id = "Pinned", name = "Stays on top"))
)
```

## Table with fixed columns

If you want to have columns stick to the left or right for some reason, you can achieve this by adding special attributes to the table.

You can set the column's attribute `fixed` to `true` (representing `FixedDir.LEFT`) or `FixedDir.LEFT` or `FixedDir.RIGHT`

```{r fixed-columns, eval = FALSE, shot = TRUE}
cols <- lapply(1:10, function(j) {
  list(
    key = paste0("c", j),
    dataKey = paste0("c", j),
    title = paste("Column", j),
    width = 150,
    fixed = if (j == 1) {
      "left"
    } else if (j == 10) {
      "right"
    }
  )
})
df <- as.data.frame(setNames(
  lapply(1:10, function(j) paste0("Row ", 1:200, " - Col ", j)),
  paste0("c", 1:10)
))
el_table_v2(
  "tv_fixed",
  data = df,
  columns = cols,
  table_v2_width = 700,
  height = 300,
  fixed = TRUE
)
```

## Grouping header

By customizing your header renderer, you can group your header as shown in this example.

> **Tip**
>
> In this case we used `JSX` feature which is not supported in the playground. You may try them out in your local environment or on online IDEs such as `codesandbox`.
> 
> It is recommended that you write your table component in JSX, since it contains VNode manipulations.

> **In R**
>
> Grouped headers are drawn with a JSX header renderer upstream; `el_table()`
> groups its headers with a column's `children`.

## Filter

Virtualized Table provides custom header renderers for creating customized headers. We can then utilize these to render filters.

> **In R**
>
> Filtering in the header is a JSX header renderer upstream; filter the data
> in R and `update_el_table_v2()` it, or use `el_table()`'s column filters.

## Sortable

You can sort the table with sort state.

Sorting is the server's: `input$<id>_column_sort` says which column and
which way.

```{r sort, eval = FALSE, shot = TRUE}
df <- data.frame(id = 1:200, value = round(runif(200) * 100))
cols <- list(
  list(key = "id", dataKey = "id", title = "Id", width = 150, sortable = TRUE),
  list(
    key = "value",
    dataKey = "value",
    title = "Value",
    width = 150,
    sortable = TRUE
  )
)
el_table_v2(
  "tv_sort",
  data = df,
  columns = cols,
  table_v2_width = 700,
  height = 300,
  sort_by = list(key = "id", order = "asc")
)
```

## Controlled Sort

You can define multiple sortable columns as needed. Keep in mind that if you define multiple sortable columns, the UI
may appear confusing to your users, as it becomes unclear which column is currently being sorted.

```{r controlled-sort, eval = FALSE, shot = TRUE}
df <- data.frame(id = 1:200, value = round(runif(200) * 100))
cols <- list(
  list(key = "id", dataKey = "id", title = "Id", width = 150, sortable = TRUE),
  list(
    key = "value",
    dataKey = "value",
    title = "Value",
    width = 150,
    sortable = TRUE
  )
)
el_table_v2(
  "tv_csort",
  data = df,
  columns = cols,
  table_v2_width = 700,
  height = 300,
  sort_state = list(id = "desc", value = "asc")
)
```

## Cross hovering

When dealing with a large list, it's easy to lose track of the current row and column you are visiting. In such cases, using this feature can be very helpful.

> **In R**
>
> Hovering across rows and columns is a JSX cell renderer upstream.

## Colspan

The virtualized table doesn't use the built-in `table` element, so `colspan` and `rowspan` behave a bit differently compared to [TableV1](table.html). However, with a customized row renderer, these features can still be implemented. In this section, we'll demonstrate how to achieve this.

> **In R**
>
> Spanning cells is a JSX row renderer upstream; `el_table(span_method =)` spans
> cells.

## Rowspan

Since we have covered [Colspan](#colspan), it's worth noting that we also have row span. It's a little bit different from colspan but the idea
is basically the same.

> **In R**
>
> Spanning cells is a JSX row renderer upstream; `el_table(span_method =)` spans
> cells.

## Rowspan and Colspan together

We can combine rowspan and colspan together to meet your business goal!

> **In R**
>
> Spanning cells is a JSX row renderer upstream; `el_table(span_method =)` spans
> cells.

## Tree data

Virtual Table can also render data in a tree-like structure. By clicking the arrow icon, you can expand or collapse the tree nodes.

```{r tree-data, eval = FALSE, shot = TRUE}
rows <- lapply(1:50, function(i) {
  list(
    id = paste0("r", i),
    name = paste("Parent", i),
    children = lapply(1:3, function(j) {
      list(id = paste0("r", i, "-", j), name = paste("Child", i, j))
    })
  )
})
el_table_v2(
  "tv_tree",
  data = rows,
  expand_column_key = "name",
  table_v2_width = 700,
  height = 300,
  columns = list(
    list(key = "name", dataKey = "name", title = "Name", width = 300),
    list(key = "id", dataKey = "id", title = "Id", width = 150)
  )
)
```

## Dynamic height rows

Virtual Table is capable of rendering rows with dynamic heights. If you're working with data and are uncertain about the content size,
this feature is ideal for rendering rows that adjust to the content's height. To enable this, pass down the `estimated-row-height` attribute.
The closer the estimated height matches the actual content, the smoother the rendering experience.

> **Tip**
>
> Each row's height is dynamically measured during rendering the rows. As a result, if you're trying to display a large amount of data,
> the UI **might be** bouncing.

`estimated_row_height` lets each row take the height of its content.

```{r dynamic-height, eval = FALSE, shot = TRUE}
df <- data.frame(
  id = 1:100,
  text = vapply(1:100, function(i) strrep("text ", (i %% 7 + 1) * 8), "")
)
el_table_v2(
  "tv_dyn",
  data = df,
  estimated_row_height = 50,
  table_v2_width = 700,
  height = 300,
  columns = list(
    list(key = "id", dataKey = "id", title = "Id", width = 80),
    list(key = "text", dataKey = "text", title = "Text", width = 600)
  )
)
```

## Detail view

Using dynamic height rendering, you can also display a detailed view within the table.

> **In R**
>
> A row's detail is a JSX row renderer upstream; `el_table()`'s expandable
> rows show one.

## Customized Footer

Render a customized footer when you want to show a concluding message or information.

```{r footer, eval = FALSE, shot = TRUE}
df <- data.frame(id = 1:200, name = paste("Name", 1:200))
el_table_v2(
  "tv_footer",
  data = df,
  table_v2_width = 700,
  height = 300,
  footer_height = 50,
  slots = list(
    footer = tags$div(
      style = "display: flex; align-items: center; justify-content: center; height: 100%",
      "Display a message in the footer"
    )
  )
)
```

## Customized Empty Renderer

Render a customized empty element.

```{r empty, eval = FALSE, shot = TRUE}
el_table_v2(
  "tv_empty",
  data = list(),
  table_v2_width = 700,
  height = 300,
  columns = list(list(key = "a", dataKey = "a", title = "A", width = 150)),
  slots = list(
    empty = tags$div(
      style = "display: flex; justify-content: center",
      el_empty()
    )
  )
)
```

## Overlay

Render an overlay on top of the table when you want to show a loading indicator or something else.

```{r overlay, eval = FALSE, shot = TRUE}
df <- data.frame(id = 1:200, name = paste("Name", 1:200))
el_table_v2(
  "tv_overlay",
  data = df,
  table_v2_width = 700,
  height = 300,
  slots = list(
    overlay = tags$div(
      class = "el-loading-mask",
      style = "display: flex; align-items: center; justify-content: center",
      el_icon("Loading", class = "is-loading", size = "26px")
    )
  )
)
```

## Manual scrolling

Use the methods provided by Table V2 to scroll manually/programmatically with desired offset/rows.

> **Tip**
>
> The second parameter for `scrollToRow` is the scrolling strategy which by default is `auto`, it calculates the position
> to scroll by itself. If you wish to scroll to a specific position, you can define the strategy yourself.
> The available options are `"auto" | "center" | "end" | "start" | "smart"`
> 
> The difference between `smart` and `auto` is that `auto` is a subset of `smart` scroll strategy.

`el_call(session, "tv_scroll", "scrollToRow", list(100))` scrolls it from
the server.

```{r manual-scroll, eval = FALSE, shot = TRUE}
df <- data.frame(id = 1:1000, name = paste("Name", 1:1000))
el_table_v2("tv_scroll", data = df, table_v2_width = 700, height = 300)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("table-v2")
```
