---
title: "Table"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Display multiple data with similar format. You can sort, filter, compare
your data in a table. `el_table()` takes a data frame; its column names, a
dot turned into `_` (Element reads a dotted `prop` as a path), are the
columns unless `columns` says otherwise. Row names that name something --
`mtcars`' car names -- become a first column.

## Basic table

```{r basic, eval = FALSE, shot = TRUE}
el_table("cars", data = head(mtcars[, 1:5], 4))
```

## Striped table

```{r striped, eval = FALSE, shot = TRUE}
el_table("striped", data = head(mtcars[, 1:5], 4), stripe = TRUE)
```

## Table with border

```{r border, eval = FALSE, shot = TRUE}
el_table("bordered", data = head(mtcars[, 1:5], 4), border = TRUE)
```

## Table with status

`row_class_name` names a class per row, through a `JS()` function; style the
class as you like.

```{r status, eval = FALSE, shot = TRUE}
tagList(
  tags$style(".el-table .warning-row { background: oldlace; }
              .el-table .success-row { background: #f0f9eb; }"),
  el_table("status", data = head(mtcars[, 1:4], 4), row_class_name = JS(
    "function({row, rowIndex}) {",
    "  return rowIndex === 1 ? 'warning-row' : rowIndex === 3 ? 'success-row' : '';",
    "}")))
```

## Table with fixed header

`height` fixes the header and scrolls the body.

```{r fixed-header, eval = FALSE, shot = TRUE}
el_table("fixedhead", data = iris, height = "250px")
```

## Table with fixed column

A column's `fixed` is `TRUE` (left), `"left"` or `"right"`.

```{r fixed-column, eval = FALSE, shot = TRUE}
el_table("fixedcol", data = head(mtcars, 4), border = TRUE, columns = c(
  list(list(prop = "mpg", label = "MPG", width = "120", fixed = TRUE)),
  lapply(names(mtcars)[-1], function(n) list(prop = n, label = n, width = "120")),
  list(list(label = "Operations", width = "120", fixed = "right",
            cell = el$button(type = "text", size = "small", "Detail")))))
```

## Fixed columns and header

```{r fixed-both, eval = FALSE, shot = TRUE}
el_table("fixedboth", data = head(mtcars, 12), height = "250px", columns = c(
  list(list(prop = "mpg", label = "MPG", width = "120", fixed = TRUE)),
  lapply(names(mtcars)[-1], function(n) list(prop = n, label = n, width = "120"))))
```

## Fluid-height table with fixed header

`max_height`: the table grows with its rows until it reaches it, then
scrolls.

```{r fluid, eval = FALSE, shot = TRUE}
el_table("fluid", data = head(mtcars[, 1:5], 10), max_height = "250px")
```

## Grouping table head

A column with `children` is a group header over them.

```{r grouping, eval = FALSE, shot = TRUE}
people <- data.frame(date = "2016-05-03", name = "Tom", state = "California",
                     city = "Los Angeles", address = "No. 189, Grove St", zip = "CA 90036")
el_table("grouped", data = people[rep(1, 3), ], border = TRUE, columns = list(
  list(prop = "date", label = "Date", width = "150"),
  list(label = "Delivery Info", children = list(
    list(prop = "name", label = "Name", width = "120"),
    list(label = "Address Info", children = list(
      list(prop = "state", label = "State", width = "120"),
      list(prop = "city", label = "City", width = "120"),
      list(prop = "address", label = "Address"),
      list(prop = "zip", label = "Zip", width = "120")))))))
```

## Single select

`highlight_current_row` marks the clicked row; `input$<id>_current_change`
reports it. `setCurrentRow()` moves it from the server -- the row named by
`el_table_row()`, since Element needs the row itself.

```{r single, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#second_container button').click()", shot_wait = 2}
ui <- el_page(
  el_table("single", data = head(iris, 4), highlight_current_row = TRUE),
  el_button("second", "Select second row"), el_button("clear", "Clear selection"),
  verbatimTextOutput("current"))

server <- function(input, output, session) {
  observeEvent(input$second, el_call(session, "single", "setCurrentRow", list(el_table_row(2))))
  observeEvent(input$clear, el_call(session, "single", "setCurrentRow"))
  output$current <- renderPrint(input$single_current_change$row_index)
}

shinyApp(ui, server)
```

## Multiple select

`selection = TRUE` adds the checkbox column and reports
`input$<id>_selected_rows`, the 1-based row numbers, and
`input$<id>_selected`, the rows. Prefer the numbers: a row of mixed types
comes back from JSON as text.

```{r multiple, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#toggle_container button').click()", shot_wait = 2}
cars <- head(mtcars[, 1:4], 5)

ui <- el_page(
  el_table("cars", data = cars, selection = TRUE),
  el_button("toggle", "Toggle rows 2 and 3"), el_button("none", "Clear selection"),
  verbatimTextOutput("picked"))

server <- function(input, output, session) {
  observeEvent(input$toggle, for (i in 2:3)
    el_call(session, "cars", "toggleRowSelection", list(el_table_row(i))))
  observeEvent(input$none, el_call(session, "cars", "clearSelection"))
  output$picked <- renderPrint(cars[input$cars_selected_rows, ])
}

shinyApp(ui, server)
```

## Sorting

A column's `sortable`; `default_sort` the starting order. `sortable =
"custom"` leaves the sorting to the server, through `input$<id>_sort_change`.

```{r sorting, eval = FALSE, shot = TRUE}
el_table("sorted", data = head(mtcars[, 1:4], 6),
         default_sort = list(prop = "mpg", order = "descending"), columns = list(
  list(prop = "mpg", label = "MPG", sortable = TRUE),
  list(prop = "cyl", label = "Cylinders", sortable = TRUE),
  list(prop = "disp", label = "Displacement")))
```

## Filter

`filters` lists the choices; `filter_method`, a `JS()` function, decides.

```{r filter, eval = FALSE, shot = TRUE}
staff <- data.frame(name = c("Tom", "Ada", "Linus", "Grace"),
                    tag = c("Home", "Office", "Home", "Office"))
el_table("filtered", data = staff, columns = list(
  list(prop = "name", label = "Name"),
  list(prop = "tag", label = "Tag", filters = list(
    list(text = "Home", value = "Home"), list(text = "Office", value = "Office")),
    filter_method = JS("function(value, row) { return row.tag === value; }"),
    cell = el$tag(":type" = "scope.row.tag === 'Home' ? 'primary' : 'success'",
                  "disable-transitions" = NA, "{{ scope.row.tag }}"))))
```

## Custom column template

A column's `cell` is markup drawn once per row, with the row as
`scope.row`. Element's own tags work there, written with `el$`. A button
reports with `rowAction()`: `rowAction('edit', scope)` sets
`input$<id>_edit` to the row's number and the row.

```{r cells, eval = FALSE, shot = TRUE, shot_js = "document.querySelectorAll('#shot .el-table__body .el-button')[1].click()", shot_wait = 2}
tasks <- data.frame(task = c("Draft", "Review", "Publish"), done = c(100, 60, 0))

ui <- el_page(
  el_table("tasks", data = tasks, columns = list(
    list(prop = "task", label = "Task"),
    list(prop = "done", label = "Progress",
         cell = el$progress(":percentage" = "scope.row.done")),
    list(label = "Operations", cell = tagList(
      el$button(size = "mini", "@click" = "rowAction('edit', scope)", "Edit"),
      el$button(size = "mini", type = "danger", "@click" = "rowAction('delete', scope)", "Delete")))
  )),
  verbatimTextOutput("which"))

server <- function(input, output, session) {
  output$which <- renderPrint(list(edit = input$tasks_edit$row_index,
                                   delete = input$tasks_delete$row_index))
}

shinyApp(ui, server)
```

## Table with custom header

`header_html` is a column's header, as markup -- pass only what you control.

```{r header, eval = FALSE, shot = TRUE}
el_table("hdr", data = head(mtcars[, 1:3], 3), columns = list(
  list(prop = "mpg", label = "MPG", header_html = "<b>MPG</b> <small>(miles/gallon)</small>"),
  list(prop = "cyl", label = "Cylinders"), list(prop = "disp", label = "Displacement")))
```

## Expandable row

A column of `type = "expand"` opens each row onto its `cell`.

```{r expand, eval = FALSE, shot = TRUE}
el_table("exp", data = data.frame(name = c("Tom", "Ada"), city = c("Los Angeles", "London"),
                                  shop = c("No. 189, Grove St", "1 Baker St")),
  default_expand_all = TRUE, columns = list(
    list(type = "expand", cell = tags$p("City: {{ scope.row.city }} -- Shop: {{ scope.row.shop }}")),
    list(prop = "name", label = "Name")))
```

## Tree data and lazy mode

Rows nest through a `children` list, keyed by `row_key`. With `lazy = TRUE`
a row's children come from the server when it opens, asked for through
`input$<id>_load` and answered with `el_load_children()`; a row with
children to load carries `hasChildren = TRUE`.

```{r tree, eval = FALSE, shot = TRUE}
org <- list(
  list(id = 1, name = "Engineering", size = 42, children = list(
    list(id = 11, name = "Platform", size = 18), list(id = 12, name = "Product", size = 24))),
  list(id = 2, name = "Design", size = 9))
el_table("org", data = org, row_key = "id", default_expand_all = TRUE,
         columns = list(list(prop = "name", label = "Team"), list(prop = "size", label = "People")))
```

```{r tree-lazy, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#shot .el-table__expand-icon').click()", shot_wait = 2}
teams <- data.frame(id = c(1, 2), name = c("Engineering", "Design"),
                    size = c(42, 9), hasChildren = c(TRUE, FALSE))

ui <- el_page(el_table("teams", data = teams, row_key = "id", lazy = TRUE,
                       columns = list(list(prop = "name", label = "Team"),
                                      list(prop = "size", label = "People"))))

server <- function(input, output, session) {
  observeEvent(input$teams_load, {
    el_load_children(id = "teams", request = input$teams_load, children = data.frame(
      id = c(11, 12), name = c("Platform", "Product"), size = c(18, 24)))
  })
}

shinyApp(ui, server)
```

## Summary row

```{r summary, eval = FALSE, shot = TRUE}
el_table("sums", data = head(mtcars[, c("mpg", "hp", "wt")], 5),
         show_summary = TRUE, sum_text = "Total", border = TRUE)
```

## Rowspan and colspan

`span_method`, a `JS()` function, returns each cell's `[rowspan, colspan]`.

```{r span, eval = FALSE, shot = TRUE}
el_table("spans", data = head(mtcars[, 1:4], 6), border = TRUE, span_method = JS(
  "function({row, column, rowIndex, columnIndex}) {",
  "  if (columnIndex === 0) return rowIndex % 2 === 0 ? [2, 1] : [0, 0];",
  "}"))
```

## Custom index

A column of `type = "index"` numbers the rows; its `index`, a number or a
`JS()` function, sets how.

```{r index, eval = FALSE, shot = TRUE}
el_table("idx", data = head(iris[, c(1, 5)], 4), columns = list(
  list(type = "index", index = JS("function(i) { return i * 2; }")),
  list(prop = "Sepal_Length", label = "Sepal length"), list(prop = "Species", label = "Species")))
```

## For Shiny

### Formatting

A column's `formatter` is a `JS()` function given the row, the column, the
value and its index; formatting in R first is usually simpler.

```{r formatter, eval = FALSE, shot = TRUE}
el_table("sales", data = data.frame(region = c("North", "South"), amount = c(1234.5, 987.25)),
  columns = list(list(prop = "region", label = "Region"),
                 list(prop = "amount", label = "Amount", align = "right", formatter = JS(
                   "function(row, col, value) { return '$' + value.toFixed(2); }"))))
```

### Row events

Every Element table event is forwarded as `input$<id>_<event>`, an event
input: a row event carries `row_index`, the `row` and the `column` prop; a
cell event adds its `value`.

```{r events, eval = FALSE, shot = TRUE, shot_js = "document.querySelectorAll('#shot .el-table__body tr')[1].querySelector('td').click()", shot_wait = 2}
ui <- el_page(el_table("flowers", data = head(iris, 4)), verbatimTextOutput("clicked"))

server <- function(input, output, session) {
  output$clicked <- renderPrint(input$flowers_row_click[c("row_index", "column")])
}

shinyApp(ui, server)
```

### Server-side paging

Pair the table with `el_pagination()` and send one page at a time; the
pager reports its page as `input$<id>`.

```{r paging, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#shot .btn-next').click()", shot_wait = 2}
page_size <- 5
page_of <- function(n) iris[(n - 1) * page_size + seq_len(page_size), ]

ui <- el_page(
  el_table("rows", data = page_of(1)),
  el_pagination("pager", total = nrow(iris), page_size = page_size,
                layout = "total, prev, pager, next"))

server <- function(input, output, session) {
  observeEvent(input$pager, update_el_table(session, "rows", data = page_of(input$pager)))
}

shinyApp(ui, server)
```

### A table that starts hidden

A table drawn inside a tab or collapse that starts closed measures its
columns as zero; `el_call(session, id, "doLayout")` measures again.
`loading = TRUE`, or `update_el_table(loading =)`, covers it with Element's
loading mask while data is fetched.

## API

```{r api, echo = FALSE, results = "asis"}
api_tables("table")
```
