---
title: "Virtualized Table"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Along with evolutionary web development, table component has always been the most popular component in our web apps especially for dashboards, data analysis. For [Table V1](table.html), with even just 1000 records of data, it can be very annoying when using it, because of the poor performance.

With Virtualized Table, you can render massive chunks of data in a blink of an eye.

> **Tip**
>
> This component is **still under testing**, use at your own risk. If you find any bugs or issues, please report them at [GitHub](https://github.com/element-plus/element-plus/issues) for us to fix. Also there were some APIs which are not mentioned in this documentation, some of them were not
> fully developed yet, which is why they are not mentioned here.
> 
> **Even though** Virtualized Table is efficient, when the data load is too large, your **network** and **memory size** can become the bottleneck of your app. So keep in mind that Virtualized Table is never the ultimate solution for everything, consider paginating your data, adding filters etc.

## Basic usage

Let's demonstrate the performance of the Virtualized Table by rendering a basic example with 10 columns and 1000 rows.

```{r basic, eval = FALSE, shot = TRUE}
generate_columns <- function(length = 10, prefix = "column-") {
  lapply(seq_len(length) - 1, function(i) {
    el_table_v2_column(paste0(prefix, i), paste("Column", i), width = 150)
  })
}
generate_data <- function(columns, length = 200, prefix = "row-") {
  rows <- data.frame(id = paste0(prefix, seq_len(length) - 1))
  for (j in seq_along(columns)) {
    rows[[columns[[j]]$dataKey]] <- paste0(
      "Row ",
      seq_len(length) - 1,
      " - Col ",
      j - 1
    )
  }
  rows
}
columns <- generate_columns(10)
data <- generate_data(columns, 1000)
el_table_v2(
  "tv_basic",
  columns = columns,
  data = data,
  table_v2_width = 700,
  height = 400,
  fixed = TRUE
)
```

## Auto resizer

When you do not want to manually pass the `width` and `height` properties to the table, you can wrap the table component with the AutoResizer.
This will automatically update the width and height for you.

Resize your browser to see how it works.

> **Tip**
>
> Make sure the parent node of the `AutoResizer` **HAS A FIXED HEIGHT**, since its default height value is set to 100%.
> Alternatively, you can define it by passing the `style` attribute to `AutoResizer`.

`auto_resize = TRUE` sizes the table to its container, which needs a
height of its own.

```{r auto-resizer, eval = FALSE, shot = TRUE}
generate_columns <- function(length = 10, prefix = "column-") {
  lapply(seq_len(length) - 1, function(i) {
    el_table_v2_column(paste0(prefix, i), paste("Column", i), width = 150)
  })
}
generate_data <- function(columns, length = 200, prefix = "row-") {
  rows <- data.frame(id = paste0(prefix, seq_len(length) - 1))
  for (j in seq_along(columns)) {
    rows[[columns[[j]]$dataKey]] <- paste0(
      "Row ",
      seq_len(length) - 1,
      " - Col ",
      j - 1
    )
  }
  rows
}
columns <- generate_columns(10)
data <- generate_data(columns, 200)
tags$div(
  style = "height: 400px",
  el_table_v2(
    "tv_auto",
    columns = columns,
    data = data,
    fixed = TRUE,
    auto_resize = TRUE
  )
)
```

## Customize Cell Renderer{#customize-cell-renderer}

Of course, you can render the table cell according to your needs. Here's a simple example of how to customize your cell.

The cells are drawn by each column's `cellRenderer`, a [JS()] function
returning Vue's `h()`, as upstream's JSX does.

```{r cell-templating, eval = FALSE, shot = TRUE}
columns <- list(
  el_table_v2_column(
    "date",
    "Date",
    width = 150,
    fixed = "left",
    cell_renderer = JS(
      "function({ cellData: date }) {",
      "  var p = date.split('-').map(function(n) { return n.padStart(2, '0'); });",
      "  var text = p.join('/');",
      "  return Vue.h(ElementPlus.ElTooltip, { content: text }, function() {",
      "    return Vue.h('span', { style: 'display: flex; align-items: center' }, [",
      "      Vue.h(ElementPlus.ElIcon, { style: 'margin-right: 12px' },",
      "        function() { return Vue.h(ElementPlusIconsVue.Timer); }),",
      "      text",
      "    ]);",
      "  });",
      "}"
    )
  ),
  el_table_v2_column(
    "name",
    "Name",
    width = 150,
    align = "center",
    cell_renderer = JS(
      "function({ cellData: name }) {",
      "  return Vue.h(ElementPlus.ElTag, null, function() { return name; });",
      "}"
    )
  ),
  el_table_v2_column(
    "operations",
    "Operations",
    cell_renderer = JS(
      "function() {",
      "  return [",
      "    Vue.h(ElementPlus.ElButton, { size: 'small' }, function() { return 'Edit'; }),",
      "    Vue.h(ElementPlus.ElButton, { size: 'small', type: 'danger' },",
      "      function() { return 'Delete'; })",
      "  ];",
      "}"
    ),
    width = 150,
    align = "center"
  )
)
data <- data.frame(
  id = paste0("random-id-", 1:200),
  name = "Tom",
  date = "2020-10-1"
)
el_table_v2(
  "tv_cell",
  columns = columns,
  data = data,
  table_v2_width = 700,
  height = 400,
  fixed = TRUE
)
```

## Table with selections

Using customized cell renderer to allow selection for your table.

A checkbox column, drawn by the `cell` and `header-cell` slots: a field
of each row, `checked`, holds the tick. `$setInput()` reports the rows
ticked to the server as `input$tv_sel_checked`; it is Shiny's
`setInputValue()`, which a template cannot otherwise reach.

```{r selection, eval = FALSE, shot = TRUE, shot_js = "document.querySelectorAll('#shot .el-table-v2__row .el-checkbox')[1].click()"}
# the grid upstream's examples use: Row i - Col j
grid <- function(cols = 10, rows = 200) {
  df <- data.frame(
    check.names = FALSE,
    setNames(
      lapply(seq_len(cols) - 1, function(j) {
        paste0("Row ", seq_len(rows) - 1, " - Col ", j)
      }),
      paste0("column-", seq_len(cols) - 1)
    )
  )
  cbind(id = paste0("row-", seq_len(rows) - 1), df)
}
grid_columns <- function(cols = 10, width = 150) {
  lapply(seq_len(cols) - 1, function(j) {
    k <- paste0("column-", j)
    el_table_v2_column(k, paste("Column", j), width = width)
  })
}
df <- grid()
df$checked <- FALSE
report <- "$setInput('tv_sel_checked', data.filter(r => r.checked).map(r => r.id))"
tags$div(
  style = "height: 400px",
  el_table_v2(
    "tv_sel",
    data = df,
    columns = c(
      list(el_table_v2_column("selection", width = 50)),
      grid_columns()
    ),
    auto_resize = TRUE,
    fixed = TRUE,
    slots = list(
      cell = template(
        HTML(paste0(
          "<el-checkbox v-if=\"column.key === 'selection'\" ",
          "v-model=\"rowData.checked\" @change=\"",
          report,
          "\" />",
          "<div v-else class=\"el-table-v2__cell-text\">",
          "{{ rowData[column.dataKey] }}</div>"
        )),
        slot = "cell",
        scope = "{ rowData, column }"
      ),
      "header-cell" = template(
        HTML(paste0(
          "<el-checkbox v-if=\"column.key === 'selection'\" ",
          ":model-value=\"data.every(r => r.checked)\" ",
          ":indeterminate=\"data.some(r => r.checked) && !data.every(r => r.checked)\" ",
          "@change=\"v => { data.forEach(r => r.checked = v); ",
          report,
          " }\" />",
          "<div v-else class=\"el-table-v2__header-cell-text\">",
          "{{ column.title }}</div>"
        )),
        slot = "header-cell",
        scope = "{ column }"
      )
    )
  )
)
```

## Inline editing

Just as we demonstrated with selections above, you can use the same method to enable inline editing.

The first column edits in place: a click turns the cell into an input,
Enter or leaving it turns it back. Each edit is reported as
`input$tv_edit_edited`.

```{r inline-editing, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#shot .table-v2-inline-editing-trigger').click()", shot_wait = 1}
# the grid upstream's examples use: Row i - Col j
grid <- function(cols = 10, rows = 200) {
  df <- data.frame(
    check.names = FALSE,
    setNames(
      lapply(seq_len(cols) - 1, function(j) {
        paste0("Row ", seq_len(rows) - 1, " - Col ", j)
      }),
      paste0("column-", seq_len(cols) - 1)
    )
  )
  cbind(id = paste0("row-", seq_len(rows) - 1), df)
}
grid_columns <- function(cols = 10, width = 150) {
  lapply(seq_len(cols) - 1, function(j) {
    k <- paste0("column-", j)
    el_table_v2_column(k, paste("Column", j), width = width)
  })
}
df <- grid()
df$editing <- FALSE
cols <- grid_columns()
cols[[1]]$title <- "Editable Column"
tags$div(
  style = "height: 400px",
  el_table_v2(
    "tv_edit",
    data = df,
    columns = cols,
    auto_resize = TRUE,
    fixed = TRUE,
    slots = list(
      cell = template(
        HTML(paste0(
          "<template v-if=\"column.key === 'column-0'\">",
          "<el-input v-if=\"rowData.editing\" v-model=\"rowData[column.dataKey]\" ",
          ":ref=\"el => el && el.focus()\" ",
          "@blur=\"rowData.editing = false\" ",
          "@keydown.enter=\"rowData.editing = false\" ",
          "@change=\"v => $setInput('tv_edit_edited', {id: rowData.id, value: v})\" />",
          "<div v-else class=\"table-v2-inline-editing-trigger\" ",
          "@click=\"rowData.editing = true\">{{ rowData[column.dataKey] }}</div>",
          "</template>",
          "<div v-else class=\"el-table-v2__cell-text\">",
          "{{ rowData[column.dataKey] }}</div>"
        )),
        slot = "cell",
        scope = "{ rowData, column }"
      )
    )
  )
)
tags$style(
  ".table-v2-inline-editing-trigger {
    border: 1px transparent dotted;
    padding: 4px;
  }
  .table-v2-inline-editing-trigger:hover {
    border-color: var(--el-color-primary);
  }"
)
```

## Table with status

You can highlight your table content to distinguish between "success, information, warning, danger" and other states.

To customize the appearance of rows, use the `row-class-name` attribute. For example, every 10th row is highlighted using the `bg-blue-200` class, and every 5th row with the `bg-red-100` class.

```{r row-class, eval = FALSE, shot = TRUE}
columns <- list(
  el_table_v2_column(
    "date",
    "Date",
    width = 150,
    fixed = "left",
    cell_renderer = JS(
      "function({ cellData: date }) {",
      "  var p = date.split('-').map(function(n) { return n.padStart(2, '0'); });",
      "  var text = p.join('/');",
      "  return Vue.h(ElementPlus.ElTooltip, { content: text }, function() {",
      "    return Vue.h('span', { style: 'display: flex; align-items: center' }, [",
      "      Vue.h(ElementPlus.ElIcon, { style: 'margin-right: 12px' },",
      "        function() { return Vue.h(ElementPlusIconsVue.Timer); }),",
      "      text",
      "    ]);",
      "  });",
      "}"
    )
  ),
  el_table_v2_column(
    "name",
    "Name",
    width = 150,
    align = "center",
    cell_renderer = JS(
      "function({ cellData: name }) {",
      "  return Vue.h(ElementPlus.ElTag, null, function() { return name; });",
      "}"
    )
  ),
  el_table_v2_column(
    "operations",
    "Operations",
    cell_renderer = JS(
      "function() {",
      "  return [",
      "    Vue.h(ElementPlus.ElButton, { size: 'small' }, function() { return 'Edit'; }),",
      "    Vue.h(ElementPlus.ElButton, { size: 'small', type: 'danger' },",
      "      function() { return 'Delete'; })",
      "  ];",
      "}"
    ),
    width = 150,
    align = "center",
    flex_grow = 1
  )
)
data <- data.frame(
  id = paste0("random-id-", 1:200),
  name = "Tom",
  date = "2020-10-1"
)
tagList(
  tags$style(
    ".bg-red-100 { background-color: #fee2e2; }
.bg-blue-200 { background-color: #bfdbfe; }"
  ),
  el_table_v2(
    "tv_rowclass",
    columns = columns,
    data = data,
    row_class = JS(
      "function({ rowIndex }) {",
      "  if (rowIndex % 10 === 5) return 'bg-red-100';",
      "  if (rowIndex % 10 === 0) return 'bg-blue-200';",
      "  return '';",
      "}"
    ),
    table_v2_width = 700,
    height = 400
  )
)
```

## Table with sticky rows

You can make some rows stick to the top of the table, and that can be very easily achieved by using the `fixed-data` attribute.

You can dynamically set the sticky row based on scroll events, as shown in this example.

The first row stays at the top while the rest scroll. As the table
scrolls, the server hears `input$tv_sticky_scroll` and pins the next
fifth row with `update_el_table_v2(fixed_data =)`.

```{r sticky-rows, eval = FALSE, shot = TRUE, shot_js = "shinyVue.call({id: 'tv_sticky', method: 'scrollToTop', args: [600]})", shot_wait = 2}
generate_columns <- function(length = 10, prefix = "column-") {
  lapply(seq_len(length) - 1, function(i) {
    el_table_v2_column(paste0(prefix, i), paste("Column", i), width = 150)
  })
}
generate_data <- function(columns, length = 200, prefix = "row-") {
  rows <- data.frame(id = paste0(prefix, seq_len(length) - 1))
  for (j in seq_along(columns)) {
    rows[[columns[[j]]$dataKey]] <- paste0(
      "Row ",
      seq_len(length) - 1,
      " - Col ",
      j - 1
    )
  }
  rows
}
columns <- generate_columns(10)
data <- generate_data(columns, 200)

ui <- el_page(
  tags$style(
    ".el-el-table-v2__fixed-header-row {
  background-color: var(--el-color-primary-light-5);
  font-weight: bold;
}"
  ),
  el_table_v2(
    "tv_sticky",
    events = "scroll",
    columns = columns,
    data = data[-1, ],
    fixed_data = data[1, ],
    row_class = JS(
      "function({ rowIndex }) {",
      "  if (rowIndex < 0 || (rowIndex + 1) % 5 === 0) return 'sticky-row';",
      "}"
    ),
    table_v2_width = 700,
    height = 400,
    fixed = TRUE
  )
)

server <- function(input, output, session) {
  sticky <- reactiveVal(0)
  observeEvent(input$tv_sticky_scroll, {
    sticky(floor(input$tv_sticky_scroll$scrollTop / 250) * 5)
  })
  observeEvent(sticky(), ignoreInit = TRUE, {
    update_el_table_v2(id = "tv_sticky", fixed_data = data[sticky() + 1, ])
  })
}

shinyApp(ui, server)
```

## Table with fixed columns

If you want to have columns stick to the left or right for some reason, you can achieve this by adding special attributes to the table.

You can set the column's attribute `fixed` to `true` (representing `FixedDir.LEFT`) or `FixedDir.LEFT` or `FixedDir.RIGHT`

Sorting is the server's: a click on a sortable header arrives as
`input$tv_fixed_column_sort`, and the server sends the rows back reversed
and the new sort with `update_el_table_v2()`.

```{r fixed-columns, eval = FALSE, shot = TRUE}
generate_columns <- function(length = 10, prefix = "column-") {
  lapply(seq_len(length) - 1, function(i) {
    el_table_v2_column(paste0(prefix, i), paste("Column", i), width = 150)
  })
}
generate_data <- function(columns, length = 200, prefix = "row-") {
  rows <- data.frame(id = paste0(prefix, seq_len(length) - 1))
  for (j in seq_along(columns)) {
    rows[[columns[[j]]$dataKey]] <- paste0(
      "Row ",
      seq_len(length) - 1,
      " - Col ",
      j - 1
    )
  }
  rows
}
columns <- generate_columns(10)
data <- generate_data(columns, 200)
columns[[1]]$fixed <- TRUE
columns[[2]]$fixed <- "left"
columns[[10]]$fixed <- "right"
for (i in 1:3) {
  columns[[i]]$sortable <- TRUE
}

ui <- el_page(
  el_table_v2(
    "tv_fixed",
    columns = columns,
    data = data,
    sort_by = list(key = "column-0", order = "asc"),
    table_v2_width = 700,
    height = 400,
    fixed = TRUE
  )
)

server <- function(input, output, session) {
  rows <- reactiveVal(data)
  observeEvent(input$tv_fixed_column_sort, {
    rows(rows()[rev(seq_len(nrow(rows()))), ])
    sort <- input$tv_fixed_column_sort
    update_el_table_v2(
      id = "tv_fixed",
      data = rows(),
      sort_by = list(key = sort$key, order = sort$order)
    )
  })
}

shinyApp(ui, server)
```

## Grouping header

By customizing your header renderer, you can group your header as shown in this example.

> **Tip**
>
> In this case we used `JSX` feature which is not supported in the playground. You may try them out in your local environment or on online IDEs such as `codesandbox`.
> 
> It is recommended that you write your table component in JSX, since it contains VNode manipulations.

Three header rows, `header_height = c(50, 40, 50)`. The `header` slot
redraws the first two as groups of four and two columns; the grouping is
upstream's own function, given as `methods` and drawing with `Vue.h()`.

```{r grouping-header, eval = FALSE, shot = TRUE}
# the grid upstream's examples use: Row i - Col j
grid <- function(cols = 10, rows = 200) {
  df <- data.frame(
    check.names = FALSE,
    setNames(
      lapply(seq_len(cols) - 1, function(j) {
        paste0("Row ", seq_len(rows) - 1, " - Col ", j)
      }),
      paste0("column-", seq_len(cols) - 1)
    )
  )
  cbind(id = paste0("row-", seq_len(rows) - 1), df)
}
grid_columns <- function(cols = 10, width = 150) {
  lapply(seq_len(cols) - 1, function(j) {
    k <- paste0("column-", j)
    el_table_v2_column(k, paste("Column", j), width = width)
  })
}
cols <- grid_columns(15, width = 100)
for (j in 1:3) {
  cols[[j]]$fixed <- "left"
}
for (j in 14:15) {
  cols[[j]]$fixed <- "right"
}
el_table_v2(
  "tv_group",
  data = grid(15),
  columns = cols,
  header_height = c(50, 40, 50),
  header_class = JS(
    "function({ headerIndex }) { return headerIndex === 1 ? 'el-primary-color' : ''; }"
  ),
  table_v2_width = 700,
  height = 400,
  fixed = TRUE,
  methods = list(
    groupCells = JS(
      "function({ cells, columns, headerIndex }) {
        if (headerIndex === 2) return cells;
        var out = [], width = 0, idx = 0;
        columns.forEach(function(column, i) {
          if (column.placeholderSign === ElementPlus.TableV2Placeholder) {
            out.push(cells[i]);
            return;
          }
          width += cells[i].props.column.width;
          idx++;
          var next = columns[i + 1];
          if (i === columns.length - 1 ||
              next.placeholderSign === ElementPlus.TableV2Placeholder ||
              idx === (headerIndex === 0 ? 4 : 2)) {
            out.push(Vue.h('div', {
              class: 'custom-header-cell',
              role: 'columnheader',
              style: Object.assign({}, cells[i].props.style, {
                width: width + 'px', display: 'flex',
                alignItems: 'center', justifyContent: 'center'
              })
            }, 'Group width ' + width));
            width = 0;
            idx = 0;
          }
        });
        return out;
      }"
    )
  ),
  slots = list(
    header = template(
      HTML('<component v-for="c in groupCells(props)" :is="c" />'),
      slot = "header",
      scope = "props"
    )
  )
)
```

## Filter

Virtualized Table provides custom header renderers for creating customized headers. We can then utilize these to render filters.

The `header-cell` slot puts a filter in the first column's header. The
filtering is the server's: Confirm sends the choice as
`input$tv_filter_on`, and the server answers with
`update_el_table_v2(data =)`.

```{r filter, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#shot .el-table-v2__demo-filter-btn').click()", shot_sel = ".el-popper", shot_wait = 1}
# the grid upstream's examples use: Row i - Col j
grid <- function(cols = 10, rows = 200) {
  df <- data.frame(
    check.names = FALSE,
    setNames(
      lapply(seq_len(cols) - 1, function(j) {
        paste0("Row ", seq_len(rows) - 1, " - Col ", j)
      }),
      paste0("column-", seq_len(cols) - 1)
    )
  )
  cbind(id = paste0("row-", seq_len(rows) - 1), df)
}
grid_columns <- function(cols = 10, width = 150) {
  lapply(seq_len(cols) - 1, function(j) {
    k <- paste0("column-", j)
    el_table_v2_column(k, paste("Column", j), width = width)
  })
}
cols <- grid_columns(width = 100)
for (j in 1:2) {
  cols[[j]]$fixed <- "left"
}
ui <- el_page(
  el_table_v2(
    "tv_filter",
    data = grid(),
    columns = cols,
    table_v2_width = 700,
    height = 400,
    fixed = TRUE,
    slots = list(
      "header-cell" = template(
        HTML(paste0(
          "<div v-if=\"column.key === 'column-0'\" ",
          "style=\"display: flex; align-items: center; gap: 8px\">",
          "<span>{{ column.title }}</span>",
          "<el-popover ref=\"filterPop\" trigger=\"click\" :width=\"200\">",
          "<template #reference><button type=\"button\" ",
          "class=\"el-table-v2__demo-filter-btn\" aria-label=\"Filter\">",
          "<el-icon :size=\"14\"><Filter /></el-icon></button></template>",
          "<el-checkbox v-model=\"column.filterOn\">Filter Text</el-checkbox>",
          "<div class=\"el-table-v2__demo-filter\">",
          "<el-button text @click=\"$refs.filterPop.hide(); ",
          "$setInput('tv_filter_on', !!column.filterOn)\">Confirm</el-button>",
          "<el-button text @click=\"column.filterOn = false; ",
          "$refs.filterPop.hide(); $setInput('tv_filter_on', false)\">",
          "Reset</el-button></div></el-popover></div>",
          "<div v-else class=\"el-table-v2__header-cell-text\">",
          "{{ column.title }}</div>"
        )),
        slot = "header-cell",
        scope = "{ column }"
      )
    )
  ),
  tags$style(
    ".el-table-v2__demo-filter {
      border-top: var(--el-border);
      margin: 12px -12px -12px;
      padding: 0 12px;
      display: flex;
      justify-content: space-between;
    }
    .el-table-v2__demo-filter-btn {
      display: flex;
      cursor: pointer;
      padding: 0;
      background: transparent;
      border: none;
    }"
  )
)
server <- function(input, output, session) {
  observeEvent(input$tv_filter_on, {
    rows <- if (input$tv_filter_on) 100 else 200
    update_el_table_v2(id = "tv_filter", data = grid(rows = rows))
  })
}
shinyApp(ui, server)
```

## Sortable

You can sort the table with sort state.

Sorting is the server's: `input$tv_sort_column_sort` says which column
and which way, and the server sends the rows back reversed with the new
`sort_by`.

```{r sort, eval = FALSE, shot = TRUE}
generate_columns <- function(length = 10, prefix = "column-") {
  lapply(seq_len(length) - 1, function(i) {
    el_table_v2_column(paste0(prefix, i), paste("Column", i), width = 150)
  })
}
generate_data <- function(columns, length = 200, prefix = "row-") {
  rows <- data.frame(id = paste0(prefix, seq_len(length) - 1))
  for (j in seq_along(columns)) {
    rows[[columns[[j]]$dataKey]] <- paste0(
      "Row ",
      seq_len(length) - 1,
      " - Col ",
      j - 1
    )
  }
  rows
}
columns <- generate_columns(10)
data <- generate_data(columns, 200)
columns[[1]]$sortable <- TRUE

ui <- el_page(
  el_table_v2(
    "tv_sort",
    columns = columns,
    data = data,
    sort_by = list(key = "column-0", order = "asc"),
    table_v2_width = 700,
    height = 400,
    fixed = TRUE
  )
)

server <- function(input, output, session) {
  rows <- reactiveVal(data)
  observeEvent(input$tv_sort_column_sort, {
    rows(rows()[rev(seq_len(nrow(rows()))), ])
    sort <- input$tv_sort_column_sort
    update_el_table_v2(
      id = "tv_sort",
      data = rows(),
      sort_by = list(key = sort$key, order = sort$order)
    )
  })
}

shinyApp(ui, server)
```

## Controlled Sort

You can define multiple sortable columns as needed. Keep in mind that if you define multiple sortable columns, the UI
may appear confusing to your users, as it becomes unclear which column is currently being sorted.

Two columns sorted at once: `sort_state` holds each column's order. A
click sets that column's order on the server, which sends the state back
with `update_el_table_v2(sort_state =)`.

```{r controlled-sort, eval = FALSE, shot = TRUE}
generate_columns <- function(length = 10, prefix = "column-") {
  lapply(seq_len(length) - 1, function(i) {
    el_table_v2_column(paste0(prefix, i), paste("Column", i), width = 150)
  })
}
generate_data <- function(columns, length = 200, prefix = "row-") {
  rows <- data.frame(id = paste0(prefix, seq_len(length) - 1))
  for (j in seq_along(columns)) {
    rows[[columns[[j]]$dataKey]] <- paste0(
      "Row ",
      seq_len(length) - 1,
      " - Col ",
      j - 1
    )
  }
  rows
}
columns <- generate_columns(10)
data <- generate_data(columns, 200)
columns[[1]]$sortable <- TRUE
columns[[2]]$sortable <- TRUE

ui <- el_page(
  el_table_v2(
    "tv_csort",
    columns = columns,
    data = data,
    sort_state = list(`column-0` = "desc", `column-1` = "asc"),
    table_v2_width = 700,
    height = 400,
    fixed = TRUE
  )
)

server <- function(input, output, session) {
  state <- list(`column-0` = "desc", `column-1` = "asc")
  rows <- data
  observeEvent(input$tv_csort_column_sort, {
    sort <- input$tv_csort_column_sort
    state[[sort$key]] <<- sort$order
    rows <<- rows[rev(seq_len(nrow(rows))), ]
    update_el_table_v2(id = "tv_csort", data = rows, sort_state = state)
  })
}

shinyApp(ui, server)
```

## Cross hovering

When dealing with a large list, it's easy to lose track of the current row and column you are visiting. In such cases, using this feature can be very helpful.

Hovering a cell lights its row and its column. `cell_props` gives every
cell a `data-key` naming its column and marks the table with the column
the pointer is over; the stylesheet does the rest.

```{r cross-hovering, eval = FALSE, shot = TRUE, shot_js = "var c = document.querySelectorAll('#shot .el-table-v2__row')[2].querySelectorAll('.el-table-v2__row-cell')[3]; c.dispatchEvent(new MouseEvent('mouseenter')); c.closest('.el-table-v2__row').classList.add('is-hovered');"}
# the grid upstream's examples use: Row i - Col j
grid <- function(cols = 10, rows = 200) {
  df <- data.frame(
    check.names = FALSE,
    setNames(
      lapply(seq_len(cols) - 1, function(j) {
        paste0("Row ", seq_len(rows) - 1, " - Col ", j)
      }),
      paste0("column-", seq_len(cols) - 1)
    )
  )
  cbind(id = paste0("row-", seq_len(rows) - 1), df)
}
grid_columns <- function(cols = 10, width = 150) {
  lapply(seq_len(cols) - 1, function(j) {
    k <- paste0("column-", j)
    el_table_v2_column(k, paste("Column", j), width = width)
  })
}
cols <- c(
  list(el_table_v2_column(
    "column-n-1",
    "Row No.",
    width = 50,
    align = "center",
    cell_renderer = JS(
      "function({ rowIndex }) { return String(rowIndex + 1); }"
    )
  )),
  grid_columns()
)
tagList(
  tags$style(HTML(paste0(
    sprintf(
      "[data-hover-col='%d'] [data-key='hovering-col-%d']",
      0:10,
      0:10
    ),
    " { background: var(--el-table-row-hover-bg-color); }",
    collapse = "\n"
  ))),
  tags$div(
    style = "height: 400px",
    el_table_v2(
      "tv_cross",
      data = grid(),
      columns = cols,
      auto_resize = TRUE,
      cell_props = JS(
        "function({ columnIndex }) {
          var table = function(e) { return e.currentTarget.closest('.el-table-v2'); };
          return {
            'data-key': 'hovering-col-' + columnIndex,
            onMouseenter: function(e) { table(e).setAttribute('data-hover-col', columnIndex); },
            onMouseleave: function(e) { table(e).removeAttribute('data-hover-col'); }
          };
        }"
      )
    )
  )
)
```

## Colspan

The virtualized table doesn't use the built-in `table` element, so `colspan` and `rowspan` behave a bit differently compared to [TableV1](table.html). However, with a customized row renderer, these features can still be implemented. In this section, we'll demonstrate how to achieve this.

The `row` slot draws each row's cells; `methods` holds upstream's own
function, which widens the second cell over the next ones with
`Vue.cloneVNode()`.

```{r colspan, eval = FALSE, shot = TRUE}
# the grid upstream's examples use: Row i - Col j
grid <- function(cols = 10, rows = 200) {
  df <- data.frame(
    check.names = FALSE,
    setNames(
      lapply(seq_len(cols) - 1, function(j) {
        paste0("Row ", seq_len(rows) - 1, " - Col ", j)
      }),
      paste0("column-", seq_len(cols) - 1)
    )
  )
  cbind(id = paste0("row-", seq_len(rows) - 1), df)
}
grid_columns <- function(cols = 10, width = 150) {
  lapply(seq_len(cols) - 1, function(j) {
    k <- paste0("column-", j)
    el_table_v2_column(k, paste("Column", j), width = width)
  })
}
el_table_v2(
  "tv_colspan",
  data = grid(),
  columns = grid_columns(),
  table_v2_width = 700,
  height = 400,
  fixed = TRUE,
  methods = list(
    rowCells = JS(
      "function({ rowIndex, cells }) {
        cells = cells.slice();
        var span = (rowIndex % 4) + 1;
        if (span > 1) {
          var width = parseInt(cells[1].props.style.width);
          for (var i = 1; i < span; i++) {
            width += parseInt(cells[1 + i].props.style.width);
            cells[1 + i] = null;
          }
          cells[1] = Vue.cloneVNode(cells[1], { style: Object.assign({},
            cells[1].props.style, { width: width + 'px',
              backgroundColor: 'var(--el-color-primary-light-3)' }) });
        }
        return cells.filter(Boolean);
      }"
    )
  ),
  slots = list(
    row = template(
      HTML('<component v-for="c in rowCells(props)" :is="c" />'),
      slot = "row",
      scope = "props"
    )
  )
)
```

## Rowspan

Since we have covered [Colspan](#colspan), it's worth noting that we also have row span. It's a little bit different from colspan but the idea
is basically the same.

The `row` slot draws each row's cells; `methods` holds upstream's own
function, which makes every other first cell two rows tall.

```{r rowspan, eval = FALSE, shot = TRUE}
# the grid upstream's examples use: Row i - Col j
grid <- function(cols = 10, rows = 200) {
  df <- data.frame(
    check.names = FALSE,
    setNames(
      lapply(seq_len(cols) - 1, function(j) {
        paste0("Row ", seq_len(rows) - 1, " - Col ", j)
      }),
      paste0("column-", seq_len(cols) - 1)
    )
  )
  cbind(id = paste0("row-", seq_len(rows) - 1), df)
}
grid_columns <- function(cols = 10, width = 150) {
  lapply(seq_len(cols) - 1, function(j) {
    k <- paste0("column-", j)
    el_table_v2_column(k, paste("Column", j), width = width)
  })
}
el_table_v2(
  "tv_rowspan",
  data = grid(),
  columns = grid_columns(),
  table_v2_width = 700,
  height = 400,
  fixed = TRUE,
  methods = list(
    rowCells = JS(
      "function({ rowIndex, cells }) {
        cells = cells.slice();
        if (rowIndex % 2 === 0 && rowIndex <= 198) {
          cells[0] = Vue.cloneVNode(cells[0], { style: Object.assign({},
            cells[0].props.style, { height: (2 * 50 - 1) + 'px',
              alignSelf: 'flex-start', zIndex: 1,
              backgroundColor: 'var(--el-color-primary-light-3)' }) });
        }
        return cells;
      }"
    )
  ),
  slots = list(
    row = template(
      HTML('<component v-for="c in rowCells(props)" :is="c" />'),
      slot = "row",
      scope = "props"
    )
  )
)
```

## Rowspan and Colspan together

We can combine rowspan and colspan together to meet your business goal!

Column and row spans together, from one `row` function in `methods`.

```{r spans, eval = FALSE, shot = TRUE}
# the grid upstream's examples use: Row i - Col j
grid <- function(cols = 10, rows = 200) {
  df <- data.frame(
    check.names = FALSE,
    setNames(
      lapply(seq_len(cols) - 1, function(j) {
        paste0("Row ", seq_len(rows) - 1, " - Col ", j)
      }),
      paste0("column-", seq_len(cols) - 1)
    )
  )
  cbind(id = paste0("row-", seq_len(rows) - 1), df)
}
grid_columns <- function(cols = 10, width = 150) {
  lapply(seq_len(cols) - 1, function(j) {
    k <- paste0("column-", j)
    el_table_v2_column(k, paste("Column", j), width = width)
  })
}
el_table_v2(
  "tv_spans",
  data = grid(),
  columns = grid_columns(),
  table_v2_width = 700,
  height = 400,
  fixed = TRUE,
  methods = list(
    rowCells = JS(
      "function({ rowIndex, cells }) {
        cells = cells.slice();
        var span = (rowIndex % 4) + 1;
        if (span > 1) {
          var width = parseInt(cells[1].props.style.width);
          for (var i = 1; i < span; i++) {
            width += parseInt(cells[1 + i].props.style.width);
            cells[1 + i] = null;
          }
          cells[1] = Vue.cloneVNode(cells[1], { style: Object.assign({},
            cells[1].props.style, { width: width + 'px',
              backgroundColor: 'var(--el-color-primary-light-3)' }) });
        }
        var style = cells[0].props.style;
        if (rowIndex % 2 === 0 && rowIndex <= 198) {
          cells[0] = Vue.cloneVNode(cells[0], { style: Object.assign({}, style,
            { height: '100px', alignSelf: 'flex-start', zIndex: 1,
              backgroundColor: 'var(--el-color-danger-light-3)' }) });
        } else {
          // the cell above covers this one: an empty box keeps the width
          cells[0] = Vue.h('div', { style: Object.assign({}, style,
            { width: parseInt(style.width) + 'px' }) });
        }
        return cells.filter(Boolean);
      }"
    )
  ),
  slots = list(
    row = template(
      HTML('<component v-for="c in rowCells(props)" :is="c" />'),
      slot = "row",
      scope = "props"
    )
  )
)
```

## Tree data

Virtual Table can also render data in a tree-like structure. By clicking the arrow icon, you can expand or collapse the tree nodes.

The rows nest through `children`; the arrow sits in the column named by
`expand_column_key`. Opening a row reports `input$tv_tree_row_expand`,
and the open rows `input$tv_tree_expanded_rows_change`.

```{r tree-data, eval = FALSE, shot = TRUE}
generate_columns <- function(length = 10, prefix = "column-") {
  lapply(seq_len(length) - 1, function(i) {
    el_table_v2_column(paste0(prefix, i), paste("Column", i), width = 150)
  })
}
generate_data <- function(columns, length = 200, prefix = "row-") {
  rows <- data.frame(id = paste0(prefix, seq_len(length) - 1))
  for (j in seq_along(columns)) {
    rows[[columns[[j]]$dataKey]] <- paste0(
      "Row ",
      seq_len(length) - 1,
      " - Col ",
      j - 1
    )
  }
  rows
}
columns <- generate_columns(10)
for (i in 1:2) {
  columns[[i]]$fixed <- "left"
}
columns[[10]]$fixed <- "right"

expand_column_key <- "column-0"
rows <- generate_data(columns, 200)
rows <- lapply(seq_len(nrow(rows)), function(i) as.list(rows[i, ]))
copy <- function(row, id, label) {
  row$id <- id
  row[[expand_column_key]] <- label
  row
}
rows[[1]]$children <- lapply(0:49, function(i) {
  copy(rows[[1]], paste0(rows[[1]]$id, "-sub-", i), paste("Sub", i))
})
rows[[3]]$children <- lapply(0:49, function(i) {
  sub <- copy(rows[[3]], paste0(rows[[3]]$id, "-sub-", i), paste("Sub", i))
  sub$children <- list(copy(
    rows[[3]],
    paste0(rows[[3]]$id, "-sub-sub-", i),
    paste("Sub-Sub", i)
  ))
  sub
})

el_table_v2(
  "tv_tree",
  events = c("row_expand", "expanded_rows_change"),
  columns = columns,
  data = rows,
  expand_column_key = expand_column_key,
  table_v2_width = 700,
  height = 400,
  fixed = TRUE
)
```

## Dynamic height rows

Virtual Table is capable of rendering rows with dynamic heights. If you're working with data and are uncertain about the content size,
this feature is ideal for rendering rows that adjust to the content's height. To enable this, pass down the `estimated-row-height` attribute.
The closer the estimated height matches the actual content, the smoother the rendering experience.

> **Tip**
>
> Each row's height is dynamically measured during rendering the rows. As a result, if you're trying to display a large amount of data,
> the UI **might be** bouncing.

`estimated_row_height` lets each row take the height of its content.
Sorting is the server's: it sorts the rows and sends them back with the
new `sort_by`.

```{r dynamic-height, eval = FALSE, shot = TRUE}
long_text <- "Quaerat ipsam necessitatibus eum quibusdam est id voluptatem cumque mollitia."
mid_text <- "Corrupti doloremque a quos vero delectus consequatur."
short_text <- "Eius optio fugiat."

set.seed(1)
data <- data.frame(
  id = paste0("random-", 1:200),
  name = "Tom",
  date = "2016-05-03",
  description = sample(c(short_text, mid_text, long_text), 200, TRUE)
)

columns <- list(
  el_table_v2_column("id", "Id", width = 150, sortable = TRUE, fixed = "left"),
  el_table_v2_column(
    "name",
    "Name",
    width = 150,
    align = "center",
    cell_renderer = JS(
      "function({ cellData: name }) {",
      "  return Vue.h(ElementPlus.ElTag, null, function() { return name; });",
      "}"
    )
  ),
  el_table_v2_column(
    "description",
    "Description",
    width = 150,
    cell_renderer = JS(
      "function({ cellData: description }) {",
      "  return Vue.h('div', { style: 'padding: 10px 0;' }, description);",
      "}"
    )
  ),
  el_table_v2_column(
    "operations",
    "Operations",
    cell_renderer = JS(
      "function() {",
      "  return [",
      "    Vue.h(ElementPlus.ElButton, { size: 'small' }, function() { return 'Edit'; }),",
      "    Vue.h(ElementPlus.ElButton, { size: 'small', type: 'danger' },",
      "      function() { return 'Delete'; })",
      "  ];",
      "}"
    ),
    width = 150,
    align = "center"
  )
)

ui <- el_page(
  el_table_v2(
    "tv_dyn",
    columns = columns,
    data = data,
    sort_by = list(key = "name", order = "asc"),
    estimated_row_height = 40,
    table_v2_width = 700,
    height = 400,
    fixed = TRUE
  )
)

server <- function(input, output, session) {
  observeEvent(input$tv_dyn_column_sort, {
    sort <- input$tv_dyn_column_sort
    rows <- data[order(data[[sort$key]], decreasing = sort$order == "desc"), ]
    update_el_table_v2(
      id = "tv_dyn",
      data = rows,
      sort_by = list(key = sort$key, order = sort$order)
    )
  })
}

shinyApp(ui, server)
```

## Detail view

Using dynamic height rendering, you can also display a detailed view within the table.

Each row has a child holding its detail; expanded, the `row` slot draws
the child as a block of text rather than cells.

```{r detailed-view, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#shot .el-table-v2__expand-icon').click()", shot_wait = 1}
# the grid upstream's examples use: Row i - Col j
grid <- function(cols = 10, rows = 200) {
  df <- data.frame(
    check.names = FALSE,
    setNames(
      lapply(seq_len(cols) - 1, function(j) {
        paste0("Row ", seq_len(rows) - 1, " - Col ", j)
      }),
      paste0("column-", seq_len(cols) - 1)
    )
  )
  cbind(id = paste0("row-", seq_len(rows) - 1), df)
}
grid_columns <- function(cols = 10, width = 150) {
  lapply(seq_len(cols) - 1, function(j) {
    k <- paste0("column-", j)
    el_table_v2_column(k, paste("Column", j), width = width)
  })
}
detail <- paste(
  "Velit sed aspernatur tempora. Natus consequatur officiis dicta vel",
  "assumenda. Itaque est temporibus minus quis. Ipsum commodiab porro vel",
  "voluptas illum. Qui quam nulla et dolore autem itaque est."
)
df <- grid()
rows <- lapply(seq_len(nrow(df)), function(i) {
  row <- as.list(df[i, ])
  row$children <- list(list(id = paste0(row$id, "-detail"), detail = detail))
  row
})
el_table_v2(
  "tv_detail",
  data = rows,
  columns = grid_columns(),
  expand_column_key = "column-0",
  estimated_row_height = 50,
  table_v2_width = 700,
  height = 400,
  slots = list(
    row = template(
      HTML(paste0(
        "<div v-if=\"props.rowData.detail\" style=\"padding: 24px\">",
        "{{ props.rowData.detail }}</div>",
        "<component v-else v-for=\"c in props.cells\" :is=\"c\" />"
      )),
      slot = "row",
      scope = "props"
    )
  )
)
```

## Customized Footer

Render a customized footer when you want to show a concluding message or information.

```{r footer, eval = FALSE, shot = TRUE}
generate_columns <- function(length = 10, prefix = "column-") {
  lapply(seq_len(length) - 1, function(i) {
    el_table_v2_column(paste0(prefix, i), paste("Column", i), width = 150)
  })
}
generate_data <- function(columns, length = 200, prefix = "row-") {
  rows <- data.frame(id = paste0(prefix, seq_len(length) - 1))
  for (j in seq_along(columns)) {
    rows[[columns[[j]]$dataKey]] <- paste0(
      "Row ",
      seq_len(length) - 1,
      " - Col ",
      j - 1
    )
  }
  rows
}
columns <- generate_columns(10)
data <- generate_data(columns, 200)
el_table_v2(
  "tv_footer",
  columns = columns,
  data = data,
  row_height = 40,
  table_v2_width = 700,
  height = 400,
  footer_height = 50,
  fixed = TRUE,
  slots = list(
    footer = tags$div(
      style = paste(
        "display: flex; align-items: center; justify-content: center;",
        "height: 100%; background-color: var(--el-color-primary-light-7);"
      ),
      "Display a message in the footer"
    )
  )
)
```

## Customized Empty Renderer

Render a customized empty element.

```{r empty, eval = FALSE, shot = TRUE}
generate_columns <- function(length = 10, prefix = "column-") {
  lapply(seq_len(length) - 1, function(i) {
    el_table_v2_column(paste0(prefix, i), paste("Column", i), width = 150)
  })
}
columns <- generate_columns(10)
el_table_v2(
  "tv_empty",
  columns = columns,
  data = list(),
  row_height = 40,
  table_v2_width = 700,
  height = 400,
  footer_height = 50,
  slots = list(
    empty = tags$div(
      style = "display: flex; align-items: center; justify-content: center; height: 100%",
      el_empty()
    )
  )
)
```

## Overlay

Render an overlay on top of the table when you want to show a loading indicator or something else.

```{r overlay, eval = FALSE, shot = TRUE}
generate_columns <- function(length = 10, prefix = "column-") {
  lapply(seq_len(length) - 1, function(i) {
    el_table_v2_column(paste0(prefix, i), paste("Column", i), width = 150)
  })
}
generate_data <- function(columns, length = 200, prefix = "row-") {
  rows <- data.frame(id = paste0(prefix, seq_len(length) - 1))
  for (j in seq_along(columns)) {
    rows[[columns[[j]]$dataKey]] <- paste0(
      "Row ",
      seq_len(length) - 1,
      " - Col ",
      j - 1
    )
  }
  rows
}
columns <- generate_columns(10)
data <- generate_data(columns, 200)
el_table_v2(
  "tv_overlay",
  columns = columns,
  data = data,
  row_height = 40,
  table_v2_width = 700,
  height = 400,
  slots = list(
    overlay = tags$div(
      class = "el-loading-mask",
      style = "display: flex; align-items: center; justify-content: center",
      el_icon(
        "Loading",
        class = "is-loading",
        color = "var(--el-color-primary)",
        size = 26
      )
    )
  )
)
```

## Manual scrolling

Use the methods provided by Table V2 to scroll manually/programmatically with desired offset/rows.

> **Tip**
>
> The second parameter for `scrollToRow` is the scrolling strategy which by default is `auto`, it calculates the position
> to scroll by itself. If you wish to scroll to a specific position, you can define the strategy yourself.
> The available options are `"auto" | "center" | "end" | "start" | "smart"`
> 
> The difference between `smart` and `auto` is that `auto` is a subset of `smart` scroll strategy.

The buttons call the table's `scrollToTop()` and `scrollToRow()` from the
server. `scrollToRow()` is given the strategy `"start"`: with the default,
Element Plus 2.14.7 also scrolls the table to its last column (see
"Limitations").

```{r manual-scroll, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#rows_btn_container button').click()", shot_wait = 2}
generate_columns <- function(length = 10, prefix = "column-") {
  lapply(seq_len(length) - 1, function(i) {
    el_table_v2_column(paste0(prefix, i), paste("Column", i), width = 150)
  })
}
generate_data <- function(columns, length = 200, prefix = "row-") {
  rows <- data.frame(id = paste0(prefix, seq_len(length) - 1))
  for (j in seq_along(columns)) {
    rows[[columns[[j]]$dataKey]] <- paste0(
      "Row ",
      seq_len(length) - 1,
      " - Col ",
      j - 1
    )
  }
  rows
}
columns <- generate_columns(10)
data <- generate_data(columns, 200)

ui <- el_page(
  tags$div(
    style = "display: flex; gap: 16px; margin-bottom: 16px",
    el_input("delta", value = "200", label = "Scroll pixels"),
    el_input("rows", value = "10", label = "Scroll rows")
  ),
  tags$div(
    style = "margin-bottom: 16px",
    el_button("pixels_btn", "Scroll by pixels"),
    el_button("rows_btn", "Scroll by rows")
  ),
  tags$div(
    style = "height: 400px",
    el_table_v2(
      "tv_scroll",
      columns = columns,
      data = data,
      fixed = TRUE,
      auto_resize = TRUE
    )
  )
)

server <- function(input, output, session) {
  observeEvent(input$pixels_btn, {
    call_el(session, "tv_scroll", "scrollToTop", list(as.numeric(input$delta)))
  })
  observeEvent(input$rows_btn, {
    call_el(
      session,
      "tv_scroll",
      "scrollToRow",
      list(as.numeric(input$rows), "start")
    )
  })
}

shinyApp(ui, server)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("table-v2")
```
