---
title: "Tabs"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Divide data collections which are related yet belong to different types.

## Basic usage

Basic and concise tabs.

Tabs provide a selective card functionality. By default the first tab is selected as active, and you can activate any tab by setting the `value` attribute.

```{r basic, eval = FALSE, shot = TRUE}
el_tabs(
  "basic",
  selected = "first",
  tabs = list(
    el_tab_pane("User", "User", name = "first"),
    el_tab_pane("Config", "Config", name = "second"),
    el_tab_pane("Role", "Role", name = "third"),
    el_tab_pane("Task", "Task", name = "fourth")
  )
)
```

## Card Style

Tabs styled as cards.

Set `type` to `card` can get a card-styled tab.

```{r card-style, eval = FALSE, shot = TRUE}
el_tabs(
  "card",
  type = "card",
  tabs = list(
    el_tab_pane("User", "User", name = "first"),
    el_tab_pane("Config", "Config", name = "second"),
    el_tab_pane("Role", "Role", name = "third"),
    el_tab_pane("Task", "Task", name = "fourth")
  )
)
```

## Border card

Border card tabs.

Set `type` to `border-card`.

```{r border-card, eval = FALSE, shot = TRUE}
el_tabs(
  "bc",
  type = "border-card",
  tabs = list(
    el_tab_pane("User", "User", name = "first"),
    el_tab_pane("Config", "Config", name = "second"),
    el_tab_pane("Role", "Role", name = "third"),
    el_tab_pane("Task", "Task", name = "fourth")
  )
)
```

## Tab position

You can use `tab-position` attribute to set the tab's position.

You can choose from four directions: `tabPosition="left|right|top|bottom"`

The radios move the tabs, with `update_el_tabs(tab_position =)`.

```{r tab-position, eval = FALSE, shot = TRUE, shot_js = "Array.from(document.querySelectorAll('#position .el-radio-button')).find(function(r){ return r.innerText.trim() === 'left'; }).click()", shot_expect = c("document.querySelector('#tabs_pos.el-tabs--left .el-tabs__header.is-left.el-tabs__header-vertical')", "document.querySelector('#tabs_pos').firstElementChild.classList.contains('el-tabs__header')")}
ui <- el_page(
  el_radio_group(
    "position",
    choices = c("top", "right", "bottom", "left"),
    value = "top",
    button = TRUE
  ),
  tags$div(style = "height: 16px"),
  el_tabs(
    "tabs_pos",
    tab_position = "top",
    tabs = list(
      el_tab_pane("User", "User"),
      el_tab_pane("Config", "Config"),
      el_tab_pane("Role", "Role"),
      el_tab_pane("Task", "Task")
    )
  )
)
server <- function(input, output, session) {
  observeEvent(input$position, ignoreInit = TRUE, {
    update_el_tabs(session, "tabs_pos", tab_position = input$position)
  })
}
shinyApp(ui, server)
```

## Custom Tab

You can use named slot to customize the tab label content.

A `label` may be markup.

```{r custom-tab, eval = FALSE, shot = TRUE}
el_tabs(
  "cus",
  type = "border-card",
  tabs = list(
    el_tab_pane(
      tagList(el_icon("Calendar"), " Route"),
      "Route",
      name = "route"
    ),
    el_tab_pane("Config", "Config", name = "config"),
    el_tab_pane("Role", "Role", name = "role"),
    el_tab_pane("Task", "Task", name = "task")
  )
)
```

## Add & close tab

Only card type Tabs support addable & closeable.

`editable = TRUE` adds the close buttons and the new-tab button; the
tabs close themselves, and a new one is the server's to make, with
`insert_el_tab()`.

```{r dynamic-tabs, eval = FALSE, shot = TRUE, shot_js = "var b = document.querySelector('#shot .el-tabs__new-tab'); b.click(); setTimeout(function(){ b.click(); }, 600)", shot_wait = 2.5}
ui <- el_page(el_tabs(
  "docs",
  type = "card",
  editable = TRUE,
  tabs = list(
    el_tab_pane("Tab 1", "Tab 1 content", name = "1"),
    el_tab_pane("Tab 2", "Tab 2 content", name = "2")
  )
))

server <- function(input, output, session) {
  n <- 2
  observeEvent(input$docs_tab_add, {
    n <<- n + 1
    insert_el_tab(
      id = "docs",
      tab = el_tab_pane("New Tab", "New Tab content", name = as.character(n))
    )
  })
}

shinyApp(ui, server)
```

## Customized add button icon

```{r customized-add-button-icon, eval = FALSE, shot = TRUE}
el_tabs(
  "icon",
  type = "card",
  editable = TRUE,
  add_icon = "CirclePlus",
  tabs = list(
    el_tab_pane("Tab 1", "Tab 1 content", name = "1"),
    el_tab_pane("Tab 2", "Tab 2 content", name = "2")
  )
)
```

## Customized trigger button of new tab

```{r customized-trigger, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#add_container button').click()", shot_wait = 1.5}
ui <- el_page(
  el_button("add", "add tab", size = "small"),
  el_tabs(
    "docs",
    type = "card",
    closable = TRUE,
    tabs = list(
      el_tab_pane("Tab 1", "Tab 1 content", name = "1"),
      el_tab_pane("Tab 2", "Tab 2 content", name = "2")
    )
  )
)

server <- function(input, output, session) {
  n <- 2
  observeEvent(input$add, {
    n <<- n + 1
    insert_el_tab(
      id = "docs",
      tab = el_tab_pane("New Tab", "New Tab content", name = as.character(n))
    )
  })
}

shinyApp(ui, server)
```

## Default value

`selected` opens a tab other than the first.

```{r default-value, eval = FALSE, shot = TRUE}
el_tabs(
  "dv",
  selected = "third",
  type = "card",
  tabs = list(
    el_tab_pane("User", "User", name = "first"),
    el_tab_pane("Config", "Config", name = "second"),
    el_tab_pane("Role", "Role", name = "third"),
    el_tab_pane("Task", "Task", name = "fourth")
  )
)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("tabs")
```
