---
title: "Tabs"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Divide data collections which are related yet belong to different types.
`tabs` is a list of `list(name =, label =, content =)`; the panes hold any
Shiny UI, components included. `input$<id>` is the selected tab's name.

## Basic usage

```{r basic, eval = FALSE, shot = TRUE}
el_tabs("basic", selected = "first", tabs = list(
  list(name = "first", label = "User", content = "User"),
  list(name = "second", label = "Config", content = "Config"),
  list(name = "third", label = "Role", content = "Role"),
  list(name = "fourth", label = "Task", content = "Task")))
```

## Card style

```{r card, eval = FALSE, shot = TRUE}
el_tabs("card", type = "card", tabs = list(
  list(name = "first", label = "User", content = "User"),
  list(name = "second", label = "Config", content = "Config"),
  list(name = "third", label = "Role", content = "Role")))
```

## Border card

```{r border, eval = FALSE, shot = TRUE}
el_tabs("bc", type = "border-card", tabs = list(
  list(name = "first", label = "User", content = el_switch("on", active_text = "Live")),
  list(name = "second", label = "Config", content = "Config"),
  list(name = "third", label = "Role", content = "Role")))
```

## Tab position

```{r position, eval = FALSE, shot = TRUE}
el_tabs("pos", tab_position = "left", tabs = list(
  list(name = "first", label = "User", content = "User"),
  list(name = "second", label = "Config", content = "Config"),
  list(name = "third", label = "Role", content = "Role")))
```

## Custom tab

A `label` may be markup.

```{r custom, eval = FALSE, shot = TRUE}
el_tabs("cus", type = "border-card", tabs = list(
  list(name = "route", label = tagList(el_icon("date"), " Route"), content = "Route"),
  list(name = "config", label = "Config", content = "Config")))
```

## Add & close tab

`editable = TRUE` adds Element's close buttons and new-tab button; the
tabs close themselves, and a new one is the server's to make, with
`insert_el_tab()`.

```{r editable, eval = FALSE, shot = TRUE, shot_js = "var b = document.querySelector('#shot .el-tabs__new-tab'); b.click(); setTimeout(function(){ b.click(); }, 600)", shot_wait = 2.5}
ui <- el_page(el_tabs("docs", type = "card", editable = TRUE, tabs = list(
  list(name = "1", label = "Tab 1", content = "Tab 1 content"),
  list(name = "2", label = "Tab 2", content = "Tab 2 content"))))

server <- function(input, output, session) {
  n <- 2
  observeEvent(input$docs_tab_add, {
    n <<- n + 1
    insert_el_tab(id = "docs", name = as.character(n), label = "New Tab",
                  content = "New Tab content")
  })
}

shinyApp(ui, server)
```

## Customized trigger button of new tab

```{r trigger, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#add_container button').click()", shot_wait = 1.5}
ui <- el_page(
  el_button("add", "add tab", size = "small"),
  el_tabs("docs", type = "card", closable = TRUE, tabs = list(
    list(name = "1", label = "Tab 1", content = "Tab 1 content"),
    list(name = "2", label = "Tab 2", content = "Tab 2 content"))))

server <- function(input, output, session) {
  n <- 2
  observeEvent(input$add, {
    n <<- n + 1
    insert_el_tab(id = "docs", name = as.character(n), label = "New Tab", content = "New Tab content")
  })
}

shinyApp(ui, server)
```

## API

```{r api, echo = FALSE, results = "asis"}
api_tables("tabs")
```
