---
title: "Tabs"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Divide data collections which are related yet belong to different types.

## Basic usage

Basic and concise tabs.

Tabs provide a selective card functionality. By default the first tab is selected as active, and you can activate any tab by setting the `value` attribute.

```{r basic, eval = FALSE, shot = TRUE}
el_tabs(
  "basic",
  selected = "first",
  tabs = list(
    list(name = "first", label = "User", content = "User"),
    list(name = "second", label = "Config", content = "Config"),
    list(name = "third", label = "Role", content = "Role"),
    list(name = "fourth", label = "Task", content = "Task")
  )
)
```

## Card Style

Tabs styled as cards.

Set `type` to `card` can get a card-styled tab.

```{r card-style, eval = FALSE, shot = TRUE}
el_tabs(
  "card",
  type = "card",
  tabs = list(
    list(name = "first", label = "User", content = "User"),
    list(name = "second", label = "Config", content = "Config"),
    list(name = "third", label = "Role", content = "Role"),
    list(name = "fourth", label = "Task", content = "Task")
  )
)
```

## Border card

Border card tabs.

Set `type` to `border-card`.

```{r border-card, eval = FALSE, shot = TRUE}
el_tabs(
  "bc",
  type = "border-card",
  tabs = list(
    list(name = "first", label = "User", content = "User"),
    list(name = "second", label = "Config", content = "Config"),
    list(name = "third", label = "Role", content = "Role"),
    list(name = "fourth", label = "Task", content = "Task")
  )
)
```

## Tab position

You can use `tab-position` attribute to set the tab's position.

You can choose from four directions: `tabPosition="left|right|top|bottom"`

```{r tab-position, eval = FALSE, shot = TRUE}
el_tabs(
  "pos",
  tab_position = "left",
  tabs = list(
    list(name = "first", label = "User", content = "User"),
    list(name = "second", label = "Config", content = "Config"),
    list(name = "third", label = "Role", content = "Role"),
    list(name = "fourth", label = "Task", content = "Task")
  )
)
```

## Custom Tab

You can use named slot to customize the tab label content.

A `label` may be markup.

```{r custom-tab, eval = FALSE, shot = TRUE}
el_tabs(
  "cus",
  type = "border-card",
  tabs = list(
    list(
      name = "route",
      label = tagList(el_icon("Calendar"), " Route"),
      content = "Route"
    ),
    list(name = "config", label = "Config", content = "Config"),
    list(name = "role", label = "Role", content = "Role"),
    list(name = "task", label = "Task", content = "Task")
  )
)
```

## Add & close tab

Only card type Tabs support addable & closeable.

`editable = TRUE` adds the close buttons and the new-tab button; the
tabs close themselves, and a new one is the server's to make, with
`insert_el_tab()`.

```{r dynamic-tabs, eval = FALSE, shot = TRUE, shot_js = "var b = document.querySelector('#shot .el-tabs__new-tab'); b.click(); setTimeout(function(){ b.click(); }, 600)", shot_wait = 2.5}
ui <- el_page(el_tabs(
  "docs",
  type = "card",
  editable = TRUE,
  tabs = list(
    list(name = "1", label = "Tab 1", content = "Tab 1 content"),
    list(name = "2", label = "Tab 2", content = "Tab 2 content")
  )
))

server <- function(input, output, session) {
  n <- 2
  observeEvent(input$docs_tab_add, {
    n <<- n + 1
    insert_el_tab(
      id = "docs",
      name = as.character(n),
      label = "New Tab",
      content = "New Tab content"
    )
  })
}

shinyApp(ui, server)
```

## Customized add button icon

```{r customized-add-button-icon, eval = FALSE, shot = TRUE}
el_tabs(
  "icon",
  type = "card",
  editable = TRUE,
  add_icon = "CirclePlus",
  tabs = list(
    list(name = "1", label = "Tab 1", content = "Tab 1 content"),
    list(name = "2", label = "Tab 2", content = "Tab 2 content")
  )
)
```

## Customized trigger button of new tab

```{r customized-trigger, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#add_container button').click()", shot_wait = 1.5}
ui <- el_page(
  el_button("add", "add tab", size = "small"),
  el_tabs(
    "docs",
    type = "card",
    closable = TRUE,
    tabs = list(
      list(name = "1", label = "Tab 1", content = "Tab 1 content"),
      list(name = "2", label = "Tab 2", content = "Tab 2 content")
    )
  )
)

server <- function(input, output, session) {
  n <- 2
  observeEvent(input$add, {
    n <<- n + 1
    insert_el_tab(
      id = "docs",
      name = as.character(n),
      label = "New Tab",
      content = "New Tab content"
    )
  })
}

shinyApp(ui, server)
```

## Default value

`selected` opens a tab other than the first.

```{r default-value, eval = FALSE, shot = TRUE}
el_tabs(
  "dv",
  selected = "third",
  type = "card",
  tabs = list(
    list(name = "first", label = "User", content = "User"),
    list(name = "second", label = "Config", content = "Config"),
    list(name = "third", label = "Role", content = "Role"),
    list(name = "fourth", label = "Task", content = "Task")
  )
)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("tabs")
```
