---
title: "Tag"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Used for marking and selection.

## Basic usage

Use the `type` attribute to define Tag's type. In addition, the `color` attribute can be used to set the background color of the Tag.

```{r basic, eval = FALSE, shot = TRUE}
types <- c("primary", "success", "info", "warning", "danger")
tagList(lapply(types, function(t) {
  el_tag(paste0("t_", t), paste("Tag", match(t, types)), type = t)
}))
```

## Removable Tag

`closable` attribute can be used to define a removable tag. It accepts a `Boolean`. By default the removal of Tag has a fading animation. If you don't want to use it, you can set the `disable-transitions` attribute, which accepts a `Boolean`, to `true`. `close` event triggers when Tag is removed.

```{r removable, eval = FALSE, shot = TRUE}
types <- c("primary", "success", "info", "warning", "danger")
tagList(lapply(types, function(t) {
  el_tag(
    paste0("r_", t),
    paste("Tag", match(t, types)),
    type = t,
    closable = TRUE
  )
}))
```

## Edit Dynamically

You can use the `close` event to add and remove tag dynamically.

Tags the user adds and removes: the list lives on the server and is drawn
with `renderUI()`.

```{r editable, eval = FALSE, shot = TRUE, shot_js = "var i = document.querySelector('#newtag_container input'); i.value = 'Tag 4'; i.dispatchEvent(new Event('input')); setTimeout(function(){ document.querySelector('#add_container button').click(); }, 400);", shot_wait = 2}
ui <- el_page(
  uiOutput("tags"),
  el_input("newtag", placeholder = "New tag", width = "140px"),
  el_button("add", "+ New Tag", size = "small")
)

server <- function(input, output, session) {
  tags_now <- reactiveVal(character(0))
  counter <- 0
  # Each tag gets an id of its own, and one observer for its close button
  add_tag <- function(label) {
    counter <<- counter + 1
    id <- paste0("tag", counter)
    tags_now(c(isolate(tags_now()), stats::setNames(label, id)))
    observeEvent(
      input[[paste0(id, "_close")]],
      once = TRUE,
      tags_now(tags_now()[names(tags_now()) != id])
    )
  }
  for (t in c("Tag 1", "Tag 2", "Tag 3")) {
    add_tag(t)
  }
  output$tags <- renderUI(tagList(Map(
    function(id, label) el_tag(id, label, closable = TRUE),
    names(tags_now()),
    tags_now()
  )))
  observeEvent(input$add, {
    req(nzchar(input$newtag))
    add_tag(input$newtag)
    update_el_input(id = "newtag", value = "")
  })
}

shinyApp(ui, server)
```

## Sizes

Besides default size, Tag component provides three additional sizes for you to choose among different scenarios.

Use attribute `size` to set additional sizes with `large`, `default` or `small`.

```{r sizes, eval = FALSE, shot = TRUE}
tagList(
  el_tag("s1", "Large", size = "large"),
  el_tag("s2", "Default"),
  el_tag("s3", "Small", size = "small"),
  tags$br(),
  tags$br(),
  el_tag("s4", "Large", size = "large", closable = TRUE),
  el_tag("s5", "Default", closable = TRUE),
  el_tag("s6", "Small", size = "small", closable = TRUE)
)
```

## Theme

Tag provide three different themes: `dark`、`light` and `plain`

Using `effect` to change, default is `light`

`effect` is `"dark"`, `"light"` (the default) or `"plain"`.

```{r theme, eval = FALSE, shot = TRUE}
types <- c("primary", "success", "info", "warning", "danger")
tagList(lapply(c("dark", "light", "plain"), function(e) {
  tags$div(
    style = "margin-bottom: 10px",
    tags$span(style = "display: inline-block; width: 50px", e),
    lapply(types, function(t) el_tag(paste0(e, t), t, type = t, effect = e))
  )
}))
```

## Rounded

Tag can also be rounded like button.

```{r rounded, eval = FALSE, shot = TRUE}
types <- c("primary", "success", "info", "warning", "danger")
tagList(lapply(c("dark", "light", "plain"), function(e) {
  tags$div(
    style = "margin-bottom: 10px",
    lapply(types, function(t) {
      el_tag(paste0("rd", e, t), t, type = t, effect = e, round = TRUE)
    })
  )
}))
```

## Checkable Tag

Sometimes because of the business needs, we might need checkbox like tag, but **button like checkbox** cannot meet our needs, here comes `check-tag`. You can use `type` prop in 2.5.4.

basic check-tag usage, the API is rather simple.

A tag that toggles, like a checkbox, is `el_check_tag()`; it reports
`input$<id>` as `TRUE` or `FALSE`.

```{r checkable, eval = FALSE, shot = TRUE}
tagList(
  el_check_tag("ct1", "Checked", value = TRUE),
  el_check_tag("ct2", "Toggle me"),
  el_check_tag("ct3", "Disabled", disabled = TRUE),
  tags$br(),
  tags$br(),
  lapply(c("primary", "success", "info", "warning", "danger"), function(t) {
    el_check_tag(paste0("ctt", t), t, type = t, value = TRUE)
  })
)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("tag")
```
