---
title: "Text"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Used for text.

## Basic

Use the `type` attribute to define Text's type.

```{r basic, eval = FALSE, shot = TRUE}
el_space(lapply(c("default", "primary", "success", "info", "warning", "danger"), function(t)
  el_text(tools::toTitleCase(t), type = if (t != "default") t)))
```

## Sizes

Use attribute `size` to set additional sizes with `large`, `default` or `small`.

```{r sizes, eval = FALSE, shot = TRUE}
el_space(el_text("Large", size = "large"), el_text("Default"), el_text("Small", size = "small"))
```

## Ellipsis

Pass the `truncated` prop to render an ellipsis when the text exceeds the width of the viewport or max-width set. `line-clamp` prop to render multiline ellipsis. Starting from version 2.14.6, `isTruncated` is exposed to indicate whether the text is truncated. You can use it to show a tooltip only when truncation occurs.

```{r truncated, eval = FALSE, shot = TRUE}
tagList(
  tags$div(el_text("Self element set width 150px", truncated = TRUE, width = "150px")),
  tags$div(style = "width: 150px", el_text("Squeezed by parent element", truncated = TRUE)),
  tags$div(el_text(HTML("The -webkit-line-clamp CSS property<br>allows limiting of the contents of<br>",
                        "a block to the specified number of lines."), line_clamp = 2)))
```

## Override

Use attribute `tag` to override element

`tag` draws the text as another element.

```{r override, eval = FALSE, shot = TRUE}
el_space(direction = "vertical",
  el_text("span"),
  el_text("This is a paragraph.", tag = "p"),
  el_text("Bold", tag = "b"),
  el_text("Italic", tag = "i"),
  el_text("This is ", el_text("subscript", tag = "sub", size = "small")),
  el_text("This is ", el_text("superscript", tag = "sup", size = "small")),
  el_text("Inserted", tag = "ins"),
  el_text("Deleted", tag = "del"),
  el_text("Marked", tag = "mark"))
```

## Mixed

Text mixed component

```{r mixed, eval = FALSE, shot = TRUE}
tagList(
  tags$p(el_text(el_icon("ElementPlus"), " Element-Plus")),
  tags$p(el_text("Rate"), el_rate("txt_rate")),
  tags$p(el_text("This is text mixed icon ", el_icon("Bell"), " and component"),
         el_button("txt_btn", "Button")))
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("text")
```
