---
title: "Timeline"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Visually display timeline.

## Basic usage

Timeline can be split into multiple activities. Timestamps are important features that distinguish them from other components. Note the difference with Steps.

```{r basic, eval = FALSE, shot = TRUE}
el_timeline(
  "tl",
  items = list(
    el_timeline_item("Event start", timestamp = "2018-04-15"),
    el_timeline_item("Approved", timestamp = "2018-04-13"),
    el_timeline_item("Success", timestamp = "2018-04-11")
  )
)
```

## Mode

Use `mode` to control the relative position of timeline and content.

> **Tip**
>
> After 2.13.1, `el-timeline` explicitly sets padding styles. If you have overridden padding styles of `ul` tag in your project, please check to ensure the layout is correct.

`mode` puts the content after the line (`"start"`), before it (`"end"`),
or on alternate sides; the radio buttons set it with
`update_el_timeline()`.

```{r mode, eval = FALSE, shot = TRUE, shot_js = "document.querySelectorAll('#tl_mode_pick .el-radio-button')[1].click()", shot_expect = "document.querySelector('#tl_mode .el-timeline').classList.contains('is-alternate')"}
ui <- el_page(
  el_radio_group(
    "tl_mode_pick",
    choices = c("start", "alternate", "alternate-reverse", "end"),
    selected = "start",
    button = TRUE
  ),
  tags$div(
    style = "margin-top: 16px",
    el_timeline(
      "tl_mode",
      mode = "start",
      items = list(
        el_timeline_item("Event start", timestamp = "2018-04-15"),
        el_timeline_item("Approved", timestamp = "2018-04-13"),
        el_timeline_item("Success", timestamp = "2018-04-11")
      )
    )
  )
)
server <- function(input, output, session) {
  observeEvent(input$tl_mode_pick, ignoreInit = TRUE, {
    update_el_timeline(session, "tl_mode", mode = input$tl_mode_pick)
  })
}
shinyApp(ui, server)
```

## Custom node

Size, color, and icons can be customized in node.

```{r custom-node, eval = FALSE, shot = TRUE}
el_timeline(
  "nodes",
  items = list(
    el_timeline_item(
      "Custom icon",
      timestamp = "2018-04-12 20:46",
      size = "large",
      type = "primary",
      icon = "MoreFilled"
    ),
    el_timeline_item(
      "Custom color",
      timestamp = "2018-04-03 20:46",
      color = "#0bbd87"
    ),
    el_timeline_item(
      "Custom size",
      timestamp = "2018-04-03 20:46",
      size = "large"
    ),
    el_timeline_item(
      "Custom hollow",
      timestamp = "2018-04-03 20:46",
      type = "primary",
      hollow = TRUE
    ),
    el_timeline_item("Default node", timestamp = "2018-04-03 20:46")
  )
)
```

## Custom timestamp

Timestamp can be placed on top of content when content is too high.

```{r custom-timestamp, eval = FALSE, shot = TRUE}
el_timeline(
  "stamps",
  items = list(
    el_timeline_item(
      el_card(
        tags$h4("Update Github template"),
        tags$p("Tom committed 2018/4/12 20:46")
      ),
      timestamp = "2018/4/12",
      placement = "top"
    ),
    el_timeline_item(
      el_card(
        tags$h4("Update Github template"),
        tags$p("Tom committed 2018/4/3 20:46")
      ),
      timestamp = "2018/4/3",
      placement = "top"
    ),
    el_timeline_item(
      el_card(
        tags$h4("Update Github template"),
        tags$p("Tom committed 2018/4/2 20:46")
      ),
      timestamp = "2018/4/2",
      placement = "top"
    )
  )
)
```

## Vertically centered

Timeline-Item is centered vertically.

```{r center, eval = FALSE, shot = TRUE}
el_timeline(
  "centred",
  items = list(
    el_timeline_item(
      el_card(
        tags$h4("Update Github template"),
        tags$p("Tom committed 2018/4/12 20:46")
      ),
      timestamp = "2018/4/12",
      placement = "top",
      center = TRUE
    ),
    el_timeline_item(
      el_card(
        tags$h4("Update Github template"),
        tags$p("Tom committed 2018/4/3 20:46")
      ),
      timestamp = "2018/4/3",
      placement = "top"
    ),
    el_timeline_item(
      "Event start",
      timestamp = "2018/4/2",
      placement = "top",
      center = TRUE
    ),
    el_timeline_item("Event end", timestamp = "2018/4/2", placement = "top")
  )
)
```

## Reverse

Use the reverse property to control the order of the nodes.

`reverse` shows the entries newest first; `update_el_timeline()` flips it.

```{r reverse, eval = FALSE, shot = TRUE}
ui <- el_page(
  el_radio_group(
    "order",
    choices = c(Ascending = "asc", Descending = "desc"),
    value = "asc"
  ),
  el_timeline(
    "tl",
    items = list(
      el_timeline_item("Event start", timestamp = "2018-04-15"),
      el_timeline_item("Approved", timestamp = "2018-04-13"),
      el_timeline_item("Success", timestamp = "2018-04-11")
    )
  )
)

server <- function(input, output, session) {
  observeEvent(
    input$order,
    update_el_timeline(id = "tl", reverse = input$order == "desc")
  )
}

shinyApp(ui, server)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("timeline")
```
