---
title: "TimeSelect"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Use Time Select for time input.

The available time range is 00:00 to 23:59

## Fixed time picker

Provide a list of fixed time for users to choose.

Use `el-time-select` label, then assign start time, end time and time step with `start`, `end` and `step`.

```{r basic, eval = FALSE, shot = TRUE}
el_time_select(
  "slot",
  start = "08:30",
  step = "00:15",
  end = "18:30",
  placeholder = "Select time",
  width = "240px"
)
```

## Time Formats

Use `format` to control format of time(hours and minutes).

Check the list [here](https://day.js.org/docs/en/display/format#list-of-all-available-formats) of all available formats of Day.js.

> **Warning**
>
> Pay attention to capitalization

```{r time-formats, eval = FALSE, shot = TRUE}
el_time_select(
  "fmt",
  start = "00:00",
  step = "00:30",
  end = "23:59",
  placeholder = "Select time",
  format = "hh:mm A",
  width = "240px"
)
```

## Fixed time range

If start( end ) time is picked at first, then the status of end( start ) time's options will change accordingly.

The end's earliest time follows the start: the server redraws it.

```{r time-range, eval = FALSE, shot = TRUE}
ui <- el_page(
  el_time_select(
    "start",
    start = "08:30",
    step = "00:15",
    end = "18:30",
    placeholder = "Start time",
    width = "240px"
  ),
  uiOutput("end_ui")
)

server <- function(input, output, session) {
  output$end_ui <- renderUI(el_time_select(
    "end",
    start = "08:30",
    step = "00:15",
    end = "18:30",
    min_time = if (isTruthy(input$start)) input$start,
    value = isolate(input$end),
    placeholder = "End time",
    width = "240px"
  ))
}

shinyApp(ui, server)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("time-select")
```
