---
title: "TimePicker"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Use Time Picker for time input. `input$<id>` is the time as text,
`"HH:mm:ss"` unless `value_format` says otherwise -- two of them for a
range.

## Fixed time picker

`el_time_select()` offers fixed times: `start`, `end` and `step`.

```{r fixed, eval = FALSE, shot = TRUE}
el_time_select("slot", placeholder = "Select time",
               picker_options = list(start = "08:30", step = "00:15", end = "18:30"))
```

## Arbitrary time picker

`selectableRange` limits what can be picked; `arrow_control` steps with
arrows instead of the mouse wheel.

```{r arbitrary, eval = FALSE, shot = TRUE}
el_time_picker("t1", placeholder = "Arbitrary time",
               picker_options = list(selectableRange = "18:30:00 - 20:30:00"))
el_time_picker("t2", arrow_control = TRUE, placeholder = "Arbitrary time",
               picker_options = list(selectableRange = "18:30:00 - 20:30:00"))
```

## Fixed time range

The end's `minTime` follows the start, from the server.

```{r fixed-range, eval = FALSE, shot = TRUE}
ui <- el_page(
  el_time_select("start", placeholder = "Start time",
                 picker_options = list(start = "08:30", step = "00:15", end = "18:30")),
  el_time_select("end", placeholder = "End time",
                 picker_options = list(start = "08:30", step = "00:15", end = "18:30"))
)

server <- function(input, output, session) {
  observeEvent(input$start, {
    update_el_time_select(id = "end", picker_options = list(
      start = "08:30", step = "00:15", end = "18:30", minTime = input$start))
  })
}

shinyApp(ui, server)
```

## Arbitrary time range

```{r range, eval = FALSE, shot = TRUE}
el_time_picker("r1", is_range = TRUE, range_separator = "To",
               start_placeholder = "Start time", end_placeholder = "End time")
el_time_picker("r2", is_range = TRUE, arrow_control = TRUE, range_separator = "To",
               start_placeholder = "Start time", end_placeholder = "End time")
```

## API

```{r api, echo = FALSE, results = "asis"}
api_tables("time-picker")
```
