---
title: "TimePicker"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Use Time Picker for time input.

## Arbitrary time picker

Can pick an arbitrary time.

By default, you can scroll the mouse wheel to pick time, alternatively you can use the control arrows when the `arrow-control` attribute is set.

```{r basic, eval = FALSE, shot = TRUE}
tagList(
  el_time_picker("t1", placeholder = "Arbitrary time"),
  el_time_picker("t2", arrow_control = TRUE, placeholder = "Arbitrary time")
)
```

## Limit the time range

You can also limit the time range.

Limit the time range by specifying `disabledHours` `disabledMinutes` and `disabledSeconds`.

`disabled_hours`, `disabled_minutes` and `disabled_seconds` limit what can
be picked -- here, 17:30 to 18:30.

```{r basic-range, eval = FALSE, shot = TRUE}
el_time_picker(
  "lim",
  value = "18:30:00",
  placeholder = "Arbitrary time",
  disabled_hours = JS(
    "function() { var r = []; for (var h = 0; h < 24; h++) if (h < 17 || h > 18) r.push(h); return r; }"
  ),
  disabled_minutes = JS(
    "function(h) { var r = []; for (var m = 0; m < 60; m++) if ((h === 17 && m < 30) || (h === 18 && m > 30)) r.push(m); return r; }"
  )
)
```

## Arbitrary time range

Can pick an arbitrary time range.

We can pick a time range by adding an `is-range` attribute. Also, `arrow-control` is supported in range mode.

```{r range, eval = FALSE, shot = TRUE}
tagList(
  el_time_picker(
    "r1",
    is_range = TRUE,
    value = c("08:40:00", "09:40:00"),
    range_separator = "To",
    start_placeholder = "Start time",
    end_placeholder = "End time"
  ),
  el_time_picker(
    "r2",
    is_range = TRUE,
    arrow_control = TRUE,
    value = c("08:40:00", "09:40:00"),
    range_separator = "To",
    start_placeholder = "Start time",
    end_placeholder = "End time"
  )
)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("time-picker")
```
