---
title: "Tooltip"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Display prompt information for mouse hover.

## Basic usage

Tooltip has 9 placements.

Use attribute `content` to set the display content when hover. The attribute `placement` determines the position of the tooltip. Its value is `[orientation]-[alignment]` with four orientations `top`, `left`, `right`, `bottom` and three alignments `start`, `end`, `null`, and the default alignment is null. Take `placement="left-end"` for example, Tooltip will display on the left of the element which you are hovering and the bottom of the tooltip aligns with the bottom of the element.

```{r basic, eval = FALSE, shot = TRUE, shot_js = "var b = document.querySelectorAll('#shot button')[4]; ['mouseenter','mouseover'].forEach(function(t){ b.dispatchEvent(new MouseEvent(t, {bubbles: true})); });", shot_sel = ".el-popper", shot_wait = 1}
places <- c("top-start", "top", "top-end", "left-start", "left", "left-end",
            "right-start", "right", "right-end", "bottom-start", "bottom", "bottom-end")
tags$div(style = "padding: 40px 80px", lapply(places, function(p)
  el_tooltip(paste0("tip_", gsub("-", "_", p)), el$button(p), placement = p,
             content = paste(p, "prompts info"), effect = "dark")))
```

## Theme

Tooltip has two built-in themes: `dark` and `light`.

> **Tip**
>
> To use customized theme, you will have to known where your tooltip is rendered into, if your tooltip is rendered into the root element, you will need to set the css rule globally.
> 
> It is recommended that not using linear gradient background color when you using customized theme and showing the arrow at the same time, because the popup arrow and the content are two different elements,
> the popup arrow's style needs to be set individually, and when it comes to the gradient background color, it might seem a little bit weird.

Set `effect` to modify theme, and the default value is `dark`.

```{r theme, eval = FALSE, shot = TRUE, shot_js = "var b = document.querySelector('#shot button'); ['mouseenter','mouseover'].forEach(function(t){ b.dispatchEvent(new MouseEvent(t, {bubbles: true})); });", shot_sel = ".el-popper", shot_wait = 1}
tagList(
  el_tooltip("dark", el$button("Dark"), content = "Top center", placement = "top"),
  el_tooltip("light", el$button("Light"), content = "Bottom center", placement = "bottom", effect = "light"),
  el_tooltip("custom", el$button("Customized theme"), content = "Bottom center", effect = "customized",
             placement = "bottom"))
```

## More Content

Display multiple lines of text and set their format.

Override attribute `content` of `el-tooltip` by adding a slot named `content`.

```{r rich-content, eval = FALSE, shot = TRUE, shot_js = "var b = document.querySelector('#shot button'); ['mouseenter','mouseover'].forEach(function(t){ b.dispatchEvent(new MouseEvent(t, {bubbles: true})); });", shot_sel = ".el-popper", shot_wait = 1}
el_tooltip("multi", el$button("Top center"), placement = "top",
           slots = list(content = tags$div("multiple lines", tags$br(), "second line")))
```

## Advanced usage

In addition to basic usages, there are some attributes that allow you to customize your own:

`transition` attribute allows you to customize the animation in which the tooltip shows or hides, and the default value is el-fade-in-linear.

`disabled` attribute allows you to disable `tooltip`. You just need set it to `true`.

In fact, Tooltip is an extension based on [ElPopper](https://github.com/element-plus/element-plus/tree/dev/packages/components/popper), you can use any attribute that are allowed in ElPopper.

Turned on and off from the server, `update_el_tooltip(disabled =)`.

```{r advanced-usage, eval = FALSE, shot = TRUE}
ui <- el_page(
  el_switch("tip_on", value = TRUE, active_text = "tooltip on"),
  el_tooltip("adv", el$button("Hover me"), content = "click the switch to turn me off",
             placement = "bottom"))
server <- function(input, output, session) {
  observeEvent(input$tip_on, update_el_tooltip(id = "adv", disabled = !input$tip_on))
}
shinyApp(ui, server)
```

> **Tip**
>
> The `router-link` component is not supported in tooltip, please use `vm.$router.push`.
> 
> Disabled form elements are not supported for Tooltip, more information can be found at [MDN](https://developer.mozilla.org/en-US/docs/Web/Events/mouseenter). You need to wrap the disabled form element with a container element for Tooltip to work.

## HTML as content

The content attribute can be set to HTML string.

> **Warning**
>
> Although `content` property supports HTML strings, dynamically rendering arbitrary HTML on your website can be very dangerous because it can easily lead to [XSS attacks](https://en.wikipedia.org/wiki/Cross-site_scripting). So when `raw-content` is on, please make sure `content` is trusted, and **never** assign user-provided `content`.

```{r html-content, eval = FALSE, shot = TRUE, shot_js = "var b = document.querySelector('#shot button'); ['mouseenter','mouseover'].forEach(function(t){ b.dispatchEvent(new MouseEvent(t, {bubbles: true})); });", shot_sel = ".el-popper", shot_wait = 1}
el_tooltip("html_tip", el$button("hover me"), raw_content = TRUE,
           content = "<span>The content can be <strong>HTML</strong></span>")
```

## Virtual triggering

Sometimes we want to render the tooltip on some other trigger element,
we can separate the trigger and the content.

> **Tip**
>
> Virtual triggering tooltip is controlled component, so that you will have to control the visibility of the tooltip your own
> when this happens, **YOU WILL NOT** be able to close the tooltip by clicking somewhere else.

> **In R**
>
> A virtual trigger is a DOM element the page's own script holds; in R, give
> the trigger itself.

## Singleton

Tooltip can also be singleton, which means you can have multiple trigger with only one tooltip instance, this function is implemented based on `Virtual triggering`

> **Tip**
>
> Known issue: when using singleton, the popup will be bouncing out from unexpected places

> **In R**
>
> Element Plus's singleton tooltip moves one tooltip between triggers held by
> the page's script; in R each trigger has a tooltip of its own.

## Controlled

Tooltip can be controlled by the parent component, by using `:visible` you can implement two way binding.

Shown and hidden from the server, `update_el_tooltip(visible =)`, and
then stays as set.

```{r controlled, eval = FALSE, shot = TRUE}
el_tooltip("ctl", el$button("Hover me"), visible = TRUE, content = "controlled")
```

## Animations

Tooltip can be customized animated, you can set the desired animation use `transition`.

> **Tip**
>
> Transition Classes, more information can be found at [Vue Transition](https://vuejs.org/guide/built-ins/transition.html#css-based-transitions).

```{r animations, eval = FALSE, shot = TRUE, shot_js = "var b = document.querySelector('#shot button'); ['mouseenter','mouseover'].forEach(function(t){ b.dispatchEvent(new MouseEvent(t, {bubbles: true})); });", shot_sel = ".el-popper", shot_wait = 1}
el_tooltip("anim", el$button("trigger me"), content = "I am an el-tooltip", transition = "slide-fade")
```

## Use the `append-to`

You must wait for the DOM to be mounted before using `targetElement`.

```{r append-to, eval = FALSE, shot = TRUE, shot_js = "var b = document.querySelector('#shot button'); ['mouseenter','mouseover'].forEach(function(t){ b.dispatchEvent(new MouseEvent(t, {bubbles: true})); });", shot_sel = ".el-popper", shot_wait = 1}
tags$div(id = "tip-host", el_tooltip("app", el$button("Hover me"), content = "Appended to #tip-host",
                                     append_to = "#tip-host"))
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("tooltip")
```
