---
title: "Tooltip"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Display prompt information on hover. The trigger can be plain markup or a
component -- folded into the tooltip's own Vue instance, so it keeps
reporting its inputs.

## Basic usage

`placement` takes twelve positions.

```{r basic, eval = FALSE, shot = TRUE, shot_js = "var b = document.querySelectorAll('#shot button')[4]; ['mouseenter','mouseover'].forEach(function(t){ b.dispatchEvent(new MouseEvent(t, {bubbles: true})); });", shot_sel = ".el-tooltip__popper", shot_wait = 1}
places <- c("top-start", "top", "top-end", "left-start", "left", "left-end",
            "right-start", "right", "right-end", "bottom-start", "bottom", "bottom-end")
tags$div(style = "padding: 40px 80px", lapply(places, function(p)
  el_tooltip(paste0("tip_", gsub("-", "_", p)), el$button(p), placement = p,
             content = paste(p, "prompts info"), effect = "dark")))
```

## Theme

```{r theme, eval = FALSE, shot = TRUE}
el_tooltip("dark", el$button("Dark"), content = "Top center", placement = "top")
el_tooltip("light", el$button("Light"), content = "Bottom center", placement = "bottom", effect = "light")
```

## More content

The `content` slot takes markup.

```{r more, eval = FALSE, shot = TRUE, shot_js = "var b = document.querySelector('#shot button'); ['mouseenter','mouseover'].forEach(function(t){ b.dispatchEvent(new MouseEvent(t, {bubbles: true})); });", shot_sel = ".el-tooltip__popper", shot_wait = 1}
el_tooltip("multi", el$button("Top center"), placement = "top",
           slots = list(content = tags$div("multiple lines", tags$br(), "second line")))
```

## Advanced usage

`disabled` turns it off -- here from a switch, through `update_el_tooltip()`;
`manual` hands showing and hiding to `update_el_tooltip(value =)`.

```{r advanced, eval = FALSE, shot = TRUE}
ui <- el_page(
  el_switch("tip_on", value = TRUE, active_text = "tooltip on"),
  el_tooltip("adv", el$button("Hover me"), content = "click the switch to turn me off",
             placement = "bottom"))

server <- function(input, output, session) {
  observeEvent(input$tip_on, update_el_tooltip(id = "adv", disabled = !input$tip_on))
}

shinyApp(ui, server)
```

## API

```{r api, echo = FALSE, results = "asis"}
api_tables("tooltip")
```
