---
title: "Tour"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

A popup component for guiding users through a product. Use when you want to guide users through a product.

## Basic usage

The most basic usage

A step's `target` is a CSS selector; the server opens the tour with
`update_el_tour()`.

```{r basic, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#begin_container button').click()", shot_sel = ".el-tour__content", shot_wait = 3.5}
ui <- el_page(
  el_button("begin", "Begin Tour", type = "primary"),
  el_divider(),
  el_space(tags$span(id = "t_up", el_button("up", "Upload")),
           tags$span(id = "t_save", el_button("save", "Save", type = "primary")),
           tags$span(id = "t_more", el_button("more", "", icon = "MoreFilled"))),
  el_tour("tour", steps = list(
    list(target = "#t_up", title = "Upload File", description = "Put you files here."),
    list(target = "#t_save", title = "Save", description = "Save your changes"),
    list(target = "#t_more", title = "Other Actions", description = "Click to see other"))))

server <- function(input, output, session) {
  observeEvent(input$begin, update_el_tour(id = "tour", open = TRUE, current = 0))
}

shinyApp(ui, server)
```

## Non modal

Use `:mask="false"` to make Tour non-modal. At the meantime it is recommended to use with `type="primary"` to emphasize the guide itself.

`mask = FALSE` leaves the page undimmed; `type = "primary"` colours the card.

```{r non-modal, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#begin_container button').click()", shot_sel = ".el-tour__content", shot_wait = 3.5}
ui <- el_page(
  el_button("begin", "Begin Tour", type = "primary"),
  el_divider(),
  el_space(tags$span(id = "t_up", el_button("up", "Upload")),
           tags$span(id = "t_save", el_button("save", "Save", type = "primary")),
           tags$span(id = "t_more", el_button("more", "", icon = "MoreFilled"))),
  el_tour("tour", type = "primary", mask = FALSE, steps = list(
    list(target = "#t_up", title = "Upload File", description = "Put you files here."),
    list(target = "#t_save", title = "Save", description = "Save your changes"),
    list(target = "#t_more", title = "Other Actions", description = "Click to see other"))))

server <- function(input, output, session) {
  observeEvent(input$begin, update_el_tour(id = "tour", open = TRUE, current = 0))
}

shinyApp(ui, server)
```

## Placement

Change the placement of the guide relative to the target, there are 12 placements available. When `target` is empty the guide will show in the center.

```{r placement, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#begin_container button').click()", shot_sel = ".el-tour__content", shot_wait = 3.5}
ui <- el_page(
  tags$span(id = "t_btn", el_button("begin", "Begin Tour", type = "primary")),
  el_tour("tour", steps = list(
    list(title = "Center", description = "Displayed in the center of screen."),
    list(title = "Right", description = "On the right of target.", placement = "right", target = "#t_btn"),
    list(title = "Top", description = "On the top of target.", placement = "top", target = "#t_btn"))))

server <- function(input, output, session) {
  observeEvent(input$begin, update_el_tour(id = "tour", open = TRUE, current = 0))
}

shinyApp(ui, server)
```

## Custom mask style

Custom mask style.

`mask` takes Element Plus's object: its `style` and `color`.

```{r mask, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#begin_container button').click()", shot_sel = ".el-tour__content", shot_wait = 3.5}
ui <- el_page(
  el_button("begin", "Begin Tour", type = "primary"),
  el_divider(),
  el_space(tags$span(id = "t_up", el_button("up", "Upload")),
           tags$span(id = "t_save", el_button("save", "Save", type = "primary"))),
  el_tour("tour", mask = list(style = list(boxShadow = "inset 0 0 15px #333"),
                              color = "rgba(80, 255, 255, .4)"), steps = list(
    list(target = "#t_up", title = "Upload File", description = "Put you files here."),
    list(target = "#t_save", title = "Save", description = "Save your changes",
         mask = list(style = list(boxShadow = "inset 0 0 15px #fff"),
                     color = "rgba(40, 0, 255, .4)")))))

server <- function(input, output, session) {
  observeEvent(input$begin, update_el_tour(id = "tour", open = TRUE, current = 0))
}

shinyApp(ui, server)
```

## Custom indicator

Custom indicator.

The `indicators` slot draws the step counter; its scope is `current` and
`total`.

```{r indicator, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#begin_container button').click()", shot_sel = ".el-tour__content", shot_wait = 3.5}
ui <- el_page(
  el_button("begin", "Begin Tour", type = "primary"),
  el_divider(),
  el_space(tags$span(id = "t_up", el_button("up", "Upload")),
           tags$span(id = "t_save", el_button("save", "Save", type = "primary"))),
  el_tour("tour", steps = list(
    list(target = "#t_up", title = "Upload File", description = "Put you files here."),
    list(target = "#t_save", title = "Save", description = "Save your changes")),
    slots = list(indicators = template(tags$span("{{ current + 1 }} / {{ total }}"),
                                       slot = "indicators", scope = "{ current, total }"))))

server <- function(input, output, session) {
  observeEvent(input$begin, update_el_tour(id = "tour", open = TRUE, current = 0))
}

shinyApp(ui, server)
```

## Target

Various parameter passing types of target. The string and Function types are supported since 2.5.2.

A target may be any selector, and need not exist until the step is shown.

```{r target, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#begin_container button').click()", shot_sel = ".el-tour__content", shot_wait = 3.5}
ui <- el_page(
  el_button("begin", "Begin Tour", type = "primary"),
  el_divider(),
  tags$div(id = "first", style = "display: inline-block; padding: 8px; border: 1px dashed #ccc", "First"),
  tags$div(class = "second", style = "display: inline-block; padding: 8px; border: 1px dashed #ccc", "Second"),
  el_tour("tour", steps = list(
    list(target = "#first", title = "By id", description = "A selector for an id."),
    list(target = ".second", title = "By class", description = "A selector for a class."))))

server <- function(input, output, session) {
  observeEvent(input$begin, update_el_tour(id = "tour", open = TRUE, current = 0))
}

shinyApp(ui, server)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("tour")
```
