---
title: "Transfer"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Move items between two lists. `data` is a data frame of `key` and
`label` (and `disabled`), and `input$<id>` the keys on the right.

## Basic usage

```{r basic, eval = FALSE, shot = TRUE}
items <- data.frame(key = 1:15, label = paste("Option", 1:15), disabled = 1:15 %% 4 == 0)
el_transfer("basic", data = items, value = c(1, 4))
```

## Filterable

```{r filterable, eval = FALSE, shot = TRUE}
states <- c("California", "Illinois", "Maryland", "Texas", "Florida", "Colorado", "Connecticut")
el_transfer("states", data = data.frame(key = seq_along(states), label = states),
            filterable = TRUE, filter_placeholder = "State abbreviations")
```

## Customizable

`titles`, `button_texts` and `format` relabel it; `render_content` draws
each item, as a `JS()` render function, or the default slot, scoped with
`option`.

```{r custom, eval = FALSE, shot = TRUE}
items <- data.frame(key = 1:8, label = paste("Option", 1:8))
el_transfer("custom", data = items, value = 1, filterable = TRUE,
            titles = c("Source", "Target"), button_texts = c("To left", "To right"),
            format = list(noChecked = "${total}", hasChecked = "${checked}/${total}"),
            slots = list(default = template(
              tags$span("{{ option.key }} - {{ option.label }}"), scope = "{ option }")))
```

## Prop aliases

Items whose fields are named otherwise: `props` says which is which.

```{r aliases, eval = FALSE, shot = TRUE}
items <- data.frame(value = 1:6, desc = paste("Option", 1:6))
el_transfer("aliases", data = items, props = list(key = "value", label = "desc"))
```

## API

```{r api, echo = FALSE, results = "asis"}
api_tables("transfer")
```
