---
title: "Transfer"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

## Basic usage

Data is passed to Transfer via the `data` attribute. The data needs to be an object array, and each object should have these attributes: `key` being the identification of the data item, `label` being the displayed text, and `disabled` indicating if the data item is disabled. Items inside the target list are in sync with the variable binding to `v-model`, and the value of that variable is an array of target item keys. So, if you don't want the target list be initially empty, you can initialize the `v-model` with an array.

`data` is a data frame of `key` and `label` (and `disabled`), and
`input$<id>` the keys on the right.

```{r basic, eval = FALSE, shot = TRUE}
items <- data.frame(
  key = 1:15,
  label = paste("Option", 1:15),
  disabled = 1:15 %% 4 == 0
)
el_transfer("basic", data = items, value = c(1, 4))
```

## Filterable

You can search and filter data items.

Set the `filterable` attribute to `true` to enable filter mode. By default, if the data item `label` contains the search keyword, it will be included in the search result. Also, you can implement you own filter method with the `filter-method` attribute. It takes a method and passes search keyword and each data item to it whenever the keyword changes. For a certain data item, if the method returns true, it will be included in the result list.

```{r filterable, eval = FALSE, shot = TRUE}
states <- c(
  "California",
  "Illinois",
  "Maryland",
  "Texas",
  "Florida",
  "Colorado",
  "Connecticut"
)
el_transfer(
  "states",
  data = data.frame(key = seq_along(states), label = states),
  filterable = TRUE,
  filter_placeholder = "State Abbreviations"
)
```

## Customizable

You can customize list titles, button texts, render function for data items, checking status texts in list footer and list footer contents.

Use `titles`, `button-texts`, `render-content` and `format` to respectively customize list titles, button texts, render function for data items, checking status texts in list header. Plus, you can also use scoped slot to customize data items. For list footer contents, two named slots are provided: `left-footer` and `right-footer`. Plus, if you want some items initially checked, you can use `left-default-checked` and `right-default-checked`. Finally, this example demonstrate the `change` event. Note that this demo can't run in JSFiddle because it doesn't support JSX syntax. In a real project, `render-content` will work if relevant dependencies are correctly configured.

`titles`, `button_texts` and `format` relabel it; the default slot,
scoped with `option`, draws each item.

```{r customizable, eval = FALSE, shot = TRUE}
items <- data.frame(key = 1:15, label = paste("Option", 1:15))
el_transfer(
  "custom",
  data = items,
  value = 1,
  filterable = TRUE,
  titles = c("Source", "Target"),
  button_texts = c("To left", "To right"),
  format = list(noChecked = "${total}", hasChecked = "${checked}/${total}"),
  slots = list(
    default = template(
      tags$span("{{ option.key }} - {{ option.label }}"),
      scope = "{ option }"
    )
  )
)
```

## Custom empty content

You can customize the content when the list is empty or when no filtering results are found.

Use `left-empty` and `right-empty` slots to customize the empty content for each panel.

```{r empty-content, eval = FALSE, shot = TRUE}
items <- data.frame(key = integer(0), label = character(0))
el_transfer(
  "empty",
  data = items,
  slots = list(
    leftEmpty = el_empty(image_size = 60, description = "No data"),
    rightEmpty = el_empty(image_size = 60, description = "No data")
  )
)
```

## Prop aliases

By default, Transfer looks for `key`, `label` and `disabled` in a data item. If your data items have different key names, you can use the `props` attribute to define aliases.

The data items in this example do not have `key`s or `label`s, instead they have `value`s and `desc`s. So you need to set aliases for `key` and `label`.

Items whose fields are named otherwise: `props` says which is which.

```{r prop-alias, eval = FALSE, shot = TRUE}
items <- data.frame(value = 1:15, desc = paste("Option", 1:15))
el_transfer(
  "aliases",
  data = items,
  props = list(key = "value", label = "desc")
)
```

## Virtual Scroll

When dealing with large amounts of data, you can enable virtual scrolling to improve performance.

Set `virtual-scroll` to `true` to enable virtual scrolling. You can also customize the item height with `item-size`. Default item size is 30px.

`virtual_scroll` draws only the rows in view, for long lists.

```{r virtual-scroll, eval = FALSE, shot = TRUE}
items <- data.frame(key = 1:10000, label = paste("Option", 1:10000))
el_transfer(
  "virtual",
  data = items,
  virtual_scroll = TRUE,
  item_size = 34,
  filterable = TRUE
)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("transfer")
```
