---
title: "Virtualized Tree"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Tree view with blazing fast scrolling performance for any amount of data

## Basic usage

Basic tree structure.

Nodes are `list(id =, label =, children =)`; only those in view are
drawn, so ten thousand cost little.

```{r basic, eval = FALSE, shot = TRUE}
make_nodes <- function(depth, prefix = "") {
  lapply(1:10, function(i) {
    key <- paste0(prefix, i)
    node <- list(id = key, label = paste("Node", key))
    if (depth > 1) {
      node$children <- make_nodes(depth - 1, paste0(key, "-"))
    }
    node
  })
}
el_tree_v2("tv2_basic", data = make_nodes(3), height = 208)
```

## Selectable

Used for node selection.

```{r selectable, eval = FALSE, shot = TRUE}
make_nodes <- function(depth, prefix = "") {
  lapply(1:10, function(i) {
    key <- paste0(prefix, i)
    node <- list(id = key, label = paste("Node", key))
    if (depth > 1) {
      node$children <- make_nodes(depth - 1, paste0(key, "-"))
    }
    node
  })
}
el_tree_v2("tv2_sel", data = make_nodes(3), show_checkbox = TRUE, height = 208)
```

> **Warning**
>
> When using show-checkbox, since `check-on-click-leaf` is true by default,
> last tree children's can be checked by clicking their nodes.

## Disabled checkbox

The checkbox of a node can be set as disabled.

In the example, `disabled` property is declared in defaultProps, and some nodes are set as `disabled: true`. The corresponding checkboxes are disabled and can't be clicked.

```{r disabled, eval = FALSE, shot = TRUE}
nodes <- list(
  list(
    id = "1",
    label = "Level one 1",
    children = list(
      list(id = "1-1", label = "Level two 1-1", disabled = TRUE),
      list(id = "1-2", label = "Level two 1-2")
    )
  ),
  list(id = "2", label = "Level one 2", disabled = TRUE)
)
el_tree_v2(
  "tv2_dis",
  data = nodes,
  show_checkbox = TRUE,
  default_expanded_keys = "1",
  height = 208
)
```

## Default expanded and default checked

Tree nodes can be initially expanded or checked

Use `default-expanded-keys` and `default-checked-keys` to set initially expanded and initially checked nodes respectively.

```{r default-state, eval = FALSE, shot = TRUE}
make_nodes <- function(depth, prefix = "") {
  lapply(1:10, function(i) {
    key <- paste0(prefix, i)
    node <- list(id = key, label = paste("Node", key))
    if (depth > 1) {
      node$children <- make_nodes(depth - 1, paste0(key, "-"))
    }
    node
  })
}
el_tree_v2(
  "tv2_def",
  data = make_nodes(3),
  show_checkbox = TRUE,
  height = 208,
  default_expanded_keys = c("1", "1-1"),
  default_checked_keys = c("1-1-1", "1-1-2")
)
```

## Custom node content

The content of tree nodes can be customized, so you can add icons or buttons as you will

The default slot, scoped with `node`, draws each node: an icon by its
state, and a prefix coloured by whether it is a leaf.

```{r custom-node, eval = FALSE, shot = TRUE, shot_js = c("document.querySelectorAll('#tv2_cus .el-tree-node__content')[0].click()", "document.querySelectorAll('#tv2_cus .el-tree-node__content')[1].click()"), shot_expect = c("document.querySelectorAll('#tv2_cus [data-el-icon=FolderOpened], #tv2_cus .el-tree-node__content .el-icon--left').length > 0", "document.querySelectorAll('#tv2_cus .prefix.is-leaf').length > 0")}
make_nodes <- function(depth, key = "node") {
  lapply(seq_len(if (depth == 1) 10 else 4), function(i) {
    id <- paste0(key, "-", i)
    node <- list(id = id, label = id)
    if (depth < 3) {
      node$children <- make_nodes(depth + 1, id)
    }
    node
  })
}
tagList(
  tags$style(
    ".prefix { color: var(--el-color-primary); margin-right: 10px; }
     .prefix.is-leaf { color: var(--el-color-success); }"
  ),
  el_tree_v2(
    "tv2_cus",
    data = make_nodes(1),
    props = list(value = "id", label = "label", children = "children"),
    height = 200,
    width = "600px",
    slots = list(
      default = template(
        scope = "{ node }",
        htmltools::HTML(paste0(
          "<el-icon class=\"el-icon--left\"><Document v-if=\"node.isLeaf\" />",
          "<Folder v-else-if=\"!node.expanded\" /><FolderOpened v-else /></el-icon>",
          "<span class=\"prefix\" :class=\"{ 'is-leaf': node.isLeaf }\">[ElementPlus]</span>",
          "<span>{{ node.label }}</span>"
        ))
      )
    )
  )
)
```

## Custom node class

The class of tree nodes can be customized

`props = list(class =)` gives each node a class of its own, from a
`JS()` function of its data.

```{r custom-node-class, eval = FALSE, shot = TRUE}
nodes <- list(
  list(
    id = "1",
    label = "Level one 1",
    children = list(list(
      id = 4,
      label = "Level two 1-1",
      isPenultimate = TRUE,
      children = list(
        list(id = 9, label = "Level three 1-1-1"),
        list(id = 10, label = "Level three 1-1-2")
      )
    ))
  ),
  list(
    id = 2,
    label = "Level one 2",
    children = list(
      list(
        id = 5,
        label = "Level two 2-1",
        isPenultimate = TRUE,
        children = list(
          list(id = 11, label = "Level three 2-1-1"),
          list(id = 12, label = "Level three 2-1-2")
        )
      ),
      list(id = 6, label = "Level two 2-2")
    )
  )
)
tagList(
  el_tree_v2(
    "tv2_classed",
    data = nodes,
    show_checkbox = TRUE,
    expand_on_click_node = FALSE,
    height = 208,
    default_expanded_keys = c("1", "2"),
    props = list(
      value = "id",
      label = "label",
      children = "children",
      class = JS(
        "function(data) { return data.isPenultimate ? 'is-penultimate' : ''; }"
      )
    )
  ),
  tags$style(".is-penultimate .el-tree-node__label { color: #626aef; }")
)
```

## Custom node icon

You can customize icons for different node states. Tree nodes expose the `expanded` property and `isLeaf` property, allowing you to dynamically render different icons based on the node's state: leaf nodes, expanded nodes, or collapsed nodes.

```{r custom-icon, eval = FALSE, shot = TRUE}
make_nodes <- function(depth, prefix = "") {
  lapply(1:10, function(i) {
    key <- paste0(prefix, i)
    node <- list(id = key, label = paste("Node", key))
    if (depth > 1) {
      node$children <- make_nodes(depth - 1, paste0(key, "-"))
    }
    node
  })
}
el_tree_v2(
  "tv2_icon",
  data = make_nodes(3),
  icon = "ArrowRightBold",
  height = 208
)
```

## Tree node filtering

The `filter-method` method can only accept the third parameter after version `2.9.1`.
Tree nodes can be filtered

Invoke the `filter` method of the Tree instance to filter tree nodes. Its parameter is the filtering keyword. Note that for it to work, `filter-method` is required, and its value is the filtering method.

`filter()`, run with `call_el()`, keeps the nodes `filter_method` passes.

```{r filter, eval = FALSE, shot = TRUE, shot_js = "var i = document.querySelector('#q_container input'); i.value = '1-1'; i.dispatchEvent(new Event('input'));", shot_wait = 2}
make_nodes <- function(depth, prefix = "") {
  lapply(1:10, function(i) {
    key <- paste0(prefix, i)
    node <- list(id = key, label = paste("Node", key))
    if (depth > 1) {
      node$children <- make_nodes(depth - 1, paste0(key, "-"))
    }
    node
  })
}

ui <- el_page(
  el_input("q", placeholder = "Please enter keyword", width = "240px"),
  el_tree_v2(
    "tv2_filter",
    data = make_nodes(3),
    height = 208,
    filter_method = JS(
      "function(query, node) { return node.label.includes(query); }"
    )
  )
)

server <- function(input, output, session) {
  observeEvent(
    input$q,
    call_el(session, "tv2_filter", "filter", list(input$q), result = FALSE)
  )
}

shinyApp(ui, server)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("tree-v2")
```
