---
title: "Tree"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Display a set of data with hierarchies. Nodes are `list(id =, label =,
children =)`; `df_to_tree_data()` builds them from a data frame.
`input$<id>` is the key of the node last clicked, `input$<id>_checked`
the keys checked.

## Basic usage

```{r basic, eval = FALSE, shot = TRUE}
levels <- list(
  list(id = 1, label = "Level one 1", children = list(
    list(id = 4, label = "Level two 1-1", children = list(list(id = 9, label = "Level three 1-1-1"))))),
  list(id = 2, label = "Level one 2", children = list(
    list(id = 5, label = "Level two 2-1"), list(id = 6, label = "Level two 2-2"))),
  list(id = 3, label = "Level one 3", children = list(
    list(id = 7, label = "Level two 3-1"), list(id = 8, label = "Level two 3-2"))))
el_tree("basic", data = levels, node_key = "id")
```

## Selectable

`show_checkbox` adds a box to every node.

```{r selectable, eval = FALSE, shot = TRUE}
el_tree("pick", show_checkbox = TRUE, node_key = "id", default_expand_all = TRUE, data = list(
  list(id = "r1", label = "Region 1", children = list(list(id = "a", label = "Area A"), list(id = "b", label = "Area B"))),
  list(id = "r2", label = "Region 2")))
```

## Custom leaf node in lazy mode

With `lazy = TRUE` each node's children come from the server, asked for
through `input$<id>_load` and answered with `el_load_children()`;
`is_leaf_field` names the field that says a node has none.

```{r lazy, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#shot .el-tree-node__content').click()", shot_wait = 2}
ui <- el_page(el_tree("zones", lazy = TRUE, node_key = "id", show_checkbox = TRUE,
                      is_leaf_field = "leaf"))

server <- function(input, output, session) {
  observeEvent(input$zones_load, {
    q <- input$zones_load
    kids <- if (q$level == 0) list(list(id = "region", label = "region"))
            else lapply(1:2, function(i) list(id = paste0(q$key, i), label = paste0("zone", i),
                                               leaf = q$level >= 2))
    el_load_children(id = "zones", request = q, children = kids)
  })
}

shinyApp(ui, server)
```

## Disabled checkbox

```{r disabled, eval = FALSE, shot = TRUE}
el_tree("dis", show_checkbox = TRUE, node_key = "id", default_expand_all = TRUE, data = list(
  list(id = 1, label = "Level one 1", children = list(
    list(id = 3, label = "Level two 2-1", children = list(
      list(id = 4, label = "Level three 3-1-1"),
      list(id = 5, label = "Level three 3-1-2", disabled = TRUE))),
    list(id = 2, label = "Level two 2-2", disabled = TRUE)))))
```

## Default expanded and default checked

`expanded` and `checked` are Element's `default-expanded-keys` and
`default-checked-keys` -- renamed, since `update_el_tree(checked =)` changes
them later.

```{r defaults, eval = FALSE, shot = TRUE}
el_tree("defs", show_checkbox = TRUE, node_key = "id", expanded = c(2, 3), checked = 5, data = list(
  list(id = 1, label = "Level one 1", children = list(list(id = 4, label = "Level two 1-1"))),
  list(id = 2, label = "Level one 2", children = list(
    list(id = 5, label = "Level two 2-1"), list(id = 6, label = "Level two 2-2"))),
  list(id = 3, label = "Level one 3", children = list(
    list(id = 7, label = "Level two 3-1"), list(id = 8, label = "Level two 3-2")))))
```

## Checking tree nodes

`update_el_tree(checked =)` sets them; `el_call()` runs Element's
`getCheckedKeys()`, `setCheckedKeys()` and the rest, a value coming back
as `input$<id>_get_checked_keys`.

```{r checking, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#set_container button').click()", shot_wait = 2}
nodes <- list(
  list(id = 1, label = "Level one 1", children = list(list(id = 4, label = "Level two 1-1"))),
  list(id = 2, label = "Level one 2", children = list(
    list(id = 5, label = "Level two 2-1"), list(id = 6, label = "Level two 2-2"))))

ui <- el_page(
  el_tree("tree", data = nodes, show_checkbox = TRUE, node_key = "id", default_expand_all = TRUE),
  el_button("set", "Check 4 and 6", size = "small"), el_button("get", "Get checked keys", size = "small"),
  el_button("reset", "Reset", size = "small"), verbatimTextOutput("keys"))

server <- function(input, output, session) {
  observeEvent(input$set, update_el_tree(id = "tree", checked = c(4, 6)))
  observeEvent(input$reset, update_el_tree(id = "tree", checked = character(0)))
  observeEvent(input$get, el_call(session, "tree", "getCheckedKeys"))
  output$keys <- renderPrint(input$tree_checked)
}

shinyApp(ui, server)
```

## Custom node content

The default slot, scoped with `node` and `data`, draws each node.

```{r custom, eval = FALSE, shot = TRUE}
el_tree("cus", node_key = "id", default_expand_all = TRUE, expand_on_click_node = FALSE,
  data = list(list(id = 1, label = "Level one 1", children = list(list(id = 4, label = "Level two 1-1")))),
  slots = list(default = template(
    tags$span(style = "flex: 1; display: flex; justify-content: space-between; padding-right: 8px",
      tags$span("{{ node.label }}"),
      tags$span(el$button(type = "text", size = "mini", "Append"),
                el$button(type = "text", size = "mini", "Delete"))),
    scope = "{ node, data }")))
```

## Tree node filtering

`filter()` keeps the nodes whose label contains the text; give
`filter_node_method` to decide otherwise.

```{r filtering, eval = FALSE, shot = TRUE, shot_js = "var i = document.querySelector('#q_container input'); i.value = 'two'; i.dispatchEvent(new Event('input'));", shot_wait = 2}
ui <- el_page(
  el_input("q", placeholder = "Filter keyword", width = "300px"),
  el_tree("filtered", node_key = "id", default_expand_all = TRUE, data = list(
    list(id = 1, label = "Level one 1", children = list(list(id = 4, label = "Level two 1-1"))),
    list(id = 2, label = "Level one 2", children = list(list(id = 5, label = "Level three 2-1"))))))

server <- function(input, output, session) {
  observeEvent(input$q, el_call(session, "filtered", "filter", list(input$q), result = FALSE))
}

shinyApp(ui, server)
```

## Accordion

Only one node of a level open at a time.

```{r accordion, eval = FALSE, shot = TRUE}
el_tree("acc", accordion = TRUE, node_key = "id", data = list(
  list(id = 1, label = "Level one 1", children = list(list(id = 4, label = "Level two 1-1"))),
  list(id = 2, label = "Level one 2", children = list(list(id = 5, label = "Level two 2-1")))))
```

## Draggable

`draggable` lets nodes be dragged; `allow_drag` and `allow_drop`, `JS()`
functions, say which and where, and `input$<id>_node_drop` reports where
one landed.

```{r draggable, eval = FALSE, shot = TRUE}
el_tree("drag", draggable = TRUE, node_key = "id", default_expand_all = TRUE,
  allow_drop = JS("function(dragging, drop, type) {",
                  "  return drop.data.label !== 'Level two 3-1' || type !== 'inner';",
                  "}"),
  data = list(
    list(id = 1, label = "Level one 1", children = list(list(id = 4, label = "Level two 1-1"))),
    list(id = 3, label = "Level one 3", children = list(list(id = 7, label = "Level two 3-1")))))
```

## API

```{r api, echo = FALSE, results = "asis"}
api_tables("tree")
```
