---
title: "Tree"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Display a set of data with hierarchies.

## Basic usage

Basic tree structure.

Nodes are `list(id =, label =, children =)`; `df_to_tree_data()` builds
them from a data frame. `input$<id>` is the key of the node last clicked,
`input$<id>_checked` the keys checked.

```{r basic, eval = FALSE, shot = TRUE}
levels <- list(
  list(id = 1, label = "Level one 1", children = list(
    list(id = 4, label = "Level two 1-1", children = list(list(id = 9, label = "Level three 1-1-1"))))),
  list(id = 2, label = "Level one 2", children = list(
    list(id = 5, label = "Level two 2-1"), list(id = 6, label = "Level two 2-2"))),
  list(id = 3, label = "Level one 3", children = list(
    list(id = 7, label = "Level two 3-1"), list(id = 8, label = "Level two 3-2"))))
el_tree("basic", data = levels, node_key = "id")
```

## Selectable

Used for node selection.

This example also shows how to load node data asynchronously.

With `lazy = TRUE` each node's children come from the server, asked for
through `input$<id>_load` and answered with `el_load_children()`.

```{r selectable, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#shot .el-tree-node__content').click()", shot_wait = 2}
ui <- el_page(el_tree("zones", lazy = TRUE, node_key = "id", show_checkbox = TRUE))

server <- function(input, output, session) {
  observeEvent(input$zones_load, {
    q <- input$zones_load
    kids <- if (q$level == 0) list(list(id = "region1", label = "Region"), list(id = "region2", label = "Region2"))
            else if (q$level > 3) list()
            else lapply(1:2, function(i) list(id = paste0(q$key, "-", i), label = paste0("zone", i)))
    el_load_children(id = "zones", request = q, children = kids)
  })
}

shinyApp(ui, server)
```

> **Warning**
>
> When using show-checkbox, since `check-on-click-leaf` is true by default,
> last tree children's can be checked by clicking their nodes.

## Custom leaf node in lazy mode

A node's data is not fetched until it is clicked, so the Tree cannot predict whether a node is a leaf node. That's why a drop-down button is added to each node, and if it is a leaf node, the drop-down button will disappear when clicked. That being said, you can also tell the Tree in advance whether the node is a leaf node, avoiding the render of the drop-down button before a leaf node.

`is_leaf_field` names the field that says a node has no children, so it
draws no expand arrow.

```{r custom-leaf, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#shot .el-tree-node__content').click()", shot_wait = 2}
ui <- el_page(el_tree("zones", lazy = TRUE, node_key = "id", show_checkbox = TRUE,
                      is_leaf_field = "leaf"))

server <- function(input, output, session) {
  observeEvent(input$zones_load, {
    q <- input$zones_load
    kids <- if (q$level == 0) list(list(id = "region", label = "region"))
            else lapply(1:2, function(i) list(id = paste0(q$key, i), label = paste0("zone", i),
                                               leaf = q$level >= 2))
    el_load_children(id = "zones", request = q, children = kids)
  })
}

shinyApp(ui, server)
```

## Lazy loading multiple times

When lazily loading node data remotely, lazy loading may sometimes fail. In this case, you can call reject to keep the node status as is and allow remote loading to continue.

> **In R**
>
> Upstream, a failed load calls `reject()` so the node can be loaded again.
> In R the server answers every `input$<id>_load`; to let a node retry,
> answer it later -- the node keeps spinning until `el_load_children()` comes.

## Disabled checkbox

The checkbox of a node can be set as disabled.

In the example, 'disabled' property is declared in defaultProps, and some nodes are set as 'disabled:true'. The corresponding checkboxes are disabled and can't be clicked.

```{r disabled, eval = FALSE, shot = TRUE}
el_tree("dis", show_checkbox = TRUE, node_key = "id", default_expand_all = TRUE, data = list(
  list(id = 1, label = "Level one 1", children = list(
    list(id = 3, label = "Level two 2-1", children = list(
      list(id = 4, label = "Level three 3-1-1"),
      list(id = 5, label = "Level three 3-1-2", disabled = TRUE))),
    list(id = 2, label = "Level two 2-2", disabled = TRUE, children = list(
      list(id = 6, label = "Level three 3-2-1"),
      list(id = 7, label = "Level three 3-2-2", disabled = TRUE)))))))
```

## Default expanded and default checked

Tree nodes can be initially expanded or checked

Use `default-expanded-keys` and `default-checked-keys` to set initially expanded and initially checked nodes respectively. Note that for them to work, `node-key` is required. Its value is the name of a key in the data object, and the value of that key should be unique across the whole tree.

`expanded` and `checked` are Element Plus's `default-expanded-keys` and
`default-checked-keys` -- renamed, since `update_el_tree(checked =)`
changes them later.

```{r default-state, eval = FALSE, shot = TRUE}
el_tree("defs", show_checkbox = TRUE, node_key = "id", expanded = c(2, 3), checked = 5, data = list(
  list(id = 1, label = "Level one 1", children = list(list(id = 4, label = "Level two 1-1"))),
  list(id = 2, label = "Level one 2", children = list(
    list(id = 5, label = "Level two 2-1"), list(id = 6, label = "Level two 2-2"))),
  list(id = 3, label = "Level one 3", children = list(
    list(id = 7, label = "Level two 3-1"), list(id = 8, label = "Level two 3-2")))))
```

## Checking tree nodes

This example shows how to get and set checked nodes. They both can be done in two approaches: node and key. If you are taking the key approach, `node-key` is required.

`update_el_tree(checked =)` sets them; `el_call()` runs Element Plus's
`getCheckedKeys()`, `setCheckedKeys()` and the rest.

```{r checking-tree, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#set_container button').click()", shot_wait = 2}
nodes <- list(
  list(id = 1, label = "Level one 1", children = list(list(id = 4, label = "Level two 1-1"))),
  list(id = 2, label = "Level one 2", children = list(
    list(id = 5, label = "Level two 2-1"), list(id = 6, label = "Level two 2-2"))))

ui <- el_page(
  el_tree("tree", data = nodes, show_checkbox = TRUE, node_key = "id", default_expand_all = TRUE),
  el_button("set", "Check 4 and 6", size = "small"), el_button("get", "Get checked keys", size = "small"),
  el_button("reset", "Reset", size = "small"), verbatimTextOutput("keys"))

server <- function(input, output, session) {
  observeEvent(input$set, update_el_tree(id = "tree", checked = c(4, 6)))
  observeEvent(input$reset, update_el_tree(id = "tree", checked = character(0)))
  observeEvent(input$get, el_call(session, "tree", "getCheckedKeys"))
  output$keys <- renderPrint(input$tree_checked)
}

shinyApp(ui, server)
```

## Custom node content

The content of tree nodes can be customized, so you can add icons or buttons as you will

There are two ways to customize template for tree nodes: `render-content` and scoped slot. Use `render-content` to assign a render function that returns the content of tree nodes. See Vue's documentation for a detailed introduction of render functions. If you prefer scoped slot, you'll have access to `node` and `data` in the scope, standing for the TreeNode object and node data of the current node respectively. Note that the `render-content` demo can't run in JSFiddle because it doesn't support JSX syntax. In a real project, `render-content` will work if relevant dependencies are correctly configured.

The default slot, scoped with `node` and `data`, draws each node.

```{r customized-node, eval = FALSE, shot = TRUE}
el_tree("cus", node_key = "id", default_expand_all = TRUE, expand_on_click_node = FALSE,
  data = list(list(id = 1, label = "Level one 1", children = list(
    list(id = 4, label = "Level two 1-1"), list(id = 5, label = "Level two 1-2")))),
  slots = list(default = template(
    tags$span(style = "flex: 1; display: flex; justify-content: space-between; padding-right: 8px",
      tags$span("{{ node.label }}"),
      tags$span(el$button(link = TRUE, type = "primary", size = "small", "Append"),
                el$button(link = TRUE, type = "danger", size = "small", "Delete"))),
    scope = "{ node, data }")))
```

## Custom node class

The class of tree nodes can be customized

. Use `props.class` to build class name of nodes.

> **In R**
>
> Upstream builds each node's class with `props.class`. In R, style nodes with
> the default slot: give the `<span>` a class from the node's data, as
> `:class="data.isPenultimate ? 'is-penultimate' : ''"`.

## Tree node filtering

Tree nodes can be filtered

Invoke the `filter` method of the Tree instance to filter tree nodes. Its parameter is the filtering keyword. Note that for it to work, `filter-node-method` is required, and its value is the filtering method.

`filter()` keeps the nodes whose label contains the text; give
`filter_node_method` to decide otherwise.

```{r filtering, eval = FALSE, shot = TRUE, shot_js = "var i = document.querySelector('#q_container input'); i.value = 'two'; i.dispatchEvent(new Event('input'));", shot_wait = 2}
ui <- el_page(
  el_input("q", placeholder = "Filter keyword", width = "300px"),
  el_tree("filtered", node_key = "id", default_expand_all = TRUE, data = list(
    list(id = 1, label = "Level one 1", children = list(list(id = 4, label = "Level two 1-1"))),
    list(id = 2, label = "Level one 2", children = list(list(id = 5, label = "Level three 2-1"))))))

server <- function(input, output, session) {
  observeEvent(input$q, el_call(session, "filtered", "filter", list(input$q), result = FALSE))
}

shinyApp(ui, server)
```

## Accordion

Only one node among the same level can be expanded at one time.

Only one node of a level open at a time.

```{r accordion, eval = FALSE, shot = TRUE}
el_tree("acc", accordion = TRUE, node_key = "id", data = list(
  list(id = 1, label = "Level one 1", children = list(list(id = 4, label = "Level two 1-1"))),
  list(id = 2, label = "Level one 2", children = list(list(id = 5, label = "Level two 2-1"))),
  list(id = 3, label = "Level one 3", children = list(list(id = 6, label = "Level two 3-1")))))
```

## Draggable

You can drag and drop Tree nodes by adding a `draggable` attribute.

`draggable` lets nodes be dragged; `allow_drag` and `allow_drop`, `JS()`
functions, say which and where, and `input$<id>_node_drop` reports where
one landed.

```{r draggable, eval = FALSE, shot = TRUE}
el_tree("drag", draggable = TRUE, node_key = "id", default_expand_all = TRUE,
  allow_drop = JS("function(dragging, drop, type) {",
                  "  return drop.data.label !== 'Level two 3-1' || type !== 'inner';",
                  "}"),
  data = list(
    list(id = 1, label = "Level one 1", children = list(list(id = 4, label = "Level two 1-1"))),
    list(id = 3, label = "Level one 3", children = list(list(id = 7, label = "Level two 3-1")))))
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("tree")
```
