---
title: "Upload"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Upload files by clicking or drag-and-drop. The files go through Shiny's own
upload channel, so `input$<id>` is the data frame `fileInput()` gives --
`name`, `size`, `type`, `datapath` -- while Element draws the list,
the progress and the thumbnails. Give `action` to send them straight to a
URL of your own instead.

## Click to upload files

`limit` caps the number of files; `on_exceed` hears when there are more.

```{r click, eval = FALSE, shot = TRUE}
ui <- el_page(
  el_upload("docs", button_label = "Click to upload", multiple = TRUE, limit = 3,
            tip = "jpg/png files with a size less than 500kb",
            on_exceed = JS("function(files, list) {",
                           "  ELEMENT.Message.warning('3 files at most');",
                           "}")),
  tableOutput("files"))

server <- function(input, output, session) {
  output$files <- renderTable(input$docs[, c("name", "size", "type")])
}

shinyApp(ui, server)
```

## Photo wall

`list_type = "picture-card"`: each file a card with its thumbnail, drawn in
the browser from the file itself.

```{r photo-wall, eval = FALSE, shot = TRUE}
el_upload("photos", list_type = "picture-card", accept = "image/*", multiple = TRUE,
          slots = list(default = el$icon("plus")))
```

## File list with thumbnails

```{r thumbnails, eval = FALSE, shot = TRUE}
el_upload("pics", list_type = "picture", button_label = "Click to upload",
          tip = "jpg/png files with a size less than 500kb", accept = "image/*",
          file_list = list(list(name = "food.jpeg",
                                url = "https://fuss10.elemecdn.com/3/63/4e7f3a15429bfda99bce42a18cdd1jpeg.jpeg")))
```

## File list control

`on_change` sees the list change; keeping only the last three files is a
line of JavaScript.

```{r control, eval = FALSE, shot = TRUE}
el_upload("latest", button_label = "Click to upload",
          on_change = JS("function(file, fileList) { if (fileList.length > 3) fileList.splice(0, fileList.length - 3); }"))
```

## Drag to upload

```{r drag, eval = FALSE, shot = TRUE}
el_upload("dropped", drag = TRUE, multiple = TRUE,
          button_label = "Drop file here or click to upload",
          tip = "jpg/png files with a size less than 500kb")
```

## Manual upload

`auto_upload = FALSE` keeps the files until `submit()` sends them -- from
the server, with `el_call()`.

```{r manual, eval = FALSE, shot = TRUE}
ui <- el_page(
  el_upload("queued", auto_upload = FALSE, multiple = TRUE, button_label = "Select file",
            tip = "Chosen files wait for the button"),
  el_button("send", "Upload to server", type = "success", size = "small"),
  tableOutput("arrived"))

server <- function(input, output, session) {
  observeEvent(input$send, el_call(id = "queued", method = "submit"))
  output$arrived <- renderTable(input$queued[, c("name", "size")])
}

shinyApp(ui, server)
```

## Failures and cancelling

A file that fails, or is stopped with `abort()`, is left out and the rest
of its batch still arrives; `input$<id>_error` names it.
`el_upload_file()` names a file for a method:

```{r abort, eval = FALSE}
el_call(session, "docs", "abort", list(el_upload_file("big.csv")))
```

## API

```{r api, echo = FALSE, results = "asis"}
api_tables("upload")
```
