---
title: "Upload"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Upload files by clicking or drag-and-drop.

## Basic Usage

Customize upload button type and text using `slot`. Set `limit` and `on-exceed` to limit the maximum number of uploads allowed and specify method when the limit is exceeded. Plus, you can abort removing a file in the `before-remove` hook.

The files go through Shiny's own upload channel, so `input$<id>` is the
data frame `fileInput()` gives -- `name`, `size`, `type`, `datapath` --
while Element Plus draws the list and the progress. `limit` caps the
number of files; `on_exceed` hears when there are more.

```{r basic, eval = FALSE, shot = TRUE}
ui <- el_page(
  el_upload("docs", button_label = "Click to upload", multiple = TRUE, limit = 3,
            tip = "jpg/png files with a size less than 500kb",
            on_exceed = JS("function(files, list) {",
                           "  ElementPlus.ElMessage.warning('3 files at most');",
                           "}")),
  tableOutput("files"))

server <- function(input, output, session) {
  output$files <- renderTable(input$docs[, c("name", "size", "type")])
}

shinyApp(ui, server)
```

## Cover Previous File

Set `limit` and `on-exceed` to automatically replace the previous file when select a new file.

With `limit = 1`, one file at a time: `on_exceed` hears the next, and
the server clears the list with `el_upload_clear()` so a new one can come.

```{r limit-cover, eval = FALSE, shot = TRUE}
ui <- el_page(
  el_upload("one", limit = 1, auto_upload = FALSE, button_label = "Select file",
            tip = "limit 1 file, clear it to choose another",
            on_exceed = JS("function() { ElementPlus.ElMessage.warning('Clear the file first'); }")),
  el_button("clear", "Clear", size = "small"))

server <- function(input, output, session) {
  observeEvent(input$clear, el_upload_clear(id = "one"))
}

shinyApp(ui, server)
```

## User Avatar

Use `before-upload` hook to limit the upload file format and size.

One picture, no list: the slot draws the box, a `JS()` hook checks the
file before it goes.

```{r avatar, eval = FALSE, shot = TRUE}
tagList(
  tags$style(".avatar-uploader .el-upload { border: 1px dashed var(--el-border-color);",
             " border-radius: 6px; width: 178px; height: 178px; display: flex;",
             " align-items: center; justify-content: center; font-size: 28px; color: #8c939d; }"),
  tags$div(class = "avatar-uploader",
    el_upload("avatar", show_file_list = FALSE, accept = "image/*",
              before_upload = JS("function(file) {",
                                 "  if (file.size / 1024 / 1024 > 2) {",
                                 "    ElementPlus.ElMessage.error('Avatar picture size can not exceed 2MB!');",
                                 "    return false;",
                                 "  }",
                                 "  return true;",
                                 "}"),
              slots = list(default = el_icon("Plus")))))
```

## Photo Wall

Use `list-type` to change the fileList style.

`list_type = "picture-card"`: each file a card with its thumbnail, drawn
in the browser from the file itself.

```{r photo-wall, eval = FALSE, shot = TRUE}
el_upload("photos", list_type = "picture-card", accept = "image/*", multiple = TRUE,
          file_list = list(list(name = "food.jpeg",
            url = "https://fuss10.elemecdn.com/3/63/4e7f3a15429bfda99bce42a18cdd1jpeg.jpeg")))
```

## Custom Thumbnail

Use `scoped-slot` to change default thumbnail template.

The `file` slot, scoped with `file`, draws each card.

```{r custom-thumbnail, eval = FALSE, shot = TRUE}
el_upload("thumbs", list_type = "picture-card", auto_upload = FALSE, accept = "image/*",
          slots = list(
            default = el_icon("Plus"),
            file = template(tags$div(
              tags$img(class = "el-upload-list__item-thumbnail", `:src` = "file.url", alt = ""),
              tags$span(class = "el-upload-list__item-actions",
                        tags$span(class = "el-upload-list__item-delete", "{{ file.name }}"))),
              slot = "file", scope = "{ file }")))
```

## File List with Thumbnail

```{r file-list-with-thumbnail, eval = FALSE, shot = TRUE}
el_upload("pics", list_type = "picture", button_label = "Click to upload",
          tip = "jpg/png files with a size less than 500kb", accept = "image/*",
          file_list = list(list(name = "food.jpeg",
            url = "https://fuss10.elemecdn.com/3/63/4e7f3a15429bfda99bce42a18cdd1jpeg.jpeg")))
```

## File List Control

Use `on-change` hook function to control upload file list.

`on_change` sees the list change; keeping only the last three files is a
line of JavaScript.

```{r file-list, eval = FALSE, shot = TRUE}
el_upload("latest", button_label = "Click to upload",
          tip = "jpg/png files with a size less than 500kb",
          on_change = JS("function(file, fileList) { if (fileList.length > 3) fileList.splice(0, fileList.length - 3); }"))
```

## Drag to Upload

You can drag your file to a certain area to upload it.

```{r drag-and-drop, eval = FALSE, shot = TRUE}
el_upload("dropped", drag = TRUE, multiple = TRUE,
          button_label = "Drop file here or click to upload",
          tip = "jpg/png files with a size less than 500kb")
```

## Upload Directory

Enable folder upload via the `directory` prop.

After enabling it, only folders can be selected, and after selecting a folder, the files within the folder will be flattened.

`directory = TRUE` picks a folder, and uploads every file in it.

```{r directory, eval = FALSE, shot = TRUE}
el_upload("folder", directory = TRUE, button_label = "Upload directory")
```

## Manual Upload

`auto_upload = FALSE` keeps the files until `submit()` sends them -- from
the server, with `el_call()`.

```{r manual, eval = FALSE, shot = TRUE}
ui <- el_page(
  el_upload("queued", auto_upload = FALSE, multiple = TRUE, button_label = "Select file",
            tip = "Chosen files wait for the button"),
  el_button("send", "Upload to server", type = "success", size = "small"),
  tableOutput("arrived"))

server <- function(input, output, session) {
  observeEvent(input$send, el_call(id = "queued", method = "submit"))
  output$arrived <- renderTable(input$queued[, c("name", "size")])
}

shinyApp(ui, server)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("upload")
```
