---
title: "Watermark"
---

```{r setup, include = FALSE}
source(file.path("..", "..", "shots.R"))
```

Add specific text or patterns to the page.

## Basic usage

The most basic usage.

```{r basic, eval = FALSE, shot = TRUE}
el_watermark(content = "Element Plus", font = list(color = "rgba(0, 0, 0, .15)"),
             tags$div(style = "height: 500px"))
```

## Multi-line watermark

Use `content` to set an array of strings to specify multi-line text watermark content.

Several lines: `content` is a vector.

```{r multi-line, eval = FALSE, shot = TRUE}
el_watermark(content = c("Element+", "Element Plus"), font = list(color = "rgba(0, 0, 0, .15)"),
             tags$div(style = "height: 500px"))
```

## Image watermark

Specify the image address via `image`. To ensure that the image is high definition and not stretched, set the width and height, and upload at least twice the width and height of the logo image address.

`image` draws a picture instead of text; `watermark_width` and `height`
size it (`width` is the box's).

```{r image, eval = FALSE, shot = TRUE}
el_watermark(watermark_width = 130, height = 30,
             image = "https://element-plus.org/images/element-plus-logo.svg",
             tags$div(style = "height: 500px"))
```

## Custom configuration

Preview the watermark effect by configuring custom parameters.

Its settings from inputs: the server redraws it as they change.

```{r custom, eval = FALSE, shot = TRUE}
ui <- el_page(
  el_row(
    el_col(span = 14, uiOutput("marked")),
    el_col(span = 10,
      el_input("content", label = "Content", value = "Element Plus"),
      el_color_picker("color", label = "Color", value = "rgba(0, 0, 0, 0.15)", show_alpha = TRUE),
      el_slider("size", label = "FontSize", value = 16, min = 8, max = 40),
      el_slider("rotate", label = "Rotate", value = -22, min = -180, max = 180),
      el_input_number("gap", label = "Gap", value = 100))))

server <- function(input, output, session) {
  output$marked <- renderUI(el_watermark(
    content = input$content, rotate = input$rotate, gap = rep(input$gap %||% 100, 2),
    font = list(fontSize = input$size, color = input$color),
    tags$div(style = "padding: 40px 20px; height: 360px",
             tags$h1("Element Plus"),
             tags$h2("A Vue 3 based component library for designers and developers"))))
}

shinyApp(ui, server)
```

## API

Element Plus's tables, and beside each entry where it is in R.

```{r api, echo = FALSE, results = "asis"}
api_tables("watermark")
```
