---
title: "Custom Defaults"
---

```{r setup, include = FALSE}
source(file.path("..", "shots.R"))
```

Element Plus sets some defaults for every component -- their size, where
popups start stacking -- when it is installed, and others for part of a
page through `el-config-provider`.

## Global

`el_page(size =, z_index =)` passes both to `app.use(ElementPlus, { size,
zIndex })` for every component on the page. `size` is `"large"`,
`"default"` or `"small"`; a component's own `size` overrides it.

```{r global, eval = FALSE, shot = TRUE}
ui <- el_page(
  size = "small",
  el_button("a", "Small by default"),
  el_button("b", "Large", size = "large"),
  el_input("c", placeholder = "Small too", width = "200px")
)

shinyApp(ui, function(input, output, session) {})
```

`use_element(size =, z_index =)` does the same on a page that is not an
`el_page()`.

## ConfigProvider

`el_config_provider()` sets defaults for the components it holds:
`size`, and Element Plus's settings for buttons, links, dialogs and
messages.

```{r provider, eval = FALSE, shot = TRUE}
tagList(
  el_config_provider(
    size = "large",
    button = list(autoInsertSpace = TRUE),
    el_button("d", "确定", type = "primary"),
    el_button("e", "Large")
  ),
  tags$div(
    style = "margin-top: 12px",
    el_button("f", "确定", type = "primary"),
    el_button("g", "Default")
  )
)
```

`message = list(max = 3)` caps how many messages show at once:

```{r messages, eval = FALSE}
ui <- el_page(el_config_provider(
  message = list(max = 3),
  el_button("toast", "Message")
))

server <- function(input, output, session) {
  observeEvent(
    input$toast,
    el_message(message = paste("At", format(Sys.time(), "%X")))
  )
}
```

## Responsive classes

Element Plus's `display.css` -- `hidden-xs-only`, `hidden-md-and-up` and the
rest -- is loaded with it, for any tag:
`tags$div(class = "hidden-sm-and-down", ...)`.
