---
title: "Dark Mode"
---

```{r setup, include = FALSE}
source(file.path("..", "shots.R"))
```

Element Plus has a dark mode: its CSS variables, redefined under the class
`dark` on `<html>`. The stylesheet ships with the package and every page
loads it, so dark mode is a class away.

## How to enable it?

Add `class = "dark"` to the page's `<html>` -- once, from the UI:

```{r static, eval = FALSE, shot = TRUE}
ui <- el_page(
  tags$script("document.documentElement.classList.add('dark');"),
  tags$style(
    "html.dark body { background: var(--el-bg-color); color: var(--el-text-color-primary); }"
  ),
  el_button("b1", "Default"),
  el_button("b2", "Primary", type = "primary"),
  el_input("i", placeholder = "Input", width = "200px"),
  el_switch("s", value = TRUE),
  el_pagination("p", total = 50)
)

shinyApp(ui, function(input, output, session) {})
```

Or let the user switch, the server toggling the class:

```{r toggle, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#shot .el-switch').click()", shot_wait = 1}
ui <- el_page(
  tags$script(HTML(
    "Shiny.addCustomMessageHandler('dark', function (on) {",
    "  document.documentElement.classList.toggle('dark', on);",
    "});"
  )),
  tags$style(
    "html.dark body { background: var(--el-bg-color); color: var(--el-text-color-primary); }"
  ),
  el_switch("dark", active_text = "Dark", inactive_text = "Light"),
  tags$div(
    style = "margin-top: 16px",
    el_card(
      header = "A card",
      tags$p("Its colours follow the mode."),
      el_button("go", "Primary", type = "primary")
    )
  )
)

server <- function(input, output, session) {
  observeEvent(
    input$dark,
    session$sendCustomMessage("dark", isTRUE(input$dark))
  )
}

shinyApp(ui, server)
```

The page around the components is Bootstrap's: the `tags$style()` above
gives its background and text Element Plus's dark colours. bslib's
`input_dark_mode()` switches Bootstrap's own dark mode, for a page whose
theme uses it.

## Custom variables

A dark theme of your own overrides Element Plus's variables under
`html.dark`:

```{r custom, eval = FALSE}
tags$style(
  "html.dark {
  --el-bg-color: #141414;
  --el-color-primary: #3b82f6;
}"
)
```

A brand colour given to `el_theme()` gets its dark tints too: `el_page()`
mixes them against the dark background, as Element Plus's dark stylesheet
does for its own blue.
