---
title: "Internationalization"
---

```{r setup, include = FALSE}
source(file.path("..", "shots.R"))
```

Element Plus components use English by default. Their own text -- a
pagination control's total, a date picker's month names, a table's
"No Data" -- comes from a locale, and Element Plus ships
`r length(shiny.element::el_locales())` of them, all bundled with this
package.

## Global configuration

`el_page(locale =)` sets the language for every component on the page, as
`app.use(ElementPlus, { locale })` does upstream:

```{r global, eval = FALSE, shot = TRUE}
ui <- el_page(locale = "zh-cn",
  el_pagination("p", total = 100, layout = "total, prev, pager, next, jumper"),
  el_date_picker("d"),
  el_table("t", data = data.frame(a = character(0))))

shinyApp(ui, function(input, output, session) {})
```

`options(shiny.element.locale =)` sets it for a session, `use_element(locale =)`
on a page that is not an `el_page()`. `el_locales()` lists the codes:

```{r list}
shiny.element::el_locales()
```

Codes are matched without regard to case: `"zh-CN"` and `"zh-cn"` are the
same.

## ConfigProvider

Upstream, `el-config-provider` can set the locale for part of a page. Here
the locale is the page's: one per page. `el_config_provider()` sets the
other defaults -- size, button and message settings -- for what it holds;
see Custom Defaults.

## Date and time localization

The date pickers' calendars follow the locale: month and day names, and
the first day of the week. The format of a date shown in the input is
`format`, in day.js's tokens (`"YYYY-MM-DD"`); the value Shiny gets is
`value_format`, unchanged by the language.

```{r dates, eval = FALSE, shot = TRUE, shot_js = "document.querySelector('#shot .el-input__inner').focus()", shot_wait = 1}
ui <- el_page(locale = "fr", el_date_picker("d", format = "DD MMMM YYYY"))

shinyApp(ui, function(input, output, session) {})
```

Text you pass in -- labels, placeholders, messages -- is yours to translate.
