---
title: "Migration from Element UI"
---

```{r setup, include = FALSE}
source(file.path("..", "shots.R"))
```

shiny.element was first built on Element UI 2 and Vue 2; that version is
tagged `v0.1.0-vue2` on GitHub. It is now built on Element Plus and Vue 3,
as Element UI's own successor is. Most code runs unchanged: the R functions,
their arguments and their inputs are the same. What follows is what does
change, and what reads the old spelling for you.

Element Plus's own migration notes -- for Vue code -- are in its
[changelog](https://element-plus.org/en-US/guide/changelog.html).

## Read for you

These keep working, converted to Element Plus's form:

| Element UI | Element Plus | Where |
|---|---|---|
| `"el-icon-search"`, `"search"` | `"Search"` | every `icon`, `prefix_icon`, `suffix_icon`, ... |
| `"el-icon-user-solid"` | `"UserFilled"` | the few icons renamed upstream |
| `"yyyy-MM-dd"`, `"timestamp"` | `"YYYY-MM-DD"`, `"x"` | date and time `format`, `value_format` |
| `el_link(underline = TRUE / FALSE)` | `"hover"` / `"never"` | `el_link()` |
| `el_icon(lib = "element-ui")` | `lib = "element-plus"` | `el_icon()` |
| `ELEMENT.Message(...)` in your `JS()` | `ElementPlus.ElMessage(...)` | `window.ELEMENT` is kept, pointing at Element Plus's services |
| `slot-scope="scope"` in `template()` | `v-slot:default="scope"` | `template(scope =)` writes it |

## Changed

**Sizes.** Element Plus has `"large"`, `"default"` and `"small"`. Element
UI's `"medium"` and `"mini"` are an error, with the values to use instead:
`"medium"` becomes `"default"`, `"mini"` becomes `"small"`.

```{r sizes, eval = FALSE, shot = TRUE}
tagList(
  el_button("l", "Large", size = "large"),
  el_button("d", "Default"),
  el_button("s", "Small", size = "small")
)
```

**Text buttons.** Element UI's `type = "text"` button is `link = TRUE` (a
coloured link-like button) or `text = TRUE` (a borderless one) in Element
Plus; `type` keeps the colour.

```{r text, eval = FALSE, shot = TRUE}
tagList(
  el_button("a", "Link button", link = TRUE, type = "primary"),
  el_button("b", "Text button", text = TRUE),
  el_button("c", "Text, filled", text = TRUE, bg = TRUE)
)
```

**Dependencies.** `element_ui_dependency()` is `element_plus_dependency()`.
`el_page()` and `use_element()` load it, so most apps never call either.

**Themes.** `el_theme(element =)` names Element Plus's CSS variables, without
the `--el-` (`"border-radius-base"`, `"component-size"`), where Element UI
named its Sass variables without the `$--`. Many names are the same; the
Sass-only ones (`"input-height"`) have CSS variable counterparts
(`"component-size"`). Nothing is compiled any more, and sass is not needed.

**The default language** is English. Element UI's default was Simplified
Chinese; `el_page(locale = "zh-cn")` brings it back.

**Menus.** A submenu is Element Plus's `el-sub-menu`; `el_menu()`'s items
build it; raw markup uses `el$sub_menu()`.

**Upload's file list** is `v-model:file-list` upstream; `el_upload()` keeps
it, and `input$<id>` is unchanged.

## Your own components

Code given to `el_widget()` -- its `methods`, `watch`, `mounted` -- runs in
a Vue 3 component instance. Vue 3's own migration guide covers the
differences; those you are likely to meet:

* `this.$set(obj, key, value)` is gone: assign, `obj[key] = value`. Vue 3
  sees new properties.
* `beforeDestroy` and `destroyed` are `beforeUnmount` and `unmounted`;
  `el_widget()` renames them for you.
* `$children` is gone; `call_el()` and the package's own lookups find a
  component by its ref.
* Filters (`{{ x | money }}`) are gone: call a method, `{{ money(x) }}`.
* `v-model` on a component binds `modelValue`, and a named one,
  `v-model:file-list`, a prop of that name.

`data` may stay a list: `el_widget()` makes it the function Vue 3 wants.

## New components

Element Plus brought components Element UI did not have, each wrapped:
`el_input_otp()`, `el_input_tag()`, `el_segmented()`, `el_select_v2()`,
`el_mention()`, `el_tree_select()`, `el_tree_v2()`, `el_table_v2()`,
`el_color_picker_panel()`, `el_date_picker_panel()`, `el_check_tag()`,
`el_anchor()`, `el_tour()`, `el_image_viewer()`, `el_countdown()`,
`el_affix()`, `el_space()`, `el_scrollbar()`, `el_watermark()`, `el_text()`,
`el_avatar_group()`, `el_splitter()` and `el_config_provider()`. The
components overview lists them in Element Plus's groups.
