---
title: "Theming, sizes and languages"
---

```{r setup, include = FALSE}
source(file.path("..", "shots.R"))
```

Element's own development guide covers its theme, its languages and its
built-in transitions; here they are from R.

## Sizing

`width` is accepted by every component and behaves like the `width` of a Shiny
input -- `"200px"`, `"50%"`, or a number meaning pixels. It lands on Element's
own markup, because the host element carries `display: contents` and generates
no box of its own.

`height` is only where Element gives it a meaning: `el_table()` fixes the
header and scrolls the body, `el_slider()` sizes a vertical track,
`el_carousel()` sets the frame. Element sizes controls through `size`
(`"medium"`, `"small"`, `"mini"`) rather than a height.

`el_page(size = "small")` sets that size for every component not given one
of its own, as `Vue.use(Element, {size: "small"})` does upstream; `z_index`
sets where Element's popups start stacking. `use_element()` takes both too.
Element's responsive helper classes -- `hidden-xs-only`, `hidden-md-and-up`
and the rest of its `display.css` -- are loaded with it, for any tag:
`tags$div(class = "hidden-sm-and-down", ...)`.

## The page around the components

Element styles its components, not the page they sit on, and most of its
components set no font of their own -- they inherit the page's. `el_page()`
therefore themes the page too: its default, `el_theme()`, is a bslib theme
carrying Element's blue, greys, borders, corners, type size and font stack,
so Shiny's own inputs and outputs match the Element ones beside them.

```{r theme, eval = FALSE, shot = TRUE}
el_row(gutter = 16,
  el_col(span = 12,
    textInput("shiny_text", "Shiny's textInput()", "Ada"),
    actionButton("shiny_go", "actionButton()", class = "btn-primary")),
  el_col(span = 12,
    tags$label("Element's el_input()"), el_input("el_text", value = "Ada"),
    tags$div(style = "margin-top: 15px",
      el_button("el_go", "el_button()", type = "primary"))))
```

`el_theme(primary = "#7c3aed")` changes the brand colour, and any other
argument of `bslib::bs_theme()` or Bootstrap variable can be overridden the
same way. The theme's `primary`, `success`, `warning`, `danger` and `info`
reach Element's components too, with the tints and shades Element derives
from each -- a plain button's pale fill, a focused input's border:

```{r theme-colors, eval = FALSE, shot = TRUE}
ui <- el_page(theme = el_theme(primary = "#7c3aed"),
  el_button("save", "Save", type = "primary"),
  el_button("draft", "Draft", type = "primary", plain = TRUE),
  el_switch("notify", value = TRUE),
  el_slider("level", value = 40, width = "240px"),
  el_pagination("pages", total = 50))

shinyApp(ui, function(input, output, session) {})
```

Element's other theme variables -- its radii, sizes, greys, some five
hundred in theme-chalk's `common/var.scss` -- go in `el_theme(element =)`,
by name without the `$--`:

```{r theme-element, eval = FALSE, shot = TRUE}
theme <- el_theme(primary = "#0f766e", element = list(
  "border-radius-base" = "12px", "border-radius-small" = "8px",
  "font-size-base" = "13px", "input-height" = "36px"))

ui <- el_page(theme = theme,
  el_input("name", placeholder = "Rounder, smaller", width = "260px"),
  el_button("go", "Go", type = "primary"),
  el_tag("t", "Tag"))

shinyApp(ui, function(input, output, session) {})
```

Element's stylesheet is built for the theme the way upstream builds one.
Brand colours alone are replaced in the shipped stylesheet, as Element's own
theme picker does; anything more compiles Element's Sass sources, bundled
with the package, as its theme tool does -- about a second, once per theme
and R session. `use_element(theme =)` does the same on a page that is not an
`el_page()`.

## Languages

Element's components have text of their own -- a pagination control's
total, a date picker's month names, a table's "No Data". `el_page(locale =)`
sets the language, English by default; `options(shiny.element.locale =)` sets
it for a session, and `el_locales()` lists the 59 Element ships.

```{r i18n, eval = FALSE, shot = TRUE}
ui <- el_page(locale = "fr",
  el_pagination("p", total = 100, layout = "total, prev, pager, next, jumper"),
  el_date_picker("d", placeholder = NULL))

shinyApp(ui, function(input, output, session) {})
```

Text you pass in is yours to translate.

## Built-in transitions

Element's transitions -- `el-fade-in-linear`, `el-fade-in`,
`el-zoom-in-center`, `el-zoom-in-top`, `el-zoom-in-bottom` -- are classes in
its stylesheet, for Vue's `<transition>` inside a component's markup, and
`el$collapse_transition()` animates a block's height:

```{r transition, eval = FALSE, shot = TRUE}
el_widget("fade", data = list(show = TRUE), dependency = element_ui_dependency(),
  markup = htmltools::tags$div(
    el$button("@click" = "show = !show", "Toggle"),
    htmltools::tag("transition", list(name = "el-fade-in-linear",
      htmltools::tags$div(`v-show` = "show", style = "margin-top: 12px; width: 200px; height: 100px; background: #409EFF; border-radius: 4px")))))
```

