---
title: "Theming"
---

```{r setup, include = FALSE}
source(file.path("..", "shots.R"))
```

Element Plus is themed through CSS variables -- `--el-color-primary` and
some hundreds more -- which its theming guide overrides on the page. Here
`el_theme()` does it, alongside the Bootstrap theme of the page around the
components. Languages, dark mode, sizes for the whole page and the built-in
transitions have guides of their own.

## Sizing

`width` is accepted by every component and behaves like the `width` of a Shiny
input -- `"200px"`, `"50%"`, or a number meaning pixels. It lands on Element's
own markup, because the host element carries `display: contents` and generates
no box of its own.

`height` is only where Element Plus gives it a meaning: `el_table()` fixes
the header and scrolls the body, `el_slider()` sizes a vertical track,
`el_carousel()` sets the frame. Element Plus sizes controls through `size`
(`"large"`, `"default"`, `"small"`) rather than a height.

`el_page(size = "small")` sets that size for every component not given one
of its own, as `app.use(ElementPlus, { size: "small" })` does upstream; `z_index`
sets where Element's popups start stacking. `use_element()` takes both too.
Element Plus's responsive helper classes -- `hidden-xs-only`,
`hidden-md-and-up` and the rest of its `display.css` -- are loaded with it,
for any tag: `tags$div(class = "hidden-sm-and-down", ...)`.

## The page around the components

Element styles its components, not the page they sit on, and most of its
components set no font of their own -- they inherit the page's. `el_page()`
therefore themes the page too: its default, `el_theme()`, is a bslib theme
carrying Element's blue, greys, borders, corners, type size and font stack,
so Shiny's own inputs and outputs match the Element ones beside them.

```{r theme, eval = FALSE, shot = TRUE}
el_row(gutter = 16,
  el_col(span = 12,
    textInput("shiny_text", "Shiny's textInput()", "Ada"),
    actionButton("shiny_go", "actionButton()", class = "btn-primary")),
  el_col(span = 12,
    tags$label("Element's el_input()"), el_input("el_text", value = "Ada"),
    tags$div(style = "margin-top: 15px",
      el_button("el_go", "el_button()", type = "primary"))))
```

`el_theme(primary = "#7c3aed")` changes the brand colour, and any other
argument of `bslib::bs_theme()` or Bootstrap variable can be overridden the
same way. The theme's `primary`, `success`, `warning`, `danger` and `info`
reach Element's components too, with the tints and shades Element derives
from each -- a plain button's pale fill, a focused input's border:

```{r theme-colors, eval = FALSE, shot = TRUE}
ui <- el_page(theme = el_theme(primary = "#7c3aed"),
  el_button("save", "Save", type = "primary"),
  el_button("draft", "Draft", type = "primary", plain = TRUE),
  el_switch("notify", value = TRUE),
  el_slider("level", value = 40, width = "240px"),
  el_pagination("pages", total = 50))

shinyApp(ui, function(input, output, session) {})
```

Element Plus's other variables -- its radii, sizes, greys, the full list in
its `theme-chalk` stylesheet -- go in `el_theme(element =)`, by name without
the `--el-`:

```{r theme-element, eval = FALSE, shot = TRUE}
theme <- el_theme(primary = "#0f766e", element = list(
  "border-radius-base" = "12px", "border-radius-small" = "8px",
  "font-size-base" = "13px", "component-size" = "36px"))

ui <- el_page(theme = theme,
  el_input("name", placeholder = "Rounder, smaller", width = "260px"),
  el_button("go", "Go", type = "primary"),
  el_tag("t", "Tag"))

shinyApp(ui, function(input, output, session) {})
```

They are set on the page as CSS variables, as Element Plus's theming guide
sets them: nothing is compiled, and a theme costs nothing to switch. A brand
colour brings its tints -- `--el-color-primary-light-3` to `-light-9`,
`-dark-2` -- for the light page and for dark mode. `use_element(theme =)`
does the same on a page that is not an `el_page()`.

## Further

- Internationalization: `el_page(locale =)`.
- Dark mode: Element Plus's `html.dark`.
- Custom defaults: `el_page(size =, z_index =)` and `el_config_provider()`.
- Built-in transitions: `el-fade-in`, `el-zoom-in-top`, `el$collapse_transition()`.
