---
title: "Built-in Transitions"
---

```{r setup, include = FALSE}
source(file.path("..", "shots.R"))
```

Element Plus's transitions are classes in its stylesheet, for Vue's
`<transition>` inside a component's markup. In R that markup is
`el_widget()`'s: here each demo is a small component of its own, its state
in `data`, with Element Plus's buttons as `el$` tags.

## Fade

Two fading effects: `el-fade-in-linear` and `el-fade-in`.

```{r fade, eval = FALSE, shot = TRUE}
box <- function(text) {
  htmltools::tags$div(
    `v-show` = "show",
    class = "transition-box",
    style = "margin: 12px 20px 0 0; width: 200px; height: 100px; border-radius: 4px;
           background: var(--el-color-primary); color: #fff; text-align: center;
           line-height: 100px; display: inline-block",
    text
  )
}
el_widget(
  "fade",
  data = list(show = TRUE),
  markup = htmltools::tags$div(
    el$button("@click" = "show = !show", "Click Me"),
    htmltools::tags$div(
      htmltools::tag(
        "transition",
        list(name = "el-fade-in-linear", box(".el-fade-in-linear"))
      ),
      htmltools::tag(
        "transition",
        list(name = "el-fade-in", box(".el-fade-in"))
      )
    )
  )
)
```

## Zoom

`el-zoom-in-center`, `el-zoom-in-top` and `el-zoom-in-bottom`.

```{r zoom, eval = FALSE, shot = TRUE}
box <- function(text) {
  htmltools::tags$div(
    `v-show` = "show",
    style = "margin: 12px 20px 0 0; width: 200px; height: 100px; border-radius: 4px;
           background: var(--el-color-primary); color: #fff; text-align: center;
           line-height: 100px; display: inline-block",
    text
  )
}
el_widget(
  "zoom",
  data = list(show = TRUE),
  markup = htmltools::tags$div(
    el$button("@click" = "show = !show", "Click Me"),
    htmltools::tags$div(
      htmltools::tag(
        "transition",
        list(name = "el-zoom-in-center", box(".el-zoom-in-center"))
      ),
      htmltools::tag(
        "transition",
        list(name = "el-zoom-in-top", box(".el-zoom-in-top"))
      ),
      htmltools::tag(
        "transition",
        list(name = "el-zoom-in-bottom", box(".el-zoom-in-bottom"))
      )
    )
  )
)
```

## Collapse

For a collapse effect, `el$collapse_transition()`: it animates a block's
height.

```{r collapse, eval = FALSE, shot = TRUE}
el_widget(
  "collapse",
  data = list(show = TRUE),
  markup = htmltools::tags$div(
    el$button("@click" = "show = !show", "Click Me"),
    htmltools::tags$div(
      style = "margin-top: 20px; height: 200px",
      el$collapse_transition(
        htmltools::tags$div(
          `v-show` = "show",
          htmltools::tags$div(
            style = "width: 200px; height: 100px; margin-bottom: 10px; border-radius: 4px;
          background: var(--el-color-primary); color: #fff; text-align: center; line-height: 100px",
            "el-collapse-transition"
          ),
          htmltools::tags$div(
            style = "width: 200px; height: 100px; border-radius: 4px;
          background: var(--el-color-primary); color: #fff; text-align: center; line-height: 100px",
            "el-collapse-transition"
          )
        )
      )
    )
  )
)
```
